### 2020-05-07 README.Rmd
updated analysis structure and README

---
title: 'Terrebonne Project Summary'
author: 
date: 
output: 
  github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

*insert terrebonne image here*

This document summarizes data within Terrebonne Bay, Louisiana (*lat. long.*) collected by Louisiana Universities Marine Consortium (LUMCON).

# Metadata summary

*data structure*

## Sampling locations map
*insert sampling locations, i.e. trawls, here*

# Environmental Data

A suite of environmental data have been collected through <a href="https://lumcon.edu/environmental-monitoring/" target="_blank">LUMCON's environmental monitoring program</a> over the course of the study period. These variables include:

- Water Temperature
- Salinity
- Specific Conductivity

### 2020-05-07 text/trawl_summary.Rmd
updated analysis structure and README

---
title: 'Trawl Summary'
author: "Jim Junker"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
      keep_md: true
      toc: true
      toc_float: true
      toc_depth: 3
      numbered_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(vegan)
library(betapart)

TB_trawl_data <- readRDS("../data/TB_trawl_data.rds")
```

#TERREBONNE BAY TRAWL ANALYSIS SUMMARY {.unlisted .unnumbered}

*insert terrebonne image here*

This document summarizes trawl catch data within Terrebonne Bay, Louisiana (*lat. long.*) conducted by the Education Department of the Louisiana Universities Marine Consortium (LUMCON) from `r paste0(unique(min(TB_trawl_data$year))," - ",unique(max(TB_trawl_data$year)))`.

# Metadata summary

## Sampling locations map
*insert sampling locations, i.e. trawls, here*

# Environmental Data

A suite of environmental data have been collected through <a href="https://lumcon.edu/environmental-monitoring/" target="_blank">LUMCON's environmental monitoring program</a> over the course of the study period. These variables include:

- Water Temperature

### 2020-05-07 Analysis/active/trawl_analysis/trawl_specaccum.R

@@ -59,23 +59,45 @@ TB_time_df <- TB_time_accum %>%
   mutate(data_type = 'continuous') %>%
   bind_rows(TB_annual_accum %>% mutate(data_type = "annual"))
 
-source("./figures/diversity_time_plots.R")
-
-
 #create moving jaccard calc by year-month
+# create a dataframe for time series of distance compared to first sampling 
+unique_combinations <- expand.grid(date_A = unique(levels(as.factor(TB_trawl_commonsite$date_id))), 
+                                   Date = unique(levels(as.factor(TB_trawl_commonsite$date_id)))) %>%
+  filter(date_A == as.character(min(TB_trawl_commonsite$date_id)))
+
+TB_date_jaccard = vegdist((TB_trawl_commonsite %>% select(-year, -month) %>% 
+                             column_to_rownames("date_id")), method = "jaccard") %>%
+  as.matrix %>% as.data.frame %>% rownames_to_column("date_A") %>% 
+  pivot_longer(cols = 2:dim(.)[2], names_to = "Date", values_to = "jaccard") %>%
+  inner_join(unique_combinations) %>% filter(date_A != date_B) %>% 
+  mutate(Date = gsub('^([0-9]{4}-)([0-9]{1})$', '\\10\\2', Date),
+         Date = as.Date(paste0(Date,"-01"), format = "%Y-%m-%d"))
+
+ggplot(Tb_date_jaccard, aes(x = Date, y = jaccard)) + 
+  geom_point() +
+  geom_line() +
+  scale_y_continuous()
+
+# partitioning beta diversity metrics from trawl dataset
+# create named list of each sampling date
+named_group_split <- function(.tbl, ...) {
+  grouped <- group_by(.tbl, ...)
+  names <- rlang::eval_bare(rlang::expr(paste(!!!group_keys(grouped), sep = " / ")))
+
+  grouped %>%
+    group_split() %>%
+    rlang::set_names(names)
+}
 
 date_lists = TB_trawl_commonsite %>%
-  group_split(date_id)
+  named_group_split(date_id) %>%
+  map(., ~.x %>% select(-year, -month,-date_id))
 
-unique_comb
+beta_lists <- lapply(date_lists, function(x,r){ betapart::beta.temp(x = x, y = r, index.family = 'jaccard')}, x = date_lists[[1]]) 
+beta_dates <- gsub('^([0-9]{4}-)([0-9]{1})$', '\\10\\2', names(beta_lists))
[…]

### 2020-05-07 datascript.R

@@ -13,25 +13,25 @@ data_import <<- function(){
   tempF_to_C <<- function(F){(5/9)*(F-32)}
   
   temp_df <<- bind_rows(temp_files) %>%
-    rename(time = 'TS', temp_F = 'F') %>%
-    mutate(yday = yday(time))
+    rename(datetime = 'TS', temp_F = 'F') %>%
+    mutate(yday = yday(datetime))
   
   do_paths <- list.files(path = "./data/", "*DO_*", full.names = TRUE)
   do_files <- lapply(do_paths, read_csv, skip = 1,
                      col_types = cols(TS = col_datetime(format = "%m/%d/%Y %H:%M")))
   
   do_df <<- bind_rows(do_files) %>%
-    rename(time = 'TS', do_mg_L = 'mg L') %>%
-    mutate(yday = yday(time))
+    rename(datetime = 'TS', do_mg_L = 'mg L') %>%
+    mutate(yday = yday(datetime))
   
   hydro_paths <- list.files(path = "./data/", "hydro{1}.*.csv", full.names= TRUE)
   hydro_files <- lapply(hydro_paths, read_csv, col_type = cols(ArrayID = col_skip(), Year = col_skip(), JDay= col_skip(),
                                                                X4 = col_skip(), X5 = col_skip(), X6 = col_skip(), Time = col_skip(), X8 = col_skip(), `Date/Time` = col_character(),
                                                                DO = col_skip(), Value4 = col_double(), Depth = col_skip(), `Depth feet` = col_skip()))
   hydro_df <<- bind_rows(hydro_files) %>%
-    rename(time = 'Date/Time', temp_C = 'Temp', temp_F = 'Water Temp F', spCon_uS_cm = 'Value4', sal_psu = 'Sal') %>%
-    mutate(time = parse_date_time(time, orders = c("%m/%d/%Y %H:%M", "%m/%d/%y %H:%M")),
-           yday = yday(time))
+    rename(datetime = 'Date/Time', temp_C = 'Temp', temp_F = 'Water Temp F', spCon_uS_cm = 'Value4', sal_psu = 'Sal') %>%
+    mutate(datetime = parse_date_time(datetime, orders = c("%m/%d/%Y %H:%M", "%m/%d/%y %H:%M")),
+           yday = yday(datetime))
   
   shallow<<- read_csv(file = "https://www.dropbox.com/s/bw1klp28wx5i7lx/TB2_Compiled_Data.csv?dl=1") %>% as.data.frame() %>%
     column_to_rownames('X1')

### 2020-05-07 figures/diversity_time_plots.R

@@ -1,12 +1,28 @@
 ### diversity by time plot ###
 
-rich_time <- ggplot(TB_time_df, aes(x = Date, y = richness, group = data_type)) +
-  geom_point(aes(colour = data_type),size = 3) + 
-  geom_line(aes(colour = data_type),size = 2) +
+ rich_time <- 
+  ggplot(TB_time_df, aes(x = Date, y = richness, group = data_type)) +
+  geom_point(aes(colour = data_type),size = 1.5) +
+  geom_line(aes(colour = data_type),size = 1.2) +
   scale_x_date(date_breaks = "1 year", date_labels = "%Y") + 
   scale_y_continuous(name = "Species Richness")+
   scale_colour_manual(name = "", values = viridis(4)[c(2,3)]) +
   theme(legend.position = c(0, 1), legend.justification = c(0, 1), legend.background = element_rect(fill = "transparent", colour = NA),
-        axis.title.x = element_blank())
+        axis.title.x = element_blank(), axis.text.x = element_blank(),
+        legend.spacing.y = unit(-0.1, 'cm'))
 
+ jaccard_time <-
+  ggplot(beta_df, aes(x = Date, y = value, group = partition)) + 
+   geom_point(aes(colour = partition), size = 1.5) +
+  geom_line(aes(colour = partition), size = 1.2) +
+  scale_y_continuous(name = "Jaccard dissimilarity", limits = c(0,1.1), expand = c(0.01,0.01))+
+  scale_colour_manual(name = "", values = viridis(7)[c(2,4,7)], labels = c("jaccard", "nestedness","turnover")) +
+  scale_x_date(date_breaks = "1 year", date_labels = "%Y") + 
+  theme(legend.background = element_rect(colour = NA, fill = 'transparent'),
+        legend.position = c(0,1), legend.justification = c(0,1), axis.title.x = element_blank(),
+        legend.spacing.y = unit(-0.2, 'cm'))
 
+ tiff("./figures/TB_temporal_diversity.tiff", res = 400, width = 5, height = 7.5, units = "in", compression = "lzw")
+ grid.arrange(rich_time, jaccard_time, ncol = 1)
+ dev.off()
+ 

### 2020-05-07 install-packages.R

@@ -8,7 +8,7 @@ if ("pacman" %in% rownames(installed.packages()) == FALSE) install.packages("pac
 # they are important for running the livedat repository
 # OG package list: pacman::p_load(git2r, httr, semver, testthat, yaml)
 
-pacman::p_load(git2r, httr, semver, testthat, yaml, data.table, 
+pacman::p_load(git2r, httr, semver, testthat, yaml, EML, data.table, 
                RCurl, plyr, tidyverse, furrr, googlesheets4,
                tictoc, chron, lubridate, httr, TTR, grid,
                gridExtra, ggridges, iNEXT, vegan, rlist, pipeR,
@@ -17,7 +17,7 @@ pacman::p_load(git2r, httr, semver, testthat, yaml, data.table,
 
 pacman::p_load_gh(c("jimjunker1/junkR"))#, "ropensci/rfishbase"))
 
-theme_mod <<- theme_bw() %+replace% theme(panel.grid = element_blank())
+# theme_mod <<- theme_bw() %+replace% theme(panel.grid = element_blank())
 theme_set(theme_mod)
 find_hull <<- function(df) df[chull(df$NMDS1, df$NMDS2),]
 

### 2020-05-11 text/trawl_summary.Rmd
updated trawl_summary.RMD, added in docs/ folder for github.pages site.

@@
 library(betapart)
+library(lubridate)
 
 TB_trawl_data <- readRDS("../data/TB_trawl_data.rds")
+
 ```
@@
 ## Sampling locations map
-*insert sampling locations, i.e. trawls, here*
+*insert sampling locations, i.e. trawls start and stop, here*
 
@@
 - Water Temperature
+- Salinity
+- Specific conductivity
+- Dissolved Oxygen
+
+```{r import environmental data, include = FALSE}
+
+  temp_paths <- list.files(path = "../data/", "*temp_*", full.names = TRUE)
+  temp_files <- lapply(temp_paths, read_csv, skip = 1,
+                       col_types = cols(TS = col_datetime(format = "%m/%d/%Y %H:%M")))
+
+  roundUP <- function(x,to=10){
+    to*(x%/%to + as.logical(x%%to))
+  }
+
+  tempF_to_C <- function(F){(5/9)*(F-32)}
+
+  temp_df <- bind_rows(temp_files) %>%
+    rename(datetime = 'TS', temp_F = 'F') %>%
+    mutate(yday = yday(datetime))
+
+  do_paths <- list.files(path = "../data/", "*DO_*", full.names = TRUE)
+  do_files <- lapply(do_paths, read_csv, skip = 1,
+                     col_types = cols(TS = col_datetime(format = "%m/%d/%Y %H:%M")))
+
+  do_df <- bind_rows(do_files) %>%
+    rename(datetime = 'TS', do_mg_L = 'mg L') %>%
+    mutate(yday = yday(datetime))
+
+  hydro_paths <- list.files(path = "../data/", "hydro{1}.*.csv", full.names= TRUE)
+  hydro_files <- lapply(hydro_paths, read_csv, col_type = cols(ArrayID = col_skip(), Year = col_skip(), JDay= col_skip(),
+                                                               X4 = col_skip(), X5 = col_skip(), X6 = col_skip(), Time = col_skip(), X8 = col_skip(), `Date/Time` = col_character(),
+                                                               DO = col_skip(), Value4 = col_double(), Depth = col_skip(), `Depth feet` = col_skip()))
+  hydro_df <- bind_rows(hydro_files) %>%
+    rename(datetime = 'Date/Time', temp_C = 'Temp', temp_F = 'Water Temp F', spCon_uS_cm = 'Value4', sal_psu = 'Sal') %>%
+    mutate(datetime = parse_date_time(datetime, orders = c("%m/%d/%Y %H:%M", "%m/%d/%y %H:%M")),
+           yday = yday(datetime))
+env_long <- hydro_df %>% select(-yday, -temp_F) %>% bind_rows(temp_df %>% mutate(temp_C = tempF_to_C(temp_F)) %>% select(-yday, -temp_F)) %>%
+  full_join(do_df %>% select(-yday)) %>%
+  # full_join(temp_df %>% mutate(temp_C = tempF_to_C(temp_F))%>% select(-yday, - temp_F), all = TRUE) %>%
+  pivot_longer(cols = temp_C:do_mg_L, names_to = "env_var", values_to = "value")
+
+```
+
+These data sets range in coverage, and are being added to continuously:
+
+`r knitr::include_graphics("../figures/env_facet_plot.png")`
+
+More data will be necessary to fully complete analyses, but this shows the emerging environmental picture.
+
+# Biological Data
+
+The education department has been conducting trawl surveys pretty consistently since 2007. These sampling dates are pretty evenly distributed throughout the year
+
+## Sampling Events
+
+```{r sampling events, include = TRUE, echo = FALSE}
+
+TB_trawl_samplings <- TB_trawl_data %>% select(Date) %>%
+  group_by(Date) %>% distinct %>% ungroup %>%
+  mutate(Date = as.Date(Date), 
+         Date_num = as.numeric(Date))
+
+date_breaks = as.numeric(as.Date(paste0(seq(2007,2020, by = 1),"-01-01")))
+date_labels = year(as.Date(date_breaks, origin = "1970-01-01"))
+
+ggplot(TB_trawl_samplings, aes(x = Date, y = 0))+ geom_vline(aes(xintercept = as.numeric(ymd(Date)))) +
+  scale_x_continuous(breaks = date_breaks, labels = date_labels) + theme_minimal() +
+  theme(axis.title = element_blank())
+
+```

### 2020-05-11 Analysis/active/time-series_analysis.R

@@ -27,3 +27,5 @@ env_long <- hydro_df %>% select(-yday, -temp_F) %>% bind_rows(temp_df %>% mutate
   pivot_longer(cols = temp_C:do_mg_L, names_to = "env_var", values_to = "value")
 
 source("./figures/env_facet_plot.R");env_plot()
+
+

### 2020-05-11 text/trawl_summary.Rmd
updated trawl_summary with species sampling summaries.

@@
 date: "`r format(Sys.time(), '%d %B, %Y')`"
+knit: (function(inputFile, encoding) { 
+      out_dir <- '../docs';
+      rmarkdown::render(inputFile,
+                        encoding=encoding, 
+                        output_file=file.path(dirname(inputFile), out_dir, 'trawl_summary.html')) })
 output: 
@@
 library(lubridate)
+library(viridis)
+
+'%ni%' <- Negate('%in%')
 
@@
 
-These data sets range in coverage, and are being added to continuously:
+These data vary in coverage and are being updated:
 
@@
 ```
+
+There are a lot of sampling trawls over the past decade (n = 359) and they are spread pretty consistently over the year, but with some periods of heavy sampling:
+
+```{r month sampling events, include=TRUE, echo=FALSE}
+
+TB_month_hist <- TB_trawl_samplings %>%
+  mutate(month_num = lubridate::month(Date), 
+         month_name = lubridate::month(Date, label = TRUE))
+
+  ggplot(TB_month_hist, aes(month_num)) + geom_bar(width = 1) +
+    scale_x_continuous(breaks = seq(1,12, by = 1), labels = lubridate::month(seq(1,12,by = 1), label = TRUE)) +
+    theme_minimal() +
+    theme(axis.title = element_blank())
+
+```
+
+## Species sampling
+
+Over the full dataset we can estimate the species accumulation by # of trawls
+
+```{r full richness curve, include = TRUE, echo=FALSE}
+
+# Full species accumulation curve (SAC)
+
+##create taxa by site matrix
+TB_trawl_commonsite <- TB_trawl_data %>%
+  select(year, month, date_id, Common_name) %>%
+  group_by(date_id, Common_name) %>%
+  distinct() %>% 
+  mutate(pres = 1) %>%
+  pivot_wider(names_from = Common_name, values_from = pres, values_fill = list(pres = 0)) %>%
+  ungroup()
+
+sp1 <- vegan::specaccum(TB_trawl_commonsite %>% select(-year, -month, -date_id))
+spp_mod.df <- data.frame(trawls = sp1[["sites"]], richness = sp1[["richness"]], richness_sd = sp1[["sd"]])
+
+ggplot(spp_mod.df, aes(x = trawls, y = richness)) + geom_path(size = 2, colour = 'red') +
+  geom_ribbon(aes(x = trawls, ymin = (richness - 1.96*richness_sd), ymax = (richness + 1.96*richness_sd)), colour = "red", fill = "red", alpha = 0.5) +
+  scale_y_continuous(name = expression(Sigma~"species"), breaks = seq(0,roundUP(max(spp_mod.df$richness), to = 10), by = 10), labels = seq(0,roundUP(max(spp_mod.df$richness), to = 10), by = 10)) +
+  scale_x_continuous(name = "Trawls", breaks = seq(0,roundUP(max(spp_mod.df$trawls), to = 10), by = 20)) +
+  theme_minimal()
+
+```
+
+And by the trawls within each year to get at the differences in sampling effort (assuming each trawl is the same). This suggests there are certain years (or trawl locations):
+
+```{r, include = TRUE, echo = FALSE, warning=FALSE}
+## SAC for each year
+TB_trawl_commondate <- TB_trawl_data %>%
+  select(year, Date, Common_name) %>%
+  group_by(Date, Common_name) %>%
+  distinct() %>% 
+  mutate(pres = 1) %>%
+  pivot_wider(names_from = Common_name, values_from = pres, values_fill = list(pres = 0)) %>%
+  ungroup()
+
+TB_trawl_taxasite_yr <- TB_trawl_commondate %>%
+  group_split(year) %>%
+  map(., ~.x %>%  select(-year, -Date) %>% vegan::specaccum(.) %>%
+       rlist::list.remove(names(.) %ni% c("sites","richness","sd")) %>%
+        bind_cols) %>% 
+  map2(., TB_trawl_commondate %>% group_split(year), ~..1 %>% 
+         mutate(year = ..2 %>% select(year) %>% unlist %>% as.factor)) %>%
+  bind_rows
+
+ggplot(TB_trawl_taxasite_yr, aes(x = sites, y = richness, group = year, colour = year)) +
+  geom_path(size = 1.5) +# geom_ribbon(aes(x = sites, ymin = (richness - 1.96*sd), ymax = (richness + 1.96*sd), fill = year), alpha = 0.2) +
+  scale_y_continuous(name = expression(Sigma~"species"),breaks = seq(0, roundUP(max(TB_trawl_taxasite_yr$richness), to = 10), by = 10), labels = seq(0, roundUP(max(TB_trawl_taxasite_yr$richness), to = 10), by = 10)) +
+  scale_x_continuous(name = "Trawls", breaks = seq(0, roundUP(max(TB_trawl_taxasite_yr$sites), to = 10), by = 5)) +
+  scale_colour_viridis(discrete = TRUE) + 
+  scale_fill_viridis(discrete = TRUE) +
+  theme_minimal()
+
+```
+
+Squinting this suggests that, generally, there might be increasing # of species more broadly.

### 2020-05-11 text/trawl_summary.Rmd
updated trawl_summary.Rmd file

@@
 library(viridis)
+library(gridExtra)
 
@@
 
-More data will be necessary to fully complete analyses, but this shows the emerging environmental picture.
+There are a number of reasons for data holes and more complete data will be necessary for any final analyses, but this shows the emerging environmental picture.
 
@@
 
-The education department has been conducting trawl surveys pretty consistently since 2007. These sampling dates are pretty evenly distributed throughout the year
+The education department has been conducting trawl surveys pretty consistently since 2007.
 
@@
 
-There are a lot of sampling trawls over the past decade (n = 359) and they are spread pretty consistently over the year, but with some periods of heavy sampling:
+There are a lot of sampling trawls over the past decade (n = 359) and they are spread over the year, with some periods of heavy sampling:
 
@@
 
-Over the full dataset we can estimate the species accumulation by # of trawls
+Over the full dataset we can estimate the species accumulation by # of trawls from the `specaccum()` function in the <a href = "https://cran.r-project.org/web/packages/vegan/index.html" target = "_blank">vegan package</a>
 
@@
 
-And by the trawls within each year to get at the differences in sampling effort (assuming each trawl is the same). This suggests there are certain years (or trawl locations):
+The trawls within each year give some insight into the differences species-effort through time (assuming each trawl is the same).
+This suggests there are certain years (or trawl locations) that have higher richness:
 
-```{r, include = TRUE, echo = FALSE, warning=FALSE}
+```{r SAC curves, include = TRUE, echo = FALSE, warning=FALSE, }
 ## SAC for each year
@@
 
-Squinting this suggests that, generally, there might be increasing # of species more broadly.
+Squinting this suggests that, generally, there might be increasing # of species based on the species-effort curves.
+The 'brighter' colors appear to be higher.
+I think we still need to dig in further to see if this is due to changing taxonomic resolution across the sampling period or an actual biological signal.
+
+## Beta diversity
+
+We can start to break this down further, and the inference that species richness might be increasing over time has some support (again, not sure yet if this is real or methodological).
+
+```{r beta partition, include = TRUE, echo = FALSE, warning = FALSE, message= FALSE, fig.height= 8}
+
+#create time-accumulation df from trawl data
+TB_trawl_data %>%
+  filter(!duplicated(Common_name)) %>%
+  mutate(richness = 1:n(), 
+         Date = as.Date(Date),
+         richness = sort(richness))-> TB_time_accum
+
+TB_annual_accum <- TB_trawl_data %>%
+  mutate(pres = 1) %>% group_by(year) %>%
+  filter(!duplicated(Common_name)) %>%
+  summarise(richness = sum(pres)) %>%
+  mutate(Date = as.Date(as.character(year), format = "%Y", origin = "2000-01-01"))
+
+# partition beta diversity into nestedness and turnover #
+# uses `betapart` package #
+TB_time_df <- TB_time_accum %>%
+  select(Date, year, richness) %>%
+  mutate(data_type = 'continuous') %>%
+  bind_rows(TB_annual_accum %>% mutate(data_type = "annual"))
+
+#create moving jaccard calc by year-month
+# create a dataframe for time series of distance compared to first sampling 
+unique_combinations <- expand.grid(date_A = unique(levels(as.factor(TB_trawl_commonsite$date_id))), 
+                                   Date = unique(levels(as.factor(TB_trawl_commonsite$date_id)))) %>%
+  filter(date_A == as.character(min(TB_trawl_commonsite$date_id)))
+
+TB_date_jaccard = vegdist((TB_trawl_commonsite %>% select(-year, -month) %>% 
+                             column_to_rownames("date_id")), method = "jaccard") %>%
+  as.matrix %>% as.data.frame %>% rownames_to_column("date_A") %>% 
+  pivot_longer(cols = 2:dim(.)[2], names_to = "Date", values_to = "jaccard") %>%
+  inner_join(unique_combinations) %>% filter(date_A != Date) %>% 
+  mutate(Date = gsub('^([0-9]{4}-)([0-9]{1})$', '\\10\\2', Date),
+         Date = as.Date(paste0(Date,"-01"), format = "%Y-%m-%d"))
+
+# partitioning beta diversity metrics from trawl dataset
+# create named list of each sampling date
+named_group_split <- function(.tbl, ...) {
+  grouped <- group_by(.tbl, ...)
+  names <- rlang::eval_bare(rlang::expr(paste(!!!group_keys(grouped), sep = " / ")))
+
+  grouped %>%
+    group_split() %>%
+    rlang::set_names(names)
+}
+
+date_lists = TB_trawl_commonsite %>%
+  named_group_split(date_id) %>%
+  map(., ~.x %>% select(-year, -month,-date_id))
+
+beta_lists <- lapply(date_lists, function(x,r){ betapart::beta.temp(x = x, y = r, index.family = 'jaccard')}, x = date_lists[[1]]) 
+beta_dates <- gsub('^([0-9]{4}-)([0-9]{1})$', '\\10\\2', names(beta_lists))
+beta_df <- bind_rows(beta_lists) %>% mutate(Date = as.Date(paste0(beta_dates,"-01"), "%Y-%m-%d")) %>% #select(Date, everything()) %>%
+  pivot_longer(-Date, names_to = "partition", values_to = "value")
+
+rich_time <- 
+  ggplot(TB_time_df, aes(x = Date, y = richness, group = data_type)) +
+  geom_point(aes(colour = data_type),size = 1.5) +
+  geom_line(aes(colour = data_type),size = 1.2) +
+  scale_x_date(date_breaks = "1 year", date_labels = "%Y") + 
+  scale_y_continuous(name = "Species Richness")+
+  scale_colour_manual(name = "", values = viridis(4)[c(2,3)]) +
+  theme_minimal() +
+  theme(legend.position = c(0, 1), legend.justification = c(0, 1), legend.background = element_rect(fill = "transparent", colour = NA),
+        axis.title.x = element_blank(), axis.text.x = element_blank(),
+        legend.spacing.y = unit(-0.1, 'cm'))
+
+ jaccard_time <-
+  ggplot(beta_df, aes(x = Date, y = value, group = partition)) + 
+   geom_point(aes(colour = partition), size = 1.5) +
+  geom_line(aes(colour = partition), size = 1.2) +
+  scale_y_continuous(name = "Jaccard dissimilarity", limits = c(0,1.1), expand = c(0.01,0.01))+
+  scale_colour_manual(name = "", values = viridis(7)[c(2,4,7)], labels = c("jaccard", "nestedness","turnover")) +
+  scale_x_date(date_breaks = "1 year", date_labels = "%Y") + 
+   theme_minimal() +
+  theme(legend.background = element_rect(colour = NA, fill = 'transparent'),
+        legend.position = c(0,1), legend.justification = c(0,1), axis.title.x = element_blank(),
+        legend.spacing.y = unit(-0.2, 'cm'))
+
+grid.arrange(rich_time, jaccard_time, ncol = 1)
+
+```
+
+The bottom panel can use a bit more explanation.
+This panel shows jaccard distance of each individual trawl from the initial trawl based on presence/absence data.
+Understanding the highlights and limitations of the analysis can give us a better picture of what is going on.
+First, a community in flux responding to directional change, we would expect the distance to increase over time.
+There is maybe slight evidence of this, but a lot of noise around that signal.
+Further, the relative effects of species turnover is quite variable over time and seems to show a larger seasonal signal relative to any trend over the time series.
+
+Taking this further,

### 2020-05-11 working_script.R

@@ -1,0 +1,23 @@
+TB_trawl_samplings <- TB_trawl_data %>% select(Date) %>%
+  group_by(Date) %>% distinct %>% ungroup %>%
+  mutate(Date = as.Date(Date), 
+         Date_num = as.numeric(Date))
+
+date_breaks = as.numeric(as.Date(paste0(seq(2007,2020, by = 1),"-01-01")))
+date_labels = year(as.Date(date_breaks, origin = "1970-01-01"))
+
+ggplot(TB_trawl_samplings, aes(x = Date, y = 0))+ geom_vline(aes(xintercept = as.numeric(ymd(Date)))) +
+  scale_x_continuous(breaks = date_breaks, labels = date_labels) +
+  theme(axis.title = element_blank()) +
+  ggtitle('Sampling events')
+                                      
+
+TB_month_hist <- TB_trawl_samplings %>%
+  mutate(month_num = lubridate::month(Date), 
+         month_name = lubridate::month(Date, label = TRUE)) 
+
+  ggplot(TB_month_hist, aes(month_num)) + geom_bar(width = 1) +
+    scale_x_continuous(breaks = seq(1,12, by = 1), labels = lubridate::month(seq(1,12,by = 1), label = TRUE)) +
+    theme_minimal() +
+    theme(axis.title = element_blank())
+  

### 2020-05-13 text/trawl_summary.Rmd
Trawl analysis updated and Common name fixes should be copmlete.

@@
 
-## Beta diversity
+## Species diversity
 
 We can start to break this down further, and the inference that species richness might be increasing over time has some support (again, not sure yet if this is real or methodological).
+2020 is an obvious outlier here because we have only conducted 3 trawls (bummer) and I don't know what that little blip is in 2014.
+One weird instance where the code is mischaracterizing something.
 
@@
 
-Taking this further,
+## Community changes
+
+Taking this further, we can look at how evenly species are distributed within the community.
+Rank-abundance plots of the community for integrated across each year show common species are always common (not surprising) and there is a lot of inter-annual variability in the less common species.
+Here, 'Species rank' is calculated based on the full time series and fixed.
+We then plot the relative abundance of each species in each year.
+The black line shows the global community rank-abundance relationship.
+
+```{r rank-abundance plots, include=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
+
+TB_ann_relN = TB_trawl_data %>% select(year, Common_name, Abundance) %>% na.omit %>%
+  group_by(year, Common_name) %>%
+  summarise(Abundance = sum(Abundance, na.rm = TRUE)) %>%
+  mutate(rel_N = Abundance/sum(Abundance, na.rm = TRUE)) %>%
+  left_join(TB_trawl_data %>% 
+              # Turn filter back on to use 2007 as reference year
+              # filter(year == 2007) %>%
+              na.omit %>%
+              group_by(Common_name) %>%
+              summarise(Abundance = sum(Abundance, na.rm = TRUE)) %>%
+              mutate(rel_N = Abundance/sum(Abundance, na.rm = TRUE)) %>%
+              mutate(rank = dense_rank(desc(rel_N))) %>%
+              select(Common_name, rank)) %>%
+  ungroup() %>%  mutate(year = as.factor(year))
+
+global_relN <- TB_trawl_data %>% 
+              # Turn filter back on to use 2007 as reference year
+              # filter(year == 2007) %>%
+              na.omit %>%
+              group_by(Common_name) %>%
+              summarise(Abundance = sum(Abundance, na.rm = TRUE)) %>%
+              mutate(rel_N = Abundance/sum(Abundance, na.rm = TRUE)) %>%
+              mutate(rank = dense_rank(desc(rel_N))) %>%
+              select(Common_name, rel_N, rank)
+
+ggplot(TB_ann_relN, aes(x = rank, y = log10(rel_N))) + 
+    geom_line(data = global_relN, aes(x = rank, y = log10(rel_N)), size = 2, color = "black") +
+  geom_line(aes(group = year, color = year), alpha = 0.7, size = 1.2) +
+  scale_y_continuous(name = expression(log[10]*"(Relative Abundance)"))+
+  scale_x_continuous(name = "Species Rank")+
+  scale_color_viridis(discrete = TRUE) +
+  theme_minimal()
+
+```
+
+These inter-annual trends aside, we see that evenness of the community doesn't show drastic differences among years.
+Sampling effort is going to explain some of this, but this also might represent some neutral (zero sum) or compensatory dynamics among species in the community.
+
+```{r annual rank-abundance, echo=FALSE, message=FALSE, warning=FALSE, include=TRUE}
+
+TB_relN_ann = TB_trawl_data %>% select(year, Common_name, Abundance) %>% na.omit %>%
+  group_by(year, Common_name) %>%
+  summarise(Abundance = sum(Abundance, na.rm = TRUE)) %>%
+  mutate(rel_N = Abundance/sum(Abundance, na.rm = TRUE),
+         rank = dense_rank(desc(rel_N))) %>%
+  ungroup() %>%  mutate(year = as.factor(year))
+
+ggplot(TB_relN_ann, aes(x = rank, y = log10(rel_N))) + 
+  geom_line(aes(group = year, color = year), alpha = 0.6, size = 1.2) +
+   scale_y_continuous(name = expression(log[10]*"(Relative Abundance)"))+
+  scale_x_continuous(name = "Species Rank")+
+  scale_color_viridis(discrete = TRUE) +
+  theme_minimal()
+
+```
+
+We can characterize the how communities shift and the important players (i.e.
+those with loadings on PC1 or PC2 of the most extreme 1%).
+This shows there is are noticeable shifts in the community composition over the years and there appears to by directional changes with time.
+
+```{r craig pca, include = TRUE, echo= FALSE, warning = FALSE, message=FALSE}
+# create taxa by site matrix with common names
+TB_trawl_commonsite <- TB_trawl_data %>%
+  select(year, month, date_id, Common_name) %>%
+  group_by(date_id, Common_name) %>%
+  distinct() %>% 
+  mutate(pres = 1) %>%
+  pivot_wider(names_from = Common_name, values_from = pres, values_fill = list(pres = 0)) %>%
+  ungroup()
+##addressing outlier points
+TB_trawl_outlier_rm <- TB_trawl_commonsite %>%
+  filter(date_id %ni% c("2018-1","2007-7"))
+
+### Legendre PC with Hellinger
+# Hellinger pre-transformation of the species matrix
+tb.h <- decostand (TB_trawl_outlier_rm %>% select(-c(1:2)) %>% column_to_rownames("date_id"), "hellinger")
+tb.h.pca <- rda(tb.h)
+tb.h.pca.summ <- summary(tb.h.pca)
+
+#pull coordinates and loadings
+TB <- data.frame(matrix(ncol=2,nrow=105, dimnames=list(NULL, c("PC1", "PC2"))))
+
+df1  <- data.frame(tb.h.pca.summ$sites[,1:2])
+TB$PC1 <- df1[,1]
+TB$PC2 <- df1[,2]
+TB$date_id <- row.names(tb.h.pca.summ$sites)
+TB <- left_join(TB, TB_trawl_outlier_rm, by=c("date_id"="date_id"))
+
+Var = factor(TB$year, levels =c("2007","2009","2010","2011",
+                                "2012","2013","2014","2015",
+                                "2016","2017","2018","2019",
+                                "2020"))
+#pull loadings
+TB.loadings  <- data.frame(tb.h.pca.summ$species[,1:2])
+TB.loadings$Species <- row.names(tb.h.pca.summ$species)
+#filtering out top species contributions
+TB.loadings.top <- TB.loadings %>%
+  filter(PC1>quantile(PC1, prob=.99) | 
+           PC1<quantile(PC1, prob=.01)| 
+           PC2>quantile(PC2, prob=.99)  | 
+           PC2<quantile(PC2, prob=.01))
+
+#analyses
+# tb.h.dl <- dist(tb.h)
+# pc_test<- betadisper(tb.h.dl, TB$year)
+# anova(pc_test)
+# permutest(pc_test, pairwise = TRUE)
+
+TB.centroids <- TB %>%
+  group_by(year) %>%
+  summarise(
+    meanPC1 = mean(PC1),
+    meanPC2 = mean(PC2)
+  )
+TB$year <- as.integer(TB$year)
+
+#figure
+ggplot(data = TB, aes(x=PC1, y=PC2, color=as.factor(year))) + 
+  geom_point(aes(color=as.factor(year)), size =3, alpha = 0.6)+
+  geom_path(data=TB.centroids, aes(x=meanPC1, y=meanPC2), arrow=arrow(), size=1, color="grey20")+
+  geom_text(data=TB.centroids, aes(x=meanPC1, y=meanPC2, label=year), color="grey20")+
+  ggrepel::geom_text_repel(data=TB.loadings.top, aes(x=PC1, y=PC2, label=Species), color="grey30")+
+  geom_hline(yintercept=0, linetype="dotted") +
+  geom_vline(xintercept=0, linetype="dotted") +
+  labs(color = "Year") +
+  theme_minimal() +
+  scale_colour_viridis(discrete = TRUE)
+
+```
+
+The environmental data will need to be completed further to begin to test if these changes are driven by the environment.
+In its absence, it might be a useful exercise to see how the composition of community traits might guide the expected patterns observed in the environment.
+
+```{r rank table, include = TRUE, echo = FALSE, warning = FALSE, message = FALSE}
+
+rank_table <- TB_relN_ann %>% group_by(Common_name) %>%
+  summarise(mean_rank = round(mean(rank),2),
+              rank_sd = round(sd(rank, na.rm = TRUE),2)) %>%
+  arrange(mean_rank) %>%
+  rename(`Common Name` = "Common_name",
+         `Mean Rank` = "mean_rank",
+         `Rank SD` = "rank_sd")
+
+knitr::kable(rank_table)
+
+```

### 2020-05-13 Analysis/active/trawl_analysis/trawl_Kmeans.R

@@ -1,9 +1,120 @@
 #trawl K-means analysis of fish data
+# create taxa by site matrix with common names
+TB_trawl_commonsite <- TB_trawl_data %>%
+  select(year, month, date_id, Common_name) %>%
+  group_by(date_id, Common_name) %>%
+  distinct() %>% 
+  mutate(pres = 1) %>%
+  pivot_wider(names_from = Common_name, values_from = pres, values_fill = list(pres = 0)) %>%
+  ungroup()
+
+
+##addressing outlier points
+TB_trawl_outlier_rm <- TB_trawl_commonsite %>%
+  filter(date_id %ni% c("2018-1","2007-7"))
+
+###Legendre PC with Hellinger
+
+#Hellinger pre-transformation of the species matrix
+tb.h <- decostand (TB_trawl_outlier_rm %>% select(-c(1:2)) %>% column_to_rownames("date_id"), "hellinger")
+tb.h.pca <- rda(tb.h)
+tb.h.pca.summ <- summary(tb.h.pca)
+
+
+#pull coordinates and loadings
+TB <- data.frame(matrix(ncol=2,nrow=105, dimnames=list(NULL, c("PC1", "PC2"))))
+
+df1  <- data.frame(tb.h.pca.summ$sites[,1:2])
+TB$PC1 <- df1[,1]
+TB$PC2 <- df1[,2]
+TB$date_id <- row.names(tb.h.pca.summ$sites)
+TB <- left_join(TB, TB_trawl_outlier_rm, by=c("date_id"="date_id"))
+
+Var = factor(TB$year, levels =c("2007","2009","2010","2011",
+                                "2012","2013","2014","2015",
+                                "2016","2017","2018","2019",
+                                "2020")) # factor variable for colours
+
+
+#pull loadings
+TB.loadings  <- data.frame(tb.h.pca.summ$species[,1:2])
+TB.loadings$Species <- row.names(tb.h.pca.summ$species)
+#filtering out top species contributions
+TB.loadings.top <- TB.loadings %>%
+  filter(PC1>quantile(PC1, prob=.99) | 
+           PC1<quantile(PC1, prob=.01)| 
+           PC2>quantile(PC2, prob=.99)  | 
+           PC2<quantile(PC2, prob=.01)) 
+#analyses
+tb.h.dl <- dist(tb.h)
+pc_test<- betadisper(tb.h.dl, TB$year)
[…]

### 2020-05-13 Analysis/active/trawl_analysis/trawl_ordination.R

@@ -1,6 +1,6 @@
 ## terrebonne bay trawl working analysis
 ## works with TB_trawl_data
-source("install-packages.R")#installs all necessary packages
+# source("install-packages.R")#installs all necessary packages
 source("datascript.R")#imports data with some minor cleanup
 
 

### 2020-05-13 Analysis/active/trawl_analysis/trawl_specaccum.R

@@ -69,11 +69,11 @@ TB_date_jaccard = vegdist((TB_trawl_commonsite %>% select(-year, -month) %>%
                              column_to_rownames("date_id")), method = "jaccard") %>%
   as.matrix %>% as.data.frame %>% rownames_to_column("date_A") %>% 
   pivot_longer(cols = 2:dim(.)[2], names_to = "Date", values_to = "jaccard") %>%
-  inner_join(unique_combinations) %>% filter(date_A != date_B) %>% 
+  inner_join(unique_combinations) %>% filter(date_A != Date) %>% 
   mutate(Date = gsub('^([0-9]{4}-)([0-9]{1})$', '\\10\\2', Date),
          Date = as.Date(paste0(Date,"-01"), format = "%Y-%m-%d"))
 
-ggplot(Tb_date_jaccard, aes(x = Date, y = jaccard)) + 
+ggplot(TB_date_jaccard, aes(x = Date, y = jaccard)) + 
   geom_point() +
   geom_line() +
   scale_y_continuous()

### 2020-05-13 datascript.R

@@ -32,7 +32,8 @@ data_import <<- function(){
     rename(datetime = 'Date/Time', temp_C = 'Temp', temp_F = 'Water Temp F', spCon_uS_cm = 'Value4', sal_psu = 'Sal') %>%
     mutate(datetime = parse_date_time(datetime, orders = c("%m/%d/%Y %H:%M", "%m/%d/%y %H:%M")),
            yday = yday(datetime))
-  
+  # 2020-05-12 
+  # these are throwing errors and not loading to do network timeout. May need to reset/update DNS servers if this continues.
   shallow<<- read_csv(file = "https://www.dropbox.com/s/bw1klp28wx5i7lx/TB2_Compiled_Data.csv?dl=1") %>% as.data.frame() %>%
     column_to_rownames('X1')
   deep<<- read_csv(file = "https://www.dropbox.com/s/581r05guoyj6aoc/Patch%20Mosaic%20Master2.csv?dl=1") %>% as.data.frame() %>%
@@ -44,199 +45,199 @@ data_import <<- function(){
   TB_2019_core_meta<<- read_csv(file = "./data/metadata/TB_2019_Core-Metadata.csv",
                                 col_types = cols(.default = "?", Date = col_date(format = "%m/%d/%Y"), Time = "i",
                                                  `Van Veen Grab` = "i", Core = "i"))
-#   sheets_auth(email = "jjunker@lumcon.edu")
-#   options(gargle_oauth_email = "jjunker@lumcon.edu")
-#   TB_trawl_meta <- sheets_get("1mUG6oYBGGONBzgXPsvS6XZkNRUIojxtI7BV8WUTh-3I")#sheetID extracted with as_sheets_ID(*sheet URL*)
-#   TB_trawl_tabs <- nrow(TB_trawl_meta[['sheets']])
-#   TB_trawl_list <- vector('list', TB_trawl_tabs)
-#   for(tab in 1:TB_trawl_tabs){
-#     TB_trawl_list[[tab]] <- sheets_read(TB_trawl_meta[['spreadsheet_id']], sheet = tab, col_types = "T?d", range = cell_cols("A:C"))
-#   }
-#   TB_trawl_data <- bind_rows(TB_trawl_list)
-# 
-# ##### Data entry fixes ####
-#    TB_trawl_data <- TB_trawl_data %>%
-#     filter(!is.na(Species)) %>%
[…]

### 2020-05-13 working_script.R

@@ -21,3 +21,36 @@ TB_month_hist <- TB_trawl_samplings %>%
     theme_minimal() +
     theme(axis.title = element_blank())
   
+  
+#### Combine relative abundance by year and plot how this ####
+  
+  TB_ann_relN = TB_trawl_data %>% select(year, Common_name, Abundance) %>% na.omit %>%
+    group_by(year, Common_name) %>%
+    summarise(Abundance = sum(Abundance, na.rm = TRUE)) %>%
+    mutate(rel_N = Abundance/sum(Abundance, na.rm = TRUE)) %>%
+    left_join(TB_trawl_data %>% 
+                # Turn filter back on to use 2007 as reference year
+                # filter(year == 2007) %>%
+                na.omit %>%
+                group_by(Common_name) %>%
+                summarise(Abundance = sum(Abundance, na.rm = TRUE)) %>%
+                mutate(rel_N = Abundance/sum(Abundance, na.rm = TRUE)) %>%
+                mutate(rank = dense_rank(desc(rel_N))) %>%
+                select(Common_name, rank))
+  
+  TB_trawl_data %>% filter(year == 2007) %>%
+    group_by(Common_name) %>%
+    summarise(Abundance = sum(Abundance, na.rm = TRUE))
+    
+  TB_relN_ann = TB_trawl_data %>% select(year, Common_name, Abundance) %>% na.omit %>%
+    group_by(year, Common_name) %>%
+    summarise(Abundance = sum(Abundance, na.rm = TRUE)) %>%
+    mutate(rel_N = Abundance/sum(Abundance, na.rm = TRUE),
+           rank = dense_rank(desc(rel_N))) %>%
+    ungroup() %>%  mutate(year = as.factor(year))
+# widen out data
+  
+  TB_relN_ann_wide <- TB_relN_ann %>%
+    pivot_wider(id_cols = c(year,Common_name), names_from = year, values_from = rank) %>%
+    group_by(Common_name)
+  

### 2020-05-27 Analysis/active/trawl_analysis/trawl_LDATS.R
initiate the LDATS analysis

@@ -1,0 +1,75 @@
+source("datascript.R")
+
+devtools::install_github("weecology/LDATS")
+library(LDATS)
+data(rodents)
+
+r_LDATS <- LDA_TS(rodents, topics = 2:5, nseeds = 2, formulas = ~1, nchangepoints = 0:1, timename = "newmoon")
+
+# give a go on trawl data set.
+# need to keep catches in raw abundance. 
+# the TS models use the total catch information 
+# as weights for the quality of information
+
+##create taxa by site matrix
+TB_trawl_taxasite <- TB_trawl_data %>%
+  select(Date, Common_name, Abundance) %>%
+  group_by(Date, Common_name) %>%
+  summarise(Abundance = sum(Abundance)) %>%
+  na.omit %>%
+  pivot_wider(names_from = Common_name, values_from = Abundance, values_fill = list(Abundance = 0)) %>%
+  ungroup() 
+
+seasonal_time <- data.frame(day = 1:365, sin_year = sin(1:365), cos_year = cos(1:365))
+
+# write.csv(TB_trawl_data %>% select(Common_name, species_mod) %>% group_by(Common_name, species_mod) %>% unique, file = "./data/spp_abbrev.csv", quote = FALSE, row.names = FALSE)
+
+#create covariate table
+TB_trawl_covariates <- TB_trawl_taxasite %>% select(Date) %>% mutate(Date = as.Date(Date),
+                                                                     time = as.integer(Date, origin = min(Date)),
+                                                                     day = lubridate::yday(Date)) %>%
+  left_join(seasonal_time) %>% data.frame
+
+TB_trawl_taxasite %>% select(-Date) %>% data.frame -> TB_trawl_taxa
+
+# combine taxa data and covariate data to list, name, and conform to LDATS inputs
+TB_LDATS <- list(TB_trawl_taxa, TB_trawl_covariates) %>%
+  setNames(.,nm = c("document_term_table","document_covariate_table")) %>%
+  LDATS::conform_LDA_TS_data(quiet = FALSE)
+
+debugonce(check_LDA_TS_inputs)
+check_LDA_TS_inputs(TB_LDATS, topics = 2:5, nseeds = 2, formulas = ~time, nchangepoints = 0:1, timename = "time", 
+                    weights = TRUE, control = list(quiet = FALSE))
+#should return NULL if everything is okay
+
[…]

### 2020-05-27 datascript.R

@@ -33,29 +33,31 @@ data_import <<- function(){
     mutate(datetime = parse_date_time(datetime, orders = c("%m/%d/%Y %H:%M", "%m/%d/%y %H:%M")),
            yday = yday(datetime))
   # 2020-05-12 
-  # these are throwing errors and not loading to do network timeout. May need to reset/update DNS servers if this continues.
-  shallow<<- read_csv(file = "https://www.dropbox.com/s/bw1klp28wx5i7lx/TB2_Compiled_Data.csv?dl=1") %>% as.data.frame() %>%
-    column_to_rownames('X1')
-  deep<<- read_csv(file = "https://www.dropbox.com/s/581r05guoyj6aoc/Patch%20Mosaic%20Master2.csv?dl=1") %>% as.data.frame() %>%
-    column_to_rownames('X1')
-  site_list<<-read_csv(file ="https://www.dropbox.com/s/fmahl3dc34ss33x/terrebonne_site_master.csv?dl=1") %>% as.data.frame()
-  TB_2018_core_meta<<-read_csv(file = "./data/metadata/TB_2018_Core-Metadata.csv", 
-                               col_types = cols(.default = "?", Date = col_date(format = "%m/%d/%Y"), Time = "i",
-                                                `Van Veen Grab` = "i", Core = "i"))
-  TB_2019_core_meta<<- read_csv(file = "./data/metadata/TB_2019_Core-Metadata.csv",
-                                col_types = cols(.default = "?", Date = col_date(format = "%m/%d/%Y"), Time = "i",
-                                                 `Van Veen Grab` = "i", Core = "i"))
-   # sheets_auth(email = "jjunker@lumcon.edu")
-   # options(gargle_oauth_email = "jjunker@lumcon.edu")
-   # TB_trawl_meta <- sheets_get("1mUG6oYBGGONBzgXPsvS6XZkNRUIojxtI7BV8WUTh-3I")#sheetID extracted with as_sheets_ID(*sheet URL*)
-   # TB_trawl_tabs <- nrow(TB_trawl_meta[['sheets']])
-   # TB_trawl_list <- vector('list', TB_trawl_tabs)
-   # for(tab in 1:TB_trawl_tabs){
-   #   TB_trawl_list[[tab]] <- sheets_read(TB_trawl_meta[['spreadsheet_id']], sheet = tab, col_types = "T?d", range = cell_cols("A:C"))
-   # }
[…]

### 2020-05-27 Analysis/active/trawl_analysis/trawl_LDATS.R
updating the trawl summary

@@ -43,9 +43,9 @@ check_LDA_TS_inputs(TB_LDATS, topics = 2:5, nseeds = 2, formulas = ~time, nchang
 #should return NULL if everything is okay
 
 lda_model_set <- LDA_set(document_term_table = TB_LDATS$document_term_table,
-                         topics = c(2:5),
-                         nseeds = 2,
-                         control = list(quiet = FALSE))
+                         topics = c(2:7),
+                         nseeds = 5,
+                         control = list(quiet = TRUE))
 
 # saveRDS(lda_model_set, file = "./data/lda_model_set.RDS")
 lda_model_set <- readRDS(file = "./data/lda_model_set.rds")
@@ -55,7 +55,7 @@ plot(selected_lda_set[[1]])
 TB_trawl_ts <- TS_on_LDA(LDA_models = selected_lda_set, 
           document_covariate_table = TB_LDATS$document_covariate_table,
           formulas = ~sin_year + cos_year,
-          nchangepoints = c(0:5),
+          nchangepoints = c(1:5),
           timename = "time",
           weights = document_weights(TB_LDATS$document_term_table),
           control = list(nit = 1000))
@@ -64,12 +64,34 @@ TB_trawl_ts <- TS_on_LDA(LDA_models = selected_lda_set,
 TB_trawl_ts <- readRDS(file = "./data/TB_trawl_ts.rds")
 
 selected_ts <- select_TS(TB_trawl_ts)
+# debugonce(check_changepoints)
 plot(selected_ts)
 
+selected_ts$nchangepoints
 
 plot(rodents$document_covariate_table$newmoon, rodents$document_covariate_table$sin_year, type = "l")
 lines(rodents$document_covariate_table$newmoon, rodents$document_covariate_table$cos_year, type = "l", col = "red")
 
 
-trawl_LDATS <- LDA_TS(TB_LDATS, topics = 8:12, nseeds = 16, formulas = ~1, nchangepoints = 0:2, timename = "time",
-                      weights = TRUE)
+trawl_LDATS <- LDA_TS(TB_LDATS,
+                      topics = 2:7,
+                      nseeds = 10,
+                      formulas = ~sin_year + cos_year,
+                      nchangepoints = 1:3,
+                      timename = "time")
+
+saveRDS(trawl_LDATS, file = "./data/TB_trawl_LDATS.rds")
+trawl_LDATS <- readRDS(file = "./data/TB_trawl_LDATS.rds")
+
+
+plot(trawl_LDATS, option = "B")
+
[…]

### 2020-08-10 text/trawl_summary.Rmd
initiate the LDATS analysis
updating the trawl summary
updated salinity and temp files and

@@
 
-#TERREBONNE BAY TRAWL ANALYSIS SUMMARY {.unlisted .unnumbered}
+# TERREBONNE BAY TRAWL ANALYSIS SUMMARY {.unlisted .unnumbered}
 
@@
 ```
+
+## LDATS
+
+This is the beginning of the LDATS summary
+
+```{r LDATS, echo = FALSE, warning=FALSE, include = TRUE, fig.height=8, fig.width=10}
+library(LDATS)
+trawl_LDATS <- readRDS(file = "../data/TB_trawl_LDATS.rds")
+plot(trawl_LDATS)
+```

### 2021-06-22 docs/ms/ms.RMD
updated workflow and added code for calculating Chao and Ricotta contribution towards dissimilarity.

---
title: "Manuscript title here"
author: 
- name: James R Junker
  affiliation: Louisiana Universities Marine Consortium
output:
   word_document:
     reference_docx: docx_template.docx
   pdf_document:
     keep_tex: true
   html_document: default
header-includes:
- \usepackage{lineno}
- \usepackage{amsmath}
- \linenumbers
linestretch: 1
bibliography: refs.bib
link-citations: no
link-color: grey
csl: ecology.csl
---

<!--- this is a note in Rmarkdown --->

# Abstract
Anthropogenic activities continue to exert long-term, varied, and increasing pressures on ecosystems causing alterations to biological diversity on broad and local scales. Shifts in biodiversity are variable, nuanced and difficult to predict. Yet, understanding how communities change through time is crucial for predicting current and future changes to biological systems and the services they provide. Explaining the extent and pace of biodiversity change will require identifying the conditions that lead to divergent biological responses, e.g., whether change happens gradually or abruptly and through individual versus cohesive species responses. In particular, disentangling the roles of extrinsic, environmental forcing and intrinsic, ecological processes is vital. We propose to combine two time series of environmental and biological change with information on species’ traits and trophic interactions to attribute biological change to its extrinsic and intrinsic drivers. The proposed work includes analysis and continuation of a data set extending nearly two decades of pelagic megafaunal communities and environment monitoring
for a shallow estuarine bay along the Gulf of Mexico Coast. To this, we add analysis and continuation of a three year dataset of benthic macrofaunal from the same bay. The project proposes to address four key questions.

\newpage

# Introduction
<!--- warming and effects in food webs --->
Anthropogenic activities continue to exert long-term, varied, and increasing pressures on ecosystems [@steffen2015] causing alterations to biological diversity on local and global scales. Shifts in biodiversity at local scales are variable and potentially more nuanced than at global scales, but generally local changes manifest primarily as changes to community composition and structure rather than declines in richness [@hillebrand2018]. These shifts in communities through time are difficult to predict, in part, due to the multidimensional nature of biodiversity [@chase2018]. Yet, understanding how communities change through time is crucial for predicting current and future changes to biological systems and ecosystem services.
<!--- Speeding up of food web: Species levels--->
Explaining the extent and pace of biodiversity change will require identifying the conditions that lead to divergent biological responses to environmental change, both natural and anthropogenic. In particular, it will be important to disentangle the roles of intrinsic (e.g., ecological) and extrinsic (e.g., environmental) drivers of biodiversity change. Intrinsic and extrinsic processes can interact, leading to temporal patterns of biodiversity change that vary in response to environmental change. For example, gradual environmental change over time can lead to gradual community shifts or these shifts may be undetectable or abrupt [@williams2011][@scheffer2003].

Disentangling the complexity of drivers and responses in community structure is especially pressing for marine systems. Marine systems have experienced greater changes than other habitats [@antao2020]. Yet, we currently lack linkages between ecological theory, primarily derived from terrestrial systems, and data in marine systems leaving unanswered questions about biodiversity changes in these habitats [@blowes2019]. We propose a framework to explore the nature of biodiversity change in an estuary bay community and connect this change to intrinsic and extrinsic drivers. This research will build towards a more coherent theory of biodiversity change through time [@shoemaker2020]. 
<!--- Connect traits to the 'speed' of ecosystem energy fluxes--->
Here, we quantified over a decade of change in a shallow estuarine community. We

# Methods

## Trawl sampling

Trawl sampling was conducted as part of the Louisiana Universities Marine Consortium's educational outreach program [https://www.lumcon.edu/education-and-outreach]<https://lumcon.edu/education-and-outreach/>. Individual trawls were conducted using *trawl apparatus description...*

## Community change

## Statistical Analyses

# Results

# Discussion

\newpage

# References

### 2021-06-22 Analysis/active/environmental-analysis/environmental-data.R

@@ -1,50 +1,0 @@
-## source in environmental data ##
-
-source("datascript.R")
-
-## combine the TB and MC datasets to fill in gaps
-full_dates = seq.Date(from = as.Date("2008-01-01"), to = Sys.Date(), by = 1) %>% data.frame %>% setNames('Date')
-
-##temperature
-temp_combined = left_join(MC_temperature_df %>% rename(MC_temp = 'temp_C'), TB_temp_df %>% rename(TB_temp = 'temp_C'), by = 'Date') %>%
-  right_join(full_dates, by = 'Date', all = TRUE) %>% ungroup() %>%
-  join(regional_temp_df)
-#bivariate plot of TB and MC temperature series
-ggplot(temp_combined, aes(x = MC_temp, y = TB_temp)) + geom_point(size = 1.2, alpha = 0.5)
-ggplot(temp_combined, aes(x = sst, y = TB_temp)) + geom_point(size = 1.2, alpha = 0.5)
-
-ggplot(temp_combined, aes(x = Date)) + geom_line(aes(y = MC_temp), colour = 'red') +
-  geom_line(aes(y = TB_temp), colour = 'blue') +
-  geom_line(aes(y = sst), colour = 'black')
-
-# build a forecasted model with Marine center and regional SST to fill NAs
-library(forecast)
-TB_temp_ts = ts(temp_combined$TB_temp)
-set.seed(42);ar.model = auto.arima(temp_combined$TB_temp, xreg = as.matrix(temp_combined[,c(2,4)]))
-ar.model
-
-TB_nas = is.na(temp_combined$TB_temp)
-sum(TB_nas)
-set.seed(123);TB_forecast = forecast(ar.model, xreg = as.matrix(temp_combined[,c(2,4)]))
-
-temperature_series = temp_combined %>% 
-  bind_cols(TB_forecast$mean) %>% 
-  rename(forecast = '...5') %>%
-  mutate(TB_tempC_series = ifelse(is.na(TB_temp), forecast,TB_temp),
-         TB_tempC_series = ifelse(is.na(TB_tempC_series), sst, TB_tempC_series))
-    
-ggplot(temperature_series, aes( x = Date)) +
-  geom_line(aes(y = TB_tempC_series), colour = 'blue') +
-  geom_line(aes(y = sst), colour = 'red')+
-  geom_line(aes(y = TB_temp), colour = 'black')
-
-## salinity
-
[…]

### 2021-06-22 Analysis/active/environmental-analysis/fit_salinity-timeseries.R

@@ -1,0 +1,124 @@
+source("datascript.R")
+
+env_series = salinity_series %>% dplyr::select(Date, MC_sal, TB_sal, sss) %>%
+  left_join(temperature_series %>% dplyr::select(Date, MC_temp, TB_temp, sst), by = "Date") %>%
+  dplyr::mutate(julian = julian(Date, origin = as.Date("2007-01-01")),
+                weekly = paste0(year(Date),"-", week(Date))) %>%
+  group_by(weekly) %>% dplyr::select(-Date) %>% dplyr::mutate(Date = min(`julian`)) %>%
+  group_by(Date, weekly) %>%
+  dplyr::summarise(across(everything(), ~mean(.x, na.rm = TRUE))) %>%
+  dplyr::mutate(across(everything(), ~replace(.x, is.nan(.x), NA)))
+
+# estimate univariate state space model
+
+sal_arss = MARSS::MARSS()
+
+set.seed(42);sal_forecast1 = forecast::auto.arima(env_series$TB_sal, xreg = as.matrix(env_series[,c(3)]), stepwise = FALSE, approximation = FALSE)
+# sal_forecast1
+# set.seed(42);sal_forecast2 = forecast::auto.arima(env_series$TB_sal, xreg = as.matrix(env_series[,c(3,5)]), stepwise = FALSE, approximation = FALSE)
+# sal_forecast2
+TB_salinity_forecast1 = forecast::forecast(sal_forecast1, xreg = as.matrix(env_series[,3]))
+# TB_salinity_forecast2 = forecast::forecast(sal_forecast2, xreg = as.matrix(env_series[,c(3,5)]))
+# env_series = env_series %>% bind_cols(forecast1_mean = TB_salinity_forecast$mean) %>%
+#   bind_cols(forecast1_up = TB_salinity_forecast$upper) %>% bind_cols(forecast1_dw = TB_salinity_forecast$lower) %>%
+kr <- KalmanRun(env_series$TB_sal, sal_forecast1$model)
+    
+id.na <- which(is.na(env_series$TB_sal))
+# for (i in id.na)
+#   y[i] <- sal_forecast1$model$Z %*% kr$states[i,]
+# alternative to the explicit loop above
+y = sapply(id.na, FUN = function(x, Z, alpha) Z %*% alpha[x,], 
+       Z = sal_forecast1$model$Z, alpha = kr$states)
+y[id.na]
+
+
+
[…]

### 2021-06-22 Analysis/active/trawl_analysis/trawl_LDATS.R

@@ -13,7 +13,7 @@ r_LDATS <- LDA_TS(rodents, topics = 2:5, nseeds = 2, formulas = ~1, nchangepoint
 
 ##create taxa by site matrix
 TB_trawl_taxasite <- TB_trawl_data %>%
-  select(Date, Common_name, Abundance) %>%
+  dplyr::select(Date, Common_name, Abundance) %>%
   group_by(Date, Common_name) %>%
   summarise(Abundance = sum(Abundance)) %>%
   na.omit %>%
@@ -22,22 +22,22 @@ TB_trawl_taxasite <- TB_trawl_data %>%
 
 seasonal_time <- data.frame(day = 1:365, sin_year = sin(1:365), cos_year = cos(1:365))
 
-# write.csv(TB_trawl_data %>% select(Common_name, species_mod) %>% group_by(Common_name, species_mod) %>% unique, file = "./data/spp_abbrev.csv", quote = FALSE, row.names = FALSE)
+# write.csv(TB_trawl_data %>% dplyr::select(Common_name, species_mod) %>% group_by(Common_name, species_mod) %>% unique, file = "./data/spp_abbrev.csv", quote = FALSE, row.names = FALSE)
 
 #create covariate table
-TB_trawl_covariates <- TB_trawl_taxasite %>% select(Date) %>% mutate(Date = as.Date(Date),
+TB_trawl_covariates <- TB_trawl_taxasite %>% dplyr::select(Date) %>% mutate(Date = as.Date(Date ,origin = min(Date)),
                                                                      time = as.integer(Date, origin = min(Date)),
                                                                      day = lubridate::yday(Date)) %>%
   left_join(seasonal_time) %>% data.frame
 
-TB_trawl_taxasite %>% select(-Date) %>% data.frame -> TB_trawl_taxa
+TB_trawl_taxasite %>% dplyr::select(-Date) %>% data.frame -> TB_trawl_taxa
 
 # combine taxa data and covariate data to list, name, and conform to LDATS inputs
 TB_LDATS <- list(TB_trawl_taxa, TB_trawl_covariates) %>%
   setNames(.,nm = c("document_term_table","document_covariate_table")) %>%
   LDATS::conform_LDA_TS_data(quiet = FALSE)
 
-debugonce(check_LDA_TS_inputs)
+# debugonce(check_LDA_TS_inputs)
[…]

### 2021-06-22 Analysis/active/trawl_analysis/trawl_sensitivity.R

@@ -8,7 +8,7 @@ source("datascript.R")
 
 # import the data
 TB_trawl_taxasite <- TB_trawl_data %>% 
-select(Date, Common_name, Abundance) %>%
+dplyr::select(Date, Common_name, Abundance) %>%
   group_by(Date, Common_name) %>%
   summarise(Abundance = sum(Abundance)) %>%
   na.omit %>%
@@ -20,22 +20,22 @@ TB_trawl_richness_yr <- TB_trawl_taxasite %>%
          month = month(Date)) %>% 
   filter(year != 2020) %>%
   filter(month %ni% c(4,5)) %>%
-  select(Date, year, month, everything()) %>%
-  named_group_split(year)
+  dplyr::select(Date, year, month, everything()) %>%
+  junkR::named_group_split(year)
 
 TB_trawl_richness <- TB_trawl_data %>% na.omit %>% mutate(year = year(Date)) %>%
   filter(year != 2020) %>% 
-  select(year, Common_name) %>% distinct %>%
+  dplyr::select(year, Common_name) %>% distinct %>%
   group_by(year) %>% count %>% bind_rows(data.frame(year= 2020, n = 75))
 
 richness_2020 <- TB_trawl_taxasite %>% na.omit %>% mutate(year = year(Date)) %>%
-  filter(year == 2020) %>% select(-year) %>%
+  filter(year == 2020) %>% dplyr::select(-year) %>%
   pivot_longer(cols = -Date, names_to = "Common_name", values_to = "Abundance") %>%
   filter(Abundance > 0 & !is.na(Abundance)) %>%
-  select(Date, Common_name) %>% distinct %>%
+  dplyr::select(Date, Common_name) %>% distinct %>%
   group_by(Date) %>% count %>% 
   rename(trawl_richness = n) %>% ungroup %>%
-  mutate(trawls = 1:n()) %>% select(-Date) %>%
+  mutate(trawls = 1:n()) %>% dplyr::select(-Date) %>%
   mutate(rel_richness = trawl_richness/75*100)
 
 
@@ -46,13 +46,13 @@ trawl_sample_simulation <- lapply(sample_n, function(x) lapply(TB_trawl_richness
 
 for(i in seq_along(trawl_sample_simulation)){
   trawl_sample_simulation[[i]] <- trawl_sample_simulation[[i]] %>%
-    bind_rows %>% mutate(trawls = i) %>% select(Date, year, month, trawls, everything())
[…]

### 2021-06-22 R/Evenness.R

@@ -1,0 +1,319 @@
+#*******************************************************************************
+#********************************************************************************
+# 
+## R scipts "Evenness" for Chao and Ricotta (2019) Ecology paper. 
+## This R code is for computing Figures 2, 3 and 4 of Chao and Ricotta (2019) paper.
+# NOTE: The packages "ggplot2", "dplyr", "ade4", "reshape2", "ggpubr", "phytools", "ape" must be 
+# installed and loaded before running the scripts. 
+# 
+#
+# The following R scripts include two parts:  
+# (1). Script for computing the profiles for six classes of evenness measures (see Figure 2 in Chao and Ricotta's paper).
+# (2). Script for computing the contribution of each species/node to taxonomic dissimarity and/or phylogenetic
+#      dissimarity measures (see Figures 3 and 4 in Chao and Ricotta's paper)
+# 
+#
+#*******************************************************************************
+#*******************************************************************************
+
+# library(ggplot2)
+# library(dplyr)
+# library(ade4)
+# library(reshape2)
+library(ggpubr)
+# library(phytools)
+# library(ape)
+
+####################################################################################
+#
+# (1). Computing the profiles for six classes of evenness measures (Table 1 and Figure 2)
+#
+####################################################################################
+
+qD <- function(p,q){
+  p <- p[p>0]
+  if(q!=1){
+    (sum(p^q))^(1/(1-q))
+  }else{
+    exp(-sum(p*log(p)))
+  }
+}
+
+#' new_fun computes all six classes of evenness measures.
+#' @param x is an observed species abundance or frequency vector. 
+#' @param q.order is a vector of diversity orders: user must specify a sequence (suggested range is from 0 to 2 in an increment of 0.05).
[…]

### 2021-06-22 R/Lorenz.R

@@ -1,0 +1,123 @@
+#*******************************************************************************
+#********************************************************************************
+#
+#
+## R scipts "Lorenz" for Chao and Ricotta (2019) Ecology paper on evenness. 
+## The R code is for plotting Appendix S4: Figure S1 in Chao and Ricotta's paper.
+# NOTE: The packages "ggplot2" must be installed and loaded before running the scripts. 
+# 
+# This code was modified by JR Junker 
+#*******************************************************************************
+#*******************************************************************************
+
+library(ggplot2)
+
+#====Functions for computing and plotting Lorenz Curve====
+#'lcs_table is used to compute the values of each Lorenz curve
+#' @param ps is a list of observed abundance/frequency vectors corresponding to multiple assemblages. 
+#' @return the values for plotting the Lorenz curve of each assemblage.
+lcs_table = function(ps, resp_var = NULL, sort_var = NULL,...){
+  lc = function(p,j){
+    if(is.vector(p)){
+    p = p[p>0]
+    s = length(p)
+    p = p/sum(p)
+    p = sort(p)
+    out_x = sapply(1:s, function(i){i/s})
+    out_y = sapply(1:s, function(i){sum(p[1:i])})
+    out = data.frame(x = c(0,out_x),y = c(0,out_y),source = names(ps)[j])
+    } else{ p <- data.frame(p)
+    p <- p[resp_var > 0,]
+    s <- nrow(p)
+    resp_string = paste0("relative_",resp_var)
+    # resp_var = as.name(resp_var)
+    p[[resp_string]] <- with(p, resp_var/sum(resp_var)) -> p.rel
+    p.rel = p.rel %>% dplyr::arrange(sort_var)
+    out_x <- sapply(1:s, function(i){i/s})
+    out_y <- sapply(1:s, function(i){sum(p.rel[1:i,resp_var])})
+    out <- data.frame(x = c(0,out_x), y = c(0,out_y), source = names(ps)[j])
+  }};debugonce(lc)
+  curves = lapply(1:length(ps),function(j){lc(ps[[j]],j)})
+  curves = do.call(rbind,curves)
+}
+
+#'lcs_plot is used to plot each curve
+#' @param curves is the output of function lcs_table.
[…]

### 2021-06-22 R/analyze_dominance.R

@@ -1,0 +1,43 @@
+##' .. content for \description{} (no empty lines) ..
+##'
+##' .. content for \details{} ..
+##'
+##' @title
+##' @param nameme1
+analyze_dominance <- function(ann_spp_flux_boots = flux_summaries[["annual_spp_flux_boots"]]) {
+  #'
+  #'
+  ## ++++ Helper functions ++++ ##
+   part_dominance = function(x){
+   
+     o = sort(x, decreasing = TRUE)
+     # m = x[o]
+     p = c()
+     
+     for(i in 1:length(o)){
+       p[i] = 100*o[i]/sum(o[i:length(o)])
+     }
+     return(p)
+   }
+  
+  ## ++++ End Helper functions ++++ ##
+  
+  ann_spp_flux_summary = ann_spp_flux_boots %>%
+    group_by(site, taxon) %>%
+    dplyr::summarise(across(matches('flux'), list(mean = ~mean(.x, na.rm = TRUE),
+                                                  quant2.5 = ~quantile(.x, 0.025, na.rm = TRUE),
+                                                  quant25 = ~quantile(.x, 0.25, na.rm = TRUE),
+                                                  quant50 = ~quantile(.x, 0.50, na.rm = TRUE),
+                                                  quant75 = ~quantile(.x, 0.75, na.rm = TRUE),
+                                                  quant97.5 = ~quantile(.x, 0.975, na.rm = TRUE))))
+  
+  # debugonce(part_dominance)
+  partial_dominance = ann_spp_flux_summary %>%
+    group_by(site) %>% select(contains('mean')) %>%
+    dplyr::arrange(desc(flux_mg_m_y_mean)) %>%
+    dplyr::mutate(rel_flux = flux_mg_m_y_mean/sum(flux_mg_m_y_mean),
+                  spp_rank = dense_rank(rel_flux),
+                  partial_dominance = part_dominance(rel_flux))
+    
+
+}

### 2021-06-22 R/analyze_gini.R

@@ -1,0 +1,35 @@
+##' .. content for \description{} (no empty lines) ..
+##'
+##' .. content for \details{} ..
+##'
+##' @title
+##' @param spp_rankings
+analyze_gini <- function(ann_spp_flux = flux_summaries[["annual_spp_flux_boots"]]) {
+
+  
+  stream_gini_df = ann_spp_flux %>% dplyr::filter(flux_mg_m_y >0) %>%
+    named_group_split(site) %>% rlist::list.subset(names(stream_order_list)) %>%
+    future_map(~.x %>% named_group_split(boot_id) %>% 
+          future_map(~.x %>% select(flux_mg_m_y) %>% unlist %>% gini_even(.)) %>% bind_rows(.id = 'boot_id')) %>%
+    bind_rows(.id = 'site')
+  
+  stream_gini_summary = stream_gini_df %>%
+    group_by(site) %>%
+    dplyr::summarise(across(matches('Gini'), list(mean = ~mean(.x, na.rm = TRUE),
+                                                  quant2.5 = ~quantile(.x, 0.025, na.rm = TRUE),
+                                                  quant25 = ~quantile(.x, 0.25, na.rm = TRUE),
+                                                  quant50 = ~quantile(.x, 0.50, na.rm = TRUE),
+                                                  quant75 = ~quantile(.x, 0.75, na.rm = TRUE),
+                                                  quant97.5 = ~quantile(.x, 0.975, na.rm = TRUE)))) %>%
+    dplyr::mutate(site = factor(site, levels = stream_order))
+  
+  return(list(stream_gini_df = stream_gini_df, stream_gini_summary = stream_gini_summary))
+  # 
+  # spp_ginis = spp_rankings %>%
+  #   map(~.x %>% 
+  #         map(~.x %>% group_by(site_id) %>%
+  #         dplyr::mutate(across(contains('mean'),  ~ .x/sum(.x), .names = "{.col}_relative")) %>%
+  #           dplyr::arrange(across(contains('rank'))) %>%
+  #           dplyr::mutate(across(contains('relative'), ~cumsum(.x), .names = "{.col}_cumulative"))))
+  
+}

### 2021-06-22 R/analyze_hill_diversity.R

@@ -1,0 +1,126 @@
+##' .. content for \description{} (no empty lines) ..
+##'
+##' .. content for \details{} ..
+##'
+##' @title
+##' @param ann_spp_flux_boots
+
+analyze_hill_diversity <- function(ann_spp_flux_summary = flux_summaries[["annual_spp_flux_summary"]]){ #  ann_spp_flux_boots = flux_summaries[["annual_spp_flux_boots"]], ann_spp_flux_summary = flux_summaries[["annual_spp_flux_summary"]]) {
+  
+  ## ++++ Helper functions ++++ ##
+  #'
+  #'
+  #'
+  #'@param x the species abundance/frequency/productivity vector
+  tax_q_profile <- function(x, q, name1){
+    x <- as.data.frame(x)
+    x$q.order <-as.character(q)
+    x1 <- x %>% pivot_longer(-q.order, names_to = 'site', values_to = 'evenness') %>%
+      dplyr::mutate(site = factor(site, levels = names(stream_order_list)))
+    ggplot(x1, aes(q.order, evenness))+
+      geom_line(aes(color = site, group = site), size = 1.1)+
+      theme_tufte(ticks = TRUE)+
+      geom_rangeframe(sides = "lb")+
+      theme(legend.position = c(1,1),
+            legend.justification = c("right", "top"), 
+            legend.title = element_blank(),
+            legend.spacing.y = unit(0.0003,'cm'),
+            legend.key.size = unit(0.4,'cm'),
+            strip.text = element_blank())+
+      scale_x_discrete(breaks=seq(0, 3, 0.5))+
+      scale_colour_manual(values = ocecolors[['temperature']][oce_temp_pos], labels = stream_temp_labels)+
+      # theme(legend.key.width = unit(2,"cm"))+
+      # theme(plot.title = element_text(size=20, face="bold.italic",hjust = 0.5))+
+      ggtitle(name1)+
+      xlab("Diversity order q")
+    #ylim(c(0, 1))
+  }
+  
+  evenness_profile_function = function(x, q.seq, evenness.type = c("E1", "E2", "E3", "E4", "E5", "E6"),...){
+    name1 = evenness.type
+    ind_evenness1 <- apply(x, 2, function(x) new_fun(x = x, q.order = q.seq, evenness.type = evenness.type))
[…]

### 2021-06-22 R/analyze_lorenz_asymmetry.R

@@ -1,0 +1,28 @@
+##' .. content for \description{} (no empty lines) ..
+##'
+##' .. content for \details{} ..
+##'
+##' @title
+##' @param lorenz_analysis
+analyze_lorenz_asymmetry <- function(lorenz_analysis) {
+  # debugonce(Lasym_strict)
+  # ord_vars = list('flux_mg_m_y','flux_mg_m_y_mean','pb_y','bio_mg_m','M_mg_ind')
+  # Lasym_boots = lorenz_analysis %>%
+  #   map2(.,ord_vars, ~.x %>%
+  #         named_group_split(site) %>%
+  #         map(~.x %>% group_by(boot_id) %>%
+  #               dplyr::summarise(Lasym = Lasym_strict(x = .x$flux_mg_m_y, ord_var = .y))))
+  # NULL
+  
+  
+
+}
+
+# debugonce(Lasym_strict)
+# lorenz_analysis[[3]] %>% named_group_split(site) %>%
+#   map(~.x %>% group_by(boot_id) %>%
+#   dplyr::summarise(Lasym = Lasym_strict(x = .$flux_mg_m_y, ord_var = 'pb_y')))
+# 
+# 
+# debugonce(Lasym_strict)
+# Lasym_strict(x$flux_mg_m_y, ord_var = pb_y)

### 2021-06-22 R/import_bioData.R

@@ -1,0 +1,215 @@
+import_bioData <- function(){
+# 2020-05-12 
+# these are throwing errors and not loading due to network timeout. May need to reset/update DNS servers if this continues.
+
+# shallow<<- read_csv(file = "https://www.dropbox.com/s/bw1klp28wx5i7lx/TB2_Compiled_Data.csv?dl=1") %>% as.data.frame() %>%
+#   column_to_rownames('X1')
+# deep<<- read_csv(file = "https://www.dropbox.com/s/581r05guoyj6aoc/Patch%20Mosaic%20Master2.csv?dl=1") %>% as.data.frame() %>%
+#   column_to_rownames('X1')
+# site_list<<-read_csv(file ="https://www.dropbox.com/s/fmahl3dc34ss33x/terrebonne_site_master.csv?dl=1") %>% as.data.frame()
+# TB_2018_core_meta<<-read_csv(file = "./data/metadata/TB_2018_Core-Metadata.csv",
+#                              col_types = cols(.default = "?", Date = col_date(format = "%m/%d/%Y"), Time = "i",
+#                                               `Van Veen Grab` = "i", Core = "i"))
+# TB_2019_core_meta<<- read_csv(file = "./data/metadata/TB_2019_Core-Metadata.csv",
+#                               col_types = cols(.default = "?", Date = col_date(format = "%m/%d/%Y"), Time = "i",
+#                                                `Van Veen Grab` = "i", Core = "i"))
+   # options(gargle_oauth_email = "jjunker@lumcon.edu")
+   gs4_auth(email = "jjunker@lumcon.edu")
+   # gs4_deauth()
+   TB_trawl_meta <- gs4_get("1mUG6oYBGGONBzgXPsvS6XZkNRUIojxtI7BV8WUTh-3I")#sheetID extracted with as_sheets_ID(*sheet URL*)
+   TB_trawl_tabs <- nrow(TB_trawl_meta[['sheets']])
+   TB_trawl_list <- vector('list', TB_trawl_tabs)
+   for(tab in 1:TB_trawl_tabs){
+     TB_trawl_list[[tab]] <- sheets_read(TB_trawl_meta[['spreadsheet_id']], sheet = tab, col_types = "T?d", range = cell_cols("A:C"))
+   }
+   TB_trawl_data <- bind_rows(TB_trawl_list) %>% dplyr::select(Date, Species, Abundance)
+#
[…]

### 2021-06-22 R/load_enviroData.R

@@ -1,0 +1,111 @@
+## source in environmental data ##
+
+load_environmental_data <- function(){
+temp_paths <- list.files(path = "./data/environment/", "Terrebonne.*temp_.*2020.*", full.names = TRUE)
+temp_files <- lapply(temp_paths, read_csv,
+                     col_types = cols('Date/Time' = col_datetime(format = "%m/%d/%Y %H:%M")))
+
+roundUP <<- function(x,to=10){
+  to*(x%/%to + as.logical(x%%to))
+}
+
+tempF_to_C <<- function(F){(5/9)*(F-32)}
+
+TB_temp_df <<- bind_rows(temp_files) %>%
+  dplyr::select(datetime = 'Date/Time', temp_C = 'Water Temp C') %>%
+  dplyr::mutate(Date = as.Date(datetime)) %>%
+  dplyr::select(-datetime) %>%
+  group_by(Date) %>%
+  summarise_all(mean, na.rm = TRUE)
+
+# do_paths <- list.files(path = "./data/", "*DO_*", full.names = TRUE)
+# do_files <- lapply(do_paths, read_csv, skip = 1,
+#                    col_types = cols(TS = col_datetime(format = "%m/%d/%Y %H:%M")))
+# 
+# TB_do_df <<- bind_rows(do_files) %>%
+#   rename(datetime = 'TS', do_mg_L = 'mg L') %>%
+#   dplyr::mutate(yday = yday(datetime))
+# 
+# hydro_paths <- list.files(path = "./data/", "hydro{1}.*.csv", full.names= TRUE)
+# hydro_files <- lapply(hydro_paths, read_csv, col_type = cols(ArrayID = col_skip(), Year = col_skip(), JDay= col_skip(),
+#                                                              X4 = col_skip(), X5 = col_skip(), X6 = col_skip(), Time = col_skip(), X8 = col_skip(), `Date/Time` = col_character(),
+#                                                              DO = col_skip(), Value4 = col_double(), Depth = col_skip(), `Depth feet` = col_skip()))
+# TB_hydro_df <<- bind_rows(hydro_files) %>%
+#   rename(datetime = 'Date/Time', temp_C = 'Temp', temp_F = 'Water Temp F', spCon_uS_cm = 'Value4', sal_psu = 'Sal') %>%
[…]

### 2021-06-22 datascript.R

@@ -1,290 +1,10 @@
-source("install-packages.R")
-# data manipulation
+source("packages.R")
+# call different data import scripts depending on changes to files.
 
-data_import <<- function(){
-  temp_paths <- list.files(path = "./data/environment/", "Terrebonne.*temp_.*2020.*", full.names = TRUE)
-  temp_files <- lapply(temp_paths, read_csv,
-                       col_types = cols('Date/Time' = col_datetime(format = "%m/%d/%Y %H:%M")))
-  
-  roundUP <<- function(x,to=10){
-    to*(x%/%to + as.logical(x%%to))
-  }
-  
-  tempF_to_C <<- function(F){(5/9)*(F-32)}
-  
-  TB_temp_df <<- bind_rows(temp_files) %>%
-    select(datetime = 'Date/Time', temp_C = 'Water Temp C') %>%
-    mutate(Date = as.Date(datetime)) %>%
-    select(-datetime) %>%
-    group_by(Date) %>%
-    summarise_all(mean, na.rm = TRUE)
-  
-  # do_paths <- list.files(path = "./data/", "*DO_*", full.names = TRUE)
-  # do_files <- lapply(do_paths, read_csv, skip = 1,
-  #                    col_types = cols(TS = col_datetime(format = "%m/%d/%Y %H:%M")))
-  # 
-  # TB_do_df <<- bind_rows(do_files) %>%
-  #   rename(datetime = 'TS', do_mg_L = 'mg L') %>%
-  #   mutate(yday = yday(datetime))
-  # 
-  # hydro_paths <- list.files(path = "./data/", "hydro{1}.*.csv", full.names= TRUE)
-  # hydro_files <- lapply(hydro_paths, read_csv, col_type = cols(ArrayID = col_skip(), Year = col_skip(), JDay= col_skip(),
-  #                                                              X4 = col_skip(), X5 = col_skip(), X6 = col_skip(), Time = col_skip(), X8 = col_skip(), `Date/Time` = col_character(),
-  #                                                              DO = col_skip(), Value4 = col_double(), Depth = col_skip(), `Depth feet` = col_skip()))
-  # TB_hydro_df <<- bind_rows(hydro_files) %>%
-  #   rename(datetime = 'Date/Time', temp_C = 'Temp', temp_F = 'Water Temp F', spCon_uS_cm = 'Value4', sal_psu = 'Sal') %>%
[…]

### 2021-06-22 install-packages.R

@@ -1,36 +1,0 @@
-# Install pacman if it isn't already installed
-if ("pacman" %in% rownames(installed.packages()) == FALSE) install.packages("pacman")
-
-# Install packages required for analysis
-# Add any packages required for your data cleaning and manipulation to the
-# `p_load` function call below
-# Do not remove the packages already listed here
-# they are important for running the livedat repository
-# OG package list: pacman::p_load(git2r, httr, semver, testthat, yaml)
-
-pacman::p_load(git2r, httr, semver, testthat, yaml, EML, data.table, 
-               RCurl, plyr, tidyverse, furrr, googlesheets4,
-               tictoc, chron, lubridate, httr, TTR, grid,
-               gridExtra, ggridges, iNEXT, vegan, rlist, pipeR,
-               viridis, broom, bbmle, ggthemes, ggeffects,
-               rfishbase, auk, betapart, plot3D, ncdf4)
-
-pacman::p_load_gh(c("jimjunker1/junkR"))#, "ropensci/rfishbase"))
-
-# theme_mod <<- theme_bw() %+replace% theme(panel.grid = element_blank())
-theme_set(theme_mod)
-find_hull <<- function(df) df[chull(df$NMDS1, df$NMDS2),]
-
-'%ni%' <<- Negate('%in%')
-
-# yday_summary <<- function(data,...){
-#   if("yday" %in% colnames(data)){
-#     data_summ = data %>%
-#       group_by(yday) %>%
-#       summarise_if(is.numeric, list(~na.rm_mean(.,na.rm = TRUE), ~max(.,na.rm = TRUE), ~min(., na.rm = TRUE))) %>%
-#       ungroup()
-#   } ifelse{
-#     
-#   }
-#     
-# }

### 2021-06-22 packages.R

@@ -1,0 +1,36 @@
+# Install pacman if it isn't already installed
+if ("pacman" %in% rownames(installed.packages()) == FALSE) install.packages("pacman")
+
+# Install packages required for analysis
+# Add any packages required for your data cleaning and manipulation to the
+# `p_load` function call below
+# Do not remove the packages already listed here
+# they are important for running the livedat repository
+# OG package list: pacman::p_load(git2r, httr, semver, testthat, yaml)
+
+pacman::p_load(git2r, httr, semver, testthat, yaml, EML, data.table, 
+               RCurl, plyr, tidyverse, furrr, googlesheets4,
+               tictoc, chron, lubridate, httr, TTR, grid,
+               gridExtra, ggridges, iNEXT, vegan, rlist, pipeR,
+               viridis, broom, bbmle, ggthemes, ggeffects, bsts,
+               rfishbase, auk, betapart, plot3D, ncdf4, forecast)
+
+devtools::install_github(c("jimjunker1/junkR"))#, "ropensci/rfishbase"))
+
+theme_mod <<- function(){theme_bw() %+replace% theme(panel.grid = element_blank())}
+theme_set(theme_mod());rm(theme_mod)
+find_hull <<- function(df) df[chull(df$NMDS1, df$NMDS2),]
+
+'%ni%' <<- Negate('%in%')
+
+# yday_summary <<- function(data,...){
+#   if("yday" %in% colnames(data)){
+#     data_summ = data %>%
+#       group_by(yday) %>%
+#       summarise_if(is.numeric, list(~na.rm_mean(.,na.rm = TRUE), ~max(.,na.rm = TRUE), ~min(., na.rm = TRUE))) %>%
+#       ungroup()
+#   } ifelse{
+#     
+#   }
+#     
+# }

### 2021-07-20 Analysis/active/trawl_analysis/trawl_LDATS.R
updating workflow and moving manuscript forward.

@@ -1,4 +1,4 @@
-source("datascript.R")
+source(here::here("datascript.R"))
 
 devtools::install_github("weecology/LDATS")
 library(LDATS)

### 2021-07-20 Analysis/active/trawl_analysis/trawl_ordination.R

@@ -1,7 +1,7 @@
 ## terrebonne bay trawl working analysis
 ## works with TB_trawl_data
 # source("install-packages.R")#installs all necessary packages
-source("datascript.R")#imports data with some minor cleanup
+source(here::here("datascript.R"))#imports data with some minor cleanup
 
 
 ## summarise the monthly sampling effort

### 2021-07-20 Analysis/active/trawl_analysis/trawl_specaccum.R

@@ -3,7 +3,7 @@
 
 ##create taxa by site matrix
 TB_trawl_commonsite <- TB_trawl_data %>%
-  select(year, month, date_id, Common_name) %>%
+  dplyr::select(year, month, date_id, Common_name) %>%
   group_by(date_id, Common_name) %>%
   distinct() %>% 
   mutate(pres = 1) %>%
@@ -99,5 +99,7 @@ beta_df <- bind_rows(beta_lists) %>% mutate(Date = as.Date(paste0(beta_dates,"-0
   pivot_longer(-Date, names_to = "partition", values_to = "value")
                        
 source("./figures/diversity_time_plots.R")
+
+
 
   

### 2021-07-20 R/analyze_rarefaction.R

@@ -1,0 +1,26 @@
+source(here::here('datascript.R'))
+
+##create taxa by site matrix
+TB_trawl_taxasite <- TB_trawl_data %>%
+  dplyr::select(Date, Common_name, Abundance) %>%
+  group_by(Date, Common_name) %>%
+  summarise(Abundance = sum(Abundance)) %>%
+  na.omit %>%
+  pivot_wider(names_from = Common_name, values_from = Abundance, values_fill = list(Abundance = 0)) %>%
+  ungroup() %>%
+  dplyr::mutate(julian_date = round(julian(Date, origin = "2007-01-05")),
+                biweekly = ceiling(julian_date/30),
+                month = month(Date),
+                year = year(Date)) %>%
+  dplyr::select(julian_date, Date,year, month, biweekly, everything())
+
+
+
+# trawl_rarefaction analysis
+
+trawl_mob_in = mobr::make_mob_in(TB_trawl_taxasite %>% dplyr::select(-julian_date:-biweekly),
+                           TB_trawl_taxasite %>% dplyr::select(julian_date:biweekly),
+                           coord_names = "")
+trawl_mod_stats = mobr::get_mob_stats(trawl_mob_in)
+
+mobr::plot_rarefaction(trawl_mob_in,'year', method = "IBR", lwd = 3, leg_loc = 'none' )

### 2021-07-20 R/clean_trawl_spp.R

@@ -1,0 +1,210 @@
+#' @title diversity_clean_spp
+#' @description This function identifies species names that are not found within
+#'  the RESTORE saltmarsh species list. For missing species names, the function attempts
+#'  to find correct names through four steps: fuzzy matching for minor transcription errors,
+#'  fuzzy matching by common name, matching by known synonyms, and finally conversion from common name
+#'  to scientific name.
+#'  @param x data.frame or coercible to data.frame; ts the unique species names from data frame
+#'  @param spp_col character; string of column name where species names are located. Default is 'species'
+#'  @param common_col character; string of column name where common names are located. This is only
+#'   necessary if species names are not found during initial fuzzy matching from species list. Default is 'common_name'
+#'  @param collapse logical; if FALSE (the default), returns a tibble with output returned from all matching steps in
+#'   individual columns. If TRUE, collapses the matched names into named vector and recodes spp_col with a warning.
+#'  @param check logical; If FALSE (the default) the function will return a list or manipulated object depending on 'collapse'
+#'  if TRUE, returns a logical for if all spp_col names are found in taxonomy_list
+#'  @param taxonomy_list string or object of taxonomy list from which to check species names.
+#'  @param ... other arguments to pass to sub functions.
+#'  @returns list of matched names, manipulated dataframe (if collapse == TRUE), or logical (TRUE == all species found)
+
+clean_trawl_spp <- function(x, spp_col = "species", common_col = "common_name", collapse = FALSE, 
+                          check = FALSE, taxonomy_list = "./raw-data/taxonomy_valid_common.rds",...) {
+  
+  ## Load required functions for matching
+  "%ni%" <- Negate("%in%")
+  require(fuzzySim)
+  # require(taxize)
+  require(tibble)
+  
+  ## Parameter checks
+  if (spp_col %ni% colnames(x)) stop("Error: spp_col is not found within the data.")
+  
+  # call in the taxonomy dataframe to reference good spp names
+  if(class(taxonomy_list) %ni% c("character","tbl_df","tbl","data.frame", "matrix")){
[…]

### 2021-07-20 R/import_bioData.R

@@ -1,4 +1,5 @@
 import_bioData <- function(){
+   source(here::here("R/clean_trawl_spp.R"))
 # 2020-05-12 
 # these are throwing errors and not loading due to network timeout. May need to reset/update DNS servers if this continues.
 
@@ -208,6 +209,11 @@ import_bioData <- function(){
             date_id = paste0(as.character(year),"-",as.character(month)))
 
 #### End scientific and common name fixes #### 
+#### Confirm Species and Common names from taxonomic databases
+   debugonce(clean_trawl_spp)
+   new_spp =  TB_trawl_data %>% clean_trawl_spp(spp_col = "species_mod", common_col = "Common_name",
+                                     taxonomy_list = here::here("data/taxonomy_valid_common.rds")) %>% unique
+   
 #### End Data entry fixes ####
  saveRDS(TB_trawl_data, file = "./data/TB_trawl_data.rds")
  biology_sysDate = Sys.Date()

### 2021-07-20 R/load_bioData.R

@@ -1,6 +1,6 @@
 # load data
 
 ## trawl data
-load_bioData <- function(){TB_trawl_data <<- readRDS(file = "./data/TB_trawl_data.rds")}
-ifelse(file.exists("./data/TB_trawl_data.rds"), suppressWarnings(load_bioData()), source("./R/import_bioData.R"));rm(load_bioData)
+load_bioData <- function(){TB_trawl_data <<- readRDS(file = here::here("data/TB_trawl_data.rds"))}
+ifelse(file.exists(here::here("data/TB_trawl_data.rds")), suppressWarnings(load_bioData()), source(here::here("R/import_bioData.R")));rm(load_bioData)
 # TB_trawl_data <<- readRDS(file = "./data/TB_trawl_data.rds")

### 2021-07-20 datascript.R

@@ -1,10 +1,10 @@
-source("packages.R")
+source(here::here("packages.R"))
 # call different data import scripts depending on changes to files.
 
 # import biology data if it has been greater than 1 month since download
-load("./data/biology_sysDate.rda")
-ifelse((Sys.Date()-biology_sysDate) >= 30, source("./R/import_bioData.R"),source("./R/load_bioData.R"))
+load(here::here("data/biology_sysDate.rda"))
+ifelse((Sys.Date()-biology_sysDate) >= 30, source(here::here("R/import_bioData.R")),source(here::here("R/load_bioData.R")))
 rm(biology_sysDate)
 
 # import environmental data
-source("./R/load_enviroData.R")
+source(here::here("R/load_enviroData.R"))

### 2021-07-20 packages.R

@@ -1,3 +1,4 @@
+here::i_am("packages.R")
 # Install pacman if it isn't already installed
 if ("pacman" %in% rownames(installed.packages()) == FALSE) install.packages("pacman")
 
@@ -8,14 +9,17 @@ if ("pacman" %in% rownames(installed.packages()) == FALSE) install.packages("pac
 # they are important for running the livedat repository
 # OG package list: pacman::p_load(git2r, httr, semver, testthat, yaml)
 
-pacman::p_load(git2r, httr, semver, testthat, yaml, EML, data.table, 
+pacman::p_load(git2r, httr, semver, testthat, yaml, here, EML, data.table, 
                RCurl, plyr, tidyverse, furrr, googlesheets4,
                tictoc, chron, lubridate, httr, TTR, grid,
                gridExtra, ggridges, iNEXT, vegan, rlist, pipeR,
                viridis, broom, bbmle, ggthemes, ggeffects, bsts,
-               rfishbase, auk, betapart, plot3D, ncdf4, forecast)
+               rfishbase, auk, betapart, plot3D, ncdf4, forecast,
+               taxize)
 
 devtools::install_github(c("jimjunker1/junkR"))#, "ropensci/rfishbase"))
+devtools::install_github('MoBiodiv/mobr')
+
 
 theme_mod <<- function(){theme_bw() %+replace% theme(panel.grid = element_blank())}
 theme_set(theme_mod());rm(theme_mod)

### 2021-07-28 analyses/trawl/trawl_README.Rmd
large restructure of repository. Manuscript started.

---
title: "Trawl-README"
author: "JRJ"
date: "`r format(Sys.time(), '%d %B, %Y')`"
knit: (function(inputFile, encoding) { 
      out_dir <- "docs";
      rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_file=file.path(here::here(), out_dir, 'trawl_README.html')) })
output: 
  html_document:
      keep_md: true
      toc: true
      toc_float: true
      toc_depth: 3
      numbered_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
here::i_am("analyses/trawl/trawl_README.Rmd")

```

This document outlines the workflow for the initial trawl analysis. The first manuscript's goals is to characterize and quantify the change in trawl communities in Terrebonne Bay from 2007 onward. Analysis sequence is:

1. "packages.R"
2. "datascript.R" (sourcing this document will call the 'packages.R' script)
3. "trawl_rarefaction.R"
4. "trawl_specaccum.R"

### 2021-07-28 docs/ms/ms.RMD
updating workflow and moving manuscript forward.
large restructure of repository. Manuscript started.

@@
 ---
+```{r Rmarkdown setup, include = FALSE, echo=F, warning=FALSE, message=FALSE}
 
+source(here::here("datascript.R"))
+
+TB_trawl_data = TB_trawl_data %>%
+   dplyr::filter(year %ni% c("2020","2021"))
+
+```
 <!--- this is a note in Rmarkdown --->
@@
 This research will build towards a more coherent theory of biodiversity change through time [@shoemaker2020].
-<!--- Connect traits to the 'speed' of ecosystem energy fluxes--->
+
 Here, we quantified over a decade of change in a shallow estuarine community. We
@@
 
-Trawl sampling was conducted as part of the Louisiana Universities Marine Consortium's educational outreach program [https://www.lumcon.edu/education-and-outreach]<https://lumcon.edu/education-and-outreach/>.
-Individual trawls were conducted using *trawl apparatus description...*
+Trawl sampling was conducted as part of the Louisiana Universities Marine Consortium's (LUMCON) educational outreach program (https://www.lumcon.edu/education-and-outreach).
+Individual trawls were conducted using *trawl apparatus description...* and
 
-## Community change
+## Community characterization
+
+Species names were checked for typos and confirmed using the *gni_parse* function from the *taxize* package [@chamberlain2020] and further standardized to consistent taxonomic resolution for entire data series (Supplemental materials).
 
@@
 
+```{r mobr_stats, echo = FALSE, warning=FALSE, message=FALSE, results='hide'}
+total_richness = length(unique(TB_trawl_data$Common_name))
+
+TB_trawl_sampling = TB_trawl_data %>%
+  # exclude 2020 & 2021
+  dplyr::filter(year %ni% c("2020","2021")) %>%
+   dplyr::select(Date, year, Common_name, Abundance) %>%
+   group_by(year) %>%
+   dplyr::summarise(trawl_days = length(unique(Date)),
+                    S = length(unique(Common_name)),
+                    individuals = sum(Abundance, na.rm = TRUE))
+
+TB_trawl_taxasite <- TB_trawl_data %>%
+  # exclude 2020 & 2021
+  dplyr::filter(year %ni% c("2020","2021")) %>%
+  dplyr::select(Date, Common_name, Abundance) %>%
+  group_by(Date, Common_name) %>%
+  summarise(Abundance = sum(Abundance)) %>%
+  na.omit %>% group_by(Date) %>%
+  # remove trawls with less than 10 individuals 
+  dplyr::filter(sum(Abundance) >=10) %>%
+  group_by(Date, Common_name) %>%
+  pivot_wider(names_from = Common_name, values_from = Abundance, values_fill = list(Abundance = 0)) %>%
+  ungroup() %>%
+  dplyr::mutate(julian_date = julian(Date, origin = as.Date("2007-01-05")),
+                biweekly = ceiling(julian_date/30),
+                month = month(Date),
+                year = year(Date)) %>%
+  dplyr::select(julian_date, Date, year, month, biweekly, everything())
+
+n_year = 50
+
+# trawl_rarefaction analysis
+
+trawl_mob_in = mobr::make_mob_in(comm = TB_trawl_taxasite %>% dplyr::select(-julian_date:-biweekly),
+                           plot_attr = TB_trawl_taxasite %>% dplyr::select(julian_date:biweekly),
+                           coord_names = "biweekly",
+                           latlong = FALSE)
+
+trawl_mob_stats = mobr::get_mob_stats(trawl_mob_in, group_var = 'year', index = c("N", "S", "S_asymp", "S_n", "S_PIE", "PIE", "pct_rare"), effort_samples = n_year, extrapolate = TRUE, boot_groups = TRUE, n_perm = 99)
+
+group_stats = trawl_mob_stats$groups_stats %>% data.frame
+
+S_n = max(group_stats$effort, na.rm = TRUE)
+
+#
+
+```
+
+Over the sampling period from `r min(TB_trawl_sampling$year, na.rm = TRUE)` to `r max(TB_trawl_sampling$year, na.rm = TRUE)`, `r length(unique(TB_trawl_data$Date))` trawls-days were conducted yielding `r format(signif(sum(TB_trawl_data$Abundance, na.rm = TRUE),3), scientific = TRUE)` individuals.
+Among years, total effort generally increased, both in number of trawl-days and individuals counted, from a minimum effort of (`r TB_trawl_sampling %>% slice_min(trawl_days) %>% dplyr::select(year) %>% unlist`) to `r max(TB_trawl_sampling$trawl_days)` (`r TB_trawl_sampling %>% slice_max(trawl_days) %>% dplyr::select(year) %>% unlist`) days and from `r min(TB_trawl_sampling$individuals, na.rm = TRUE)` (`r TB_trawl_sampling %>% slice_min(individuals) %>% dplyr::select(year) %>% unlist`) to `r format(signif(max(TB_trawl_sampling$individuals, na.rm = TRUE),3), scientific = TRUE)` (`r TB_trawl_sampling %>% slice_max(individuals) %>% dplyr::select(year) %>% unlist`) individuals.
+In total, `r length(unique(TB_trawl_data$Common_name))` unique species were identified and new species were consistently observed throughout the sampling period (Figure 1).
+Within a calendar year, we estimated the asymptotic species richness (*S~asymp~*) which was relatively stable for the first five years (2007 -- 2012), reaching a minimum value of `r group_stats %>% dplyr::filter(index == "S_asymp") %>% slice_min(median) %>% dplyr::select(median) %>% unlist %>% as.numeric %>% round(0)` (`r group_stats %>% dplyr::filter(index == "S_asymp") %>% slice_min(median) %>% dplyr::select(lower) %>% unlist %>% as.numeric %>% round(0)` -- `r group_stats %>% dplyr::filter(index == "S_asymp") %>% slice_min(median) %>% dplyr::select(upper) %>% unlist %>% as.numeric %>% round(0)`) in `r group_stats %>% dplyr::filter(index == "S_asymp") %>% slice_min(median) %>% dplyr::select(group)`.
+Estimated *S~asymp~* increased in 2013 to a series maximum of `r group_stats %>% dplyr::filter(index == "S_asymp") %>% slice_max(median) %>% dplyr::select(median) %>% unlist %>% as.numeric %>% round(0)` (`r group_stats %>% dplyr::filter(index == "S_asymp") %>% slice_max(median) %>% dplyr::select(lower) %>% unlist %>% as.numeric %>% round(0)` -- `r group_stats %>% dplyr::filter(index == "S_asymp") %>% slice_max(median) %>% dplyr::select(upper) %>% unlist %>% as.numeric %>% round(0)`) in `r group_stats %>% data.frame %>% dplyr::filter(index == "S_asymp") %>% slice_max(median) %>% dplyr::select(group)`.
+However, given the large differences in effort among years, variability in *S~asymp~* may be partly attributable to sampling effects among years.
+Therefore, we also calculated rarefied richness at `r S_n` individuals, *S~`r S_n`~*,  for each year.
+Here, effort-controlled species richness, *S~`r S_n`~*, diverged qualitatively from *S~asymp~* and was generally constant, ranging from `r group_stats %>% dplyr::filter(effort > 100) %>% slice_min(median) %>% dplyr::select(median) %>% round(1)` (`r group_stats %>% dplyr::filter(effort > 100) %>% slice_min(median) %>% dplyr::select(lower) %>% round(1)` -- `r group_stats %>% dplyr::filter(effort > 100) %>% slice_min(median) %>% dplyr::select(upper) %>% round(1)`) to `r group_stats %>% dplyr::filter(effort > 100) %>% slice_max(median) %>% dplyr::select(median) %>% round(1)` (`r group_stats %>% dplyr::filter(effort > 100) %>% slice_max(median) %>% dplyr::select(lower) %>% round(1)` -- `r group_stats %>% dplyr::filter(effort > 100) %>% slice_max(median) %>% dplyr::select(upper) %>% round(1)`) (Figure 1).
+
+```{r figure 1, echo = FALSE, warning = FALSE, message=FALSE, fig.align='center', fig.cap="Figure 1.
+Multiple measures of species richness within the trawl community between the years 2007 to 2019 show continual accumulation of species (purple points and line) through the timeseries.
+The estimated asymptotic species richness over a calendar year (Sasymp; median values and 95% percentile interval represented by yellow points and area), suggests increasing numbers of species within the community over time.
+However, rarefied species richness controlled to 900 individuals (S900; median values and 95% percentil interval represented by green line and area) suggests the perceived increase in Sasymp may represent an effect of increased sampling effort"}
+
+TB_trawl_data %>%
+  # exclude 2020 & 2021
+  dplyr::filter(year %ni% c("2020","2021")) %>%
+  dplyr::filter(!duplicated(Common_name, nmax = (total_richness) )) %>%
+  dplyr::mutate(Date = as.Date(Date)) %>%
+  arrange(Date) %>%
+  dplyr::mutate(richness = 1:n())-> TB_time_accum
+
+TB_annual_accum <- TB_trawl_data %>%
+  # exclude 2020 & 2021
+  dplyr::filter(year %ni% c("2020","2021")) %>%
+  mutate(pres = 1) %>% group_by(year) %>%
+  filter(!duplicated(Common_name)) %>%
+  summarise(richness = sum(pres)) %>%
+  mutate(Date = as.Date(paste(as.character(year),"01","01", sep = "-"), format = "%Y-%m-%d", origin = "2000-01-01"))
+
+# partition beta diversity into nestedness and turnover #
+# uses `betapart` package #
+TB_time_df <- TB_time_accum %>%
+  dplyr::select(Date, year, richness) %>%
+  mutate(data_type = 'continuous',
+         r_lower = NA_real_,
+         r_upper = NA_real_) %>%
+  bind_rows(TB_annual_accum %>% 
+              mutate(data_type = "ann_raw",
+                     r_lower = NA_real_,
+                     r_upper = NA_real_)) %>%
+  bind_rows(group_stats %>% 
+              dplyr::filter(effort > 100) %>%
+              dplyr::select(year ='group', richness = 'median', r_lower = 'lower', r_upper = 'upper') %>%
+              dplyr::mutate(year = as.numeric(as.character(year)),
+                            Date = as.Date(paste(year,"01","01", sep = "-"), format = "%Y-%m-%d"),
+                            data_type = "rarefied")) %>%
+  bind_rows(group_stats %>% 
+              dplyr::filter(index == 'S_asymp') %>%
+              dplyr::select(year ='group', richness = 'median', r_lower = 'lower', r_upper = 'upper') %>%
+              dplyr::mutate(year = as.numeric(as.character(year)),
+                            Date = as.Date(paste(year,"01","01", sep = "-"), format = "%Y-%m-%d"),
+                            data_type = "ann_asymp")) %>%
+  dplyr::mutate(data_type = factor(data_type, levels = c("continuous", "rarefied", "ann_raw", "ann_asymp"))) %>%
+  dplyr::filter(data_type != "ann_raw")
+
+rich_time <-
+  ggplot(TB_time_df, aes(x = Date, y = richness, group = data_type)) +
+  geom_ribbon(data = TB_time_df %>%
+                dplyr::filter(data_type == "ann_asymp"),
+              aes(x = Date, ymin = r_lower, ymax= r_upper),
+              color = viridis(n = 3, alpha = c(1,1,1), option = 'viridis')[3],
+              fill = viridis(n = 3, alpha = c(1,1,0.1), option = 'viridis')[3],
+              inherit.aes = FALSE)+
+  geom_ribbon(data = TB_time_df %>%
+                dplyr::filter(data_type == "rarefied"),
+              aes(x = Date, ymin = r_lower, ymax= r_upper),
+              color = viridis(n = 3, alpha = c(1,1,1), option = 'viridis')[2],
+              fill = viridis(n = 3, alpha = c(1,0.2,1), option = 'viridis')[2],
+              inherit.aes = FALSE)+
+  geom_segment(data = TB_time_df %>% 
+                 dplyr::filter(data_type %ni% 'continuous') %>%
+                 pivot_wider(Date, names_from = data_type, values_from = richness),
+               aes(x = Date, xend = Date, y = ann_asymp, yend = rarefied ), 
+               color = viridis(n = 3, alpha = c(1,1,1), option = 'viridis')[3],
+               inherit.aes = F) +
+  geom_point(data = TB_time_df, aes(colour = data_type),size = 1.5) +
+  geom_line(data = TB_time_df %>% dplyr::filter(!grepl('ann_asymp', data_type)), aes(colour = data_type),size = 1.2) +
+  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +
+  scale_y_continuous(name = "Species Richness")+
+  scale_colour_manual(labels = c("continuous", expression(italic("S"[900])),expression(italic("S"["asymp"]))), values = viridis(n = 3, alpha = c(1,1,1), option = 'viridis')) +
+  # scale_alpha_manual(values = c(1,1,0.3))+
+  theme(legend.position = c(0, 1), legend.justification = c(0, 1), legend.background = element_rect(fill = "transparent", colour = NA),
+        legend.title = element_blank(), legend.text.align = 0,
+        # axis.title.x = element_blank(), axis.text.x = element_blank(),
+        legend.spacing.y = unit(-0.1, 'cm'))
+
+rich_time
+
+```
+
+```{r figure 2, echo=FALSE, warning=FALSE, message=FALSE, fig.align='center'}
+group_stats %>%
+  dplyr::filter(index == "S_PIE") %>%
+  ggplot()+
+  geom_point(aes(x = Date, y = median))
+```
+
 # Discussion
+
+# Acknowledgements
 

### 2021-07-28 trawl_summary.Rmd
large restructure of repository. Manuscript started.

--- 2020-08-10 text/trawl_summary.Rmd
@@
 knit: (function(inputFile, encoding) { 
-      out_dir <- '../docs';
+      out_dir <- './docs';
       rmarkdown::render(inputFile,
@@
 
-TB_trawl_data <- readRDS("../data/TB_trawl_data.rds")
+TB_trawl_data <- readRDS(here::here("data/TB_trawl_data.rds"))
 
@@
 
-```{r import environmental data, include = FALSE}
-
-  temp_paths <- list.files(path = "../data/", "*temp_*", full.names = TRUE)
-  temp_files <- lapply(temp_paths, read_csv, skip = 1,
-                       col_types = cols(TS = col_datetime(format = "%m/%d/%Y %H:%M")))
-
-  roundUP <- function(x,to=10){
-    to*(x%/%to + as.logical(x%%to))
-  }
-
-  tempF_to_C <- function(F){(5/9)*(F-32)}
-
-  temp_df <- bind_rows(temp_files) %>%
-    rename(datetime = 'TS', temp_F = 'F') %>%
-    mutate(yday = yday(datetime))
-
-  do_paths <- list.files(path = "../data/", "*DO_*", full.names = TRUE)
-  do_files <- lapply(do_paths, read_csv, skip = 1,
-                     col_types = cols(TS = col_datetime(format = "%m/%d/%Y %H:%M")))
-
-  do_df <- bind_rows(do_files) %>%
-    rename(datetime = 'TS', do_mg_L = 'mg L') %>%
-    mutate(yday = yday(datetime))
-
-  hydro_paths <- list.files(path = "../data/", "hydro{1}.*.csv", full.names= TRUE)
-  hydro_files <- lapply(hydro_paths, read_csv, col_type = cols(ArrayID = col_skip(), Year = col_skip(), JDay= col_skip(),
-                                                               X4 = col_skip(), X5 = col_skip(), X6 = col_skip(), Time = col_skip(), X8 = col_skip(), `Date/Time` = col_character(),
-                                                               DO = col_skip(), Value4 = col_double(), Depth = col_skip(), `Depth feet` = col_skip()))
-  hydro_df <- bind_rows(hydro_files) %>%
-    rename(datetime = 'Date/Time', temp_C = 'Temp', temp_F = 'Water Temp F', spCon_uS_cm = 'Value4', sal_psu = 'Sal') %>%
-    mutate(datetime = parse_date_time(datetime, orders = c("%m/%d/%Y %H:%M", "%m/%d/%y %H:%M")),
-           yday = yday(datetime))
-env_long <- hydro_df %>% select(-yday, -temp_F) %>% bind_rows(temp_df %>% mutate(temp_C = tempF_to_C(temp_F)) %>% select(-yday, -temp_F)) %>%
-  full_join(do_df %>% select(-yday)) %>%
-  # full_join(temp_df %>% mutate(temp_C = tempF_to_C(temp_F))%>% select(-yday, - temp_F), all = TRUE) %>%
-  pivot_longer(cols = temp_C:do_mg_L, names_to = "env_var", values_to = "value")
-
-```
-
-These data vary in coverage and are being updated:
-
-`r knitr::include_graphics("../figures/env_facet_plot.png")`
+<!-- # These data vary in coverage and are being updated: -->
+<!-- #  -->
+<!-- # `r knitr::include_graphics("./figures/env_facet_plot.png")` -->
 
@@
   geom_ribbon(aes(x = trawls, ymin = (richness - 1.96*richness_sd), ymax = (richness + 1.96*richness_sd)), colour = "red", fill = "red", alpha = 0.5) +
-  scale_y_continuous(name = expression(Sigma~"species"), breaks = seq(0,roundUP(max(spp_mod.df$richness), to = 10), by = 10), labels = seq(0,roundUP(max(spp_mod.df$richness), to = 10), by = 10)) +
-  scale_x_continuous(name = "Trawls", breaks = seq(0,roundUP(max(spp_mod.df$trawls), to = 10), by = 20)) +
+  scale_y_continuous(name = expression(Sigma~"species"), breaks = seq(0,plyr::round_any(max(spp_mod.df$richness), accuracy = 10, f = ceiling), by = 10), labels = seq(0,plyr::round_any(max(spp_mod.df$richness),10, ceiling), by = 10)) +
+  scale_x_continuous(name = "Trawls", breaks = seq(0,plyr::round_any(max(spp_mod.df$trawls), 10, ceiling), by = 20)) +
   theme_minimal()
@@
   geom_path(size = 1.5) +# geom_ribbon(aes(x = sites, ymin = (richness - 1.96*sd), ymax = (richness + 1.96*sd), fill = year), alpha = 0.2) +
-  scale_y_continuous(name = expression(Sigma~"species"),breaks = seq(0, roundUP(max(TB_trawl_taxasite_yr$richness), to = 10), by = 10), labels = seq(0, roundUP(max(TB_trawl_taxasite_yr$richness), to = 10), by = 10)) +
-  scale_x_continuous(name = "Trawls", breaks = seq(0, roundUP(max(TB_trawl_taxasite_yr$sites), to = 10), by = 5)) +
+  scale_y_continuous(name = expression(Sigma~"species"),breaks = seq(0, plyr::round_any(max(TB_trawl_taxasite_yr$richness), 10, ceiling), by = 10), labels = seq(0, plyr::round_any(max(TB_trawl_taxasite_yr$richness), 10, f = ceiling), by = 10)) +
+  scale_x_continuous(name = "Trawls", breaks = seq(0, plyr::round_any(max(TB_trawl_taxasite_yr$sites), 10, f = ceiling), by = 5)) +
   scale_colour_viridis(discrete = TRUE) + 
@@
 #create time-accumulation df from trawl data
+total_richness = length(unique(TB_trawl_data$Common_name))
 TB_trawl_data %>%
-  filter(!duplicated(Common_name)) %>%
-  mutate(richness = 1:n(), 
-         Date = as.Date(Date),
-         richness = sort(richness))-> TB_time_accum
+  dplyr::filter(!duplicated(Common_name, nmax = total_richness )) %>%
+  dplyr::mutate(Date = as.Date(Date)) %>%
+  arrange(Date) %>%
+  dplyr::mutate(richness = 1:n())-> TB_time_accum
 

### 2021-07-28 R/analyze_rarefaction.R

@@ -1,26 +1,0 @@
-source(here::here('datascript.R'))
-
-##create taxa by site matrix
-TB_trawl_taxasite <- TB_trawl_data %>%
-  dplyr::select(Date, Common_name, Abundance) %>%
-  group_by(Date, Common_name) %>%
-  summarise(Abundance = sum(Abundance)) %>%
-  na.omit %>%
-  pivot_wider(names_from = Common_name, values_from = Abundance, values_fill = list(Abundance = 0)) %>%
-  ungroup() %>%
-  dplyr::mutate(julian_date = round(julian(Date, origin = "2007-01-05")),
-                biweekly = ceiling(julian_date/30),
-                month = month(Date),
-                year = year(Date)) %>%
-  dplyr::select(julian_date, Date,year, month, biweekly, everything())
-
-
-
-# trawl_rarefaction analysis
-
-trawl_mob_in = mobr::make_mob_in(TB_trawl_taxasite %>% dplyr::select(-julian_date:-biweekly),
-                           TB_trawl_taxasite %>% dplyr::select(julian_date:biweekly),
-                           coord_names = "")
-trawl_mod_stats = mobr::get_mob_stats(trawl_mob_in)
-
-mobr::plot_rarefaction(trawl_mob_in,'year', method = "IBR", lwd = 3, leg_loc = 'none' )

### 2021-07-28 analyses/trawl/R/analyze_hill_diversity.R

@@ -5,8 +5,36 @@
 ##' @title
 ##' @param ann_spp_flux_boots
 
-analyze_hill_diversity <- function(ann_spp_flux_summary = flux_summaries[["annual_spp_flux_summary"]]){ #  ann_spp_flux_boots = flux_summaries[["annual_spp_flux_boots"]], ann_spp_flux_summary = flux_summaries[["annual_spp_flux_summary"]]) {
-  
+here::i_am("analyses/trawl/R/analyze_hill_diversity.R")
+library(hillR)
+
+##create taxa by site matrix
+TB_trawl_taxasite <- TB_trawl_data %>%
+  dplyr::select(Date, Common_name, Abundance) %>%
+  dplyr::filter(year(Date) %ni% c("2020","2021")) %>%
+  group_by(Date, Common_name) %>%
+  summarise(Abundance = sum(Abundance)) %>%
+  na.omit %>% group_by(Date) %>%
+  # remove trawls with less than 10 individuals 
+  dplyr::filter(sum(Abundance) >=10) %>%
+  group_by(Date, Common_name) %>%
+  pivot_wider(names_from = Common_name, values_from = Abundance, values_fill = list(Abundance = 0)) %>%
+  ungroup() %>%
+  dplyr::mutate(julian_date = julian(Date, origin = as.Date("2007-01-05")),
+                biweekly = ceiling(julian_date/30),
+                month = month(Date),
+                year = year(Date)) %>%
+  dplyr::select(julian_date, Date,year, month, biweekly, everything())
+
+## Estimated qD = 2 for all communities
+
+hillR::hill_taxa(TB_trawl_taxasite %>% dplyr::select(-julian_date:-biweekly), q = 2) %>% 
+  data.frame %>% dplyr::mutate(Date = TB_trawl_taxasite$Date) %>%
+  ggplot(aes(x =Date, y =.)) +
+  geom_point()+
+  geom_line()
+
+plot(site_hill2)
   ## ++++ Helper functions ++++ ##
   #'
   #'

### 2021-07-28 analyses/trawl/R/analyze_rarefaction.R

@@ -1,0 +1,81 @@
+source(here::here('datascript.R'))
+
+##create taxa by site matrix
+TB_trawl_taxasite <- TB_trawl_data %>%
+  dplyr::select(Date, Common_name, Abundance) %>%
+  dplyr::filter(year(Date) %ni% c("2020","2021")) %>%
+  group_by(Date, Common_name) %>%
+  summarise(Abundance = sum(Abundance)) %>%
+  na.omit %>% group_by(Date) %>%
+  # remove trawls with less than 10 individuals 
+  dplyr::filter(sum(Abundance) >=10) %>%
+  group_by(Date, Common_name) %>%
+  pivot_wider(names_from = Common_name, values_from = Abundance, values_fill = list(Abundance = 0)) %>%
+  ungroup() %>%
+  dplyr::mutate(julian_date = julian(Date, origin = as.Date("2007-01-05")),
+                biweekly = ceiling(julian_date/30),
+                month = month(Date),
+                year = year(Date)) %>%
+  dplyr::select(julian_date, Date,year, month, biweekly, everything())
+
+
+TB_trawl_sampling = TB_trawl_data %>%
+  dplyr::filter(year(Date) %ni% c("2020","2021")) %>%
+  dplyr::select(Date, year, Common_name, Abundance) %>%
+  group_by(year) %>%
+  dplyr::summarise(trawl_days = length(unique(Date)),
+                   S = length(unique(Common_name)),
+                   individuals = sum(Abundance, na.rm = TRUE))
+
+min(TB_trawl_sampling$year, na.rm = TRUE)
+
+TB_trawl_sampling %>% slice_min(trawl_days) %>% dplyr::select(year) %>% unlist
+# trawl_rarefaction analysis
+r = 2
+trawl_sum = rowSums(TB_trawl_taxasite %>% dplyr::select(-julian_date:-biweekly))
+n_ref <- round(min(r * trawl_sum[trawl_sum > 0]))
+
+
+full_stats = mobr::calc_biodiv(TB_trawl_taxasite %>% dplyr::select(-julian_date:-biweekly), 
+                  groups = TB_trawl_taxasite$year,
+                  index = c("S_n","S_asymp","S_PIE","S","N"),
+                  effort = n_ref,
+                  extrapolate = T,
+                  return_NA = F)
+
+
[…]

### 2021-07-28 analyses/trawl/R/import_bioData.R

@@ -1,5 +1,5 @@
-import_bioData <- function(){
-   source(here::here("R/clean_trawl_spp.R"))
+# import_bioData <- function(){
+   # source(here::here("R/clean_trawl_spp.R"))
 # 2020-05-12 
 # these are throwing errors and not loading due to network timeout. May need to reset/update DNS servers if this continues.
 
@@ -17,21 +17,26 @@ import_bioData <- function(){
    # options(gargle_oauth_email = "jjunker@lumcon.edu")
    gs4_auth(email = "jjunker@lumcon.edu")
    # gs4_deauth()
-   TB_trawl_meta <- gs4_get("1mUG6oYBGGONBzgXPsvS6XZkNRUIojxtI7BV8WUTh-3I")#sheetID extracted with as_sheets_ID(*sheet URL*)
-   TB_trawl_tabs <- nrow(TB_trawl_meta[['sheets']])
-   TB_trawl_list <- vector('list', TB_trawl_tabs)
-   for(tab in 1:TB_trawl_tabs){
-     TB_trawl_list[[tab]] <- sheets_read(TB_trawl_meta[['spreadsheet_id']], sheet = tab, col_types = "T?d", range = cell_cols("A:C"))
-   }
-   TB_trawl_data <- bind_rows(TB_trawl_list) %>% dplyr::select(Date, Species, Abundance)
+   TB_trawl_worksheet <- gs4_get("1mUG6oYBGGONBzgXPsvS6XZkNRUIojxtI7BV8WUTh-3I")#sheetID extracted with as_sheets_ID(*sheet URL*)
+   # get the tab indices for years, excluding any metadata tabs
+   TB_trawl_tabs <- googlesheets4::sheet_names(TB_trawl_worksheet)
+   TB_trawl_tabs <- TB_trawl_tabs[!grepl("metadata",TB_trawl_worksheet[['sheets']]$name, ignore.case = TRUE)]
+   
+   # read in from all spreadsets
+  
+ TB_trawl_data <- lapply(TB_trawl_tabs, function(x){
+      googlesheets4::read_sheet(TB_trawl_worksheet, sheet = x, col_types = "Dcd-")
+   }) %>% bind_rows %>%
+      dplyr::select(Date, Species, Abundance)
 #
 ##### Data entry fixes ####
    TB_trawl_data <- TB_trawl_data %>%
     filter(!is.na(Species)) %>%
[…]

### 2021-07-28 analyses/trawl/R/load_bioData.R

@@ -2,5 +2,5 @@
 
 ## trawl data
 load_bioData <- function(){TB_trawl_data <<- readRDS(file = here::here("data/TB_trawl_data.rds"))}
-ifelse(file.exists(here::here("data/TB_trawl_data.rds")), suppressWarnings(load_bioData()), source(here::here("R/import_bioData.R")));rm(load_bioData)
+ifelse(file.exists(here::here("data/TB_trawl_data.rds")), suppressWarnings(load_bioData()), source(here::here("analyses/trawl/R/import_bioData.R")));rm(load_bioData)
 # TB_trawl_data <<- readRDS(file = "./data/TB_trawl_data.rds")

### 2021-07-28 analyses/trawl/R/trawl_(dis)similarity.R

@@ -1,0 +1,13 @@
+
+
+# Calculated dissimilarity for all temporal distances based on pres-absence
+
+TB_trawl_taxasite <- TB_trawl_data %>%
+  dplyr::select(year, month, date_id, species_mod) %>%
+  dplyr::filter(year != "2021") %>%
+  group_by(date_id, species_mod) %>%
+  distinct() %>% 
+  mutate(pres = 1) %>%
+  pivot_wider(names_from = species_mod, values_from = pres, values_fill = list(pres = 0)) %>%
+  ungroup()
+

### 2021-07-28 analyses/trawl/R/trawl_ordination.R

@@ -18,7 +18,7 @@ source(here::here("datascript.R"))#imports data with some minor cleanup
 
 ##create taxa by site matrix
 TB_trawl_taxasite <- TB_trawl_data %>%
-  select(year, month, date_id, species_mod) %>%
+  dplyr::select(year, month, date_id, species_mod) %>%
   group_by(date_id, species_mod) %>%
   distinct() %>% 
   mutate(pres = 1) %>%
@@ -26,16 +26,18 @@ TB_trawl_taxasite <- TB_trawl_data %>%
   ungroup()
 
 set.seed(123)
-TB_NMDS <- vegan::metaMDS(TB_trawl_taxasite %>% select(-c(1:2)) %>% column_to_rownames("date_id"), distance = "jaccard", trymax = 1000, autotransform = FALSE)
+TB_NMDS <- vegan::metaMDS(TB_trawl_taxasite %>% dplyr::select(-c(1:2)) %>% column_to_rownames("date_id"), distance = "jaccard",
+                          try = 1000, trymax = 3000, maxit = 9999, autotransform = FALSE, parallel = 3)
 TB_NMDS
+vegan::stressplot(TB_NMDS)
 plot(TB_NMDS)
 
 TB_NMDS.scrs <- as.data.frame(scores(TB_NMDS, display = 'sites'))
-TB_NMDS.scrs <- TB_NMDS.scrs %>% bind_cols(TB_trawl_taxasite %>% select(1:2)) %>% mutate(year = factor(year))
+TB_NMDS.scrs <- TB_NMDS.scrs %>% bind_cols(TB_trawl_taxasite %>% dplyr::select(1,3:5)) %>% mutate(year = factor(year))
 TB_NMDS.spp <- as.data.frame(scores(TB_NMDS, display = "species"))
 
 set.seed(123)
-vec.spp <- envfit(TB_NMDS, TB_trawl_taxasite %>% select(-c(1:2)) %>% column_to_rownames("date_id"), permutations = 1000, na.rm = TRUE)
+vec.spp <- envfit(TB_NMDS, TB_trawl_taxasite %>% dplyr::select(-c(1:2)) %>% column_to_rownames("date_id"), permutations = 1000, na.rm = TRUE)
 vec.spp
 
 sig_spp = unname(which(vec.spp[['vectors']]$pvals < 0.001))
[…]

### 2021-07-28 analyses/trawl/R/trawl_specaccum.R

@@ -1,9 +1,10 @@
-
+source(here::here('datascript.R'))
 # Full species accumulation curve (SAC)
 
 ##create taxa by site matrix
 TB_trawl_commonsite <- TB_trawl_data %>%
   dplyr::select(year, month, date_id, Common_name) %>%
+  dplyr::filter(year!="2021") %>%
   group_by(date_id, Common_name) %>%
   distinct() %>% 
   mutate(pres = 1) %>%
@@ -21,6 +22,7 @@ source("./figures/SAC_full_plot.R");SAC_full_plot()
 ## SAC for each year
 TB_trawl_commondate <- TB_trawl_data %>%
   select(year, Date, Common_name) %>%
+  dplyr::filter(year %ni% c("2020","2021")) %>%
   group_by(Date, Common_name) %>%
   distinct() %>% 
   mutate(pres = 1) %>%
@@ -40,32 +42,42 @@ TB_trawl_taxasite_yr <- TB_trawl_commondate %>%
 source("./figures/SAC_yr_plot.R");SAC_yr_plot()
 
 #create time-accumulation df from trawl data
+total_richness = length(unique(TB_trawl_data$Common_name))
+saveRDS(total_richness, here::here("data/total_richness.rds"))
+
 TB_trawl_data %>%
-  filter(!duplicated(Common_name)) %>%
-  mutate(richness = 1:n(), 
-         Date = as.Date(Date),
-         richness = sort(richness))-> TB_time_accum
+  # exclude 2020 & 2021
+  dplyr::filter(year %ni% c("2020","2021")) %>%
+  dplyr::filter(!duplicated(Common_name, nmax = total_richness )) %>%
+  dplyr::mutate(Date = as.Date(Date)) %>%
+  arrange(Date) %>%
+  dplyr::mutate(richness = 1:n())-> TB_time_accum
 
 TB_annual_accum <- TB_trawl_data %>%
+  # exclude 2020 & 2021
+  dplyr::filter(year %ni% c("2020","2021")) %>%
   mutate(pres = 1) %>% group_by(year) %>%
   filter(!duplicated(Common_name)) %>%
   summarise(richness = sum(pres)) %>%
-  mutate(Date = as.Date(as.character(year), format = "%Y", origin = "2000-01-01"))
+  mutate(Date = as.Date(paste(as.character(year),"01","01", sep = "-"), format = "%Y-%m-%d", origin = "2000-01-01"))
+
 
[…]

### 2021-07-28 datascript.R

@@ -1,10 +1,11 @@
 source(here::here("packages.R"))
+here::i_am("datascript.R")
 # call different data import scripts depending on changes to files.
 
 # import biology data if it has been greater than 1 month since download
 load(here::here("data/biology_sysDate.rda"))
-ifelse((Sys.Date()-biology_sysDate) >= 30, source(here::here("R/import_bioData.R")),source(here::here("R/load_bioData.R")))
+ifelse((Sys.Date()-biology_sysDate) >= 30, source(here::here("analyses/trawl/R/import_bioData.R")),source(here::here("analyses/trawl/R/load_bioData.R")))
 rm(biology_sysDate)
 
 # import environmental data
-source(here::here("R/load_enviroData.R"))
+# source(here::here("R/load_enviroData.R"))

### 2021-07-28 figures/diversity_time_plots.R

@@ -8,8 +8,8 @@
   scale_y_continuous(name = "Species Richness")+
   scale_colour_manual(name = "", values = viridis(4)[c(2,3)]) +
   theme(legend.position = c(0, 1), legend.justification = c(0, 1), legend.background = element_rect(fill = "transparent", colour = NA),
-        axis.title.x = element_blank(), axis.text.x = element_blank(),
-        legend.spacing.y = unit(-0.1, 'cm'))
+        # axis.title.x = element_blank(), axis.text.x = element_blank(),
+        legend.spacing.y = unit(-0.1, 'cm'));rich_time
 
  jaccard_time <-
   ggplot(beta_df, aes(x = Date, y = value, group = partition)) + 

### 2021-07-28 packages.R

@@ -1,3 +1,4 @@
+here::here()
 here::i_am("packages.R")
 # Install pacman if it isn't already installed
 if ("pacman" %in% rownames(installed.packages()) == FALSE) install.packages("pacman")
@@ -18,7 +19,9 @@ pacman::p_load(git2r, httr, semver, testthat, yaml, here, EML, data.table,
                taxize)
 
 devtools::install_github(c("jimjunker1/junkR"))#, "ropensci/rfishbase"))
-devtools::install_github('MoBiodiv/mobr')
+# library(junkR)
+# devtools::install_github('MoBiodiv/mobr')
+library(mobr)
 
 
 theme_mod <<- function(){theme_bw() %+replace% theme(panel.grid = element_blank())}

### 2021-08-02 docs/ms/ms.RMD
updated manuscript with the inclusion of 2D and 1D diversity orders through time.

@@
 
+# set specific variables used in methods
+## how many bootstrap permutations to run with replacement? Keep low until final draft
+nperm = 99
+## how many individuals for count for Sn, Sn = 18 * n_year
+n_year = 50
+
 ```
@@
 # Abstract
+
 Anthropogenic activities continue to exert long-term, varied, and increasing pressures on ecosystems causing alterations to biological diversity on broad and local scales.
@@
 # Introduction
+
 <!--- warming and effects in food webs --->
@@
 
+## Sampling area
+
+This study was focused on Terrebonne Bay, located in the northern Gulf of Mexico of Louisiana, USA (29^$\circ$^11.200'N, 90^$\circ$^36.560'W; Figure S1).
+Terrebonne Bay is a broad (1,761 km2), shallow estuary (average depth 2m), separated from the Gulf of Mexico by two barrier island chains and connected by four tidal passes.
+The bay-estuary complex is part of an abandoned distributary of the Mississippi River and therefore no longer receives any significant riverine inputs.
+Thus, the majority of its freshwater inputs are from the local drainage basin [@bianchi2009].
+While water column salinity and density are homogenous, strong salinity gradients exist seaward from the marsh to the barrier islands [@bianchi2009].
+Tides in Terrebonne Bay are diurnal with a semidiurnal component, ranging 20-80 cm [@inoue2000].
+
 ## Trawl sampling
@@
 Trawl sampling was conducted as part of the Louisiana Universities Marine Consortium's (LUMCON) educational outreach program (https://www.lumcon.edu/education-and-outreach).
-Individual trawls were conducted using *trawl apparatus description...* and
+Individual trawls were conducted using *trawl apparatus description...* and occasionally multiple
 
@@
 Species names were checked for typos and confirmed using the *gni_parse* function from the *taxize* package [@chamberlain2020] and further standardized to consistent taxonomic resolution for entire data series (Supplemental materials).
+
+mobr package [@mcglinn2019]
+
+Trawls with >20 individuals counted (This should be reconsidered when we aggregate at the annual scale)
+Bootstrapping methods were used by resampling with replacement `r nperm` times.
+From these permutations the 2.5% and 97.5% percentiles of yearly statistics were taken to estimate 95% percentile intervals.
+With this procedure we estimate:
+- *S~asymp~* for each year using the Chao1 estimator [@chao1984][@chao1987] a metric which is highly correlated with richness, *S* [@mcgill2011]
+- because of differences in effort, we estimated effort-controlled rarefied species richness, *S~n~*, which provides the expected number of species given a defined number of *n* individuals sampled [@gotelli2001].
+*S~n~* estimates for yearly aggregated data, *n* was calculated by the minimum samples within a year multipled by `r n_year`.
+- We used the hillR package [@li2018] to calculate the diversity order 2, which corresponds to the effective number of dominant (highly abundant) species.
 
@@
   na.omit %>% group_by(Date) %>%
-  # remove trawls with less than 10 individuals 
-  dplyr::filter(sum(Abundance) >=10) %>%
+  # remove trawls with less than 20 individuals 
+  # dplyr::filter(sum(Abundance) >=20) %>%
   group_by(Date, Common_name) %>%
@@
 
-trawl_mob_stats = mobr::get_mob_stats(trawl_mob_in, group_var = 'year', index = c("N", "S", "S_asymp", "S_n", "S_PIE", "PIE", "pct_rare"), effort_samples = n_year, extrapolate = TRUE, boot_groups = TRUE, n_perm = 99)
+trawl_mob_stats = mobr::get_mob_stats(trawl_mob_in, group_var = 'year', index = c("N", "S", "S_asymp", "S_n", "S_PIE", "PIE", "pct_rare"), effort_samples = n_year, extrapolate = TRUE, boot_groups = TRUE, n_perm = nperm)
 
@@
 
-Over the sampling period from `r min(TB_trawl_sampling$year, na.rm = TRUE)` to `r max(TB_trawl_sampling$year, na.rm = TRUE)`, `r length(unique(TB_trawl_data$Date))` trawls-days were conducted yielding `r format(signif(sum(TB_trawl_data$Abundance, na.rm = TRUE),3), scientific = TRUE)` individuals.
-Among years, total effort generally increased, both in number of trawl-days and individuals counted, from a minimum effort of (`r TB_trawl_sampling %>% slice_min(trawl_days) %>% dplyr::select(year) %>% unlist`) to `r max(TB_trawl_sampling$trawl_days)` (`r TB_trawl_sampling %>% slice_max(trawl_days) %>% dplyr::select(year) %>% unlist`) days and from `r min(TB_trawl_sampling$individuals, na.rm = TRUE)` (`r TB_trawl_sampling %>% slice_min(individuals) %>% dplyr::select(year) %>% unlist`) to `r format(signif(max(TB_trawl_sampling$individuals, na.rm = TRUE),3), scientific = TRUE)` (`r TB_trawl_sampling %>% slice_max(individuals) %>% dplyr::select(year) %>% unlist`) individuals.
+Over the sampling period from `r min(TB_trawl_sampling$year, na.rm = TRUE)` to `r max(TB_trawl_sampling$year, na.rm = TRUE)`, `r length(unique(TB_trawl_data$Date))` trawls-days were performed yielding `r format(signif(sum(TB_trawl_data$Abundance, na.rm = TRUE),3), scientific = TRUE)` individuals.
+Among years, total effort generally increased, both in number of trawl-days and individuals counted, from a minimum effort of `r min(TB_trawl_sampling$trawl_days)` (`r TB_trawl_sampling %>% slice_min(trawl_days) %>% dplyr::select(year) %>% unlist`) to `r max(TB_trawl_sampling$trawl_days)` (`r TB_trawl_sampling %>% slice_max(trawl_days) %>% dplyr::select(year) %>% unlist`) days and from `r min(TB_trawl_sampling$individuals, na.rm = TRUE)` (`r TB_trawl_sampling %>% slice_min(individuals) %>% dplyr::select(year) %>% unlist`) to `r format(signif(max(TB_trawl_sampling$individuals, na.rm = TRUE),3), scientific = TRUE)` (`r TB_trawl_sampling %>% slice_max(individuals) %>% dplyr::select(year) %>% unlist`) individuals.
 In total, `r length(unique(TB_trawl_data$Common_name))` unique species were identified and new species were consistently observed throughout the sampling period (Figure 1).
@@
 
-```{r figure 1, echo = FALSE, warning = FALSE, message=FALSE, fig.align='center', fig.cap="Figure 1.
+```{r figure 1, echo = FALSE, warning = FALSE, message=FALSE, fig.cap="Figure 1.
 Multiple measures of species richness within the trawl community between the years 2007 to 2019 show continual accumulation of species (purple points and line) through the timeseries.
@@
 
-```{r figure 2, echo=FALSE, warning=FALSE, message=FALSE, fig.align='center'}
+Considering the consistent accumulation of new species throughout the sampling series and the relatively stable effort-controlled richness, we
+
+```{r figure 2, echo=FALSE, warning=FALSE, message=FALSE}
+
+TB_trawl_taxasite_yr <- TB_trawl_taxasite %>%
+  dplyr::select(-julian_date,-Date,-month,-biweekly) %>%
+  group_by(year) %>%
+  dplyr::mutate(year = as.Date(paste(year,"01","01", sep = "-"), format = "%Y-%m-%d")) %>%
+  dplyr::summarise(across(where(is.numeric), ~sum(.x, na.rm = TRUE)))
+
+# TB_trawl_yr_qD = TB_trawl_taxasite_yr %>%
+#   split(nrow(.)) %>%
+#   purrr::map2(., c(0,1,2), ~hillR::hill_taxa(.x %>% dplyr::select(-year), q = .y)) %>% 
+#   setNames(., nm = c("q0","q1","q2")) %>%
+#   bind_cols() %>%
+#   dplyr::mutate(year = TB_trawl_taxasite_yr$year)
+
+# TB_trawl_yr_qD %>%
+# # group_stats %>%
+# #   dplyr::filter(index == "S_PIE") %>%
+# #   dplyr::mutate(group = as.Date(group, format = "%Y")) %>%
+#   ggplot()+
+#   geom_point(aes(x = year, y = q2))+
+#   geom_path(aes(x = year, y = q2))+
+#   # geom_point(aes(x = year, y = q1))+
+#   # geom_path(aes(x = year, y = q1))+
+#   # geom_ribbon(aes(x = group, ymin = lower, ymax = upper), alpha = 0.3)+
+#   scale_color_manual(values = viridis(n =2, option = 'viridis' ))+
+#   scale_fill_manual(values = viridis(n = 2, option = 'viridis'))+
+#   scale_y_continuous(limits = c(0,10))
+q2_boots = boot_sample_groups(TB_trawl_taxasite %>% dplyr::select(-julian_date,-Date,-month,-biweekly), 
+                   group_var = 'year',
+                   qD = 2,
+                   n_perm = nperm)
+
+q1_boots = boot_sample_groups(TB_trawl_taxasite %>% dplyr::select(-julian_date,-Date,-month,-biweekly), 
+                   group_var = 'year',
+                   qD = 1,
+                   n_perm = nperm)
+
 group_stats %>%
-  dplyr::filter(index == "S_PIE") %>%
+  dplyr::filter(index == "pct_rare") %>%
+  dplyr::mutate(group = as.Date(group, format = "%Y")) %>%
   ggplot()+
-  geom_point(aes(x = Date, y = median))
+  geom_point(aes(x =group, y = median))+
+  geom_path(aes(x = group, y = median))+
+  geom_ribbon(aes(x = group, ymin = lower, ymax = upper), alpha = 0.3)+
+  scale_color_manual(values = viridis(n =1, option = 'viridis' ))+
+  scale_fill_manual(values = viridis(n = 1, option = 'viridis'))#+
+  # scale_y_continuous(limits = c(0,10))
+
 ```

### 2021-08-02 analyses/trawl/R/analyze_hill_diversity.R

@@ -3,7 +3,6 @@
 ##' .. content for \details{} ..
 ##'
 ##' @title
-##' @param ann_spp_flux_boots
 
 here::i_am("analyses/trawl/R/analyze_hill_diversity.R")
 library(hillR)
@@ -27,12 +26,31 @@ TB_trawl_taxasite <- TB_trawl_data %>%
   dplyr::select(julian_date, Date,year, month, biweekly, everything())
 
 ## Estimated qD = 2 for all communities
+biweekly_sampling = TB_trawl_taxasite %>%
+  group_by(biweekly) %>%
+  dplyr::summarise(n = n()) %>%
+  right_join(TB_trawl_taxasite %>% dplyr::select(Date, ))
 
-hillR::hill_taxa(TB_trawl_taxasite %>% dplyr::select(-julian_date:-biweekly), q = 2) %>% 
-  data.frame %>% dplyr::mutate(Date = TB_trawl_taxasite$Date) %>%
-  ggplot(aes(x =Date, y =.)) +
-  geom_point()+
-  geom_line()
+trawl_qD = hillR::hill_taxa(TB_trawl_taxasite %>% dplyr::select(-julian_date:-biweekly), q = 2) %>% 
+  data.frame %>% dplyr::mutate(Date = TB_trawl_taxasite$Date,
+                               qD= 2) %>% 
+  bind_rows(
+hillR::hill_taxa(TB_trawl_taxasite %>% dplyr::select(-julian_date:-biweekly), q= 1) %>%
+  data.frame %>% dplyr::mutate(Date = TB_trawl_taxasite$Date,
+                               qD = 1)) %>%
+  bind_rows(hillR::hill_taxa(TB_trawl_taxasite %>% dplyr::select(-julian_date:-biweekly), q= 0) %>%
+              data.frame %>% dplyr::mutate(Date = TB_trawl_taxasite$Date,
+                                           qD = 0))
+
+ggplot(trawl_qD, aes(x =Date, y =., group = qD, color = qD)) +
+  geom_point(size = 2, alpha = 0.5)+
+  geom_line(alpha = 0.5)+
+  geom_smooth( se = FALSE, span = 0.1)+
+  scale_y_continuous(limits = c(0,10))
+
+
+
+
 
 plot(site_hill2)
   ## ++++ Helper functions ++++ ##

### 2021-08-02 analyses/trawl/R/analyze_rarefaction.R

@@ -30,6 +30,10 @@ TB_trawl_sampling = TB_trawl_data %>%
 min(TB_trawl_sampling$year, na.rm = TRUE)
 
 TB_trawl_sampling %>% slice_min(trawl_days) %>% dplyr::select(year) %>% unlist
+ ## Explore the (dis)similarities at different timescales
+
+
+
 # trawl_rarefaction analysis
 r = 2
 trawl_sum = rowSums(TB_trawl_taxasite %>% dplyr::select(-julian_date:-biweekly))
@@ -43,11 +47,18 @@ full_stats = mobr::calc_biodiv(TB_trawl_taxasite %>% dplyr::select(-julian_date:
                   extrapolate = T,
                   return_NA = F)
 
+## Run the mobr to estimate w
+
+
+
 
 trawl_mob_in = mobr::make_mob_in(comm = TB_trawl_taxasite %>% dplyr::select(-julian_date:-biweekly),
                                  plot_attr = TB_trawl_taxasite %>% dplyr::select(julian_date:biweekly),
-                                 coord_names = "biweekly",
+                                 coord_names = "julian_date",
                                  latlong = FALSE)
+
+mobr::plot_rarefaction(trawl_mob_in, group_var = 'year', method = 'sSBR', )
+
 trawl_mob_stats = mobr::get_mob_stats(trawl_mob_in, group_var = 'year', index = c("N", "S", "S_asymp", "S_n", "S_PIE", "PIE"), effort_samples = n_year, extrapolate = TRUE, boot_groups = TRUE, n_perm = 199)
 # trawl_mob_stats = mobr::get_mob_stats(trawl_mob_in, group_var = 'year', index = c("N", "S", "S_asymp", "S_n", "S_PIE", "PIE"), extrapolate = TRUE)
 x = trawl_mob_stats$groups_stats

### 2021-08-02 analyses/trawl/R/full_analyses.R

@@ -1,0 +1,150 @@
+# full analysis
+source(here::here('datascript.R'))
+library(hillR)
+
+
+##create taxa by site matrix
+TB_trawl_taxasite <- TB_trawl_data %>%
+  dplyr::select(Date, Common_name, Abundance) %>%
+  dplyr::filter(year(Date) %ni% c("2020","2021")) %>%
+  group_by(Date, Common_name) %>%
+  summarise(Abundance = sum(Abundance)) %>%
+  na.omit %>% group_by(Date) %>%
+  # remove trawls with less than 10 individuals 
+  dplyr::filter(sum(Abundance) >=10) %>%
+  group_by(Date, Common_name) %>%
+  pivot_wider(names_from = Common_name, values_from = Abundance, values_fill = list(Abundance = 0)) %>%
+  ungroup() %>%
+  dplyr::mutate(julian_date = julian(Date, origin = as.Date("2007-01-05")),
+                biweekly = ceiling(julian_date/30),
+                month = month(Date),
+                year = year(Date)) %>%
+  dplyr::select(julian_date, Date,year, month, biweekly, everything())
+
+## check sample-level statistics
+TB_trawl_sampling = TB_trawl_data %>%
+  dplyr::filter(year(Date) %ni% c("2020","2021")) %>%
+  dplyr::select(Date, year, Common_name, Abundance) %>%
+  group_by(year) %>%
+  dplyr::summarise(trawl_days = length(unique(Date)),
+                   S = length(unique(Common_name)),
+                   individuals = sum(Abundance, na.rm = TRUE))
+
+min(TB_trawl_sampling$year, na.rm = TRUE)
+# 2007
+
+# when do we have the fewest samples
+TB_trawl_sampling %>% slice_min(trawl_days) %>% dplyr::select(year) %>% unlist
+# 2011
+
+#create time-accumulation df from trawl data
+total_richness = length(unique(TB_trawl_data$Common_name));
+#138L
+
+# create time data frame to calculate accumulation of different species abundances over time
+TB_trawl_data %>%
+  # exclude 2020 & 2021
+  dplyr::filter(year %ni% c("2020","2021")) %>%
+  dplyr::filter(!duplicated(Common_name, nmax = total_richness )) %>%
+  dplyr::mutate(Date = as.Date(Date)) %>%
+  arrange(Date) %>%
[…]

### 2021-08-02 analyses/trawl/R/trawl_specaccum.R

@@ -71,14 +71,15 @@ TB_time_df <- TB_time_accum %>%
 
 #create moving jaccard calc by year-month
 # create a dataframe for time series of distance compared to first sampling 
-unique_combinations <- expand.grid(date_A = unique(levels(as.factor(TB_trawl_commonsite$date_id))), 
-                                   Date = unique(levels(as.factor(TB_trawl_commonsite$date_id)))) #%>%
-  # filter(date_A == as.character(min(TB_trawl_commonsite$date_id)))
+unique_combinations <- expand.grid(date_A = unique(levels(as.factor(TB_trawl_taxasite$Date))), 
+                                   Date = unique(levels(as.factor(TB_trawl_taxasite$Date)))) %>%
+   filter(date_A == as.character(min(TB_trawl_taxasite$Date)))
 
 
-
-TB_date_jaccard = vegdist((TB_trawl_commonsite %>% dplyr::select(-year, -month) %>% 
-                             column_to_rownames("date_id")), method = "jaccard") %>%
+?betapart
+TB_date_jaccard = vegdist((TB_trawl_taxasite %>% dplyr::select(-julian_date:-month) %>% 
+                             group_by('biweekly')
+                             column_to_rownames("biweekly")), method = "jaccard") %>%
   as.matrix %>% as.data.frame %>% rownames_to_column("date_A") %>% 
   pivot_longer(cols = 2:dim(.)[2], names_to = "Date", values_to = "jaccard") %>%
   inner_join(unique_combinations) %>% filter(date_A != Date) %>% 

### 2021-08-02 packages.R

@@ -29,6 +29,36 @@ theme_set(theme_mod());rm(theme_mod)
 find_hull <<- function(df) df[chull(df$NMDS1, df$NMDS2),]
 
 '%ni%' <<- Negate('%in%')
+# bootstrapped sampling for estimating variability withing groups
+boot_sample_groups = function(abund_mat, group_var, qD, n_perm,...) {
+  boot_list = vector('list', n_perm)
+  
+  # sample rows and calculate abundance vector
+  sample_hill = function(boot_n,...){
+    sample_dat = by(abund_mat, INDICES = abund_mat[,group_var], FUN = sample_frac,
+                  replace = TRUE)
+    class(sample_dat) = "list"
+    sample_dat = bind_rows(sample_dat)
+  
+  agg_groups = stats::aggregate(sample_dat[,-1], by = sample_dat[,1],
+                               FUN = 'sum')
+  
+  group_col = agg_groups[,group_var]
+  qD_col = paste0("q",parse(text = qD))
+  boot_col = paste0("boot", parse(text = boot_n))
+  
+  dat_groups = agg_groups %>% 
+    apply(., 1, function(x) hillR::hill_taxa(comm = x, q = qD))%>%
+    bind_cols(group_col,.) %>%
+    setNames(., c(group_var, qD_col)) %>%
+    dplyr::mutate(boot_id = boot_col)
+    
+  return(dat_groups)
+  }
+  # debugonce(sample_hill)
+  boot_list = purrr::map(1:n_perm, ~sample_hill(boot_n = .x)) %>% bind_rows
+  return(boot_list)
+}
 
 # yday_summary <<- function(data,...){
 #   if("yday" %in% colnames(data)){

### 2021-08-05 docs/ms/ms.RMD
updated manuscript and workflow.

@@
 source(here::here("datascript.R"))
+source(here::here("analyses/trawl/R/Lorenz.R"))
 
@@
 <!--- this is a note in Rmarkdown --->
+\newpage
 
@@
 Trawl sampling was conducted as part of the Louisiana Universities Marine Consortium's (LUMCON) educational outreach program (https://www.lumcon.edu/education-and-outreach).
-Individual trawls were conducted using *trawl apparatus description...* and occasionally multiple
+Individual trawls were conducted using *trawl apparatus description...* for 10 - 20 min.
+When multiple trawls were conducted on a single day, species counts were summed across all trawls and
 
@@
 Species names were checked for typos and confirmed using the *gni_parse* function from the *taxize* package [@chamberlain2020] and further standardized to consistent taxonomic resolution for entire data series (Supplemental materials).
+We measured multiple aspects of species richness, first to track the uncorrected accumulation of species over time we filtered species from the data set after first occurrence.
+We then aggreagated all trawls within a calendar year and calculated two measures of species richness, accounting for differences in sampling effort among years.
+The first measure was asymptotic species richness, *S~asymp~*, using the Chao1 estimator [@chao1984][@chao1987].
+This metric is highly correlated with measured richness, *S* [@mcgill2011], but attempts to extrapolate the total species richness based on incomplete sampling.
+Second, we attempted to account for differences in effort among years by estimating the effort-controlled rarefied species richness, *S~n~*, which provides the expected number of species given a defined number of *n* individuals sampled [@gotelli2001].
+*S~n~* estimates for yearly aggregated data, *n* was calculated by the minimum samples within a year multiplied by `r n_year`.
+We calculated *S~asymp~* and *S~n~* using the mobr package [@mcglinn2019][@mcglinn2021a].
 
-mobr package [@mcglinn2019]
+Beyond actual and expected numbers of species, we calculated additional measures of biodiversity to capture community change through time.
+To quantify changes in the distribution of abundant and rare species, we calculated specific orders of diversity, the percentage of rare species, and evenness in species abundances on annually aggregated species abundances.
+An order of diversity, *^q^D*, where *q* represents a non-negative integer, captures the "effective numbers of species" based on varying degrees of rarity of the species in a community [@hill1973].
+We used the the *hill_taxa* function in the hillR package [@li2018] to estimate the effective species for diversity order 2 (i.e., *^2^D*).
+*^2^D* is equivalent to the reciprocal of Simpson's diversity [@simpson1949] (i.e., 1/Simpson's index) which emphasizes the importance of dominant (highly abundant) species.
+At the other end of the abundance spectrum, we calculated the percentage of rare species in the community as the number of species with abundances below a threshold of $0.05*n$, divided by the total number of species x 100.
+Here, *n* is the number of individuals in the sample and the value of 0.05 was chosen because it has been shown to capture rarity well and is generally uncorrelated with other metrics of biodiversity.
+Lastly, to integrate changes in abundance of dominant and rare species within the community, we calculated the evenness of species abundances with the Gini coefficient [@gini1921], normalized for differences in species richness among years, $G^*$ [@solomon1975; @chao2019], :
 
-Trawls with >20 individuals counted (This should be reconsidered when we aggregate at the annual scale)
-Bootstrapping methods were used by resampling with replacement `r nperm` times.
+$$ G^* = (2 \sum_{i = 1}^S ip_i -2)/(S-1)$$
+
+where, in a community of *S* species, species' relative abundances, $p_{i}$, are ordered such that $p_{1} \geq p_{2} \geq ...p_{S}$ for all species of the community.
+For all metrics, variability was calculated with bootstrapping methods by resampling with replacement `r nperm` times.
 From these permutations the 2.5% and 97.5% percentiles of yearly statistics were taken to estimate 95% percentile intervals.
-With this procedure we estimate:
-- *S~asymp~* for each year using the Chao1 estimator [@chao1984][@chao1987] a metric which is highly correlated with richness, *S* [@mcgill2011]
-- because of differences in effort, we estimated effort-controlled rarefied species richness, *S~n~*, which provides the expected number of species given a defined number of *n* individuals sampled [@gotelli2001].
-*S~n~* estimates for yearly aggregated data, *n* was calculated by the minimum samples within a year multipled by `r n_year`.
-- We used the hillR package [@li2018] to calculate the diversity order 2, which corresponds to the effective number of dominant (highly abundant) species.
 
@@
 Therefore, we also calculated rarefied richness at `r S_n` individuals, *S~`r S_n`~*,  for each year.
-Here, effort-controlled species richness, *S~`r S_n`~*, diverged qualitatively from *S~asymp~* and was generally constant, ranging from `r group_stats %>% dplyr::filter(effort > 100) %>% slice_min(median) %>% dplyr::select(median) %>% round(1)` (`r group_stats %>% dplyr::filter(effort > 100) %>% slice_min(median) %>% dplyr::select(lower) %>% round(1)` -- `r group_stats %>% dplyr::filter(effort > 100) %>% slice_min(median) %>% dplyr::select(upper) %>% round(1)`) to `r group_stats %>% dplyr::filter(effort > 100) %>% slice_max(median) %>% dplyr::select(median) %>% round(1)` (`r group_stats %>% dplyr::filter(effort > 100) %>% slice_max(median) %>% dplyr::select(lower) %>% round(1)` -- `r group_stats %>% dplyr::filter(effort > 100) %>% slice_max(median) %>% dplyr::select(upper) %>% round(1)`) (Figure 1).
+Here, effort-controlled species richness, *S~`r S_n`~*, diverged qualitatively from *S~asymp~* and was generally constant with an apparent slight increase in more recent sampling years.
+Overall, *S~`r S_n`~* ranged from `r group_stats %>% dplyr::filter(effort > 100) %>% slice_min(median) %>% dplyr::select(median) %>% round(1)` (`r group_stats %>% dplyr::filter(effort > 100) %>% slice_min(median) %>% dplyr::select(lower) %>% round(1)` -- `r group_stats %>% dplyr::filter(effort > 100) %>% slice_min(median) %>% dplyr::select(upper) %>% round(1)`) to `r group_stats %>% dplyr::filter(effort > 100) %>% slice_max(median) %>% dplyr::select(median) %>% round(1)` (`r group_stats %>% dplyr::filter(effort > 100) %>% slice_max(median) %>% dplyr::select(lower) %>% round(1)` -- `r group_stats %>% dplyr::filter(effort > 100) %>% slice_max(median) %>% dplyr::select(upper) %>% round(1)`) (Figure 1).
 
@@
 
-# partition beta diversity into nestedness and turnover #
-# uses `betapart` package #
+### create timeseries figure
 TB_time_df <- TB_time_accum %>%
@@
   dplyr::filter(data_type != "ann_raw")
+
+S_n_lab = paste0("S[",S_n,"]")
 
@@
   scale_y_continuous(name = "Species Richness")+
-  scale_colour_manual(labels = c("continuous", expression(italic("S"[900])),expression(italic("S"["asymp"]))), values = viridis(n = 3, alpha = c(1,1,1), option = 'viridis')) +
+  scale_colour_manual(labels = c("continuous", bquote(italic("S"[.(S_n[1])])),expression(italic("S"["asymp"]))), values = viridis(n = 3, alpha = c(1,1,1), option = 'viridis')) +
   # scale_alpha_manual(values = c(1,1,0.3))+
@@
         # axis.title.x = element_blank(), axis.text.x = element_blank(),
-        legend.spacing.y = unit(-0.1, 'cm'))
+        legend.spacing.y = unit(-0.1, 'cm'))+
+  scale_x_date(date_breaks = 'year', limits = c(as.Date("2007-01-01"),as.Date("2019-06-01")),
+               date_labels = "%Y")
 
@@
 
-Considering the consistent accumulation of new species throughout the sampling series and the relatively stable effort-controlled richness, we
+```{r turnover, echo = FALSE, warning=FALSE, message=FALSE}
 
-```{r figure 2, echo=FALSE, warning=FALSE, message=FALSE}
+## quantify loss and appearance of species in the timeseries
+TB_trawl_data %>%
+  # exclude 2020 & 2021
+  dplyr::filter(year %ni% c("2020","2021")) %>%
+  group_by(year, Common_name) %>%
+  dplyr::summarise(Abundance = sum(Abundance, na.rm = TRUE)) %>%
+  group_by(year) %>%
+  pivot_wider( names_from = 'Common_name', values_from = 'Abundance', values_fill = 0) %>%
+  ungroup %>%
+  # dplyr::mutate(time.var = 1:n()) %>%
+  pivot_longer(c(-year), names_to = 'Common_name', values_to = 'Abundance')-> TB_trawl_yr
 
-TB_trawl_taxasite_yr <- TB_trawl_taxasite %>%
-  dplyr::select(-julian_date,-Date,-month,-biweekly) %>%
-  group_by(year) %>%
-  dplyr::mutate(year = as.Date(paste(year,"01","01", sep = "-"), format = "%Y-%m-%d")) %>%
-  dplyr::summarise(across(where(is.numeric), ~sum(.x, na.rm = TRUE)))
+trawl_yr_turnover = purrr::map(c('appearance','disappearance','total'),
+                                     ~codyn::turnover(df = TB_trawl_yr,
+                                                      time.var = 'year',
+                                                      species.var = 'Common_name',
+                                                      abundance.var = 'Abundance',
+                                                      metric = .x) %>%
+                                       data.frame %>%
+                                       dplyr::mutate(Date = as.Date(paste0(unique(TB_trawl_yr$year)[-1],"-01-01"), format = "%Y-%m-%d"),
+                                                     variable = .x) %>%
+                                       dplyr::rename(value = !!names(.[1])) %>%
+                                       bind_rows(data.frame(value = NA_real_, time.var = NA_real_, Date = as.Date("2008-01-01"), variable =.x))) %>%
+                                     bind_rows
+gains = trawl_yr_turnover %>%
+  dplyr::filter(variable == "appearance")
 
-# TB_trawl_yr_qD = TB_trawl_taxasite_yr %>%
-#   split(nrow(.)) %>%
-#   purrr::map2(., c(0,1,2), ~hillR::hill_taxa(.x %>% dplyr::select(-year), q = .y)) %>% 
-#   setNames(., nm = c("q0","q1","q2")) %>%
-#   bind_cols() %>%
-#   dplyr::mutate(year = TB_trawl_taxasite_yr$year)
+losses = trawl_yr_turnover %>%
+  dplyr::filter(variable == "disappearance")
 
-# TB_trawl_yr_qD %>%
-# # group_stats %>%
-# #   dplyr::filter(index == "S_PIE") %>%
-# #   dplyr::mutate(group = as.Date(group, format = "%Y")) %>%
-#   ggplot()+
-#   geom_point(aes(x = year, y = q2))+
-#   geom_path(aes(x = year, y = q2))+
-#   # geom_point(aes(x = year, y = q1))+
-#   # geom_path(aes(x = year, y = q1))+
-#   # geom_ribbon(aes(x = group, ymin = lower, ymax = upper), alpha = 0.3)+
-#   scale_color_manual(values = viridis(n =2, option = 'viridis' ))+
-#   scale_fill_manual(values = viridis(n = 2, option = 'viridis'))+
-#   scale_y_continuous(limits = c(0,10))
+total = trawl_yr_turnover %>%
+  dplyr::filter(variable == "total")
+
+```
+
+Consistent with the pattern of continued accumulation of new species throughout the sampling series and the relatively stable effort-controlled richness, species gains and losses generally balanced (Figure 2 ).
+Total turnover averaged `r round(mean(total$value, na.rm = TRUE),2)` and decreased with time from a peak turnover of `r round(max(total$value, na.rm = TRUE),2)` in `r total %>% slice_max(value) %>% dplyr::select(year)` to `r total %>% dplyr::filter(year == '2019') %>% dplyr::select(value) %>% round(2)` in the final year of record, 2019 (Figure 2).
+The contribution of species gains to total turnover averaged `r round(mean(gains$value, na.rm = TRUE),2)` and ranged from `r round(max(gains$value, na.rm = TRUE),2)` to `r round(min(gains$value, na.rm = TRUE),2)`, whereas, species losses average `r round(mean(losses$value, na.rm = TRUE),2)` and ranged from `r round(max(losses$value, na.rm = TRUE),2)` to `r round(min(losses$value, na.rm = TRUE),2)`.
+
+```{r turnover plot ,echo = FALSE, warning=FALSE, message=FALSE, fig.cap = "Figure 2. Total species "}
+trawl_yr_turnover %>%
+  ggplot()+
+  geom_line(aes(x = Date, y = value, group = variable, color = variable), size = 1.1)+
+  scale_color_manual(values = viridis(n = 3, option = 'viridis'))+
+  scale_y_continuous(name = 'Species turnover',limits = c(0,0.7), expand = c(0.01,0.01))+
+  scale_x_date(date_breaks = 'year', limits = c(as.Date("2007-01-01"),as.Date("2019-06-01")),
+               date_labels = "%Y")+
+  theme(legend.position = c(0,0),
+        legend.justification = c(0,0),
+        legend.background = element_rect(fill = 'transparent', color = NA),
+        legend.title = element_blank(),
+        axis.title.x = element_blank())
+```
+
+```{r annual qD, echo=FALSE, warning=FALSE, message=FALSE}
+set.seed(123)
 q2_boots = boot_sample_groups(TB_trawl_taxasite %>% dplyr::select(-julian_date,-Date,-month,-biweekly), 
@@
                    n_perm = nperm)
-
+set.seed(123)
 q1_boots = boot_sample_groups(TB_trawl_taxasite %>% dplyr::select(-julian_date,-Date,-month,-biweekly), 
@@
 
+qD_df = q2_boots %>% 
+  # summarise q2 by year
+  group_by(year) %>%
+  dplyr::summarise(across(q2, list(mean = ~mean(.x, na.rm = TRUE),
+                                   median = ~quantile(.x, 0.5, na.rm = TRUE),
+                                   quant2.5= ~quantile(.x, 0.025, na.rm = TRUE),
+                                   quant25= ~quantile(.x, 0.25, na.rm = TRUE),
+                                   quant75= ~quantile(.x, 0.75, na.rm = TRUE),
+                                   quant97.5= ~quantile(.x, 0.975, na.rm = TRUE)), .names = "{.fn}")) %>%
+  dplyr::mutate(Date = as.Date(paste(year,"01","01", sep = "-"), format = "%Y-%m-%d"),
+                q_order = "q2") %>%
+  bind_rows(
+    q1_boots %>%
+      # summarise q1 by year
+      group_by(year) %>%
+      dplyr::summarise(across(q1, list(mean = ~mean(.x, na.rm = TRUE),
+                                       median = ~quantile(.x, 0.5, na.rm = TRUE),
+                                       quant2.5= ~quantile(.x, 0.025, na.rm = TRUE),
+                                       quant25= ~quantile(.x, 0.25, na.rm = TRUE),
+                                       quant75= ~quantile(.x, 0.75, na.rm = TRUE),
+                                       quant97.5= ~quantile(.x, 0.975, na.rm = TRUE)), .names = "{.fn}")) %>%
+      dplyr::mutate(Date = as.Date(paste(year,"01","01", sep = "-"), format = "%Y-%m-%d"),
+                    q_order = "q1")
+   )
+
+annual_evenness_boots = boot_gini_groups(TB_trawl_taxasite %>% dplyr::select(-julian_date,-Date,-month,-biweekly), 
+                                group_var = 'year',
+                                n_perm = nperm)
+
+annual_evenness_df = annual_evenness_boots %>%
+  dplyr::select(-boot_id) %>%
+  pivot_longer(-year, names_to = 'measure', values_to = 'value') %>%
+  group_by(year,measure) %>%
+  dplyr::summarise(across(value, list(mean = ~mean(.x, na.rm = TRUE),
+                                      median = ~quantile(.x, 0.5, na.rm = TRUE),
+                                      quant2.5= ~quantile(.x, 0.025, na.rm = TRUE),
+                                      quant25= ~quantile(.x, 0.25, na.rm = TRUE),
+                                      quant75= ~quantile(.x, 0.75, na.rm = TRUE),
+                                      quant97.5= ~quantile(.x, 0.975, na.rm = TRUE)), .names = "{.fn}")) %>%
+  dplyr::mutate(Date = as.Date(paste(year,"01","01", sep = "-"), format = "%Y-%m-%d")) %>%
+  ungroup
+
+group_stats %>%
+  dplyr::filter(index == "pct_rare") -> rarity
+
+```
+
+Species turnover was likley confined to species with moderate to low relative abundances.
+The effective number of highly abundant species, *^2^D*, was variable but stable through time with calculated values *ca.* `r qD_df %>% dplyr::filter(q_order == 'q2') %>% dplyr::summarise(across(median, ~median(.x ,na.rm = TRUE))) %>% round(2)` $\pm$ `r qD_df %>% dplyr::filter(q_order == 'q2') %>% dplyr::summarise(across(median, ~sd(.x, na.rm = TRUE))) %>% round(1)` (mean $\pm$ 1 SD) (range: `r qD_df %>% dplyr::filter(q_order == 'q2')%>% slice_min(median) %>% dplyr::select(median) %>% round(2)` to  `r qD_df %>% dplyr::filter(q_order == 'q2') %>% slice_max(median) %>% dplyr::select(median) %>% round(1)`; Figure 3 __*supplemental?*__).
+In contrast, the percentage of rare species increased through time from `r rarity %>% slice_min(group) %>% dplyr::select(median) %>% round(2)` (`r rarity %>% slice_min(group) %>% dplyr::select(lower) %>% round(2)` -- `r rarity %>% slice_min(group) %>% dplyr::select(upper) %>% round(2)`, 95% percentile interval [PI]) to `r rarity %>% slice_max(group) %>% dplyr::select(median) %>% round(2)` `r rarity %>% slice_max(group) %>% dplyr::select(lower) %>% round(2)` -- `r rarity %>% slice_max(group) %>% dplyr::select(upper) %>% round(2)`, 95% PI; Figure 3A).
+Additionally, the normalized evenness in species relative abundances showed a consistent decline through time from a median value of `r annual_evenness_df %>% dplyr::filter(measure == 'gini_norm') %>% slice_min(Date) %>% dplyr::select(median) %>% round(2)` in `r min(annual_evenness_df$year,na.rm = TRUE)` (`r annual_evenness_df %>% dplyr::filter(measure == 'gini_norm') %>% slice_min(Date) %>% dplyr::select(quant2.5) %>% round(2)` -- `r annual_evenness_df %>% dplyr::filter(measure == 'gini_norm') %>% slice_min(Date) %>% dplyr::select(quant97.5) %>% round(2)`, 95% PI) to `r annual_evenness_df %>% dplyr::filter(measure=='gini_norm') %>% slice_max(Date) %>% dplyr::select(median) %>% round(2)` (`r annual_evenness_df %>% dplyr::filter(measure == 'gini_norm') %>% slice_max(Date) %>% dplyr::select(quant2.5) %>% round(2)` -- `r annual_evenness_df %>% dplyr::filter(measure == 'gini_norm') %>% slice_max(Date) %>% dplyr::select(quant97.5) %>% round(2)`, 95% PI) in `r max(annual_evenness_df$year, na.rm = TRUE)`.
+
+```{r diversity2 plot, echo = FALSE, warning=FALSE, message=FALSE, fig.cap="Figure 3.
+Temporal trends in order of diversity q = 2, ^2^D highlight relative stability in the number of dominant species in the community through time.
+^2^D is equivalent to 1/Simpson's diversity index and captures the effective number of highly abundant species in the community."}
+qD_df %>%
+  dplyr::filter(q_order == "q2") %>%
+  ggplot()+
+  geom_ribbon(aes(x = Date, ymin = quant2.5, ymax = quant97.5, group = q_order, fill = q_order), alpha = 0.5)+
+  geom_line(aes(x = Date, y = median, group = q_order, color = q_order), size = 1.2)+
+  geom_point(aes(x = Date, y= mean, group = q_order), shape = 6)+
+  scale_y_continuous(name = expression("Effective species ("~italic(''^2*D)~")"),limits = c(0,11))+
+  scale_color_manual(labels = c("q2"), values = viridis(n = 1, option = 'viridis'))+
+  scale_fill_manual(labels = c("q2"),values = viridis(n = 1, alpha = 0.5, option = 'viridis'))+
+  theme(legend.title = element_blank(),
+        legend.position = "none",
+        legend.justification = c(0,1))
+
+```
+
+```{r evenness, echo = FALSE, warning=FALSE, message=FALSE, fig.cap= "Figure 4." }
+
+annual_evenness_df %>%
+  dplyr::filter(measure == 'gini_raw') %>%
+  ggplot()+
+  geom_ribbon(aes(x = Date, ymin = quant2.5, ymax = quant97.5), alpha = 0.3) +
+  geom_line(aes(x = Date, y = median), size = 1.1) +
+  geom_point(aes(x = Date, y = median), shape = 22, size = 3)+
+  scale_y_continuous(name = "Normalized Gini coefficient", limits = c(0,NA), expand = c(0.01,0.01))+
+  scale_x_date(date_breaks = 'year', limits = c(as.Date("2007-01-01"),as.Date("2019-06-01")),
+               date_labels = "%Y")+
+  theme(axis.title.x = element_blank())-> evenness_plot
+
 group_stats %>%
@@
   ggplot()+
-  geom_point(aes(x =group, y = median))+
-  geom_path(aes(x = group, y = median))+
+  geom_point(aes(x =group, y = median), size = 3, shape = 22)+
+  geom_path(aes(x = group, y = median), size = 1.1)+
   geom_ribbon(aes(x = group, ymin = lower, ymax = upper), alpha = 0.3)+
+  scale_y_continuous(name = "Percent rare species (%)", limits = c(70,100), expand = c(0.01,0.01))+
   scale_color_manual(values = viridis(n =1, option = 'viridis' ))+
-  scale_fill_manual(values = viridis(n = 1, option = 'viridis'))#+
-  # scale_y_continuous(limits = c(0,10))
+  scale_fill_manual(values = viridis(n = 1, option = 'viridis'))+
+  scale_x_date(date_breaks = 'year', limits = c(as.Date("2007-01-01"),as.Date("2019-06-01")),
+               date_labels = "%Y")+
+  theme(axis.title.x = element_blank())-> rarity_plot
+
+gridExtra::grid.arrange(rarity_plot, evenness_plot, ncol = 1)
 

### 2021-08-05 analyses/trawl/R/full_analyses.R

@@ -1,7 +1,10 @@
 # full analysis
 source(here::here('datascript.R'))
+source(here::here("analyses/trawl/R/Lorenz.R"))
 library(hillR)
+nperm = 99
 
+add_row_2008 = data.frame(Date = as.Date("2008-01-01"))
 
 ##create taxa by site matrix
 TB_trawl_taxasite <- TB_trawl_data %>%
@@ -37,6 +40,7 @@ min(TB_trawl_sampling$year, na.rm = TRUE)
 TB_trawl_sampling %>% slice_min(trawl_days) %>% dplyr::select(year) %>% unlist
 # 2011
 
+###### TEMPORAL PATTERNS OF RICHNESS -----------
 #create time-accumulation df from trawl data
 total_richness = length(unique(TB_trawl_data$Common_name));
 #138L
@@ -106,6 +110,37 @@ beta_dates <- gsub('^([0-9]{4}-)([0-9]{1})$', '\\10\\2', names(beta_lists))
 beta_df <- bind_rows(beta_lists) %>% mutate(Date = as.Date(paste0(beta_dates,"-01"), "%Y-%m-%d")) %>% #select(Date, everything()) %>%
   pivot_longer(-Date, names_to = "partition", values_to = "value")
 
+#### TURNOVER ------------
+## quantify loss and appearance of species in the timeseries
+TB_trawl_data %>%
+  # exclude 2020 & 2021
+  dplyr::filter(year %ni% c("2020","2021")) %>%
+  group_by(year, Common_name) %>%
+  dplyr::summarise(Abundance = sum(Abundance, na.rm = TRUE)) %>%
+  group_by(year) %>%
+  pivot_wider( names_from = 'Common_name', values_from = 'Abundance', values_fill = 0) %>%
+  ungroup %>%
+  # dplyr::mutate(time.var = 1:n()) %>%
+  pivot_longer(c(-year), names_to = 'Common_name', values_to = 'Abundance')-> TB_trawl_yr
+  
+trawl_yr_turnover_list = purrr::map(c('appearance','disappearance','total'),
+                                     ~codyn::turnover(df = TB_trawl_yr,
+                                                      time.var = 'year',
+                                                      species.var = 'Common_name',
+                                                      abundance.var = 'Abundance',
+                                                      metric = .x) %>%
+                                       data.frame %>%
[…]

### 2021-08-05 packages.R

@@ -16,7 +16,7 @@ pacman::p_load(git2r, httr, semver, testthat, yaml, here, EML, data.table,
                gridExtra, ggridges, iNEXT, vegan, rlist, pipeR,
                viridis, broom, bbmle, ggthemes, ggeffects, bsts,
                rfishbase, auk, betapart, plot3D, ncdf4, forecast,
-               taxize)
+               taxize, hillR, codyn, gridExtra)
 
 devtools::install_github(c("jimjunker1/junkR"))#, "ropensci/rfishbase"))
 # library(junkR)
@@ -59,6 +59,39 @@ boot_sample_groups = function(abund_mat, group_var, qD, n_perm,...) {
   boot_list = purrr::map(1:n_perm, ~sample_hill(boot_n = .x)) %>% bind_rows
   return(boot_list)
 }
+
+# bootstrapped sampling for estimating variability withing groups
+boot_gini_groups = function(abund_mat, group_var, n_perm,...) {
+  boot_list = vector('list', n_perm)
+  
+  # sample rows and calculate abundance vector
+  sample_even = function(boot_n,...){
+      sample_dat = by(abund_mat, INDICES = abund_mat[,group_var], FUN = sample_frac,
+                    replace = TRUE)
+    class(sample_dat) = "list"
+    sample_dat = bind_rows(sample_dat)
+    
+    agg_groups = stats::aggregate(sample_dat[,-1], by = sample_dat[,1],
+                                  FUN = 'sum')
+    
+    group_col = agg_groups[,group_var]
+    boot_col = paste0("boot", parse(text = boot_n))
+    agg_dat = agg_groups[,-1]
+    
+    dat_groups =  agg_dat %>%
+      apply(., 1, gini_even) %>%
+      t %>% data.frame %>%
+      bind_cols(group_col,.) %>%
+      setNames(., c(group_var, 'gini_raw','gini_norm')) %>%
+      dplyr::mutate(boot_id = boot_col)
+    
+    return(dat_groups)
+  }
+  # debugonce(sample_even)
+  boot_list = purrr::map(1:n_perm, ~sample_even(boot_n = .x)) %>% bind_rows
+  return(boot_list)
+}
+
 
 # yday_summary <<- function(data,...){
 #   if("yday" %in% colnames(data)){

### 2021-08-08 docs/ms/ms.RMD
update befre discussion with CRM

@@
 source(here::here("analyses/trawl/R/Lorenz.R"))
+source(here::here("analyses/trawl/R/Evenness.R"))
 
@@
 Explaining the extent and pace of biodiversity change will require identifying the conditions that lead to divergent biological responses, e.g., whether change happens gradually or abruptly and through individual versus cohesive species responses.
-In particular, disentangling the roles of extrinsic, environmental forcing and intrinsic, ecological processes is vital.
-We propose to combine two time series of environmental and biological change with information on species’ traits and trophic interactions to attribute biological change to its extrinsic and intrinsic drivers.
-The proposed work includes analysis and continuation of a data set extending nearly two decades of pelagic megafaunal communities and environment monitoring
-for a shallow estuarine bay along the Gulf of Mexico Coast.
-To this, we add analysis and continuation of a three year dataset of benthic macrofaunal from the same bay.
-The project proposes to address four key questions.
 
@@
 
-<!--- warming and effects in food webs --->
+<!---  --->
 Anthropogenic activities continue to exert long-term, varied, and increasing pressures on ecosystems [@steffen2015] causing alterations to biological diversity on local and global scales.
@@
 Yet, understanding how communities change through time is crucial for predicting current and future changes to biological systems and ecosystem services.
-<!--- Speeding up of food web: Species levels--->
+<!--- --->
 Explaining the extent and pace of biodiversity change will require identifying the conditions that lead to divergent biological responses to environmental change, both natural and anthropogenic.
@@
 
-Here, we quantified over a decade of change in a shallow estuarine community. We
+Here, we quantified biodiversity changes within a shallow estuarine community over a decade to understand shifts in total species richness, the relative distribution of abundant and rare species, and potential change points in community composition through time...
 
@@
 Individual trawls were conducted using *trawl apparatus description...* for 10 - 20 min.
-When multiple trawls were conducted on a single day, species counts were summed across all trawls and
+When multiple trawls were conducted on a single day, species counts were summed across all trawls...
 
@@
 We measured multiple aspects of species richness, first to track the uncorrected accumulation of species over time we filtered species from the data set after first occurrence.
-We then aggreagated all trawls within a calendar year and calculated two measures of species richness, accounting for differences in sampling effort among years.
+We then aggregated all trawls within a calendar year and calculated two measures of species richness, accounting for differences in sampling effort among years.
 The first measure was asymptotic species richness, *S~asymp~*, using the Chao1 estimator [@chao1984][@chao1987].
@@
 Second, we attempted to account for differences in effort among years by estimating the effort-controlled rarefied species richness, *S~n~*, which provides the expected number of species given a defined number of *n* individuals sampled [@gotelli2001].
-*S~n~* estimates for yearly aggregated data, *n* was calculated by the minimum samples within a year multiplied by `r n_year`.
+*S~n~* estimates for yearly aggregated data, *n* was calculated by the minimum number of trawls within a year multiplied by `r n_year`.
 We calculated *S~asymp~* and *S~n~* using the mobr package [@mcglinn2019][@mcglinn2021a].
@@
 
+TB_trawl_taxasite_yr <- TB_trawl_data %>%
+  # exclude 2020 & 2021
+  dplyr::filter(year %ni% c("2020","2021")) %>%
+  dplyr::select(year, Common_name, Abundance) %>%
+  group_by(year, Common_name) %>%
+  summarise(Abundance = sum(Abundance, na.rm = TRUE)) %>%
+  na.omit %>% #gropu_by(year) %>%
+  # remove trawls with less than 20 individuals 
+  # dplyr::filter(sum(Abundance) >=20) %>%
+  group_by(year, Common_name) %>%
+  pivot_wider(names_from = Common_name, values_from = Abundance, values_fill = list(Abundance = 0)) %>%
+  ungroup() %>%
+  dplyr::select( year, everything())
+
 n_year = 50
@@
 
-trawl_mob_in = mobr::make_mob_in(comm = TB_trawl_taxasite %>% dplyr::select(-julian_date:-biweekly),
-                           plot_attr = TB_trawl_taxasite %>% dplyr::select(julian_date:biweekly),
-                           coord_names = "biweekly",
-                           latlong = FALSE)
+## Estimated mobr for biweekly  for all communities
+# TB_trawl_biweekly = TB_trawl_data %>%
+#   # exclude 2020 & 2021
+#   dplyr::filter(year %ni% c("2020","2021")) %>%
+#   dplyr::mutate(julian_date = julian(Date, origin = as.Date("2007-01-05")),
+#                 biweekly = ceiling(julian_date/14)) %>%
+#   group_by(year,biweekly, Common_name) %>%
+#   dplyr::summarise(Abundance = sum(Abundance, na.rm = TRUE)) %>%
+#   group_by(year,biweekly) %>%
+#   pivot_wider( names_from = 'Common_name', values_from = 'Abundance', values_fill = 0) %>%
+#   ungroup
 
-trawl_mob_stats = mobr::get_mob_stats(trawl_mob_in, group_var = 'year', index = c("N", "S", "S_asymp", "S_n", "S_PIE", "PIE", "pct_rare"), effort_samples = n_year, extrapolate = TRUE, boot_groups = TRUE, n_perm = nperm)
+# trawl_mob_in = mobr::make_mob_in(comm = TB_trawl_biweekly %>% dplyr::select(-biweekly),
+#                                  plot_attr = TB_trawl_biweekly %>% dplyr::select(year,biweekly),
+#                                  coord_names = "biweekly",
+#                                  latlong = FALSE)
 
-group_stats = trawl_mob_stats$groups_stats %>% data.frame
+# trawl_mob_in = mobr::make_mob_in(comm = TB_trawl_taxasite %>% dplyr::select(-julian_date:-biweekly),
+#                                  plot_attr = TB_trawl_taxasite %>% dplyr::select(julian_date:biweekly),
+#                                  coord_names = "biweekly",
+#                                  latlong = FALSE)
 
-S_n = max(group_stats$effort, na.rm = TRUE)
+# trawl_mob_stats = mobr::get_mob_stats(trawl_mob_in, group_var = 'year', index = c("N", "S", "S_asymp", "S_n", "S_PIE", "PIE", "pct_rare"), effort_samples = n_year, extrapolate = TRUE, boot_groups = TRUE, n_perm = nperm)
 
+# group_stats = trawl_mob_stats$groups_stats %>% data.frame
+
+chao1_yr = TB_trawl_taxasite_yr[,-1] %>%
+  apply(., 1, mobr::calc_chao1) %>%
+  bind_cols(TB_trawl_taxasite_yr$year,.) %>%
+  setNames(., c("year","S_asymp")) %>%
+  dplyr::mutate(Date = as.Date(paste0(year,"-01-01"), format = "%Y-%m-%d"))
+
+S_n = min(TB_trawl_sampling$trawl_days, na.rm = TRUE)*n_year
+
+Sn_yr = TB_trawl_taxasite_yr[,-1] %>%
+  apply(., 1, function(x) mobr::rarefaction(x, effort = S_n, method = "IBR", extrapolate = TRUE)) %>%
+  bind_cols(TB_trawl_taxasite_yr$year,.) %>%
+  setNames(., c("year","S_n")) %>%
+  dplyr::mutate(Date = as.Date(paste0(year,"-01-01"), format = "%Y-%m-%d"))
+
+pct_rare =TB_trawl_taxasite_yr[,-1] %>%
+  apply(., 1, function(x) pct_rare(x, 0.05)) %>%
+  bind_cols(TB_trawl_taxasite_yr$year,.) %>%
+  setNames(., c("year","pct_rare")) %>%
+  dplyr::mutate(Date = as.Date(paste0(year,"-01-01"), format = "%Y-%m-%d"))
+
+group_stats = left_join(chao1_yr, Sn_yr) %>%
+  left_join(pct_rare) %>%
+  dplyr::select(Date, year, everything()) %>%
+  group_by(Date, year) %>%
+  pivot_longer(c(S_n,S_asymp,pct_rare),names_to = "index", values_to = "median" ) %>%
+  ungroup
 #
@@
 In total, `r length(unique(TB_trawl_data$Common_name))` unique species were identified and new species were consistently observed throughout the sampling period (Figure 1).
-Within a calendar year, we estimated the asymptotic species richness (*S~asymp~*) which was relatively stable for the first five years (2007 -- 2012), reaching a minimum value of `r group_stats %>% dplyr::filter(index == "S_asymp") %>% slice_min(median) %>% dplyr::select(median) %>% unlist %>% as.numeric %>% round(0)` (`r group_stats %>% dplyr::filter(index == "S_asymp") %>% slice_min(median) %>% dplyr::select(lower) %>% unlist %>% as.numeric %>% round(0)` -- `r group_stats %>% dplyr::filter(index == "S_asymp") %>% slice_min(median) %>% dplyr::select(upper) %>% unlist %>% as.numeric %>% round(0)`) in `r group_stats %>% dplyr::filter(index == "S_asymp") %>% slice_min(median) %>% dplyr::select(group)`.
-Estimated *S~asymp~* increased in 2013 to a series maximum of `r group_stats %>% dplyr::filter(index == "S_asymp") %>% slice_max(median) %>% dplyr::select(median) %>% unlist %>% as.numeric %>% round(0)` (`r group_stats %>% dplyr::filter(index == "S_asymp") %>% slice_max(median) %>% dplyr::select(lower) %>% unlist %>% as.numeric %>% round(0)` -- `r group_stats %>% dplyr::filter(index == "S_asymp") %>% slice_max(median) %>% dplyr::select(upper) %>% unlist %>% as.numeric %>% round(0)`) in `r group_stats %>% data.frame %>% dplyr::filter(index == "S_asymp") %>% slice_max(median) %>% dplyr::select(group)`.
+Within a calendar year, we estimated the asymptotic species richness (*S~asymp~*) which was relatively stable for the first five years (2007 -- 2012), reaching a minimum value of `r group_stats %>% dplyr::filter(index == "S_asymp") %>% slice_min(median) %>% dplyr::select(median) %>% unlist %>% as.numeric %>% round(0)` in `r group_stats %>% dplyr::filter(index == "S_asymp") %>% slice_min(median) %>% dplyr::select(year)`.
+Estimated *S~asymp~* increased in 2013 to a series maximum of `r group_stats %>% dplyr::filter(index == "S_asymp") %>% slice_max(median) %>% dplyr::select(median) %>% unlist %>% as.numeric %>% round(0)` in `r group_stats %>% data.frame %>% dplyr::filter(index == "S_asymp") %>% slice_max(median) %>% dplyr::select(year)`.
 However, given the large differences in effort among years, variability in *S~asymp~* may be partly attributable to sampling effects among years.
@@
 Here, effort-controlled species richness, *S~`r S_n`~*, diverged qualitatively from *S~asymp~* and was generally constant with an apparent slight increase in more recent sampling years.
-Overall, *S~`r S_n`~* ranged from `r group_stats %>% dplyr::filter(effort > 100) %>% slice_min(median) %>% dplyr::select(median) %>% round(1)` (`r group_stats %>% dplyr::filter(effort > 100) %>% slice_min(median) %>% dplyr::select(lower) %>% round(1)` -- `r group_stats %>% dplyr::filter(effort > 100) %>% slice_min(median) %>% dplyr::select(upper) %>% round(1)`) to `r group_stats %>% dplyr::filter(effort > 100) %>% slice_max(median) %>% dplyr::select(median) %>% round(1)` (`r group_stats %>% dplyr::filter(effort > 100) %>% slice_max(median) %>% dplyr::select(lower) %>% round(1)` -- `r group_stats %>% dplyr::filter(effort > 100) %>% slice_max(median) %>% dplyr::select(upper) %>% round(1)`) (Figure 1).
+Overall, *S~`r S_n`~* ranged from `r group_stats %>% dplyr::filter(index == "S_n") %>% slice_min(median) %>% dplyr::select(median) %>% round(1)` to `r group_stats %>% dplyr::filter(index == "S_n") %>% slice_max(median) %>% dplyr::select(median) %>% round(1)` (Figure 1).
 
@@
   dplyr::filter(year %ni% c("2020","2021")) %>%
-  dplyr::filter(!duplicated(Common_name, nmax = (total_richness) )) %>%
+  dplyr::filter(!duplicated(Common_name )) %>%
   dplyr::mutate(Date = as.Date(Date)) %>%
@@
   dplyr::select(Date, year, richness) %>%
-  mutate(data_type = 'continuous',
-         r_lower = NA_real_,
-         r_upper = NA_real_) %>%
+  mutate(data_type = 'continuous') %>%
   bind_rows(TB_annual_accum %>% 
-              mutate(data_type = "ann_raw",
-                     r_lower = NA_real_,
-                     r_upper = NA_real_)) %>%
+              mutate(data_type = "ann_raw")) %>%
   bind_rows(group_stats %>% 
-              dplyr::filter(effort > 100) %>%
-              dplyr::select(year ='group', richness = 'median', r_lower = 'lower', r_upper = 'upper') %>%
-              dplyr::mutate(year = as.numeric(as.character(year)),
-                            Date = as.Date(paste(year,"01","01", sep = "-"), format = "%Y-%m-%d"),
-                            data_type = "rarefied")) %>%
+              dplyr::filter(index == "S_n") %>%
+              dplyr::select(Date, year, richness = 'median') %>%
+              dplyr::mutate(data_type = "rarefied")) %>%
   bind_rows(group_stats %>% 
               dplyr::filter(index == 'S_asymp') %>%
-              dplyr::select(year ='group', richness = 'median', r_lower = 'lower', r_upper = 'upper') %>%
-              dplyr::mutate(year = as.numeric(as.character(year)),
-                            Date = as.Date(paste(year,"01","01", sep = "-"), format = "%Y-%m-%d"),
-                            data_type = "ann_asymp")) %>%
+              dplyr::select(Date, year, richness = 'median') %>%
+              dplyr::mutate(data_type = "ann_asymp")) %>%
   dplyr::mutate(data_type = factor(data_type, levels = c("continuous", "rarefied", "ann_raw", "ann_asymp"))) %>%
@@
   ggplot(TB_time_df, aes(x = Date, y = richness, group = data_type)) +
-  geom_ribbon(data = TB_time_df %>%
-                dplyr::filter(data_type == "ann_asymp"),
-              aes(x = Date, ymin = r_lower, ymax= r_upper),
-              color = viridis(n = 3, alpha = c(1,1,1), option = 'viridis')[3],
-              fill = viridis(n = 3, alpha = c(1,1,0.1), option = 'viridis')[3],
-              inherit.aes = FALSE)+
-  geom_ribbon(data = TB_time_df %>%
-                dplyr::filter(data_type == "rarefied"),
-              aes(x = Date, ymin = r_lower, ymax= r_upper),
-              color = viridis(n = 3, alpha = c(1,1,1), option = 'viridis')[2],
-              fill = viridis(n = 3, alpha = c(1,0.2,1), option = 'viridis')[2],
-              inherit.aes = FALSE)+
   geom_segment(data = TB_time_df %>% 
@@
   geom_line(data = TB_time_df %>% dplyr::filter(!grepl('ann_asymp', data_type)), aes(colour = data_type),size = 1.2) +
-  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +
+  scale_x_date(date_breaks = "1 year", date_labels = "%Y",limits = c(as.Date("2007-01-01"),as.Date("2019-06-01"))) +
   scale_y_continuous(name = "Species Richness")+
@@
         # axis.title.x = element_blank(), axis.text.x = element_blank(),
-        legend.spacing.y = unit(-0.1, 'cm'))+
-  scale_x_date(date_breaks = 'year', limits = c(as.Date("2007-01-01"),as.Date("2019-06-01")),
-               date_labels = "%Y")
+        legend.spacing.y = unit(-0.1, 'cm'))
 
@@
 
-```{r turnover plot ,echo = FALSE, warning=FALSE, message=FALSE, fig.cap = "Figure 2. Total species "}
+```{r turnover plot ,echo = FALSE, warning=FALSE, message=FALSE, fig.cap = "Figure 2. Total species turnover and partitioning"}
 trawl_yr_turnover %>%
@@
    ) 
+# 
+# annual_evenness_boots = boot_gini_groups(TB_trawl_taxasite %>% dplyr::select(-julian_date,-Date,-month,-biweekly), 
+#                                 group_var = 'year',
+#                                 n_perm = nperm)
+# 
+# annual_evenness_df = annual_evenness_boots %>%
+#   dplyr::select(-boot_id) %>%
+#   pivot_longer(-year, names_to = 'measure', values_to = 'value') %>%
+#   group_by(year,measure) %>%
+#   dplyr::summarise(across(value, list(mean = ~mean(.x, na.rm = TRUE),
+#                                       median = ~quantile(.x, 0.5, na.rm = TRUE),
+#                                       quant2.5= ~quantile(.x, 0.025, na.rm = TRUE),
+#                                       quant25= ~quantile(.x, 0.25, na.rm = TRUE),
+#                                       quant75= ~quantile(.x, 0.75, na.rm = TRUE),
+#                                       quant97.5= ~quantile(.x, 0.975, na.rm = TRUE)), .names = "{.fn}")) %>%
+#   dplyr::mutate(Date = as.Date(paste(year,"01","01", sep = "-"), format = "%Y-%m-%d")) %>%
+#   ungroup
 
-annual_evenness_boots = boot_gini_groups(TB_trawl_taxasite %>% dplyr::select(-julian_date,-Date,-month,-biweekly), 
-                                group_var = 'year',
-                                n_perm = nperm)
-
-annual_evenness_df = annual_evenness_boots %>%
-  dplyr::select(-boot_id) %>%
-  pivot_longer(-year, names_to = 'measure', values_to = 'value') %>%
-  group_by(year,measure) %>%
-  dplyr::summarise(across(value, list(mean = ~mean(.x, na.rm = TRUE),
-                                      median = ~quantile(.x, 0.5, na.rm = TRUE),
-                                      quant2.5= ~quantile(.x, 0.025, na.rm = TRUE),
-                                      quant25= ~quantile(.x, 0.25, na.rm = TRUE),
-                                      quant75= ~quantile(.x, 0.75, na.rm = TRUE),
-                                      quant97.5= ~quantile(.x, 0.975, na.rm = TRUE)), .names = "{.fn}")) %>%
+annual_evenness_df = TB_trawl_taxasite_yr %>%
+  dplyr::select(-year) %>%
+  apply(., 1, gini_even) %>%
+      t() %>%
+      data.frame() %>%
+      bind_cols(TB_trawl_taxasite_yr$year, .) %>%
+      setNames(., c("year", "gini_raw", "gini_norm")) %>%
+  pivot_longer(-year, names_to = "measure", values_to = "median") %>%
   dplyr::mutate(Date = as.Date(paste(year,"01","01", sep = "-"), format = "%Y-%m-%d")) %>%
@@
 
-Species turnover was likley confined to species with moderate to low relative abundances.
+Species turnover was likely confined to species with moderate to low relative abundances.
 The effective number of highly abundant species, *^2^D*, was variable but stable through time with calculated values *ca.* `r qD_df %>% dplyr::filter(q_order == 'q2') %>% dplyr::summarise(across(median, ~median(.x ,na.rm = TRUE))) %>% round(2)` $\pm$ `r qD_df %>% dplyr::filter(q_order == 'q2') %>% dplyr::summarise(across(median, ~sd(.x, na.rm = TRUE))) %>% round(1)` (mean $\pm$ 1 SD) (range: `r qD_df %>% dplyr::filter(q_order == 'q2')%>% slice_min(median) %>% dplyr::select(median) %>% round(2)` to  `r qD_df %>% dplyr::filter(q_order == 'q2') %>% slice_max(median) %>% dplyr::select(median) %>% round(1)`; Figure 3 __*supplemental?*__).
-In contrast, the percentage of rare species increased through time from `r rarity %>% slice_min(group) %>% dplyr::select(median) %>% round(2)` (`r rarity %>% slice_min(group) %>% dplyr::select(lower) %>% round(2)` -- `r rarity %>% slice_min(group) %>% dplyr::select(upper) %>% round(2)`, 95% percentile interval [PI]) to `r rarity %>% slice_max(group) %>% dplyr::select(median) %>% round(2)` `r rarity %>% slice_max(group) %>% dplyr::select(lower) %>% round(2)` -- `r rarity %>% slice_max(group) %>% dplyr::select(upper) %>% round(2)`, 95% PI; Figure 3A).
-Additionally, the normalized evenness in species relative abundances showed a consistent decline through time from a median value of `r annual_evenness_df %>% dplyr::filter(measure == 'gini_norm') %>% slice_min(Date) %>% dplyr::select(median) %>% round(2)` in `r min(annual_evenness_df$year,na.rm = TRUE)` (`r annual_evenness_df %>% dplyr::filter(measure == 'gini_norm') %>% slice_min(Date) %>% dplyr::select(quant2.5) %>% round(2)` -- `r annual_evenness_df %>% dplyr::filter(measure == 'gini_norm') %>% slice_min(Date) %>% dplyr::select(quant97.5) %>% round(2)`, 95% PI) to `r annual_evenness_df %>% dplyr::filter(measure=='gini_norm') %>% slice_max(Date) %>% dplyr::select(median) %>% round(2)` (`r annual_evenness_df %>% dplyr::filter(measure == 'gini_norm') %>% slice_max(Date) %>% dplyr::select(quant2.5) %>% round(2)` -- `r annual_evenness_df %>% dplyr::filter(measure == 'gini_norm') %>% slice_max(Date) %>% dplyr::select(quant97.5) %>% round(2)`, 95% PI) in `r max(annual_evenness_df$year, na.rm = TRUE)`.
+In contrast, the percentage of rare species increased slightly through time from `r rarity %>% slice_min(year) %>% dplyr::select(median) %>% round(2)` to `r rarity %>% slice_max(year) %>% dplyr::select(median) %>% round(2)`.
+Additionally, the evenness in species abundances showed a clear decline through time from a median value of `r annual_evenness_df %>% dplyr::filter(measure == 'gini_norm') %>% slice_min(Date) %>% dplyr::select(median) %>% round(2)` in `r min(annual_evenness_df$year,na.rm = TRUE)` to `r annual_evenness_df %>% dplyr::filter(measure=='gini_norm') %>% slice_max(Date) %>% dplyr::select(median) %>% round(2)` in `r max(annual_evenness_df$year, na.rm = TRUE)`.
 
@@
 Temporal trends in order of diversity q = 2, ^2^D highlight relative stability in the number of dominant species in the community through time.
-^2^D is equivalent to 1/Simpson's diversity index and captures the effective number of highly abundant species in the community."}
+^2^D is equivalent to 1/Simpson's diversity index and captures the effective number of highly abundant species in the community.", include=FALSE}
 qD_df %>%
@@
 
-```{r evenness, echo = FALSE, warning=FALSE, message=FALSE, fig.cap= "Figure 4." }
+```{r evenness, echo = FALSE, warning=FALSE, message=FALSE, fig.cap= "Figure 4. Species rarity and evenness in relative abundances through the data series." }
 
 annual_evenness_df %>%
-  dplyr::filter(measure == 'gini_raw') %>%
+  dplyr::filter(measure == 'gini_norm') %>%
   ggplot()+
-  geom_ribbon(aes(x = Date, ymin = quant2.5, ymax = quant97.5), alpha = 0.3) +
+  # geom_ribbon(aes(x = Date, ymin = quant2.5, ymax = quant97.5), alpha = 0.3) +
   geom_line(aes(x = Date, y = median), size = 1.1) +
   geom_point(aes(x = Date, y = median), shape = 22, size = 3)+
-  scale_y_continuous(name = "Normalized Gini coefficient", limits = c(0,NA), expand = c(0.01,0.01))+
+  scale_y_continuous(name = "Normalized Gini coefficient", limits = c(0,0.2), expand = c(0.01,0.01))+
   scale_x_date(date_breaks = 'year', limits = c(as.Date("2007-01-01"),as.Date("2019-06-01")),
@@
   dplyr::filter(index == "pct_rare") %>%
-  dplyr::mutate(group = as.Date(group, format = "%Y")) %>%
+  dplyr::mutate(year = as.Date(year, format = "%Y")) %>%
   ggplot()+
-  geom_point(aes(x =group, y = median), size = 3, shape = 22)+
-  geom_path(aes(x = group, y = median), size = 1.1)+
-  geom_ribbon(aes(x = group, ymin = lower, ymax = upper), alpha = 0.3)+
-  scale_y_continuous(name = "Percent rare species (%)", limits = c(70,100), expand = c(0.01,0.01))+
+  geom_point(aes(x =Date, y = median), size = 3, shape = 22)+
+  geom_path(aes(x = Date, y = median), size = 1.1)+
+  scale_y_continuous(name = "Percent rare species (%)", limits = c(75 ,100), expand = c(0.01,0.01))+
   scale_color_manual(values = viridis(n =1, option = 'viridis' ))+
@@
 
+```{r evenness profile, echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Figure 5.
+Species evenness profiles based on Hill numbers relative to annual species richness.
+^0^D is equal to the total number of species"}
+TB_trawl_yr_evenness = TB_trawl_taxasite_yr %>%
+  split(., seq(1:nrow(.))) %>%
+  purrr::map(~new_fun(.x, seq(0,4,0.1), "E3")) %>%
+  setNames(., nm = TB_trawl_taxasite_yr$year) %>%
+  purrr::map(function(a) a %>% t %>% data.frame %>%
+               setNames(., nm = seq(0,4,0.1))) %>%
+          bind_rows(.id = 'year') %>%
+  pivot_longer(-year, names_to = 'q', values_to = 'eff_spp') %>%
+  dplyr::mutate(Date = as.Date(paste0(year,"-01-01"), format = "%Y-%m-%d")) %>%
+  dplyr::mutate(across(q, as.numeric))
+
+TB_trawl_q1_plot =
+  TB_trawl_yr_evenness %>%
+  dplyr::filter(q == 1) %>%
+  ggplot()+
+  geom_line(aes(x = Date, y = eff_spp))+
+  scale_y_continuous(name = 'Eff. Species (%)', limits = c(0,0.2))+
+  scale_x_date(breaks = as.Date(c("2007-01-01","2013-01-01","2019-01-01"),format = "%Y-%m-%d"),
+               date_labels = "%Y")+
+  theme(axis.title.x = element_blank())+
+  annotate('text', x = as.Date(Inf), y = as.Date(Inf), label = expression(italic(""^1*D)), size =5,
+           hjust = 1, vjust = 1)
+
+TB_trawl_q2_plot =
+  TB_trawl_yr_evenness %>%
+  dplyr::filter(q == 2) %>%
+  ggplot()+
+  geom_line(aes(x = Date, y = eff_spp))+
+  scale_y_continuous(name = 'Eff. Species (%)', limits = c(0,0.15))+
+  scale_x_date(breaks = as.Date(c("2007-01-01","2013-01-01","2019-01-01"),format = "%Y-%m-%d"),
+               date_labels = "%Y")+
+  theme(axis.title.x = element_blank(),
+        axis.title.y = element_blank())+
+  annotate('text', x = as.Date(Inf), y = as.Date(Inf), label = expression(italic(""^2*D)), size =5,
+           hjust = 1, vjust = 1)
+
+TB_trawl_yr_evenness %>%
+  ggplot() +
+  geom_path(aes(x = q, y = eff_spp, group = year, color = year), size = 1.1)+
+  scale_y_continuous(name = 'Effective species (%)', limits = c(0,1), expand = c(0.01,0.01))+
+  scale_x_continuous(name = expression(italic(""^q*D)), limits = c(0,3), expand = c(0.02,0.02)) +
+  scale_color_manual(values = viridis(n = 12, option = 'viridis')) +
+  annotation_custom(
+    ggplotGrob(TB_trawl_q1_plot),
+    xmin = 0.75, xmax = 1.9, ymin = 0.5, ymax = 1
+  )+
+  annotation_custom(
+    ggplotGrob(TB_trawl_q2_plot),
+    xmin = 2, xmax = 3, ymin = 0.5, ymax = 1
+  )+
+  theme(legend.title = element_blank(),
+        legend.position = 'top')+
+  guides(color=guide_legend(nrow=2,byrow=TRUE))
+
+```
+
 # Discussion

### 2021-08-08 analyses/trawl/R/Evenness.R

@@ -195,91 +195,7 @@ draw_dis_spe <- function(data, title_name, type = "tax"){
   return(g)
 }
 
-######plot tree (see the phylogenetic tree in Figure 1)#### 
-plot.phylog <- function (x, y = NULL,
-                         f.phylog = 0.5, cleaves = 1, cnodes = 0,
-                         labels.leaves = names(x$leaves), clabel.leaves = 1,
-                         labels.nodes = names(x$nodes), clabel.nodes = 0,
-                         sub = "", csub = 1.25, possub = "bottomleft", draw.box = FALSE, ...)
-{
-  if (!inherits(x, "phylog")) 
-    stop("Non convenient data")
-  leaves.number <- length(x$leaves)
-  leaves.names <- names(x$leaves)
-  nodes.number <- length(x$nodes)
-  nodes.names <- names(x$nodes)
-  if (length(labels.leaves) != leaves.number) labels.leaves <- names(x$leaves)
-  if (length(labels.nodes) != nodes.number) labels.nodes <- names(x$nodes)
-  leaves.car <- gsub("[_]"," ",labels.leaves)
-  nodes.car <- gsub("[_]"," ",labels.nodes)
-  mar.old <- par("mar")
-  on.exit(par(mar=mar.old))
-  
-  par(mar = c(0.1, 0.1, 0.1, 0.1))
-  
-  if (f.phylog < 0.05) f.phylog <- 0.05 
-  if (f.phylog > 0.95) f.phylog <- 0.95 
-  
-  maxx <- max(x$droot)
-  plot.default(0, 0, type = "n", xlab = "", ylab = "", xaxt = "n", 
-               yaxt = "n", xlim = c(-maxx*0.15, maxx/f.phylog), ylim = c(-0.05, 1), xaxs = "i", 
-               yaxs = "i", frame.plot = FALSE)
-  
-  x.leaves <- x$droot[leaves.names]
-  x.nodes <- x$droot[nodes.names]
-  if (is.null(y)) y <- (leaves.number:1)/(leaves.number + 1)
-  else y <- (leaves.number+1-y)/(leaves.number+1)
-  names(y) <- leaves.names
-  xcar <- maxx*1.05
-  xx <- c(x.leaves, x.nodes)
-  
-  if (clabel.leaves > 0) {
-    for (i in 1:leaves.number) {
-      text(xcar, y[i], leaves.car[i], adj = 0, cex = par("cex") * 
[…]

### 2021-08-08 analyses/trawl/R/analyze_rarefaction.R

@@ -49,15 +49,27 @@ full_stats = mobr::calc_biodiv(TB_trawl_taxasite %>% dplyr::select(-julian_date:
 
 ## Run the mobr to estimate w
 
+## Estimated mobr for biweekly  for all communities
+TB_trawl_biweekly = TB_trawl_data %>%
+  # exclude 2020 & 2021
+  dplyr::filter(year %ni% c("2020","2021")) %>%
+  dplyr::mutate(julian_date = julian(Date, origin = as.Date("2007-01-05")),
+                biweekly = ceiling(julian_date/14)) %>%
+  group_by(year,biweekly, Common_name) %>%
+  dplyr::summarise(Abundance = sum(Abundance, na.rm = TRUE)) %>%
+  group_by(year,biweekly) %>%
+  pivot_wider( names_from = 'Common_name', values_from = 'Abundance', values_fill = 0) %>%
+  ungroup 
 
 
-
-trawl_mob_in = mobr::make_mob_in(comm = TB_trawl_taxasite %>% dplyr::select(-julian_date:-biweekly),
-                                 plot_attr = TB_trawl_taxasite %>% dplyr::select(julian_date:biweekly),
-                                 coord_names = "julian_date",
+trawl_mob_in = mobr::make_mob_in(comm = TB_trawl_biweekly %>% dplyr::select(-biweekly),
+                                 plot_attr = TB_trawl_biweekly %>% dplyr::select(year,biweekly),
+                                 coord_names = "biweekly",
                                  latlong = FALSE)
 
-mobr::plot_rarefaction(trawl_mob_in, group_var = 'year', method = 'sSBR', )
+
+x = mobr::plot_rarefaction(trawl_mob_in, group_var = 'year', method = 'sSBR')
+  scale_color_manual(values = viridis(n = 12, option ='viridis'))
 
 trawl_mob_stats = mobr::get_mob_stats(trawl_mob_in, group_var = 'year', index = c("N", "S", "S_asymp", "S_n", "S_PIE", "PIE"), effort_samples = n_year, extrapolate = TRUE, boot_groups = TRUE, n_perm = 199)
 # trawl_mob_stats = mobr::get_mob_stats(trawl_mob_in, group_var = 'year', index = c("N", "S", "S_asymp", "S_n", "S_PIE", "PIE"), extrapolate = TRUE)
[…]

### 2021-08-08 analyses/trawl/R/full_analyses.R

@@ -1,7 +1,8 @@
 # full analysis
 source(here::here('datascript.R'))
 source(here::here("analyses/trawl/R/Lorenz.R"))
-library(hillR)
+source(here::here("analyses/trawl/R/Evenness.R"))
+
 nperm = 99
 
 add_row_2008 = data.frame(Date = as.Date("2008-01-01"))
@@ -19,7 +20,7 @@ TB_trawl_taxasite <- TB_trawl_data %>%
   pivot_wider(names_from = Common_name, values_from = Abundance, values_fill = list(Abundance = 0)) %>%
   ungroup() %>%
   dplyr::mutate(julian_date = julian(Date, origin = as.Date("2007-01-05")),
-                biweekly = ceiling(julian_date/30),
+                biweekly = ceiling(julian_date/14),
                 month = month(Date),
                 year = year(Date)) %>%
   dplyr::select(julian_date, Date,year, month, biweekly, everything())
@@ -122,6 +123,11 @@ TB_trawl_data %>%
   ungroup %>%
   # dplyr::mutate(time.var = 1:n()) %>%
   pivot_longer(c(-year), names_to = 'Common_name', values_to = 'Abundance')-> TB_trawl_yr
+
+TB_trawl_taxasite_yr = TB_trawl_yr %>%
+  group_by(year) %>%
+  pivot_wider(names_from = Common_name, values_from = Abundance) %>%
+  dplyr::select(-Minnow, -`Sygnathus Scovelli`)
   
 trawl_yr_turnover_list = purrr::map(c('appearance','disappearance','total'),
                                      ~codyn::turnover(df = TB_trawl_yr,
@@ -161,10 +167,65 @@ TB_trawl_taxasite <- TB_trawl_data %>%
   dplyr::select(julian_date, Date,year, month, biweekly, everything())
 
 ## Estimated qD = 2 for all communities
-biweekly_sampling = TB_trawl_taxasite %>%
+TB_trawl_biweekly = TB_trawl_data %>%
+  # exclude 2020 & 2021
+  dplyr::filter(year %ni% c("2020","2021")) %>%
+  dplyr::mutate(julian_date = julian(Date, origin = as.Date("2007-01-05")),
+                biweekly = ceiling(julian_date/14)) %>%
[…]

### 2021-08-08 analyses/trawl/R/old/trawl_Kmeans.R

@@ -1,7 +1,9 @@
+BiocManager::install("ggtree")
+
 #trawl K-means analysis of fish data
 # create taxa by site matrix with common names
 TB_trawl_commonsite <- TB_trawl_data %>%
-  select(year, month, date_id, Common_name) %>%
+  dplyr::select(year, month, date_id, Common_name) %>%
   group_by(date_id, Common_name) %>%
   distinct() %>% 
   mutate(pres = 1) %>%
@@ -16,7 +18,7 @@ TB_trawl_outlier_rm <- TB_trawl_commonsite %>%
 ###Legendre PC with Hellinger
 
 #Hellinger pre-transformation of the species matrix
-tb.h <- decostand (TB_trawl_outlier_rm %>% select(-c(1:2)) %>% column_to_rownames("date_id"), "hellinger")
+tb.h <- decostand (TB_trawl_outlier_rm %>% dplyr::select(-c(1:2)) %>% column_to_rownames("date_id"), "hellinger")
 tb.h.pca <- rda(tb.h)
 tb.h.pca.summ <- summary(tb.h.pca)
 
@@ -72,7 +74,7 @@ ggplot(data = TB, aes(x=PC1, y=PC2, color=as.factor(year))) +
   scale_colour_viridis(discrete = TRUE)
 
 ###Cluster Analysis
-spe <- TB_trawl_outlier_rm %>% select(-c(1:2)) %>% column_to_rownames("date_id")
+spe <- TB_trawl_outlier_rm %>% dplyr::select(-c(1:2)) %>% column_to_rownames("date_id")
 spe.norm <- decostand(spe, "normalize")
 spe.ch <- vegdist(spe.norm, "euc") 
 

### 2021-08-08 analyses/trawl/R/old/trawl_LDATS.R

@@ -15,10 +15,15 @@ r_LDATS <- LDA_TS(rodents, topics = 2:5, nseeds = 2, formulas = ~1, nchangepoint
 TB_trawl_taxasite <- TB_trawl_data %>%
   dplyr::select(Date, Common_name, Abundance) %>%
   group_by(Date, Common_name) %>%
-  summarise(Abundance = sum(Abundance)) %>%
+  summarise(Abundance = sum(Abundance, na.rm = TRUE)) %>%
+  dplyr::filter(year(Date) %ni% c("2020","2021")) %>%
+  # dplyr::filter(sum(Abundance) > 10) %>%
   na.omit %>%
   pivot_wider(names_from = Common_name, values_from = Abundance, values_fill = list(Abundance = 0)) %>%
+  dplyr::select(-Minnow, -`Sygnathus Scovelli`) %>%
   ungroup() 
+
+rowSums(TB_trawl_taxasite[,-1], na.rm = TRUE)
 
 seasonal_time <- data.frame(day = 1:365, sin_year = sin(1:365), cos_year = cos(1:365))
 
@@ -38,7 +43,7 @@ TB_LDATS <- list(TB_trawl_taxa, TB_trawl_covariates) %>%
   LDATS::conform_LDA_TS_data(quiet = FALSE)
 
 # debugonce(check_LDA_TS_inputs)
-check_LDA_TS_inputs(TB_LDATS, topics = 2:5, nseeds = 2, formulas = ~time, nchangepoints = 0:1, timename = "time", 
+check_LDA_TS_inputs(TB_LDATS, topics = 1:5, nseeds = 4, formulas = ~time, nchangepoints = 0:1, timename = "time", 
                     weights = TRUE, control = list(quiet = FALSE))
 #should return NULL if everything is okay
 
@@ -47,8 +52,8 @@ lda_model_set <- LDA_set(document_term_table = TB_LDATS$document_term_table,
                          nseeds = 5,
                          control = list(quiet = TRUE))
 
-# saveRDS(lda_model_set, file = "./data/lda_model_set.RDS")
-lda_model_set <- readRDS(file = "./data/lda_model_set.rds")
+saveRDS(lda_model_set, file = "./data/lda_model_set.RDS")
+# lda_model_set <- readRDS(file = "./data/lda_model_set.rds")
 selected_lda_set <- select_LDA(lda_model_set)
[…]

### 2021-08-08 packages.R

@@ -10,88 +10,116 @@ if ("pacman" %in% rownames(installed.packages()) == FALSE) install.packages("pac
 # they are important for running the livedat repository
 # OG package list: pacman::p_load(git2r, httr, semver, testthat, yaml)
 
-pacman::p_load(git2r, httr, semver, testthat, yaml, here, EML, data.table, 
-               RCurl, plyr, tidyverse, furrr, googlesheets4,
-               tictoc, chron, lubridate, httr, TTR, grid,
-               gridExtra, ggridges, iNEXT, vegan, rlist, pipeR,
-               viridis, broom, bbmle, ggthemes, ggeffects, bsts,
-               rfishbase, auk, betapart, plot3D, ncdf4, forecast,
-               taxize, hillR, codyn, gridExtra)
+pacman::p_load(
+  git2r, httr, semver, testthat, yaml, here, EML, data.table,
+  RCurl, plyr, tidyverse, furrr, googlesheets4,
+  tictoc, chron, lubridate, httr, TTR, grid, egg,
+  gridExtra, ggridges, iNEXT, vegan, rlist, pipeR,
+  viridis, broom, bbmle, ggthemes, ggeffects, bsts,
+  rfishbase, auk, betapart, plot3D, ncdf4, forecast,
+  taxize, hillR, codyn, gridExtra, fuzzySim
+)
 
-devtools::install_github(c("jimjunker1/junkR"))#, "ropensci/rfishbase"))
+devtools::install_github(c("jimjunker1/junkR")) # , "ropensci/rfishbase"))
 # library(junkR)
 # devtools::install_github('MoBiodiv/mobr')
 library(mobr)
 
 
-theme_mod <<- function(){theme_bw() %+replace% theme(panel.grid = element_blank())}
-theme_set(theme_mod());rm(theme_mod)
-find_hull <<- function(df) df[chull(df$NMDS1, df$NMDS2),]
+theme_mod <<- function() {
+  theme_bw() %+replace% theme(panel.grid = element_blank())
+}
+theme_set(theme_mod())
+rm(theme_mod)
+find_hull <<- function(df) df[chull(df$NMDS1, df$NMDS2), ]
 
-'%ni%' <<- Negate('%in%')
+"%ni%" <<- Negate("%in%")
 # bootstrapped sampling for estimating variability withing groups
-boot_sample_groups = function(abund_mat, group_var, qD, n_perm,...) {
[…]

### 2021-08-25 sub-projects/trawl/R/Evenness.R
workflow redo fixed links for new workflow.

@@ -1,3 +1,4 @@
+here::i_am("sub-projects/trawl/R/Evenness.R")
 #*******************************************************************************
 #********************************************************************************
 # 

### 2021-08-25 sub-projects/trawl/R/analyze_hill_diversity.R

@@ -4,7 +4,7 @@
 ##'
 ##' @title
 
-here::i_am("analyses/trawl/R/analyze_hill_diversity.R")
+here::i_am("sub-projects/trawl/R/analyze_hill_diversity.R")
 library(hillR)
 
 ##create taxa by site matrix

### 2021-08-25 sub-projects/trawl/R/analyze_rarefaction.R

@@ -1,4 +1,5 @@
 source(here::here('datascript.R'))
+here::i_am("sub-porjects/trawl/R/analyze_rarefaction.R")
 
 ##create taxa by site matrix
 TB_trawl_taxasite <- TB_trawl_data %>%

### 2021-08-25 sub-projects/trawl/R/full_analyses.R

@@ -1,16 +1,16 @@
 # full analysis
 source(here::here('datascript.R'))
-source(here::here("analyses/trawl/R/Lorenz.R"))
-source(here::here("analyses/trawl/R/Evenness.R"))
+source(here::here("sub-projects/trawl/R/Lorenz.R"))
+source(here::here("sub-projects/trawl/R/Evenness.R"))
 
 nperm = 99
 
-add_row_2008 = data.frame(Date = as.Date("2008-01-01"))
+year_removals = c("2007","2020","2021")
 
 ##create taxa by site matrix
 TB_trawl_taxasite <- TB_trawl_data %>%
   dplyr::select(Date, Common_name, Abundance) %>%
-  dplyr::filter(year(Date) %ni% c("2020","2021")) %>%
+  dplyr::filter(year(Date) %ni% year_removals) %>%
   group_by(Date, Common_name) %>%
   summarise(Abundance = sum(Abundance)) %>%
   na.omit %>% group_by(Date) %>%
@@ -19,7 +19,7 @@ TB_trawl_taxasite <- TB_trawl_data %>%
   group_by(Date, Common_name) %>%
   pivot_wider(names_from = Common_name, values_from = Abundance, values_fill = list(Abundance = 0)) %>%
   ungroup() %>%
-  dplyr::mutate(julian_date = julian(Date, origin = as.Date("2007-01-05")),
+  dplyr::mutate(julian_date = julian(Date, origin = as.Date("2009-01-01")),
                 biweekly = ceiling(julian_date/14),
                 month = month(Date),
                 year = year(Date)) %>%
@@ -27,7 +27,7 @@ TB_trawl_taxasite <- TB_trawl_data %>%
 
 ## check sample-level statistics
 TB_trawl_sampling = TB_trawl_data %>%
-  dplyr::filter(year(Date) %ni% c("2020","2021")) %>%
+  dplyr::filter(year(Date) %ni% year_removals) %>%
   dplyr::select(Date, year, Common_name, Abundance) %>%
   group_by(year) %>%
   dplyr::summarise(trawl_days = length(unique(Date)),
@@ -49,7 +49,7 @@ total_richness = length(unique(TB_trawl_data$Common_name));
 # create time data frame to calculate accumulation of different species abundances over time
 TB_trawl_data %>%
[…]

### 2021-08-25 sub-projects/trawl/R/trawl_specaccum.R

@@ -1,4 +1,6 @@
 source(here::here('datascript.R'))
+here::i_am('sub-projects/trawl/R/trawl_specaccum.R')
+
 # Full species accumulation curve (SAC)
 
 ##create taxa by site matrix

### 2021-08-25 sub-projects/trawl/docs/ms/ms.RMD

--- 2021-08-08 docs/ms/ms.RMD
@@
 ```{r Rmarkdown setup, include = FALSE, echo=F, warning=FALSE, message=FALSE}
+here::i_am("sub-projects/trawl/docs/ms/ms.RMD")
 
 source(here::here("datascript.R"))
-source(here::here("analyses/trawl/R/Lorenz.R"))
-source(here::here("analyses/trawl/R/Evenness.R"))
+source(here::here("sub-project/trawl/R/Lorenz.R"))
+source(here::here("sub-projects/trawl/R/Evenness.R"))
 
 TB_trawl_data = TB_trawl_data %>%
-   dplyr::filter(year %ni% c("2020","2021"))
+   dplyr::filter(year %ni% c("2007","2020","2021"))
 
@@
 We measured multiple aspects of species richness, first to track the uncorrected accumulation of species over time we filtered species from the data set after first occurrence.
-We then aggregated all trawls within a calendar year and calculated two measures of species richness, accounting for differences in sampling effort among years.
+We then calculated two measures of species richness, accounting for differences in abundance among trawls.
 The first measure was asymptotic species richness, *S~asymp~*, using the Chao1 estimator [@chao1984][@chao1987].
-This metric is highly correlated with measured richness, *S* [@mcgill2011], but attempts to extrapolate the total species richness based on incomplete sampling.
-Second, we attempted to account for differences in effort among years by estimating the effort-controlled rarefied species richness, *S~n~*, which provides the expected number of species given a defined number of *n* individuals sampled [@gotelli2001].
-*S~n~* estimates for yearly aggregated data, *n* was calculated by the minimum number of trawls within a year multiplied by `r n_year`.
+This metric is highly correlated with measured richness, *S* [@mcgill2011], but attempts to extrapolate the total species richness based on incomplete sampling of the community.
+Second, we estimated effort-controlled rarefied species richness, *S~n~*, which provides the expected number of species given a defined number of *n* individuals sampled [@gotelli2001].
+For *S~n~* estimates for trawls, *n* was calculated by the minimum number of individuals within a trawl multiplied by `r n_year`.
 We calculated *S~asymp~* and *S~n~* using the mobr package [@mcglinn2019][@mcglinn2021a].
@@
 TB_trawl_sampling = TB_trawl_data %>%
-  # exclude 2020 & 2021
-  dplyr::filter(year %ni% c("2020","2021")) %>%
    dplyr::select(Date, year, Common_name, Abundance) %>%
@@
 TB_trawl_taxasite <- TB_trawl_data %>%
-  # exclude 2020 & 2021
-  dplyr::filter(year %ni% c("2020","2021")) %>%
+
   dplyr::select(Date, Common_name, Abundance) %>%

### 2021-11-18 sub-projects/trawl/docs/ms/ms.RMD
new workflow and progress on manuscript

@@
 ---
-title: "Manuscript title here"
+title: "A decade of biodiversity change in an estuarine assemblage: fits and starts and natural events"
 author:
-- name: James R Junker
-  affiliation: Louisiana Universities Marine Consortium
+   - James R Junker:
+     email: james.junker1@gmail.com
+     institute: [glrc, lumcon]
+     correspondence: yes
+   - Craig R McClain:
+     institute: lumcon
+institute:
+   - glrc: Great Lakes Research Center, Michigan Technological University, Houghton, MI USA
+   - lumcon: Louisiana Universities Marine Consortium, Chauvin, LA USA
 output:
    word_document:
-     reference_docx: docx_template.docx
+      reference_docx: working_docx_template.docx
+      toc: no
+      pandoc_args:
+      - '--lua-filter=scholarly-metadata.lua'
+      - '--lua-filter=author-info-blocks.lua'
    pdf_document:
@@
    html_document: default
+   pandoc_args:
+      - '--lua-filter=scholarly-metadata.lua'
+      - '--lua-filter=author-info-blocks.lua'
 header-includes:
@@
 - \usepackage{amsmath}
+- \usepackage{indentfirst}
 - \linenumbers
+indent: true
 linestretch: 1
@@
 ---
+
 ```{r Rmarkdown setup, include = FALSE, echo=F, warning=FALSE, message=FALSE}
@@
 source(here::here("datascript.R"))
-source(here::here("sub-project/trawl/R/Lorenz.R"))
+source(here::here("sub-projects/trawl/R/Lorenz.R"))
 source(here::here("sub-projects/trawl/R/Evenness.R"))
+# which years should we remove
+year_removals = c("2007","2020","2021")
 
+# create the base data set
 TB_trawl_data = TB_trawl_data %>%
-   dplyr::filter(year %ni% c("2007","2020","2021"))
+   dplyr::filter(year %ni% year_removals)
+
+TB_trawl_taxasite <- TB_trawl_data %>%
+  dplyr::filter(year(Date) %ni% year_removals) %>%
+  dplyr::mutate(Date = as.Date(paste0(as.character(year),"-",as.character(month),"-01"))) %>%
+  dplyr::select(Date, date_id, Common_name, Abundance) %>%
+  group_by(Date, date_id, Common_name) %>%
+  summarise(Abundance = sum(Abundance)) %>%
+  na.omit %>% group_by(Date, date_id, Common_name) %>%
+  # # remove trawls with less than 10 individuals 
+  # dplyr::filter(sum(Abundance) >=10) %>%
+  # group_by(Date, date_id, Common_name) %>%
+  pivot_wider(names_from = Common_name, values_from = Abundance, values_fill = list(Abundance = 0)) %>%
+  ungroup() %>%
+  dplyr::select(Date, date_id, everything())
+
+TB_trawl_taxasite_long = TB_trawl_taxasite %>%
+  pivot_longer(-Date:-date_id, names_to = "Common_name", values_to = "Abundance")
+
+# # create bootstrapped data set to estimate variability
+# TB_trawl_boots = TB_trawl_data %>%
+#   group_by(year) %>%
+#   modelr::bootstrap(TB_trawl_data)
 
@@
 ## how many individuals for count for Sn, Sn = 18 * n_year
-n_year = 50
+n_mth = 2
+#
 
@@
 
-Anthropogenic activities continue to exert long-term, varied, and increasing pressures on ecosystems causing alterations to biological diversity on broad and local scales.
-Shifts in biodiversity are variable, nuanced and difficult to predict.
-Yet, understanding how communities change through time is crucial for predicting current and future changes to biological systems and the services they provide.
-Explaining the extent and pace of biodiversity change will require identifying the conditions that lead to divergent biological responses, e.g., whether change happens gradually or abruptly and through individual versus cohesive species responses.
+Anthropogenic activities continue to exert long-term, varied, and increasing pressures on marine ecosystems causing alterations to biological diversity on broad and local scales.
+Shifts in biodiversity are variable, nuanced and difficult to predict, yet, understanding how communities change through time is crucial for predicting current and future changes to biological systems and the services they provide.
+We document a decade of biodiversity change in a shallow estuarine nekton community...
 
@@
 Individual trawls were conducted using *trawl apparatus description...* for 10 - 20 min.
-When multiple trawls were conducted on a single day, species counts were summed across all trawls...
+To minimize the effects of trawl-to-trawl variability, we combined all trawls monthly.
 
@@
 Species names were checked for typos and confirmed using the *gni_parse* function from the *taxize* package [@chamberlain2020] and further standardized to consistent taxonomic resolution for entire data series (Supplemental materials).
-We measured multiple aspects of species richness, first to track the uncorrected accumulation of species over time we filtered species from the data set after first occurrence.
-We then calculated two measures of species richness, accounting for differences in abundance among trawls.
-The first measure was asymptotic species richness, *S~asymp~*, using the Chao1 estimator [@chao1984][@chao1987].
+To track trends in species richness through time, we calculated  effort-controlled  species richness, *S~n~*, which provides the expected number of species given a defined number of *n* randomly sampled individuals [@gotelli2001].
+For annual and monthly *S~n~* calculations, *n* was set as the minimum number of individuals sampled.
+We also calculated the uncorrected accumulation of species over time by filtering species from the data set after first occurrence.
+We then calculated asymptotic species richness, *S~asymp~*, using the Chao1 estimator [@chao1984; @chao1987].
 This metric is highly correlated with measured richness, *S* [@mcgill2011], but attempts to extrapolate the total species richness based on incomplete sampling of the community.
-Second, we estimated effort-controlled rarefied species richness, *S~n~*, which provides the expected number of species given a defined number of *n* individuals sampled [@gotelli2001].
-For *S~n~* estimates for trawls, *n* was calculated by the minimum number of individuals within a trawl multiplied by `r n_year`.
-We calculated *S~asymp~* and *S~n~* using the mobr package [@mcglinn2019][@mcglinn2021a].
+We calculated *S~asymp~* and *S~n~* using the mobr package [@mcglinn2019; @mcglinn2021a].
 
 Beyond actual and expected numbers of species, we calculated additional measures of biodiversity to capture community change through time.
-To quantify changes in the distribution of abundant and rare species, we calculated specific orders of diversity, the percentage of rare species, and evenness in species abundances on annually aggregated species abundances.
+We estimated community turnover, the combination of gains and losses relative to total species richness, and the contributions of species gains and losses using the `codyn` package [@hallett2020].
+To quantify changes in the distribution of abundant and rare species, we calculated specific orders of diversity, the percentage of rare species, and evenness in species abundances.
 An order of diversity, *^q^D*, where *q* represents a non-negative integer, captures the "effective numbers of species" based on varying degrees of rarity of the species in a community [@hill1973].
@@
 
+We calculated the contribution of each species to community dis/similarity across orders of diversity
+
 ## Statistical Analyses
+
+To test for changes in species richness over time, we fit bayesian implementations of generalized additive models (GAMs) using the `mgcv` [@wood2011] and  `brms` package in R [@burkner2017; @burkner2018].
 
@@
 
+```{r env data, echo=FALSE, warning=FALSE, message=FALSE}
+
+```
+
 ```{r mobr_stats, echo = FALSE, warning=FALSE, message=FALSE, results='hide'}
-total_richness = length(unique(TB_trawl_data$Common_name))
 
-TB_trawl_sampling = TB_trawl_data %>%
+## Goals estimate the rarified richness through time
+## Show changes in evenness and Hill #s
+## Look at compositon 
+## Show who is contributing
+## Show patterns of most important contributors
+# estimate the contribution of each species to diversity changes
+
+#### ----
+
+## Annual statistics for first paragraph outline
+TB_trawl_sampling_yr = TB_trawl_data %>%
+  dplyr::filter(year(Date) %ni% year_removals) %>%
   dplyr::select(Date, year, Common_name, Abundance) %>%
@@
 
-TB_trawl_taxasite <- TB_trawl_data %>%
+total_richness = length(unique(TB_trawl_taxasite_long$Common_name))
 
-  dplyr::select(Date, Common_name, Abundance) %>%
-  group_by(Date, Common_name) %>%
-  summarise(Abundance = sum(Abundance)) %>%
-  na.omit %>% group_by(Date) %>%
-  # remove trawls with less than 20 individuals 
-  # dplyr::filter(sum(Abundance) >=20) %>%
-  group_by(Date, Common_name) %>%
-  pivot_wider(names_from = Common_name, values_from = Abundance, values_fill = list(Abundance = 0)) %>%
-  ungroup() %>%
-  dplyr::mutate(julian_date = julian(Date, origin = as.Date("2007-01-05")),
-                biweekly = ceiling(julian_date/30),
-                month = month(Date),
-                year = year(Date)) %>%
-  dplyr::select(julian_date, Date, year, month, biweekly, everything())
-
+## Annual summaries of richness, etc.
 TB_trawl_taxasite_yr <- TB_trawl_data %>%
-  # exclude 2020 & 2021
-  dplyr::filter(year %ni% c("2020","2021")) %>%
+  # exclude 2007, 2020 & 2021
+  dplyr::filter(year %ni% year_removals) %>%
   dplyr::select(year, Common_name, Abundance) %>%
@@
 
-n_year = 50
-
-# trawl_rarefaction analysis
-
-## Estimated mobr for biweekly  for all communities
-# TB_trawl_biweekly = TB_trawl_data %>%
-#   # exclude 2020 & 2021
-#   dplyr::filter(year %ni% c("2020","2021")) %>%
-#   dplyr::mutate(julian_date = julian(Date, origin = as.Date("2007-01-05")),
-#                 biweekly = ceiling(julian_date/14)) %>%
-#   group_by(year,biweekly, Common_name) %>%
-#   dplyr::summarise(Abundance = sum(Abundance, na.rm = TRUE)) %>%
-#   group_by(year,biweekly) %>%
-#   pivot_wider( names_from = 'Common_name', values_from = 'Abundance', values_fill = 0) %>%
-#   ungroup
-
-# trawl_mob_in = mobr::make_mob_in(comm = TB_trawl_biweekly %>% dplyr::select(-biweekly),
-#                                  plot_attr = TB_trawl_biweekly %>% dplyr::select(year,biweekly),
-#                                  coord_names = "biweekly",
-#                                  latlong = FALSE)
-
-# trawl_mob_in = mobr::make_mob_in(comm = TB_trawl_taxasite %>% dplyr::select(-julian_date:-biweekly),
-#                                  plot_attr = TB_trawl_taxasite %>% dplyr::select(julian_date:biweekly),
-#                                  coord_names = "biweekly",
-#                                  latlong = FALSE)
-
-# trawl_mob_stats = mobr::get_mob_stats(trawl_mob_in, group_var = 'year', index = c("N", "S", "S_asymp", "S_n", "S_PIE", "PIE", "pct_rare"), effort_samples = n_year, extrapolate = TRUE, boot_groups = TRUE, n_perm = nperm)
-
-# group_stats = trawl_mob_stats$groups_stats %>% data.frame
-
-chao1_yr = TB_trawl_taxasite_yr[,-1] %>%
+## yearly stats
+yr_chao1 = TB_trawl_taxasite_yr[,-1] %>%
   apply(., 1, mobr::calc_chao1) %>%
@@
 
-S_n = min(TB_trawl_sampling$trawl_days, na.rm = TRUE)*n_year
+S_n_yr = min(TB_trawl_sampling_yr$individuals, na.rm = TRUE)
 
-Sn_yr = TB_trawl_taxasite_yr[,-1] %>%
-  apply(., 1, function(x) mobr::rarefaction(x, effort = S_n, method = "IBR", extrapolate = TRUE)) %>%
+yr_Sn = TB_trawl_taxasite_yr[,-1] %>%
+  apply(., 1, function(x) mobr::rarefaction(x, effort = S_n_yr, method = "IBR", extrapolate = TRUE)) %>%
   bind_cols(TB_trawl_taxasite_yr$year,.) %>%
@@
 
-pct_rare =TB_trawl_taxasite_yr[,-1] %>%
+ yr_pct_rare =TB_trawl_taxasite_yr[,-1] %>%
   apply(., 1, function(x) pct_rare(x, 0.05)) %>%
@@
 
-group_stats = left_join(chao1_yr, Sn_yr) %>%
-  left_join(pct_rare) %>%
+yr_group_stats = left_join(yr_chao1, yr_Sn) %>%
+  left_join(yr_pct_rare) %>%
   dplyr::select(Date, year, everything()) %>%
@@
 #
+TB_trawl_sampling_mth = TB_trawl_taxasite_long %>%
+  dplyr::select(Date, date_id, Common_name, Abundance) %>%
+  dplyr::filter(Abundance > 0) %>%
+  group_by(Date, date_id) %>%
+  dplyr::summarise(S = length(unique(Common_name)),
+                   individuals = sum(Abundance, na.rm = TRUE))
+
+S_n_mth = min(TB_trawl_sampling_mth$individuals, na.rm = TRUE)
+## monthly stats
+mth_chao1 = TB_trawl_taxasite[,-c(1,2)] %>%
+  apply(., 1, mobr::calc_chao1) %>%
+  bind_cols(TB_trawl_taxasite$date_id,.) %>%
+  setNames(., c("date_id","S_asymp")) %>%
+  left_join(TB_trawl_taxasite[,c(1,2)],.,by = 'date_id')
+
+mth_Sn = TB_trawl_taxasite[,-c(1,2)] %>%
+  apply(., 1, function(x) mobr::rarefaction(x, effort = S_n_mth, method = "IBR", extrapolate = TRUE)) %>%
+  bind_cols(TB_trawl_taxasite$date_id,.) %>%
+  setNames(., c("date_id","S_n")) %>%
+  left_join(TB_trawl_taxasite[,c(1,2)],.,by = 'date_id')
+
+mth_pct_rare =TB_trawl_taxasite[,-c(1,2)] %>%
+  apply(., 1, function(x) pct_rare(x, 0.05)) %>%
+  bind_cols(TB_trawl_taxasite$date_id,.) %>%
+  setNames(., c("date_id","pct_rare")) %>%
+  left_join(TB_trawl_taxasite[,c(1,2)],.,by = 'date_id')
+
+mth_group_stats = left_join(mth_chao1, mth_Sn) %>%
+  left_join(mth_pct_rare) %>%
+  dplyr::select(Date, date_id, everything()) %>%
+  group_by(Date, date_id) %>%
+  pivot_longer(c(S_n,S_asymp, pct_rare),names_to = "index", values_to = "median" ) %>%
+  ungroup
 
@@
 
+<!--- Outline the general patterns annually and  --->
 Over the sampling period from `r min(TB_trawl_sampling$year, na.rm = TRUE)` to `r max(TB_trawl_sampling$year, na.rm = TRUE)`, `r length(unique(TB_trawl_data$Date))` trawls-days were performed yielding `r format(signif(sum(TB_trawl_data$Abundance, na.rm = TRUE),3), scientific = TRUE)` individuals.
 Among years, total effort generally increased, both in number of trawl-days and individuals counted, from a minimum effort of `r min(TB_trawl_sampling$trawl_days)` (`r TB_trawl_sampling %>% slice_min(trawl_days) %>% dplyr::select(year) %>% unlist`) to `r max(TB_trawl_sampling$trawl_days)` (`r TB_trawl_sampling %>% slice_max(trawl_days) %>% dplyr::select(year) %>% unlist`) days and from `r min(TB_trawl_sampling$individuals, na.rm = TRUE)` (`r TB_trawl_sampling %>% slice_min(individuals) %>% dplyr::select(year) %>% unlist`) to `r format(signif(max(TB_trawl_sampling$individuals, na.rm = TRUE),3), scientific = TRUE)` (`r TB_trawl_sampling %>% slice_max(individuals) %>% dplyr::select(year) %>% unlist`) individuals.
-In total, `r length(unique(TB_trawl_data$Common_name))` unique species were identified and new species were consistently observed throughout the sampling period (Figure 1).
-Within a calendar year, we estimated the asymptotic species richness (*S~asymp~*) which was relatively stable for the first five years (2007 -- 2012), reaching a minimum value of `r group_stats %>% dplyr::filter(index == "S_asymp") %>% slice_min(median) %>% dplyr::select(median) %>% unlist %>% as.numeric %>% round(0)` in `r group_stats %>% dplyr::filter(index == "S_asymp") %>% slice_min(median) %>% dplyr::select(year)`.
-Estimated *S~asymp~* increased in 2013 to a series maximum of `r group_stats %>% dplyr::filter(index == "S_asymp") %>% slice_max(median) %>% dplyr::select(median) %>% unlist %>% as.numeric %>% round(0)` in `r group_stats %>% data.frame %>% dplyr::filter(index == "S_asymp") %>% slice_max(median) %>% dplyr::select(year)`.
+In total, `r length(unique(TB_trawl_data$Common_name))` unique species were identified and new species were consistently observed throughout the sampling period (Figure S1).
+Within a calendar year, asymptotic species richness (*S~asymp~*) was relatively stable from 2009 to 2012, reaching a minimum value of `r yr_group_stats %>% dplyr::filter(index == "S_asymp") %>% slice_min(median) %>% dplyr::select(median) %>% unlist %>% as.numeric %>% round(0)` in `r yr_group_stats %>% dplyr::filter(index == "S_asymp") %>% slice_min(median) %>% dplyr::select(year)`.
+Estimated *S~asymp~* increased in 2013 to a series maximum of `r yr_group_stats %>% dplyr::filter(index == "S_asymp") %>% slice_max(median) %>% dplyr::select(median) %>% unlist %>% as.numeric %>% round(0)` in `r yr_group_stats %>% data.frame %>% dplyr::filter(index == "S_asymp") %>% slice_max(median) %>% dplyr::select(year)`.
 However, given the large differences in effort among years, variability in *S~asymp~* may be partly attributable to sampling effects among years.
-Therefore, we also calculated rarefied richness at `r S_n` individuals, *S~`r S_n`~*,  for each year.
-Here, effort-controlled species richness, *S~`r S_n`~*, diverged qualitatively from *S~asymp~* and was generally constant with an apparent slight increase in more recent sampling years.
-Overall, *S~`r S_n`~* ranged from `r group_stats %>% dplyr::filter(index == "S_n") %>% slice_min(median) %>% dplyr::select(median) %>% round(1)` to `r group_stats %>% dplyr::filter(index == "S_n") %>% slice_max(median) %>% dplyr::select(median) %>% round(1)` (Figure 1).
+Therefore, we also calculated rarefied richness at `r S_n_yr` individuals, *S~`r S_n_yr`~*,  for each year.
+Here, effort-controlled species richness, *S~`r S_n_yr`~*, diverged qualitatively from *S~asymp~* and was generally constant with an apparent slight increase in more recent sampling years.
+Overall, *S~`r S_n_yr`~* ranged from `r yr_group_stats %>% dplyr::filter(index == "S_n_yr") %>% slice_min(median) %>% dplyr::select(median) %>% round(1)` to `r yr_group_stats %>% dplyr::filter(index == "S_n_yr") %>% slice_max(median) %>% dplyr::select(median) %>% round(1)` among all years.
+Monthly, of rarefied richness averaged `r round(mean(mth_sn$S_n, na.rm = TRUE),1)` [range: `r round(min(mth_sn$S_n, na.rm = TRUE),1)`--`r round(max(mth_sn$S_n, na.rm = TRUE),1)`] and exhibited seasonal oscillations, but no detectable trend over time (Figure 1a, Table S1).
 
@@
 
-TB_trawl_data %>%
-  # exclude 2020 & 2021
-  dplyr::filter(year %ni% c("2020","2021")) %>%
+TB_trawl_taxasite_long %>%
   dplyr::filter(!duplicated(Common_name )) %>%
@@
 
-TB_annual_accum <- TB_trawl_data %>%
-  # exclude 2020 & 2021
-  dplyr::filter(year %ni% c("2020","2021")) %>%
-  mutate(pres = 1) %>% group_by(year) %>%
-  filter(!duplicated(Common_name)) %>%
-  summarise(richness = sum(pres)) %>%
-  mutate(Date = as.Date(paste(as.character(year),"01","01", sep = "-"), format = "%Y-%m-%d", origin = "2000-01-01"))
-
 ### create timeseries figure
-TB_time_df <- TB_time_accum %>%
-  dplyr::select(Date, year, richness) %>%
-  mutate(data_type = 'continuous') %>%
-  bind_rows(TB_annual_accum %>% 
-              mutate(data_type = "ann_raw")) %>%
-  bind_rows(group_stats %>% 
-              dplyr::filter(index == "S_n") %>%
-              dplyr::select(Date, year, richness = 'median') %>%
-              dplyr::mutate(data_type = "rarefied")) %>%
-  bind_rows(group_stats %>% 
-              dplyr::filter(index == 'S_asymp') %>%
-              dplyr::select(Date, year, richness = 'median') %>%
-              dplyr::mutate(data_type = "ann_asymp")) %>%
-  dplyr::mutate(data_type = factor(data_type, levels = c("continuous", "rarefied", "ann_raw", "ann_asymp"))) %>%
-  dplyr::filter(data_type != "ann_raw")
-
-S_n_lab = paste0("S[",S_n,"]")
-
-rich_time <-
-  ggplot(TB_time_df, aes(x = Date, y = richness, group = data_type)) +
-  geom_segment(data = TB_time_df %>% 
-                 dplyr::filter(data_type %ni% 'continuous') %>%
-                 pivot_wider(Date, names_from = data_type, values_from = richness),
-               aes(x = Date, xend = Date, y = ann_asymp, yend = rarefied ), 
-               color = viridis(n = 3, alpha = c(1,1,1), option = 'viridis')[3],
-               inherit.aes = F) +
-  geom_point(data = TB_time_df, aes(colour = data_type),size = 1.5) +
-  geom_line(data = TB_time_df %>% dplyr::filter(!grepl('ann_asymp', data_type)), aes(colour = data_type),size = 1.2) +
-  scale_x_date(date_breaks = "1 year", date_labels = "%Y",limits = c(as.Date("2007-01-01"),as.Date("2019-06-01"))) +
-  scale_y_continuous(name = "Species Richness")+
-  scale_colour_manual(labels = c("continuous", bquote(italic("S"[.(S_n[1])])),expression(italic("S"["asymp"]))), values = viridis(n = 3, alpha = c(1,1,1), option = 'viridis')) +
-  # scale_alpha_manual(values = c(1,1,0.3))+
-  theme(legend.position = c(0, 1), legend.justification = c(0, 1), legend.background = element_rect(fill = "transparent", colour = NA),
-        legend.title = element_blank(), legend.text.align = 0,
-        # axis.title.x = element_blank(), axis.text.x = element_blank(),
-        legend.spacing.y = unit(-0.1, 'cm'))
-
-rich_time
+mth_group_stats %>%
+  dplyr::filter(index == 'S_n') %>%
+  ggplot(aes( x= Date, y = median))+
+  scale_y_continuous(name = expression("Rarefied richness ("*italic(S[n])*")"), limits = c(0,12))+
+  scale_x_date(date_breaks = "1 year", date_labels = "%Y",limits = c(as.Date("2009-01-01"),as.Date("2019-12-31"))) +
+  geom_point(size = 1.5) +
+  geom_line(size = 1.2) 
+  theme()
 
@@
 ## quantify loss and appearance of species in the timeseries
-TB_trawl_data %>%
-  # exclude 2020 & 2021
-  dplyr::filter(year %ni% c("2020","2021")) %>%
-  group_by(year, Common_name) %>%
-  dplyr::summarise(Abundance = sum(Abundance, na.rm = TRUE)) %>%
-  group_by(year) %>%
-  pivot_wider( names_from = 'Common_name', values_from = 'Abundance', values_fill = 0) %>%
-  ungroup %>%
-  # dplyr::mutate(time.var = 1:n()) %>%
-  pivot_longer(c(-year), names_to = 'Common_name', values_to = 'Abundance')-> TB_trawl_yr
-
-trawl_yr_turnover = purrr::map(c('appearance','disappearance','total'),
-                                     ~codyn::turnover(df = TB_trawl_yr,
-                                                      time.var = 'year',
+trawl_mth_turnover = purrr::map(c('appearance','disappearance','total'),
+                                     ~codyn::turnover(df = TB_trawl_taxasite_long,
+                                                      time.var = 'date_id',
                                                       species.var = 'Common_name',
@@
 
-Consistent with the pattern of continued accumulation of new species throughout the sampling series and the relatively stable effort-controlled richness, species gains and losses generally balanced (Figure 2 ).
-Total turnover averaged `r round(mean(total$value, na.rm = TRUE),2)` and decreased with time from a peak turnover of `r round(max(total$value, na.rm = TRUE),2)` in `r total %>% slice_max(value) %>% dplyr::select(year)` to `r total %>% dplyr::filter(year == '2019') %>% dplyr::select(value) %>% round(2)` in the final year of record, 2019 (Figure 2).
-The contribution of species gains to total turnover averaged `r round(mean(gains$value, na.rm = TRUE),2)` and ranged from `r round(max(gains$value, na.rm = TRUE),2)` to `r round(min(gains$value, na.rm = TRUE),2)`, whereas, species losses average `r round(mean(losses$value, na.rm = TRUE),2)` and ranged from `r round(max(losses$value, na.rm = TRUE),2)` to `r round(min(losses$value, na.rm = TRUE),2)`.
+Consistent with the pattern of continued accumulation of new species throughout the sampling series and relatively stable effort-controlled richness, species gains (`r round(mean(gains$value, na.rm = TRUE),2)` $\pm$ `r round(sd(gains$value, na.rm = TRUE),2)` SD) and losses (`r round(mean(losses$value, na.rm = TRUE),2)` $\pm$ `r round(sd(losses$value, na.rm = TRUE),2)` SD) generally balanced over time (Figure 1b).
+Total turnover was variable but relatively stable (`r round(mean(total$value, na.rm = TRUE),2)` $\pm$ `r round(sd(total$value, na.rm = TRUE),2)` SD) and exhibited no detectable trend or coherent seasonal component.
 
-```{r turnover plot ,echo = FALSE, warning=FALSE, message=FALSE, fig.cap = "Figure 2. Total species turnover and partitioning"}
-trawl_yr_turnover %>%
+```{r turnover plot ,echo = FALSE, warning=FALSE, message=FALSE, fig.cap = "Figure 2. Total species turnover and partitioning of species gains and losses over time."}
+trawl_mth_turnover %>%
+  na.omit %>%
   ggplot()+
@@
   scale_color_manual(values = viridis(n = 3, option = 'viridis'))+
-  scale_y_continuous(name = 'Species turnover',limits = c(0,0.7), expand = c(0.01,0.01))+
-  scale_x_date(date_breaks = 'year', limits = c(as.Date("2007-01-01"),as.Date("2019-06-01")),
+  scale_y_continuous(name = 'Species turnover',limits = c(0,1), expand = c(0.01,0.01))+
+  scale_x_date(date_breaks = 'year', limits = c(as.Date("2009-01-01"),as.Date("2019-12-31")),
                date_labels = "%Y")+
-  theme(legend.position = c(0,0),
-        legend.justification = c(0,0),
+  theme(legend.position = c(0,1),
+        legend.justification = c(0,1),
         legend.background = element_rect(fill = 'transparent', color = NA),
@@
   scale_y_continuous(name = "Normalized Gini coefficient", limits = c(0,0.2), expand = c(0.01,0.01))+
-  scale_x_date(date_breaks = 'year', limits = c(as.Date("2007-01-01"),as.Date("2019-06-01")),
+  scale_x_date(date_breaks = 'year', limits = c(as.Date("2009-01-01"),as.Date("2019-12-31")),
                date_labels = "%Y")+
   theme(axis.title.x = element_blank())-> evenness_plot
+
+evenness_plot
+
+```
+
+```{r spp contributions, echo=FALSE, warning=FALSE, message=FALSE}
+
+### create ordering based on relative abundances -------------
+TB_trawl_order =  TB_trawl_data %>%
+  dplyr::select(Date, Common_name, Abundance) %>%
+  dplyr::filter(year(Date) %ni% year_removals) %>%
+  group_by(Date) %>%
+  dplyr::mutate(rel_abun = Abundance/sum(Abundance, na.rm = TRUE)) %>%
+  dplyr::select(-Abundance) %>%
+  group_by(Common_name) %>%
+  dplyr::summarise(rel_abun = mean(rel_abun, na.rm = TRUE)) %>%
+  arrange(desc(rel_abun)) %>%
+  na.omit %>%
+  dplyr::select(Common_name) %>%
+  unlist %>% unname
+
+TB_trawl_order_names = fuzzySim::spCodes(TB_trawl_order, nchar.gen = 4, nchar.sp = 6)
+
+TB_trawl_taxasite_yr_dis = TB_trawl_taxasite_yr %>%
+  pivot_longer(-year,names_to = 'Common_name', values_to = 'Abundance') %>%
+  pivot_wider(names_from = 'year', values_from = 'Abundance') %>%
+  column_to_rownames('Common_name')
+
+TB_trawl_q2_dis = dis1(TB_trawl_taxasite_yr_dis, q = 2, type = 'tax') %>%
+  .[,TB_trawl_order] %>%
+  data.frame %>%
+  rownames_to_column('dis_type') %>%
+  dplyr::filter(dis_type == "UqN") %>%
+  pivot_longer(-dis_type, names_to = 'Common_name', values_to = 'value') %>%
+  dplyr::mutate(Common_name = factor(Common_name, make.names(TB_trawl_order)))
+
+TB_trawl_q1_dis = dis1(TB_trawl_taxasite_yr_dis, q = 1, type = 'tax') %>%
+  .[,TB_trawl_order] %>%
+  data.frame %>%
+  rownames_to_column('dis_type') %>%
+  dplyr::filter(dis_type == "UqN") %>%
+  pivot_longer(-dis_type, names_to = 'Common_name', values_to = 'value') %>%
+  dplyr::mutate(Common_name = factor(Common_name, make.names(TB_trawl_order)))
+
+TB_trawl_q0_dis = dis1(TB_trawl_taxasite_yr_dis, q = 0, type = 'tax') %>%
+  .[,TB_trawl_order] %>%
+  data.frame %>%
+  rownames_to_column('dis_type') %>%
+  dplyr::filter(dis_type == "UqN") %>%
+  pivot_longer(-dis_type, names_to = 'Common_name', values_to = 'value') %>%
+  dplyr::mutate(Common_name = factor(Common_name, make.names(TB_trawl_order)))
+
+q0_dis_plot = TB_trawl_q0_dis %>%
+  ggplot()+
+  geom_col(aes(x= Common_name, y = value));q0_dis_plot
+
+q1_dis_plot = TB_trawl_q1_dis %>%
+  ggplot()+
+  geom_col(aes(x= Common_name, y = value));q1_dis_plot
+
+q2_dis_plot = TB_trawl_q2_dis %>%
+  ggplot()+
+  geom_col(aes(x= Common_name, y = value));q2_dis_plot
+
+```
+
+# Discussion
+
+# Acknowledgements
+
+\newpage
+
+# References
+
+\newpage
+
+```{r supplemental figure 1, echo=FALSE, warning=FALSE, message=FALSE}
+
+TB_trawl_data %>%
+  # exclude 2020 & 2021
+  dplyr::filter(year %ni% year_removals) %>%
+  dplyr::filter(!duplicated(Common_name )) %>%
+  dplyr::mutate(Date = as.Date(Date)) %>%
+  arrange(Date) %>%
+  dplyr::mutate(richness = 1:n())-> TB_time_accum
+
+TB_annual_accum <- TB_trawl_data %>%
+  # exclude 2020 & 2021
+  dplyr::filter(year %ni% year_removals) %>%
+  mutate(pres = 1) %>% group_by(year) %>%
+  filter(!duplicated(Common_name)) %>%
+  summarise(richness = sum(pres)) %>%
+  mutate(Date = as.Date(paste(as.character(year),"01","01", sep = "-"), format = "%Y-%m-%d", origin = "2000-01-01"))
+
+### create timeseries figure
+TB_time_df <- TB_time_accum %>%
+  dplyr::select(Date, year, richness) %>%
+  mutate(data_type = 'continuous') %>%
+  bind_rows(TB_annual_accum %>% 
+              mutate(data_type = "ann_raw")) %>%
+  bind_rows(group_stats %>% 
+              dplyr::filter(index == "S_n") %>%
+              dplyr::select(Date, year, richness = 'median') %>%
+              dplyr::mutate(data_type = "rarefied")) %>%
+  bind_rows(group_stats %>% 
+              dplyr::filter(index == 'S_asymp') %>%
+              dplyr::select(Date, year, richness = 'median') %>%
+              dplyr::mutate(data_type = "ann_asymp")) %>%
+  dplyr::mutate(data_type = factor(data_type, levels = c("continuous", "rarefied", "ann_raw", "ann_asymp"))) %>%
+  dplyr::filter(data_type == "S_n")
+
+S_n_lab = paste0("S[",S_n,"]")
+
+rich_time <-
+  ggplot(TB_time_df, aes(x = Date, y = richness, group = data_type)) +
+  geom_segment(data = TB_time_df %>%
+                 dplyr::filter(data_type %ni% 'continuous') %>%
+                 pivot_wider(Date, names_from = data_type, values_from = richness),
+               aes(x = Date, xend = Date, y = ann_asymp, yend = rarefied ),
+               color = viridis(n = 3, alpha = c(1,1,1), option = 'viridis')[3],
+               inherit.aes = F) +
+  geom_point(data = TB_time_df, aes(colour = data_type),size = 1.5) +
+  geom_line(data = TB_time_df %>% dplyr::filter(!grepl('ann_asymp', data_type)), aes(colour = data_type),size = 1.2) +
+  scale_x_date(date_breaks = "1 year", date_labels = "%Y",limits = c(as.Date("2009-01-01"),as.Date("2019-12-31"))) +
+  scale_y_continuous(name = "Species Richness")+
+  scale_colour_manual(labels = c("continuous", bquote(italic("S"[.(S_n[1])])),expression(italic("S"["asymp"]))), values = viridis(n = 3, alpha = c(1,1,1), option = 'viridis')) +
+  # scale_alpha_manual(values = c(1,1,0.3))+
+  theme(legend.position = c(0, 1), legend.justification = c(0, 1), legend.background = element_rect(fill = "transparent", colour = NA),
+        legend.title = element_blank(), legend.text.align = 0,
+        # axis.title.x = element_blank(), axis.text.x = element_blank(),
+        legend.spacing.y = unit(-0.1, 'cm'))
+
+```
+
+```{r rarity plot, message=FALSE, warning=FALSE, echo=FALSE}
 
@@
   scale_fill_manual(values = viridis(n = 1, option = 'viridis'))+
-  scale_x_date(date_breaks = 'year', limits = c(as.Date("2007-01-01"),as.Date("2019-06-01")),
+  scale_x_date(date_breaks = 'year', limits = c(as.Date("2009-01-01"),as.Date("2019-12-31")),
                date_labels = "%Y")+
@@
 
-gridExtra::grid.arrange(rarity_plot, evenness_plot, ncol = 1)
-
 ```
 
-```{r evenness profile, echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Figure 5.
+```{r S2 evenness profile, echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Figure 5.
 Species evenness profiles based on Hill numbers relative to annual species richness.
@@
   scale_y_continuous(name = 'Eff. Species (%)', limits = c(0,0.2))+
-  scale_x_date(breaks = as.Date(c("2007-01-01","2013-01-01","2019-01-01"),format = "%Y-%m-%d"),
+  scale_x_date(breaks = as.Date(c("2009-01-01","2014-01-01","2019-01-01"),format = "%Y-%m-%d"),
                date_labels = "%Y")+
@@
   scale_y_continuous(name = 'Eff. Species (%)', limits = c(0,0.15))+
-  scale_x_date(breaks = as.Date(c("2007-01-01","2013-01-01","2019-01-01"),format = "%Y-%m-%d"),
+  scale_x_date(breaks = as.Date(c("2009-01-01","2014-01-01","2019-01-01"),format = "%Y-%m-%d"),
                date_labels = "%Y")+
@@
 ```
-
-# Discussion
-
-# Acknowledgements
-
-\newpage
-
-# References

### 2021-11-18 analyses/core_analysis.R

@@ -1,18 +1,0 @@
-## TB benthic core analysis
-
-# working script for updating metadata and sample counts for each sampling date.
-
-TB_2018_core_meta = TB_2018_core_meta %>% mutate(Date = as.Date(Date, format = "%m/%d/%Y"))
-TB_2019_core_meta = TB_2019_core_meta %>% rename(Date = "Date Taken") %>% mutate(Date = as.Date(Date, format = "%m/%d/%Y"))
-
-TB_2018_core_summ = TB_2018_core_meta %>% group_by(Date, Station) %>% summarise(core_count = n())
-TB_2019_core_summ = TB_2019_core_meta %>% group_by(Date, Station) %>% summarise(core_count = n())
-
-TB_core_summ = bind_rows(TB_2018_core_summ, TB_2019_core_summ)
-
-#get number of cores processed
-shallow_summ <- shallow %>% rownames_to_column("site") %>% 
-  mutate(site = str_remove(site,"-.+")) %>%
-  group_by(site) %>%
-  summarise(N = n())
-

### 2021-11-18 analyses/environmental-analysis/fit_salinity-timeseries.R

@@ -1,124 +1,0 @@
-source("datascript.R")
-
-env_series = salinity_series %>% dplyr::select(Date, MC_sal, TB_sal, sss) %>%
-  left_join(temperature_series %>% dplyr::select(Date, MC_temp, TB_temp, sst), by = "Date") %>%
-  dplyr::mutate(julian = julian(Date, origin = as.Date("2007-01-01")),
-                weekly = paste0(year(Date),"-", week(Date))) %>%
-  group_by(weekly) %>% dplyr::select(-Date) %>% dplyr::mutate(Date = min(`julian`)) %>%
-  group_by(Date, weekly) %>%
-  dplyr::summarise(across(everything(), ~mean(.x, na.rm = TRUE))) %>%
-  dplyr::mutate(across(everything(), ~replace(.x, is.nan(.x), NA)))
-
-# estimate univariate state space model
-
-sal_arss = MARSS::MARSS()
-
-set.seed(42);sal_forecast1 = forecast::auto.arima(env_series$TB_sal, xreg = as.matrix(env_series[,c(3)]), stepwise = FALSE, approximation = FALSE)
-# sal_forecast1
-# set.seed(42);sal_forecast2 = forecast::auto.arima(env_series$TB_sal, xreg = as.matrix(env_series[,c(3,5)]), stepwise = FALSE, approximation = FALSE)
-# sal_forecast2
-TB_salinity_forecast1 = forecast::forecast(sal_forecast1, xreg = as.matrix(env_series[,3]))
-# TB_salinity_forecast2 = forecast::forecast(sal_forecast2, xreg = as.matrix(env_series[,c(3,5)]))
-# env_series = env_series %>% bind_cols(forecast1_mean = TB_salinity_forecast$mean) %>%
-#   bind_cols(forecast1_up = TB_salinity_forecast$upper) %>% bind_cols(forecast1_dw = TB_salinity_forecast$lower) %>%
-kr <- KalmanRun(env_series$TB_sal, sal_forecast1$model)
-    
-id.na <- which(is.na(env_series$TB_sal))
-# for (i in id.na)
-#   y[i] <- sal_forecast1$model$Z %*% kr$states[i,]
-# alternative to the explicit loop above
-y = sapply(id.na, FUN = function(x, Z, alpha) Z %*% alpha[x,], 
-       Z = sal_forecast1$model$Z, alpha = kr$states)
-y[id.na]
-
-
-
[…]

### 2021-11-18 analyses/inactive/XX_data_import.R

@@ -1,24 +1,0 @@
-# data manipulation
-
-data_import <<- function(){
-temp_paths <- list.files(path = "./data/", "*temp_*", full.names = TRUE)
-temp_files <- lapply(temp_paths, read_csv, skip = 1,
-                     col_types = cols(TS = col_datetime(format = "%m/%d/%Y %H:%M")))
-
-temp_df <<- bind_rows(temp_files)
-
-do_paths <- list.files(path = "./data/", "*DO_*", full.names = TRUE)
-do_files <- lapply(do_paths, read_csv, skip = 1,
-                   col_types = cols(TS = col_datetime(format = "%m/%d/%Y %H:%M")))
-
-do_df <<- bind_rows(do_files)
-
-hydro_paths <- list.files(path = "./data/", "hydro{1}.*.csv", full.names= TRUE)
-hydro_files <- lapply(hydro_paths, read_csv, col_type = cols(ArrayID = col_skip(), Year = col_skip(), JDay= col_skip(),
-X4 = col_skip(), X5 = col_skip(), X6 = col_skip(), Time = col_skip(), X8 = col_skip(), `Date/Time` = col_character(),
-Value4 = col_skip(), Depth = col_skip(), `Depth feet` = col_skip()))
-hydro_df <<- bind_rows(hydro_files) %>%
-  rename(time = 'Date/Time', temp_C = 'Temp', temp_F = 'Water Temp F', sal_psu = 'Sal', do_mg_L = 'DO') %>%
-  mutate(time = parse_date_time(time, orders = c("%m/%d/%Y %H:%M", "%m/%d/%y %H:%M")))
-}
-data_import()

### 2021-11-18 analyses/inactive/working_gamma_script.R

@@ -1,88 +1,0 @@
-# working script for gamma diversity from dropbox
-# just to get a handle on the data
-
-
-shallow_total <- shallow %>%
-  select(-Group)  %>%
-  summarise_all(sum) 
-
-shallow_total[shallow_total==0] <- NA
-shallow_total <- shallow_total[!is.na(shallow_total)]
-
-
-deep_total <- deep %>%
-  select(-Group,-`Sub-Group`, -Site) %>% #drops the columns group and sub.group
-  summarise_all(sum)
-
-deep_total[deep_total==0] <- NA
-deep_total <- deep_total[!is.na(deep_total)]
-
-
-
-#basic stats
-#look at the diversity on the Expected Number of Species at 400 individuals!!!!
-#it does the flip flop you thought could occur
-
-gamma_div <- data.frame(diversity(shallow_total))
-colnames(gamma_div )[1] <- "H"
-gamma_div$simp <- diversity(shallow_total, "simpson")
-gamma_div$rich <- specnumber(shallow_total)
-gamma_div$abund <-sum(shallow_total)
-gamma_div$Group <- "Shallow"
-gamma_div $rare400 <- rarefy(shallow_total, 400)
-
-
-gamma_div[2,'H'] <-diversity(deep_total)
-gamma_div[2,'simp'] <- diversity(deep_total, "simpson")
-gamma_div[2,'rich'] <- specnumber(deep_total)
-gamma_div[2,'abund'] <-sum(deep_total)
-gamma_div[2,'Group'] <- "Deep"
-gamma_div[2,'rare400'] <- rarefy(deep_total, 400)
-
-
-#rarefaction
-
-
-#rarefaction analysis and plot
-out1 <- iNEXT(deep_total, q=0, datatype="abundance")
-ggiNEXT(out1, type=1) + theme_bw(base_size=10) + xlim(0,700) + ylim (0,80)
-
-out2 <- iNEXT(shallow_total, q=0, datatype="abundance")
-ggiNEXT(out2, type=1) + theme_bw(base_size=10) + xlim(0,700) + ylim (0,80)
-
-
-#get everything on the same plot with even more tedious and ridicolous code
-#this is not worth explaining other than it extracts out the bits of data needed from the
-#mess that iNext spits out so we can plot it how would like.
-
-df_deep <- fortify(out1, type=1)
-df_shallow <- fortify(out2, type=1)
-
[…]

### 2021-11-18 analyses/inactive/working_script.R

@@ -1,3 +1,0 @@
-## working
-source("install-packages.R")#installs all necessary packages
-source("datascript.R")#imports data with some minor cleanup

### 2021-11-18 analyses/time-series_analysis.R

@@ -1,31 +1,0 @@
-#time series analysis
-source("install-packages.R")#installs all necessary packages
-source("datascript.R")#imports data with some minor cleanup
-
-
-hydro_summ <- hydro_df %>%
-  na.omit() %>%
-  group_by(yday) %>% 
-  summarise_at(vars(temp_C, temp_F, spCon_uS_cm, sal_psu), list(~na.rm_mean(., na.rm = TRUE), ~max(., na.rm = TRUE), ~min(.,na.rm = TRUE))) %>%
-  ungroup() %>%
-  mutate(DATE = as.Date(yday-1,  origin = "2020-01-01"))
-
-do_summ <- do_df %>%
-  na.omit() %>%
-  group_by(yday) %>%
-  summarise_at(vars(do_mg_L), list(~na.rm_mean(.,na.rm = TRUE), ~max(.,na.rm = TRUE), ~min(., na.rm = TRUE))) %>%
-  ungroup() %>%
-  mutate(DATE = as.Date(yday-1, origin = "2020-01-01"))
-
-ggplot(hydro_df, aes(x = time, y = sal_psu)) + geom_line()
-
-ggplot(hydro_df, aes(x = time, y = temp_F)) + geom_line()
-
-env_long <- hydro_df %>% select(-yday, -temp_F) %>% bind_rows(temp_df %>% mutate(temp_C = tempF_to_C(temp_F)) %>% select(-yday, -temp_F)) %>%
-  full_join(do_df %>% select(-yday)) %>%
-  # full_join(temp_df %>% mutate(temp_C = tempF_to_C(temp_F))%>% select(-yday, - temp_F), all = TRUE) %>%
-  pivot_longer(cols = temp_C:do_mg_L, names_to = "env_var", values_to = "value")
-
-source("./figures/env_facet_plot.R");env_plot()
-
-

### 2021-11-18 analyses/woodfall_GOM_analyses.R

@@ -1,456 +1,0 @@
-require(dplyr)
-require(ggplot2)
-require(vegan)
-require(tidyr)
-require(stringr)
-library(ggrepel)
-require(gridExtra)
-library(tibble)
-
-################palettes################
-study_color_pallette <- scale_color_manual(values = c("Quercus rubra" = "indianred1",
-                                                      "Quercus virginiana" = "navajowhite2",
-                                                      "Pinus echinata" = "olivedrab3" , 
-                                                      "Pinus elliottii" = "olivedrab4",
-                                                      "Celtis laevigata" = "palegoldenrod", 
-                                                      "1" = "grey30", 
-                                                      "2" = "grey60"))
-study_color_pallette2 <- scale_fill_manual(values = c("Quercus rubra" = "indianred1",
-                                                      "Quercus virginiana" = "navajowhite2",
-                                                      "Pinus echinata" = "olivedrab3" , 
-                                                      "Pinus elliottii" = "olivedrab4",
-                                                      "Celtis laevigata" = "palegoldenrod", 
-                                                      "1" = "grey30", 
-                                                      "2" = "grey60"))
-                                             
-
-################load data################
-setwd("~/Dropbox/Return of the Woodfall/New Structure/Wood Falls/Data")
-logbytaxa<- data.frame(read.csv("woodfall_logbytaxa.csv", header=TRUE, stringsAsFactors=FALSE))
-glimpse(logbytaxa)
-head(logbytaxa)
-
-logsummary <-  data.frame(read.csv("woodfall_logs.csv", header=TRUE, stringsAsFactors=FALSE))
-
-NCOL <- ncol(logbytaxa)
-
-#removing stations and species with zero total abundance
-logbytaxa2 <- logbytaxa %>%
-  replace(is.na(.), 0) %>% #replace all NAs (missing data cells) with zeros
[…]

### 2021-11-18 docs/EML_metadata/metadata.R

@@ -1,76 +1,0 @@
-#  metadata creation file  #
-##  Hydro monitoring data  ##
-attributes <-
-  tibble::tribble(
-    ~attributeName, ~attributeDefinition,                                                 ~formatString, ~definition,        ~unit,   ~numberType,
-    "datetime",    "datetime stamp of collection. 2020-01-01 00:00:01",                 "YYYY-MM-DD HH:MM:SS",            NA, NA,       NA,
-    "year",       "year, 2012",                                                         "YYYY",        NA,                 NA,       NA,
-    "day",        "Julian day. Range: 1 - 209.",                                      "DDD",         NA,                 NA,       NA,
-    "i.flag",     "is variable Real, Interpolated or Bad (character/factor)",           NA,            NA,                 NA,       NA,
-    "variable",   "what variable being measured (character/factor)", NA,            NA,                 NA,       NA,
-    "value.i",    "value of measured variable on year/day/hour.min. Real",       NA,            NA,                 NA,       NA)
-
-i.flag <- c(R = "real",
-            I = "interpolated",
-            B = "bad")
-variable <- c(
-  temp_F  = "Temperature in Fahrenheit",
-  temp_C = "Temperature in Celcius",
-  do_mg_L = "Dissolved Oxygen Concentration mg/L",
-  spCon_uS_cm  = "Specific conductivity microSeimens/cm",
-  sal_psu = "Salinity in Practical Salinity Units (PSU; g/kg)"
-  )
-
-value.i <- c(
-  temp_F  = paste0(expression(degree*"F")),
-  temp_C = paste0(expression(degree*"C")),
-  do_mg_L = "[DO]; mg/L",
-  spCon_us_cm = paste0(expression(mu*"Siemens/cm")),
-  sal_psu = "Practical Salinity Units"
-)
-
-## Write these into the data.frame format
-factors <- rbind(
-  data.frame(
-    attributeName = "i.flag",
-    code = names(i.flag),
-    definition = unname(i.flag)
-  ),
-  data.frame(
-    attributeName = "variable",
-    code = names(variable),
-    definition = unname(variable)
-  ),
-  data.frame(
-    attributeName = "value.i",
-    code = names(value.i),
-    definition = unname(value.i)
-  )
-)
-
-
-attributeList <- EML::set_attributes(attributes, factors, col_classes = c("Date", "Date", "Date", "factor", "factor", "numeric"))
-
[…]

### 2021-11-18 docs/grant-docs/grant-figs.R

@@ -1,242 +1,0 @@
-# NSF-BIO-OCE grant figures
-source("install-packages.R")
-TB_trawl_data <- readRDS("./data/TB_trawl_data.rds")
-
-temp_TS = read_csv(file = "./data/TerrebonneBay_temp_2008-2020.csv", col_type = cols(ArrayID = col_skip(), yeardata = col_skip(), jday= col_skip(),
-                                                                               X4 = col_skip(), X5 = col_skip(), X6 = col_skip(), timedata = col_skip(),
-                                                                               X8 = col_skip(), `Date/Time` = col_datetime(format = "%m/%d/%Y %H:%M"),
-                                                                               `Water Temp C` = col_number(), `Water Temp <U+00B0>F` = col_skip())) %>%
-  rename(datetime = "Date/Time", temp_C = "Water Temp C") %>%
-  mutate(Date = as.Date(datetime,origin = "1970-01-01")) %>%
-  group_by(Date) %>%
-  summarise_at(vars("temp_C"), na.rm_mean)
-
-sal_TS = read_csv(file = "./data/TerrebonneBay_salinity_2008-2020.csv", col_type = cols(ArrayID = col_skip(), yeardata = col_skip(), jday = col_skip(), X4 = col_skip(),
-                                                                                        X5 = col_skip(), X6 = col_skip(), timedata = col_skip(), X8 = col_skip(), 
-                                                                                        X9 = col_datetime(format = "%m/%d/%Y %H:%M"), salinity1_avg = col_number())) %>%
-                    rename(datetime = 'X9',sal_psu = 'salinity1_avg') %>%
-  na.omit %>%
-  mutate(Date = as.Date(datetime,origin = "1970-01-01")) %>%
-  group_by(Date) %>%
-  summarise_at(vars("sal_psu"), na.rm_mean)
-
-date_TS = seq.Date(as.Date("2000-01-01"), as.Date(Sys.Date()), by = 'days') %>% data.frame %>% setNames(.,c("Date"))
-env_summ <- date_TS %>% left_join(temp_TS, all = TRUE) %>% left_join(sal_TS, all = TRUE)
-
[…]

### 2021-11-18 figures/SAC_yr_plot.R

@@ -1,12 +1,0 @@
-SAC_yr_plot <- function(){
-SAC_yr = ggplot(TB_trawl_taxasite_yr, aes(x = sites, y = richness, group = year, colour = year)) +
-  geom_path(size = 1.5) +# geom_ribbon(aes(x = sites, ymin = (richness - 1.96*sd), ymax = (richness + 1.96*sd), fill = year), alpha = 0.2) +
-  scale_y_continuous(name = expression(Sigma~"species"),breaks = seq(0, roundUP(max(TB_trawl_taxasite_yr$richness), to = 10), by = 10), labels = seq(0, roundUP(max(TB_trawl_taxasite_yr$richness), to = 10), by = 10)) +
-  scale_x_continuous(name = "Trawls", breaks = seq(0, roundUP(max(TB_trawl_taxasite_yr$sites), to = 10), by = 5)) +
-  scale_colour_viridis(discrete = TRUE) + scale_fill_viridis(discrete = TRUE);SAC_yr
-
-### need to break this out by individual trawls not by month ##
-tiff(file = "./figures/trawl_specaccum_yr.tiff", height = 5, width = 5, units = "in", res = 450, compression = "lzw")
-SAC_yr
-dev.off()
-}

### 2021-11-18 figures/diversity_time_plots.R

@@ -1,28 +1,0 @@
-### diversity by time plot ###
-
- rich_time <- 
-  ggplot(TB_time_df, aes(x = Date, y = richness, group = data_type)) +
-  geom_point(aes(colour = data_type),size = 1.5) +
-  geom_line(aes(colour = data_type),size = 1.2) +
-  scale_x_date(date_breaks = "1 year", date_labels = "%Y") + 
-  scale_y_continuous(name = "Species Richness")+
-  scale_colour_manual(name = "", values = viridis(4)[c(2,3)]) +
-  theme(legend.position = c(0, 1), legend.justification = c(0, 1), legend.background = element_rect(fill = "transparent", colour = NA),
-        # axis.title.x = element_blank(), axis.text.x = element_blank(),
-        legend.spacing.y = unit(-0.1, 'cm'));rich_time
-
- jaccard_time <-
-  ggplot(beta_df, aes(x = Date, y = value, group = partition)) + 
-   geom_point(aes(colour = partition), size = 1.5) +
-  geom_line(aes(colour = partition), size = 1.2) +
-  scale_y_continuous(name = "Jaccard dissimilarity", limits = c(0,1.1), expand = c(0.01,0.01))+
-  scale_colour_manual(name = "", values = viridis(7)[c(2,4,7)], labels = c("jaccard", "nestedness","turnover")) +
-  scale_x_date(date_breaks = "1 year", date_labels = "%Y") + 
-  theme(legend.background = element_rect(colour = NA, fill = 'transparent'),
-        legend.position = c(0,1), legend.justification = c(0,1), axis.title.x = element_blank(),
-        legend.spacing.y = unit(-0.2, 'cm'))
-
- tiff("./figures/TB_temporal_diversity.tiff", res = 400, width = 5, height = 7.5, units = "in", compression = "lzw")
- grid.arrange(rich_time, jaccard_time, ncol = 1)
- dev.off()
- 

### 2021-11-18 figures/env_facet_plot.R

@@ -1,10 +1,0 @@
-env_plot <- function(){
-env_facet_plot <- ggplotGrob(ggplot(env_long, aes(x = datetime, y = value, group = env_var, colour = env_var)) +
-                               geom_line() + scale_colour_viridis_d() +
-                               facet_grid(rows = vars(env_var), scales = "free_y")+
-  theme(axis.title = element_blank(), legend.position = "none"))
-
-png(file = "./figures/env_facet_plot.png", res = 400, height = 10, width = 5, units = "in")
-grid.draw(env_facet_plot)
-dev.off()
-}

### 2021-11-18 figures/figure_script.R

@@ -1,47 +1,0 @@
-# working figures #
-TB_core_day = TB_core_summ %>%
-  mutate(yday = yday(Date)) %>%
-  group_by(yday) %>%
-  mutate(day = as.Date(yday-1,  origin = "2020-01-01"))
-
-hydro_plot = ggplot(hydro_summ, aes(x = DATE)) + 
-  geom_line(aes(y = temp_C_na.rm_mean), colour = 'blue', size = 1.5)+
-  geom_line(aes(y = sal_psu_na.rm_mean), colour = 'lightblue', size = 1.5)+
-  geom_ribbon(aes(ymin = temp_C_min, ymax = temp_C_max), fill = 'blue', alpha = 0.5)+
-  geom_ribbon(aes(ymin= sal_psu_min, ymax = sal_psu_max), fill = 'lightblue', alpha = 0.5) +
-  scale_y_continuous(name = expr("Temperature ("*degree*"C) | Salinity (PSU)"))+
-  scale_x_date(breaks = "1 months", date_labels = "%b", limits = c(as.Date("2020-01-01"),as.Date("2020-12-31")), expand = c(0,0.5)) +
-  geom_vline(data = TB_core_day, aes(xintercept = day), size = 2) +
-  theme(panel.grid.minor.x = element_line(colour = 'lightgrey'),
-        panel.grid.major.x = element_line(colour = 'lightgrey'));hydro_plot
-
-do_plot = ggplot(do_summ, aes(x = DATE)) +
-  geom_line(aes(y = na.rm_mean), colour = 'red', size = 1.5) +
-  geom_ribbon(aes(ymin = min, ymax = max), fill = 'red', alpha = 0.5)+
-  scale_y_continuous(name = 'Dissolved Oxygen (mg/L)', limits = c(0,NA))+
-  scale_x_date(breaks = "1 months", date_labels = "%b", limits = c(as.Date("2020-01-01"),as.Date("2020-12-31")), expand = c(0,0.5)) +
-  geom_vline(data = TB_core_day, aes(xintercept = day), size = 2)+
-  theme(axis.text.x = element_blank(), axis.title.x = element_blank(),
-        panel.grid.minor.x = element_line(colour = 'lightgrey'),
-        panel.grid.major.x = element_line(colour = 'lightgrey'));do_plot
-
-tiff(file = "./figures/env_plot.tiff", res = 400, width = 5, height = 4, units = "in", compression = "lzw")
[…]

### 2021-11-18 misc-files/old-workflow/testthat/test-datascript.R

@@ -1,9 +1,0 @@
-# library(testthat)
-# context("checks that datascript is working")
-# 
-# test_that("printed value is correct", {
-#   
-#   expect_output(str(source("./datascript.R")), 
-#                    "Have this script run whatever data cleaning you do")
-# 
-# })

### 2021-11-18 misc-files/old-workflow/testthat/test-periods.R

@@ -1,12 +1,0 @@
-library(testthat)
-library(dplyr)
-context("checks that period values are valid")
-
-base_data <- read.csv('../data/starting-data.csv', 
-                      stringsAsFactors = F)
-
-test_that("period numbers are valid", {
-  
-  expect_true(all(base_data$period < 1000))
-  
-})

### 2021-11-18 misc-files/old-workflow/testthat/test-sites.R

@@ -1,18 +1,0 @@
-library(testthat)
-library(tidyverse)
-context("checks that input sites are valid")
-site_list<-read_csv(file ="https://www.dropbox.com/s/fmahl3dc34ss33x/terrebonne_site_master.csv?dl=1") %>% as.data.frame()
-TB_2018_core_meta<-read_csv(file = "../data/metadata/TB_2018_Core-Metadata.csv", 
-                             col_types = cols(.default = "?", Date = col_date(format = "%m/%d/%Y"), Time = "i",
-                                              `Van Veen Grab` = "i", Core = "i"))
-TB_2019_core_meta<- read_csv(file = "../data/metadata/TB_2019_Core-Metadata.csv",
-                              col_types = cols(.default = "?", Date = col_date(format = "%m/%d/%Y"), Time = "i",
-                                               `Van Veen Grab` = "i", Core = "i"))
-core_data = bind_rows(TB_2018_core_meta, TB_2019_core_meta)
-
-
-test_that("sites are valid", {
-  
-  expect_true(all(core_data$Station %in% site_list$siteID))
-  
-})

### 2021-11-18 sub-projects/trawl/R/full_analyses.R

@@ -9,24 +9,34 @@ year_removals = c("2007","2020","2021")
 
 ##create taxa by site matrix
 TB_trawl_taxasite <- TB_trawl_data %>%
-  dplyr::select(Date, Common_name, Abundance) %>%
   dplyr::filter(year(Date) %ni% year_removals) %>%
-  group_by(Date, Common_name) %>%
+  dplyr::mutate(Date = as.Date(paste0(as.character(year),"-",as.character(month),"-01"))) %>%
+  dplyr::select(Date, date_id, Common_name, Abundance) %>%
+  group_by(Date, date_id, Common_name) %>%
   summarise(Abundance = sum(Abundance)) %>%
-  na.omit %>% group_by(Date) %>%
-  # remove trawls with less than 10 individuals 
-  dplyr::filter(sum(Abundance) >=10) %>%
-  group_by(Date, Common_name) %>%
+  na.omit %>% group_by(Date, date_id, Common_name) %>%
+  # # remove trawls with less than 10 individuals 
+  # dplyr::filter(sum(Abundance) >=10) %>%
+  # group_by(Date, date_id, Common_name) %>%
   pivot_wider(names_from = Common_name, values_from = Abundance, values_fill = list(Abundance = 0)) %>%
   ungroup() %>%
-  dplyr::mutate(julian_date = julian(Date, origin = as.Date("2009-01-01")),
-                biweekly = ceiling(julian_date/14),
-                month = month(Date),
-                year = year(Date)) %>%
-  dplyr::select(julian_date, Date,year, month, biweekly, everything())
+  dplyr::select(Date, date_id, everything())
 
-## check sample-level statistics
-TB_trawl_sampling = TB_trawl_data %>%
+TB_trawl_taxasite_long = TB_trawl_taxasite %>%
+  pivot_longer(-Date:-date_id, names_to = "Common_name", values_to = "Abundance")
+
+
+## Goals estimate the rarified richness through time
+## Show changes in evenness and Hill #s
+## Look at compositon 
+## Show who is contributing
+## Show patterns of most important contributors
+# estimate the contribution of each species to diversity changes
+
+#### ---- 
+
+## Annual statistics for first paragraph outline
+TB_trawl_sampling_yr = TB_trawl_data %>%
   dplyr::filter(year(Date) %ni% year_removals) %>%
[…]

### 2021-11-18 sub-projects/trawl/R/import_bioData.R

@@ -21,11 +21,15 @@ here::i_am("sub-projects/trawl/R/import_bioData.R")
    TB_trawl_worksheet <- gs4_get("1mUG6oYBGGONBzgXPsvS6XZkNRUIojxtI7BV8WUTh-3I")#sheetID extracted with as_sheets_ID(*sheet URL*)
    # get the tab indices for years, excluding any metadata tabs
    TB_trawl_tabs <- googlesheets4::sheet_names(TB_trawl_worksheet)
-   TB_trawl_tabs <- TB_trawl_tabs[!grepl("metadata|Notes",TB_trawl_worksheet[['sheets']]$name, ignore.case = TRUE)]
+   TB_trawl_datatabs <- TB_trawl_tabs[!grepl("metadata|Notes",TB_trawl_worksheet[['sheets']]$name, ignore.case = TRUE)]
+   TB_trawl_metatab <- TB_trawl_tabs[grepl("metadata", TB_trawl_worksheet[['sheets']]$name, ignore.case = TRUE)]
    
-   # read in from all spreadsets
+   # read in and clean metadata
+   TB_trawl_meta <- googlesheets4::read_sheet(TB_trawl_worksheet, sheet = TB_trawl_metatab, range = "A:B", col_types = "Dn" )
+      
+   # read in from all data spreadsheets
   
- TB_trawl_data <- lapply(TB_trawl_tabs, function(x){
+ TB_trawl_data <- lapply(TB_trawl_datatabs, function(x){
       googlesheets4::read_sheet(TB_trawl_worksheet, sheet = x, range = "A:C", col_types = "Dcd")
    }) %>% bind_rows %>%
       dplyr::select(Date, Species, Abundance)
@@ -214,14 +218,15 @@ here::i_am("sub-projects/trawl/R/import_bioData.R")
     mutate(Date = as.Date(Date, origin = "2007-01-05"),
            species_mod = recode(species_mod, !!!keyval),
            Common_name = recode(Common_name, !!!commonkey),
-           date_id = paste0(as.character(year),"-",as.character(month)))
+           date_id = as.Date(paste0(as.character(year),"-",as.character(month),"-01")),
+           date_id = julian(date_id, origin = as.Date("2007-01-01")))
    
    
    
 # unique(as.factor(TB_trawl_data$species_mod))
 #### End scientific and common name fixes #### 
 #### Confirm Species and Common names from taxonomic databases
-   
+
 trawl_spp_parse <- taxize::gn_parse(TB_trawl_data %>%
[…]

### 2021-11-18 sub-projects/trawl/R/load_enviroData.R

@@ -2,7 +2,7 @@ here::i_am('sub-projects/trawl/R/load_enviroData.R')
 ## source in environmental data ##
 
 load_environmental_data <- function(){
-temp_paths <- list.files(path = "./data/environment/", "Terrebonne.*temp_.*2020.*", full.names = TRUE)
+temp_paths <- list.files(path = here::here("data/environment"), "Terrebonne.*temp_.*2020.*", full.names = TRUE)
 temp_files <- lapply(temp_paths, read_csv,
                      col_types = cols('Date/Time' = col_datetime(format = "%m/%d/%Y %H:%M")))
 
@@ -36,7 +36,7 @@ TB_temp_df <<- bind_rows(temp_files) %>%
 #   dplyr::mutate(datetime = parse_date_time(datetime, orders = c("%m/%d/%Y %H:%M", "%m/%d/%y %H:%M")),
 #          yday = yday(datetime))
 
-sal_paths = list.files(path = "./data/environment/", "Terrebonne.*salinity.*2020.*", full.names = TRUE)
+sal_paths = list.files(path = here::here("data/environment"), "Terrebonne.*salinity.*2020.*", full.names = TRUE)
 TB_salinity_df <<- lapply(sal_paths, read_csv,
                           col_types = cols('Date/Time' = col_datetime(format = "%m/%d/%Y %H:%M"))) %>%
   bind_rows %>%
@@ -46,7 +46,7 @@ TB_salinity_df <<- lapply(sal_paths, read_csv,
   group_by(Date) %>%
   summarise_all(mean, na.rm = TRUE)
 
-marine_center_paths = list.files(path = "./data/environment/", "MarineCenter{1}.*.csv", full.names = TRUE)
+marine_center_paths = list.files(path = here::here("data/environment"), "MarineCenter{1}.*.csv", full.names = TRUE)
 marine_center_files = lapply(marine_center_paths, read_csv, col_type = cols(`Date/Time` = col_character())) %>%
   map(~.x %>% dplyr::rename(datetime = 'Date/Time') %>%
         dplyr::mutate(datetime = parse_date_time(datetime, orders = c("%m/%d/%Y %H:%M", "%m/%d/%y %H:%M")),
@@ -60,7 +60,7 @@ MC_temperature_df <<- marine_center_files[[2]] %>% dplyr::select(Date, temp_C = 
 MC_depth_df <<- marine_center_files[[3]] %>% dplyr::select(Date, depth_m = 'Water Depth M')
[…]

### 2021-11-24 sub-projects/trawl/docs/ms/ms.RMD
updating trawl biodiversity change manuscript

@@
 
-# # create bootstrapped data set to estimate variability
-# TB_trawl_boots = TB_trawl_data %>%
-#   group_by(year) %>%
-#   modelr::bootstrap(TB_trawl_data)
+TB_trawl_taxasite_long %>%
+  dplyr::filter(!duplicated(Common_name )) %>%
+  dplyr::mutate(Date = as.Date(Date)) %>%
+  arrange(Date) %>%
+  dplyr::mutate(richness = 1:n())-> TB_time_accum
 
@@
 #
+iter = 7000
+warmup = 5000
+thin = 10
+adapt_delta = 0.99
 
@@
 Intrinsic and extrinsic processes can interact, leading to temporal patterns of biodiversity change that vary in response to environmental change.
-For example, gradual environmental change over time can lead to gradual community shifts or these shifts may be undetectable or abrupt [@williams2011][@scheffer2003].
+For example, gradual environmental change over time can lead to gradual community shifts or these shifts may be undetectable or abrupt [@williams2011; @scheffer2003].
 
@@
 Thus, the majority of its freshwater inputs are from the local drainage basin [@bianchi2009].
-While water column salinity and density are homogenous, strong salinity gradients exist seaward from the marsh to the barrier islands [@bianchi2009].
+While water column salinity and density are homogeneous, strong salinity gradients exist seaward from the marsh to the barrier islands [@bianchi2009].
 Tides in Terrebonne Bay are diurnal with a semidiurnal component, ranging 20-80 cm [@inoue2000].
@@
 
-To test for changes in species richness over time, we fit bayesian implementations of generalized additive models (GAMs) using the `mgcv` [@wood2011] and  `brms` package in R [@burkner2017; @burkner2018].
+To detect trends in species richness and other dimensions of biodiversity (e.g., turnover, evenness, etc.) we used generalized additive models (GAMs) with a bayesian implementations using the `mgcv` [@wood2011] and  `brms` packages in R [@burkner2017; @burkner2018].
+Full models included smoothing spline terms for both trawl date and season as:
+$$y = \beta_0 + f_{season}(x_1) + f_{time}(x_2) + \varepsilon,\;\;\; \varepsilon ~ N(0, \sigma^{2} \Lambda) $$
+where, $y$ is the response variable (e.g., richness, turnover, evenness, etc.), $\beta_0$ is an intercept $f_{season}$ and $f_{time}$ represent seaonsal and trawl data smooth functions for month of year and day since beginning of the series, January 1, 2009.
+Seasonal terms were fit with cyclic cubic regression splines with smoothing dimension *k* = 12 to allow for continuity between December and January among model years.
+Models were
 
@@
 
+## quantify loss and appearance of species in the timeseries
+trawl_mth_turnover = purrr::map(c('appearance','disappearance','total'),
+                                ~codyn::turnover(df = TB_trawl_taxasite_long %>% dplyr::select(-Date),
+                                                 time.var = 'date_id',
+                                                 species.var = 'Common_name',
+                                                 abundance.var = 'Abundance',
+                                                 metric = .x) %>%
+                                  data.frame %>%
+                                  dplyr::mutate(date_id = date_id,
+                                                variable = .x) %>%
+                                  dplyr::rename(value = !!names(.[1])) %>%
+                                  bind_rows(data.frame(value = NA_real_, variable =.x))) %>%
+  bind_rows %>%
+  left_join(TB_trawl_taxasite[,c(1,2)],.,by = 'date_id')
+
+gains = trawl_mth_turnover %>%
+  dplyr::filter(variable == "appearance")
+
+losses = trawl_mth_turnover %>%
+  dplyr::filter(variable == "disappearance")
+
+total = trawl_mth_turnover %>%
+  dplyr::filter(variable == "total")
+
 ```
@@
 
-```{r figure 1, echo = FALSE, warning = FALSE, message=FALSE, fig.cap="Figure 1.
+```{r figure 1, echo = FALSE, warning = FALSE, message=FALSE, fig.height=8.5, fig.width=3.7, fig.cap="Figure 1.
 Multiple measures of species richness within the trawl community between the years 2007 to 2019 show continual accumulation of species (purple points and line) through the timeseries.
@@
 
-TB_trawl_taxasite_long %>%
-  dplyr::filter(!duplicated(Common_name )) %>%
-  dplyr::mutate(Date = as.Date(Date)) %>%
-  arrange(Date) %>%
-  dplyr::mutate(richness = 1:n())-> TB_time_accum
+## Goals estimate the rarified richness through time
+## Show changes in evenness and Hill #s
 
@@
   ggplot(aes( x= Date, y = median))+
-  scale_y_continuous(name = expression("Rarefied richness ("*italic(S[n])*")"), limits = c(0,12))+
-  scale_x_date(date_breaks = "1 year", date_labels = "%Y",limits = c(as.Date("2009-01-01"),as.Date("2019-12-31"))) +
-  geom_point(size = 1.5) +
-  geom_line(size = 1.2) 
-  theme()
+  scale_y_continuous(name = expression("Rarefied richness ("~italic(~S[n])~")"), limits = c(1,12),
+                     breaks = c(1,5,10),expand = c(0.01,0.01))+
+  scale_x_date(date_breaks = "year", limits = c(as.Date("2009-01-01"),as.Date("2019-12-31")),
+               date_labels = "%Y",expand = c(0.01,0.01))+
+  geom_point()+
+  geom_line()+
+  theme_tufte()+
+  geom_rangeframe(sides = "l")+
+  annotate('text', label = "A", x = as.Date("2009-01-30"), y = 11, family ='serif')+
+  theme(axis.title.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        axis.text.x = element_blank(),
+        panel.grid.minor.x = element_line(color = 'lightgray'),
+        plot.margin = unit(c(0.0,0.1,-0.1,0.0), 'cm')) -> rich_time;
+rich_time
+trawl_mth_turnover %>%
+  dplyr::filter(variable == 'total') %>%
+  na.omit %>%
+  ggplot(aes(x = Date, y = value, group = variable, color = variable))+
+  geom_point()+
+  geom_line(size = 1)+
+  scale_color_manual(values = viridis(n = 1, option = 'viridis', begin = .75))+
+  scale_y_continuous(name = 'Species turnover',limits = c(0,1), expand = c(0.01,0.01),
+                     breaks = c(0,0.2 ,0.4, 0.6, 0.8), labels = c(0,0.2,0.4,0.6,0.8))+
+  scale_x_date(date_breaks = 'year', limits = c(as.Date("2009-01-01"),as.Date("2019-12-31")),
+               date_labels = "%Y",expand = c(0.01,0.01))+
+  theme_tufte()+
+  geom_rangeframe(sides = "lb", color = 'black')+
+  annotate('text', label = "B", x = as.Date("2009-01-30"), y = 0.95, family = 'serif', vjust = 0)+
+  theme(legend.position = "none",
+        legend.justification = c(0,1),
+        axis.title.x = element_blank(),
+        plot.margin = unit(c(-0.18,0.15,0.0,0.0), 'cm'),
+        panel.grid.minor.x = element_line(color = 'lightgray'),
+        plot.background = element_rect(fill = 'transparent', color = NA)) -> turnover_time
+
+g2 <- ggplotGrob(rich_time)
+g3 <- ggplotGrob(turnover_time)
+g2$widths <- unit.pmax(g2$widths, g3$widths)
+g3$widths <- unit.pmax(g2$widths, g3$widths)
+grid.arrange(g2,g3, layout_matrix = rbind(1,1,1,1,2,2))
 
@@
 
-```{r turnover, echo = FALSE, warning=FALSE, message=FALSE}
-
-## quantify loss and appearance of species in the timeseries
-trawl_mth_turnover = purrr::map(c('appearance','disappearance','total'),
-                                     ~codyn::turnover(df = TB_trawl_taxasite_long,
-                                                      time.var = 'date_id',
-                                                      species.var = 'Common_name',
-                                                      abundance.var = 'Abundance',
-                                                      metric = .x) %>%
-                                       data.frame %>%
-                                       dplyr::mutate(Date = as.Date(paste0(unique(TB_trawl_yr$year)[-1],"-01-01"), format = "%Y-%m-%d"),
-                                                     variable = .x) %>%
-                                       dplyr::rename(value = !!names(.[1])) %>%
-                                       bind_rows(data.frame(value = NA_real_, time.var = NA_real_, Date = as.Date("2008-01-01"), variable =.x))) %>%
-                                     bind_rows
-gains = trawl_yr_turnover %>%
-  dplyr::filter(variable == "appearance")
-
-losses = trawl_yr_turnover %>%
-  dplyr::filter(variable == "disappearance")
-
-total = trawl_yr_turnover %>%
-  dplyr::filter(variable == "total")
+```{r}
 
@@
 Total turnover was variable but relatively stable (`r round(mean(total$value, na.rm = TRUE),2)` $\pm$ `r round(sd(total$value, na.rm = TRUE),2)` SD) and exhibited no detectable trend or coherent seasonal component.
+Species turnover was likely confined to species with moderate relative abundances.
+While we observed declines in the effective number of species for highly rare (^0.1^D; population-level effects `r summary(q0.1_bayes_full_mod)[['fixed']]['sdate_id_1','Estimate']`, 95% CI: `r summary(q0.1_bayes_full_mod)[['fixed']]['sdate_id_1','l-95% CI']`--`r `summary(q0.1_bayes_full_mod)[['fixed']]['sdate_id_1','u-95% CI']`) and highly abundant species (^2^D; `r summary(q2_bayes_full_mod)[['fixed']]['sdate_id_1','Estimate']`, 95% CI: `r summary(q02_bayes_full_mod)[['fixed']]['sdate_id_1','l-95% CI']`--`r `summary(q2_bayes_full_mod)[['fixed']]['sdate_id_1','u-95% CI']`), declines were greater in the for diversity orders describing moderately abundant species (^0.5^D; `r summary(q0.5_bayes_full_mod)[['fixed']]['sdate_id_1','Estimate']`, 95% CI: `r summary(q0.5_bayes_full_mod)[['fixed']]['sdate_id_1','l-95% CI']`--`r `summary(q0.5_bayes_full_mod)[['fixed']]['sdate_id_1','u-95% CI']` and ^1^D; `r summary(q1_bayes_full_mod)[['fixed']]['sdate_id_1','Estimate']`, 95% CI: `r summary(q1_bayes_full_mod)[['fixed']]['sdate_id_1','l-95% CI']`--`r `summary(q1_bayes_full_mod)[['fixed']]['sdate_id_1','u-95% CI']`,  Figure 2).
 
-```{r turnover plot ,echo = FALSE, warning=FALSE, message=FALSE, fig.cap = "Figure 2. Total species turnover and partitioning of species gains and losses over time."}
-trawl_mth_turnover %>%
-  na.omit %>%
-  ggplot()+
-  geom_line(aes(x = Date, y = value, group = variable, color = variable), size = 1.1)+
-  scale_color_manual(values = viridis(n = 3, option = 'viridis'))+
-  scale_y_continuous(name = 'Species turnover',limits = c(0,1), expand = c(0.01,0.01))+
-  scale_x_date(date_breaks = 'year', limits = c(as.Date("2009-01-01"),as.Date("2019-12-31")),
-               date_labels = "%Y")+
-  theme(legend.position = c(0,1),
-        legend.justification = c(0,1),
-        legend.background = element_rect(fill = 'transparent', color = NA),
-        legend.title = element_blank(),
-        axis.title.x = element_blank())
-```
-
-```{r annual qD, echo=FALSE, warning=FALSE, message=FALSE}
-set.seed(123)
-q2_boots = boot_sample_groups(TB_trawl_taxasite %>% dplyr::select(-julian_date,-Date,-month,-biweekly), 
-                   group_var = 'year',
-                   qD = 2,
-                   n_perm = nperm)
-set.seed(123)
-q1_boots = boot_sample_groups(TB_trawl_taxasite %>% dplyr::select(-julian_date,-Date,-month,-biweekly), 
-                              group_var = 'year',
-                              qD = 1,
-                              n_perm = nperm)
-
-qD_df = q2_boots %>% 
-  # summarise q2 by year
-  group_by(year) %>%
-  dplyr::summarise(across(q2, list(mean = ~mean(.x, na.rm = TRUE),
-                                   median = ~quantile(.x, 0.5, na.rm = TRUE),
-                                   quant2.5= ~quantile(.x, 0.025, na.rm = TRUE),
-                                   quant25= ~quantile(.x, 0.25, na.rm = TRUE),
-                                   quant75= ~quantile(.x, 0.75, na.rm = TRUE),
-                                   quant97.5= ~quantile(.x, 0.975, na.rm = TRUE)), .names = "{.fn}")) %>%
-  dplyr::mutate(Date = as.Date(paste(year,"01","01", sep = "-"), format = "%Y-%m-%d"),
-                q_order = "q2") %>%
-  bind_rows(
-    q1_boots %>%
-      # summarise q1 by year
-      group_by(year) %>%
-      dplyr::summarise(across(q1, list(mean = ~mean(.x, na.rm = TRUE),
-                                       median = ~quantile(.x, 0.5, na.rm = TRUE),
-                                       quant2.5= ~quantile(.x, 0.025, na.rm = TRUE),
-                                       quant25= ~quantile(.x, 0.25, na.rm = TRUE),
-                                       quant75= ~quantile(.x, 0.75, na.rm = TRUE),
-                                       quant97.5= ~quantile(.x, 0.975, na.rm = TRUE)), .names = "{.fn}")) %>%
-      dplyr::mutate(Date = as.Date(paste(year,"01","01", sep = "-"), format = "%Y-%m-%d"),
-                    q_order = "q1")
-   ) 
-# 
-# annual_evenness_boots = boot_gini_groups(TB_trawl_taxasite %>% dplyr::select(-julian_date,-Date,-month,-biweekly), 
-#                                 group_var = 'year',
-#                                 n_perm = nperm)
-# 
-# annual_evenness_df = annual_evenness_boots %>%
-#   dplyr::select(-boot_id) %>%
-#   pivot_longer(-year, names_to = 'measure', values_to = 'value') %>%
-#   group_by(year,measure) %>%
-#   dplyr::summarise(across(value, list(mean = ~mean(.x, na.rm = TRUE),
-#                                       median = ~quantile(.x, 0.5, na.rm = TRUE),
-#                                       quant2.5= ~quantile(.x, 0.025, na.rm = TRUE),
-#                                       quant25= ~quantile(.x, 0.25, na.rm = TRUE),
-#                                       quant75= ~quantile(.x, 0.75, na.rm = TRUE),
-#                                       quant97.5= ~quantile(.x, 0.975, na.rm = TRUE)), .names = "{.fn}")) %>%
-#   dplyr::mutate(Date = as.Date(paste(year,"01","01", sep = "-"), format = "%Y-%m-%d")) %>%
-#   ungroup
-
-annual_evenness_df = TB_trawl_taxasite_yr %>%
-  dplyr::select(-year) %>%
-  apply(., 1, gini_even) %>%
-      t() %>%
-      data.frame() %>%
-      bind_cols(TB_trawl_taxasite_yr$year, .) %>%
-      setNames(., c("year", "gini_raw", "gini_norm")) %>%
-  pivot_longer(-year, names_to = "measure", values_to = "median") %>%
-  dplyr::mutate(Date = as.Date(paste(year,"01","01", sep = "-"), format = "%Y-%m-%d")) %>%
-  ungroup
-
-group_stats %>%
-  dplyr::filter(index == "pct_rare") -> rarity
-
-```
-
-Species turnover was likely confined to species with moderate to low relative abundances.
-The effective number of highly abundant species, *^2^D*, was variable but stable through time with calculated values *ca.* `r qD_df %>% dplyr::filter(q_order == 'q2') %>% dplyr::summarise(across(median, ~median(.x ,na.rm = TRUE))) %>% round(2)` $\pm$ `r qD_df %>% dplyr::filter(q_order == 'q2') %>% dplyr::summarise(across(median, ~sd(.x, na.rm = TRUE))) %>% round(1)` (mean $\pm$ 1 SD) (range: `r qD_df %>% dplyr::filter(q_order == 'q2')%>% slice_min(median) %>% dplyr::select(median) %>% round(2)` to  `r qD_df %>% dplyr::filter(q_order == 'q2') %>% slice_max(median) %>% dplyr::select(median) %>% round(1)`; Figure 3 __*supplemental?*__).
+These changes in the distribution of relative abundances within the community led to an ultimate decrease in the community evenness through time.
 In contrast, the percentage of rare species increased slightly through time from `r rarity %>% slice_min(year) %>% dplyr::select(median) %>% round(2)` to `r rarity %>% slice_max(year) %>% dplyr::select(median) %>% round(2)`.
@@
 
-```{r diversity2 plot, echo = FALSE, warning=FALSE, message=FALSE, fig.cap="Figure 3.
+```{r diversity2 plot, echo = FALSE, warning=FALSE, message=FALSE, fig.cap="Figure 2.
 Temporal trends in order of diversity q = 2, ^2^D highlight relative stability in the number of dominant species in the community through time.
-^2^D is equivalent to 1/Simpson's diversity index and captures the effective number of highly abundant species in the community.", include=FALSE}
-qD_df %>%
-  dplyr::filter(q_order == "q2") %>%
-  ggplot()+
-  geom_ribbon(aes(x = Date, ymin = quant2.5, ymax = quant97.5, group = q_order, fill = q_order), alpha = 0.5)+
-  geom_line(aes(x = Date, y = median, group = q_order, color = q_order), size = 1.2)+
-  geom_point(aes(x = Date, y= mean, group = q_order), shape = 6)+
-  scale_y_continuous(name = expression("Effective species ("~italic(''^2*D)~")"),limits = c(0,11))+
-  scale_color_manual(labels = c("q2"), values = viridis(n = 1, option = 'viridis'))+
-  scale_fill_manual(labels = c("q2"),values = viridis(n = 1, alpha = 0.5, option = 'viridis'))+
+^2^D is equivalent to 1/Simpson's diversity index and captures the effective number of highly abundant species in the community.", include=FALSE}#### patterns of Hill diversity through time}
+## hill
+
+hill_time0 = hill_taxa(TB_trawl_taxasite %>% dplyr::select(-Date, -date_id), q = 0) %>%
+  data.frame %>%  dplyr::mutate(q = "q0") %>% setNames(., c('value','q')) %>%
+  bind_cols(TB_trawl_taxasite %>% dplyr::select(Date, date_id),.)
+hill_time0.1 = hill_taxa(TB_trawl_taxasite %>% dplyr::select(-Date, -date_id), q = 0.1) %>%
+  data.frame %>%  dplyr::mutate(q = "q0.1") %>% setNames(., c('value','q')) %>%
+  bind_cols(TB_trawl_taxasite %>% dplyr::select(Date, date_id),.)
+hill_time0.5 = hill_taxa(TB_trawl_taxasite %>% dplyr::select(-Date, -date_id), q = 0.5) %>%
+  data.frame %>%  dplyr::mutate(q = "q0.5") %>% setNames(., c('value','q')) %>%
+  bind_cols(TB_trawl_taxasite %>% dplyr::select(Date, date_id),.)
+hill_time1 = hill_taxa(TB_trawl_taxasite %>% dplyr::select(-Date, -date_id), q = 1)%>%
+  data.frame %>% dplyr::mutate(q = "q1") %>% setNames(., c('value','q')) %>%
+  bind_cols(TB_trawl_taxasite %>% dplyr::select(Date, date_id),.)
+hill_time2 = hill_taxa(TB_trawl_taxasite %>% dplyr::select(-Date, -date_id), q = 2)%>%
+  data.frame %>% dplyr::mutate(q = "q2") %>% setNames(., c('value','q')) %>%
+  bind_cols(TB_trawl_taxasite %>% dplyr::select(Date, date_id),.)
+
+hill_time = vctrs::vec_c(hill_time0,hill_time0.5,hill_time1,hill_time2) %>%
+  group_by(Date, date_id) %>%
+  pivot_wider(names_from = 'q', values_from = 'value') %>%
+  left_join(mth_group_stats %>%
+              dplyr::mutate(month = month(Date)) %>%
+              group_by(Date,month, date_id) %>%
+              pivot_wider(names_from = "index", values_from = "median")) %>%
+  dplyr::mutate(q0_eff = q0/q0,
+                q0.1_eff = (q0.1/q0)*100,
+                q0.5_eff = (q0.5/q0)*100,
+                q1_eff = (q1/q0)*100,
+                q2_eff = (q2/q0)*100,
+                q1_sn = q1/S_n,
+                q2_sn = q2/S_n)
+
+q0.1_bayes_full_mod = brm(bf(q0.1_eff ~ s(date_id) + s(month, bs = 'cc', k = 12)),
+                        data = hill_time, family = gaussian(),
+                        cores = 4, seed = 42,
+                        iter = 7000, warmup = 5000, thin = 10,
+                        control = list(adapt_delta = 0.99),
+                        save_pars = save_pars(all = TRUE),
+                        file = here::here("sub-projects/trawl/derived-data/q0.1_full.rds"),
+                        file_refit = 'on_change')
+
+ceff0.1 <- conditional_effects(q0.1_bayes_full_mod, 'date_id')
+
+ceff0.1_df = data.frame(
+  date = ceff0.1$date_id$date_id,
+  qD = "0.1",
+  estimate = ceff0.1$date_id$estimate__,
+  upper = ceff0.1$date_id$upper__,
+  lower = ceff0.1$date_id$lower__
+)
+q0.5_bayes_full_mod = brm(bf(q0.5_eff ~ s(date_id) + s(month, bs = 'cc', k = 12)),
+                        data = hill_time, family = gaussian(),
+                        cores = 4, seed = 42,
+                        iter = 7000, warmup = 5000, thin = 10,
+                        control = list(adapt_delta = 0.99),
+                        save_pars = save_pars(all = TRUE),
+                        file = here::here("sub-projects/trawl/derived-data/q0.5_full.rds"),
+                        file_refit = 'on_change')
+
+ceff0.5 <- conditional_effects(q0.5_bayes_full_mod, 'date_id')
+
+ceff0.5_df = data.frame(
+  date = ceff0.5$date_id$date_id,
+  qD = "0.5",
+  estimate = ceff0.5$date_id$estimate__,
+  upper = ceff0.5$date_id$upper__,
+  lower = ceff0.5$date_id$lower__
+)
+
+q1_bayes_full_mod = brm(bf(q1_eff ~ s(date_id) + s(month, bs = 'cc', k = 12)),
+                        data = hill_time, family = gaussian(),
+                        cores = 4, seed = 42,
+                        iter = 7000, warmup = 5000, thin = 10,
+                        control = list(adapt_delta = 0.99),
+                        save_pars = save_pars(all = TRUE),
+                        file = here::here("sub-projects/trawl/derived-data/q1_full.rds"),
+                        file_refit = 'on_change')
+
+ceff1 <- conditional_effects(q1_bayes_full_mod, 'date_id')
+
+ceff1_df = data.frame(
+  date = ceff1$date_id$date_id,
+  qD = "1",
+  estimate = ceff1$date_id$estimate__,
+  upper = ceff1$date_id$upper__,
+  lower = ceff1$date_id$lower__
+)
+
+q2_bayes_full_mod = brm(bf(q2_eff ~ s(date_id) + s(month, bs = 'cc', k = 12)),
+                        data = hill_time, family = gaussian(),
+                        cores = 4, seed = 42,
+                        iter = 7000, warmup = 5000, thin = 10,
+                        control = list(adapt_delta = 0.99),
+                        save_pars = save_pars(all = TRUE),
+                        file = here::here("sub-projects/trawl/derived-data/q2_full.rds"),
+                        file_refit = 'on_change')
+ceff2 <- conditional_effects(q2_bayes_full_mod, 'date_id')
+
+ceff2_df = data.frame(
+  date = ceff2$date_id$date_id,
+  qD = "2",
+  estimate = ceff2$date_id$estimate__,
+  upper = ceff2$date_id$upper__,
+  lower = ceff2$date_id$lower__
+)
+
+ceff_full = vctrs::vec_c(ceff01_df, ceff0.5_df, ceff1_df, ceff2_df) %>%
+  dplyr::mutate(Date = as.Date(date_id, origin = "2007-01-01"))
+
+hill_time %>%
+  dplyr::select(Date, date_id, q0.1_eff:q2_eff) %>%
+  pivot_longer(-Date:-date_id, names_to = "qD", values_to = "value") %>%
+  bind_rows(ceff_full) %>%
+  ggplot(aes(x = Date, y = value, group = qD, color = qD))+
+  geom_ribbon(data = ceff_full, aes(x = Date, ymin = lower, ymax = upper, group = qD, fill = qD),
+              color = NA, alpha =0.3, inherit.aes = FALSE)+
+  geom_line(data= ceff_full, aes(x = Date, y = estimate, group = qD, color = qD), inherit.aes = FALSE)+
+  geom_point(size = 1.5,show.legend=FALSE)+
+  geom_path(size = 1.2,show.legend=FALSE)+
+  guides(fill = 'none')+
+  scale_color_manual(values = viridis(n = 4),labels = c(expression(italic(''^0.1*D)),
+                                                        expression(italic(''^0.5*D)),
+                                                      expression(italic(''^1*D)),
+                                                      expression(italic(''^2*D)))) +
+  scale_fill_manual(values = viridis(n = 4),labels = c(expression(italic(''^0.1*D)),
+                                                       expression(italic(''^0.5*D)),
+                                                      expression(italic(''^1*D)),
+                                                      expression(italic(''^2*D))))+
+  scale_y_continuous(name = expression("Effective species (%)"), limits = c(0,100),
+                     expand = c(0.01,0.01)) +
+  scale_x_date(date_breaks = 'year', limits = c(as.Date("2009-01-01"),as.Date("2019-12-31")),
+               date_labels = "%Y", expand = c(0.01,0.01))+
+  guides(color = guide_legend(nrow = 1))+
   theme(legend.title = element_blank(),
-        legend.position = "none",
-        legend.justification = c(0,1))
+        legend.background = element_rect(fill = 'transparent', color = NA),
+        legend.position = c(0,1),
+        legend.justification = c(0,1),
+        axis.title.x= element_blank())
 

### 2021-11-24 datascript.R

@@ -7,5 +7,12 @@ load(here::here("data/biology_sysDate.rda"))
 ifelse((Sys.Date()-biology_sysDate) >= 30, source(here::here("sub-projects/trawl/R/import_bioData.R")),source(here::here("sub-projects/trawl/R/load_bioData.R")))
 rm(biology_sysDate)
 
+# important model variables for referencing
+iter = 7000
+warmup = 5000
+thin = 10
+adapt_delta = 0.99
+
+
 # import environmental data
 # source(here::here("R/load_enviroData.R"))

### 2021-11-24 docs/EML_metadata/metadata.R

@@ -1,0 +1,76 @@
+#  metadata creation file  #
+##  Hydro monitoring data  ##
+attributes <-
+  tibble::tribble(
+    ~attributeName, ~attributeDefinition,                                                 ~formatString, ~definition,        ~unit,   ~numberType,
+    "datetime",    "datetime stamp of collection. 2020-01-01 00:00:01",                 "YYYY-MM-DD HH:MM:SS",            NA, NA,       NA,
+    "year",       "year, 2012",                                                         "YYYY",        NA,                 NA,       NA,
+    "day",        "Julian day. Range: 1 - 209.",                                      "DDD",         NA,                 NA,       NA,
+    "i.flag",     "is variable Real, Interpolated or Bad (character/factor)",           NA,            NA,                 NA,       NA,
+    "variable",   "what variable being measured (character/factor)", NA,            NA,                 NA,       NA,
+    "value.i",    "value of measured variable on year/day/hour.min. Real",       NA,            NA,                 NA,       NA)
+
+i.flag <- c(R = "real",
+            I = "interpolated",
+            B = "bad")
+variable <- c(
+  temp_F  = "Temperature in Fahrenheit",
+  temp_C = "Temperature in Celcius",
+  do_mg_L = "Dissolved Oxygen Concentration mg/L",
+  spCon_uS_cm  = "Specific conductivity microSeimens/cm",
+  sal_psu = "Salinity in Practical Salinity Units (PSU; g/kg)"
+  )
+
+value.i <- c(
+  temp_F  = paste0(expression(degree*"F")),
+  temp_C = paste0(expression(degree*"C")),
+  do_mg_L = "[DO]; mg/L",
+  spCon_us_cm = paste0(expression(mu*"Siemens/cm")),
+  sal_psu = "Practical Salinity Units"
+)
+
+## Write these into the data.frame format
+factors <- rbind(
+  data.frame(
+    attributeName = "i.flag",
+    code = names(i.flag),
+    definition = unname(i.flag)
+  ),
+  data.frame(
+    attributeName = "variable",
+    code = names(variable),
+    definition = unname(variable)
+  ),
+  data.frame(
+    attributeName = "value.i",
+    code = names(value.i),
+    definition = unname(value.i)
+  )
+)
+
+
+attributeList <- EML::set_attributes(attributes, factors, col_classes = c("Date", "Date", "Date", "factor", "factor", "numeric"))
+
[…]

### 2021-11-24 docs/grant-docs/grant-figs.R

@@ -1,0 +1,242 @@
+# NSF-BIO-OCE grant figures
+source("install-packages.R")
+TB_trawl_data <- readRDS("./data/TB_trawl_data.rds")
+
+temp_TS = read_csv(file = "./data/TerrebonneBay_temp_2008-2020.csv", col_type = cols(ArrayID = col_skip(), yeardata = col_skip(), jday= col_skip(),
+                                                                               X4 = col_skip(), X5 = col_skip(), X6 = col_skip(), timedata = col_skip(),
+                                                                               X8 = col_skip(), `Date/Time` = col_datetime(format = "%m/%d/%Y %H:%M"),
+                                                                               `Water Temp C` = col_number(), `Water Temp <U+00B0>F` = col_skip())) %>%
+  rename(datetime = "Date/Time", temp_C = "Water Temp C") %>%
+  mutate(Date = as.Date(datetime,origin = "1970-01-01")) %>%
+  group_by(Date) %>%
+  summarise_at(vars("temp_C"), na.rm_mean)
+
+sal_TS = read_csv(file = "./data/TerrebonneBay_salinity_2008-2020.csv", col_type = cols(ArrayID = col_skip(), yeardata = col_skip(), jday = col_skip(), X4 = col_skip(),
+                                                                                        X5 = col_skip(), X6 = col_skip(), timedata = col_skip(), X8 = col_skip(), 
+                                                                                        X9 = col_datetime(format = "%m/%d/%Y %H:%M"), salinity1_avg = col_number())) %>%
+                    rename(datetime = 'X9',sal_psu = 'salinity1_avg') %>%
+  na.omit %>%
+  mutate(Date = as.Date(datetime,origin = "1970-01-01")) %>%
+  group_by(Date) %>%
+  summarise_at(vars("sal_psu"), na.rm_mean)
+
+date_TS = seq.Date(as.Date("2000-01-01"), as.Date(Sys.Date()), by = 'days') %>% data.frame %>% setNames(.,c("Date"))
+env_summ <- date_TS %>% left_join(temp_TS, all = TRUE) %>% left_join(sal_TS, all = TRUE)
+
[…]

### 2021-11-24 sub-projects/trawl/R/full_analyses.R

@@ -129,30 +129,6 @@ mth_group_stats = left_join(mth_chao1, mth_Sn) %>%
   pivot_longer(c(S_n,S_asymp, pct_rare),names_to = "index", values_to = "median" ) %>%
   ungroup
 
-# trawl_rarefaction analysis
-
-## Estimated mobr for monthly
-# trawl_mob_in = mobr::make_mob_in(comm = TB_trawl_trawl %>% dplyr::select(-date_id, -Date),
-#                                  plot_attr = TB_trawl_taxasite %>% dplyr::select(date_id, Date),
-#                                  coord_names = "date_id",
-#                                  latlong = FALSE)
-# 
-# trawl_mob_stats = mobr::get_mob_stats(trawl_mob_in, group_var = NULL, index = c("N", "S", "S_asymp", "S_n", "S_PIE", "PIE", "pct_rare"), effort_samples = S_n_mth, extrapolate = TRUE, boot_groups = FALSE, n_perm = nperm)
-
-## Figure of the temporal trends of 
-
-S_n_lab = paste0("S[",S_n,"]")
-
-# rich_time <-
-mth_group_stats %>%
-  dplyr::filter(index == 'S_n') %>%
-  ggplot(aes( x= Date, y = median))+
-  scale_y_continuous(name = expression("Rarefied richness ("*italic(S[n])*")"), limits = c(0,12))+
-  scale_x_date(date_breaks = "year", date_labels = "%Y")+
-  geom_point()+
-  geom_line()
-
-
 ## quantify loss and appearance of species in the timeseries
 trawl_mth_turnover = purrr::map(c('appearance','disappearance','total'),
                                 ~codyn::turnover(df = TB_trawl_taxasite_long %>% dplyr::select(-Date),
@@ -176,51 +152,112 @@ losses = trawl_mth_turnover %>%
 
 total = trawl_mth_turnover %>%
   dplyr::filter(variable == "total")
+
 mean(gains$value)
 mean(losses$value)
-trawl_mth_turnover %>%
-  na.omit %>%
-  ggplot()+
-  geom_line(aes(x = Date, y = value, group = variable, color = variable), size = 1.1)+
-  scale_color_manual(values = viridis(n = 3, option = 'viridis'))+
-  scale_y_continuous(name = 'Species turnover',limits = c(0,1), expand = c(0.01,0.01))+
-  scale_x_date(date_breaks = 'year', limits = c(as.Date("2009-01-01"),as.Date("2019-12-31")),
-               date_labels = "%Y")+
[…]

### 2022-06-17 sub-projects/trawl/docs/ms/ms.RMD
Big commit. Updated qD models and plots. work on manuscript to finalize results

--- 2021-11-18 sub-projects/trawl/docs/ms/ms.RMD
@@
 author:
-   - James R Junker:
+   - name: James R Junker
      email: james.junker1@gmail.com
      institute: [glrc, lumcon]
-     correspondence: yes
-   - Craig R McClain:
+     correspondence: true
+   - name: Craig R McClain
      institute: lumcon
@@
 ```{r Rmarkdown setup, include = FALSE, echo=F, warning=FALSE, message=FALSE}
+
+knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
 here::i_am("sub-projects/trawl/docs/ms/ms.RMD")
@@
 source(here::here("sub-projects/trawl/R/Evenness.R"))
+
+library(mgcv)
+library(brms)
+library(bayesplot)
+
+rerunEven  = FALSE
+rerunD = FALSE
 # which years should we remove
-year_removals = c("2007","2020","2021")
+year_removals = c("2007","2020","2021","2022")
 
@@
 TB_trawl_taxasite <- TB_trawl_data %>%
-  dplyr::filter(year(Date) %ni% year_removals) %>%
   dplyr::mutate(Date = as.Date(paste0(as.character(year),"-",as.character(month),"-01"))) %>%
@@
   group_by(Date, date_id, Common_name) %>%
-  summarise(Abundance = sum(Abundance)) %>%
+  dplyr::summarise(Abundance = sum(Abundance)) %>%
   na.omit %>% group_by(Date, date_id, Common_name) %>%
@@
 
-# # create bootstrapped data set to estimate variability
-# TB_trawl_boots = TB_trawl_data %>%
-#   group_by(year) %>%
-#   modelr::bootstrap(TB_trawl_data)
+TB_trawl_taxasite_long %>%
+  dplyr::filter(!duplicated(Common_name )) %>%
+  dplyr::mutate(Date = as.Date(Date)) %>%
+  arrange(Date) %>%
+  dplyr::mutate(richness = 1:n())-> TB_time_accum
+
+TB_trawl_effort_mth = TB_trawl_data %>%
+  dplyr::filter(year(Date) %ni% year_removals) %>%
+  dplyr::select(Date, date_id) %>%
+  group_by(date_id) %>%
+  dplyr::summarise(trawl_n = n()) %>%
+  dplyr::mutate(Date = as.Date(date_id, origin = "2007-01-01")) %>%
+  dplyr::select(Date, trawl_n)
 
@@
 Yet, understanding how communities change through time is crucial for predicting current and future changes to biological systems and ecosystem services.
+
 <!--- --->
@@
 Intrinsic and extrinsic processes can interact, leading to temporal patterns of biodiversity change that vary in response to environmental change.
-For example, gradual environmental change over time can lead to gradual community shifts or these shifts may be undetectable or abrupt [@williams2011][@scheffer2003].
+For example, gradual environmental change over time can lead to gradual community shifts or these shifts may be undetectable or abrupt [@williams2011; @scheffer2003].
 
+<!--- --->
 Disentangling the complexity of drivers and responses in community structure is especially pressing for marine systems.
@@
 
+<!--- --->
 Here, we quantified biodiversity changes within a shallow estuarine community over a decade to understand shifts in total species richness, the relative distribution of abundant and rare species, and potential change points in community composition through time...
@@
 This study was focused on Terrebonne Bay, located in the northern Gulf of Mexico of Louisiana, USA (29^$\circ$^11.200'N, 90^$\circ$^36.560'W; Figure S1).
-Terrebonne Bay is a broad (1,761 km2), shallow estuary (average depth 2m), separated from the Gulf of Mexico by two barrier island chains and connected by four tidal passes.
-The bay-estuary complex is part of an abandoned distributary of the Mississippi River and therefore no longer receives any significant riverine inputs.
+Terrebonne Bay is a broad (1,761 km2), shallow estuary (average depth ~2m), separated from the Gulf of Mexico by two barrier island chains and connected by four tidal passes.
+The bay-estuary complex is part of an abandoned distributary of the Mississippi River and therefore no longer receives significant riverine inputs.
 Thus, the majority of its freshwater inputs are from the local drainage basin [@bianchi2009].
-While water column salinity and density are homogenous, strong salinity gradients exist seaward from the marsh to the barrier islands [@bianchi2009].
+While water column salinity and density are homogeneous, strong salinity gradients exist seaward from the marsh to the barrier islands [@bianchi2009].
 Tides in Terrebonne Bay are diurnal with a semidiurnal component, ranging 20-80 cm [@inoue2000].
@@
 
-Trawl sampling was conducted as part of the Louisiana Universities Marine Consortium's (LUMCON) educational outreach program (https://www.lumcon.edu/education-and-outreach).
+Trawl sampling was conducted as part of the Louisiana Universities Marine Consortium's (LUMCON) educational outreach program (https://www.lumcon.edu/education-and-outreach) from 2009 to 2019.
 Individual trawls were conducted using *trawl apparatus description...* for 10 - 20 min.
-To minimize the effects of trawl-to-trawl variability, we combined all trawls monthly.
+To dampen potentially volatile trawl-to-trawl variability, we combined all trawls monthly and therefore report changes based on monthly aggregated trawl sampling.
 
@@
 
-Species names were checked for typos and confirmed using the *gni_parse* function from the *taxize* package [@chamberlain2020] and further standardized to consistent taxonomic resolution for entire data series (Supplemental materials).
+Species names were checked for typos and confirmed using the *gni_parse* function from the *taxize* package [@chamberlain2020] and further standardized to consistent taxonomic resolution for the entire data series (Supplemental materials).
 To track trends in species richness through time, we calculated  effort-controlled  species richness, *S~n~*, which provides the expected number of species given a defined number of *n* randomly sampled individuals [@gotelli2001].
@@
 
-To test for changes in species richness over time, we fit bayesian implementations of generalized additive models (GAMs) using the `mgcv` [@wood2011] and  `brms` package in R [@burkner2017; @burkner2018].
+To detect trends in species richness and other dimensions of biodiversity (e.g., turnover, evenness, etc.) we used generalized additive models (GAMs) with a bayesian implementations using the `mgcv` [@wood2011] and  `brms` packages in R [@burkner2017; @burkner2018].
+Full models included alinear term for trawl date and smoothing spline terms for month:
+$$y = \beta_0 + \beta_1 * time + f_{season}(x_1) + \varepsilon,\;\;\; \varepsilon ~ N(0, \sigma^{2} \Lambda) $$
+where, $y$ is the response variable (e.g., richness, turnover, evenness, etc.), $\beta_0$ is an intercept, $\beta_1$ a coefficient for trawl date, and $f_{season}$ represents seasonal smooth functions for month of year.
+Seasonal terms were fit with cyclic cubic regression splines with smoothing dimension *k* = 12 to allow for continuity between December and January among model years.
 
 # Results
-
-```{r env data, echo=FALSE, warning=FALSE, message=FALSE}
-
-```
 
@@
 
+mth_even = TB_trawl_taxasite %>%
+  dplyr::select(-Date, -date_id) %>%
+  apply(., 1, gini_even) %>%
+  t() %>%
+  data.frame() %>%
+  bind_cols(TB_trawl_taxasite[,c('Date','date_id')], .) %>%
+  setNames(., c("Date","date_id", "gini_raw", "gini_norm")) %>%
+  dplyr::mutate(month = month(Date)) %>%
+  # pivot_longer(-Date:-date_id, names_to = "measure", values_to = "median") %>%
+  ungroup
+
+# mth_even %>%
+#   ggplot(aes(x = Date, y = gini_norm))+
+#   geom_point()+
+#   geom_line()+
+#   scale_y_continuous(name = 'Normalized Gini coefficient', limits = c(0,0.5))+
+#   scale_x_date(date_breaks = 'year', limits = c(as.Date("2009-01-01"),as.Date("2019-12-31")),
+#                date_labels = "%Y")
+
+mth_group_stats = mth_group_stats %>%
+  bind_rows(mth_even %>%
+              pivot_longer(-Date:-date_id, names_to = 'index', values_to = 'median'))
+
+## quantify loss and appearance of species in the timeseries
+trawl_mth_turnover = purrr::map(c('appearance','disappearance','total'),
+                                ~codyn::turnover(df = TB_trawl_taxasite_long %>% dplyr::select(-Date),
+                                                 time.var = 'date_id',
+                                                 species.var = 'Common_name',
+                                                 abundance.var = 'Abundance',
+                                                 metric = .x) %>%
+                                  data.frame %>%
+                                  dplyr::mutate(date_id = date_id,
+                                                variable = .x) %>%
+                                  dplyr::rename(value = !!names(.[1])) %>%
+                                  bind_rows(data.frame(value = NA_real_, variable =.x))) %>%
+  bind_rows %>%
+  left_join(TB_trawl_taxasite[,c(1,2)],.,by = 'date_id')
+
+gains = trawl_mth_turnover %>%
+  dplyr::filter(variable == "appearance")
+
+losses = trawl_mth_turnover %>%
+  dplyr::filter(variable == "disappearance")
+
+total = trawl_mth_turnover %>%
+  dplyr::filter(variable == "total")
+
+## add trendline in for A and B
+
+```
+
+```{r evenness, echo = FALSE, warning=FALSE, message=FALSE }
+if(rerunEven){
+source(here::here("sub-projects/trawl/R/run_evenness_models.R"))
+} else if(!all(file.exists(c(here::here("sub-projects/trawl/derived-data/even_null.rds"),
+                             here::here("sub-projects/trawl/derived-data/even_s.rds"),
+                             here::here("sub-projects/trawl/derived-data/even_full.rds"))))){
+  source(here::here("sub-projects/trawl/R/run_evenness_models.R"))
+} else{
+  even_bayes_full_mod = readRDS(here::here("sub-projects/trawl/derived-data/even_full.rds"))
+  even_bayes_s_mod = readRDS(here::here("sub-projects/trawl/derived-data/even_s.rds"))
+  even_bayes_null_mod = readRDS(here::here("sub-projects/trawl/derived-data/even_null.rds"))
+}
+
 ```
@@
 <!--- Outline the general patterns annually and  --->
-Over the sampling period from `r min(TB_trawl_sampling$year, na.rm = TRUE)` to `r max(TB_trawl_sampling$year, na.rm = TRUE)`, `r length(unique(TB_trawl_data$Date))` trawls-days were performed yielding `r format(signif(sum(TB_trawl_data$Abundance, na.rm = TRUE),3), scientific = TRUE)` individuals.
-Among years, total effort generally increased, both in number of trawl-days and individuals counted, from a minimum effort of `r min(TB_trawl_sampling$trawl_days)` (`r TB_trawl_sampling %>% slice_min(trawl_days) %>% dplyr::select(year) %>% unlist`) to `r max(TB_trawl_sampling$trawl_days)` (`r TB_trawl_sampling %>% slice_max(trawl_days) %>% dplyr::select(year) %>% unlist`) days and from `r min(TB_trawl_sampling$individuals, na.rm = TRUE)` (`r TB_trawl_sampling %>% slice_min(individuals) %>% dplyr::select(year) %>% unlist`) to `r format(signif(max(TB_trawl_sampling$individuals, na.rm = TRUE),3), scientific = TRUE)` (`r TB_trawl_sampling %>% slice_max(individuals) %>% dplyr::select(year) %>% unlist`) individuals.
+Over the sampling period from `r min(TB_trawl_sampling_yr$year, na.rm = TRUE)` to `r max(TB_trawl_sampling_yr$year, na.rm = TRUE)`, `r length(unique(TB_trawl_data$Date))` trawl-days were performed yielding `r format(signif(sum(TB_trawl_data$Abundance, na.rm = TRUE),3), scientific = TRUE)` individuals.
+Among years, total effort generally increased, both in number of trawl-days and individuals counted, from a minimum effort of `r min(TB_trawl_sampling_yr$trawl_days)` (`r TB_trawl_sampling_yr %>% slice_min(trawl_days) %>% dplyr::select(year) %>% unlist`) to `r max(TB_trawl_sampling_yr$trawl_days)` (`r TB_trawl_sampling_yr %>% slice_max(trawl_days) %>% dplyr::select(year) %>% unlist`) days and from `r min(TB_trawl_sampling_yr$individuals, na.rm = TRUE)` (`r TB_trawl_sampling_yr %>% slice_min(individuals) %>% dplyr::select(year) %>% unlist`) to `r format(signif(max(TB_trawl_sampling_yr$individuals, na.rm = TRUE),3), scientific = TRUE)` (`r TB_trawl_sampling_yr %>% slice_max(individuals) %>% dplyr::select(year) %>% unlist`) individuals.
 In total, `r length(unique(TB_trawl_data$Common_name))` unique species were identified and new species were consistently observed throughout the sampling period (Figure S1).
@@
 Here, effort-controlled species richness, *S~`r S_n_yr`~*, diverged qualitatively from *S~asymp~* and was generally constant with an apparent slight increase in more recent sampling years.
-Overall, *S~`r S_n_yr`~* ranged from `r yr_group_stats %>% dplyr::filter(index == "S_n_yr") %>% slice_min(median) %>% dplyr::select(median) %>% round(1)` to `r yr_group_stats %>% dplyr::filter(index == "S_n_yr") %>% slice_max(median) %>% dplyr::select(median) %>% round(1)` among all years.
-Monthly, of rarefied richness averaged `r round(mean(mth_sn$S_n, na.rm = TRUE),1)` [range: `r round(min(mth_sn$S_n, na.rm = TRUE),1)`--`r round(max(mth_sn$S_n, na.rm = TRUE),1)`] and exhibited seasonal oscillations, but no detectable trend over time (Figure 1a, Table S1).
+Overall, *S~`r S_n_yr`~* ranged from `r yr_group_stats %>% dplyr::filter(index == "S_n") %>% slice_min(median) %>% dplyr::select(median) %>% round(1)` to `r yr_group_stats %>% dplyr::filter(index == "S_n") %>% slice_max(median) %>% dplyr::select(median) %>% round(1)` among all years.
+Monthly, of rarefied richness averaged `r round(mean(mth_Sn$S_n, na.rm = TRUE),1)` [range: `r round(min(mth_Sn$S_n, na.rm = TRUE),1)`--`r round(max(mth_Sn$S_n, na.rm = TRUE),1)`] and exhibited seasonal oscillations, but no detectable trend over time (Figure 1A, Table S1).
 
-```{r figure 1, echo = FALSE, warning = FALSE, message=FALSE, fig.cap="Figure 1.
-Multiple measures of species richness within the trawl community between the years 2007 to 2019 show continual accumulation of species (purple points and line) through the timeseries.
-The estimated asymptotic species richness over a calendar year (Sasymp; median values and 95% percentile interval represented by yellow points and area), suggests increasing numbers of species within the community over time.
-However, rarefied species richness controlled to 900 individuals (S900; median values and 95% percentil interval represented by green line and area) suggests the perceived increase in Sasymp may represent an effect of increased sampling effort"}
+```{r figure 1, echo = FALSE, warning = FALSE, message=FALSE, fig.height=8.5, fig.width=8.5, fig.cap="Figure 1.
+A) Rarefied species richness within the nekton community between the years 2009 to 2019 show variable, but consistent, numbers of species over time.
+B) Despite no trend in the total number of species, the trawl community showed continual turnover throughout."}
 
-TB_trawl_taxasite_long %>%
-  dplyr::filter(!duplicated(Common_name )) %>%
-  dplyr::mutate(Date = as.Date(Date)) %>%
-  arrange(Date) %>%
-  dplyr::mutate(richness = 1:n())-> TB_time_accum
+## Goals estimate the rarified richness through time
+## Show changes in evenness and Hill #s
 
@@
   ggplot(aes( x= Date, y = median))+
-  scale_y_continuous(name = expression("Rarefied richness ("*italic(S[n])*")"), limits = c(0,12))+
-  scale_x_date(date_breaks = "1 year", date_labels = "%Y",limits = c(as.Date("2009-01-01"),as.Date("2019-12-31"))) +
-  geom_point(size = 1.5) +
-  geom_line(size = 1.2) 
-  theme()
+  scale_y_continuous(name = expression("Rarefied richness ("~italic(~S[n])~")"), limits = c(1,12),
+                     breaks = c(1,5,10),expand = c(0.01,0.01))+
+  scale_x_date(date_breaks = "year", limits = c(as.Date("2009-01-01"),as.Date("2019-12-31")),
+               date_labels = "%Y",expand = c(0.01,0.01))+
+  geom_point(size = 2)+
+  geom_line(size = 1.2)+
+  theme_tufte()+
+  geom_rangeframe(sides = "l")+
+  annotate('text', label = "A", x = as.Date("2009-01-30"), y = 11, family ='serif', size = 8, hjust = 0)+
+  theme(axis.title.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        axis.text.x = element_blank(),
+        # panel.grid.minor.x = element_line(color = 'lightgray'),
+        plot.margin = unit(c(0.0,0.1,-0.1,0.0), 'cm'), 
+        plot.background = element_rect(fill = 'transparent', color = NA),
+        panel.background = element_rect(fill = 'transparent', color = NA),
+        axis.title.y = element_text(family = 'serif', size = 16),
+        axis.text = element_text(family = 'serif', size = 14)) -> rich_time;
+
+trawl_mth_turnover %>%
+  dplyr::filter(variable == 'total') %>%
+  na.omit %>%
+  ggplot(aes(x = Date, y = value, group = variable, color = variable))+
+  geom_point(size = 2)+
+  geom_line(size = 1.2)+
+  scale_color_manual(values = viridis(n = 1, option = 'viridis', begin = .75))+
+  scale_y_continuous(name = 'Species turnover',limits = c(0,1), expand = c(0.01,0.01),
+                     breaks = c(0,0.2 ,0.4, 0.6, 0.8), labels = c(0,0.2,0.4,0.6,0.8))+
+  scale_x_date(date_breaks = 'year', limits = c(as.Date("2009-01-01"),as.Date("2019-12-31")),
+               date_labels = "%Y",expand = c(0.01,0.01))+
+  theme_tufte()+
+  geom_rangeframe(sides = "lb", color = 'black')+
+  annotate('text', label = "B", x = as.Date("2009-01-30"), y = 1, family = 'serif', vjust = 1, size = 8, hjust = 0)+
+  theme(legend.position = "none",
+        legend.justification = c(0,1),
+        axis.title.x = element_blank(),
+        plot.margin = unit(c(-0.18,0.15,0.0,0.0), 'cm'),
+        # panel.grid.minor.x = element_line(color = 'lightgray'),
+        plot.background = element_rect(fill = 'transparent', color = NA), 
+        axis.title.y = element_text(family = 'serif', size = 16),
+        axis.text = element_text(family = 'serif', size = 14)) -> turnover_time
+
+g2 <- ggplotGrob(rich_time)
+g3 <- ggplotGrob(turnover_time)
+g2$widths <- unit.pmax(g2$widths, g3$widths)
+g3$widths <- unit.pmax(g2$widths, g3$widths)
+grid.arrange(g2,g3, layout_matrix = rbind(1,1,1,1,2,2))
 
@@
 
-```{r turnover, echo = FALSE, warning=FALSE, message=FALSE}
+```{r diversity2 plot, echo = FALSE, warning=FALSE, message=FALSE, fig.cap= "Figure 2.
+A) Temporal trends in the effective number of species of select orders of diversity (q = 0.1, 1,2).
+Effective species are presented as percentages of ^0^D, or species richness.
+^0.1^D highlights the trends in the percentage of species considered very rare, while ^1^D treats rare and dominant species equally, and ^2^D highlights the number of dominant species in the community through time.
+^1^D is equivalent to exp(Shannon-Weiner H) and ^2^D is equivalent to 1/Simpson's diversity index.
+B) The estimated temporal trend for ^q^D orders (q = 0.1--3) from conditional effects of time in generalized additive models.
+The black line represents the mean estimate surrouned by 25^th^ and 75^th^ (dark grey) and 5^th^ and 95^th^ percentiles (light grey) of the posterior distribution."}
 
-## quantify loss and appearance of species in the timeseries
-trawl_mth_turnover = purrr::map(c('appearance','disappearance','total'),
-                                     ~codyn::turnover(df = TB_trawl_taxasite_long,
-                                                      time.var = 'date_id',
-                                                      species.var = 'Common_name',
-                                                      abundance.var = 'Abundance',
-                                                      metric = .x) %>%
-                                       data.frame %>%
-                                       dplyr::mutate(Date = as.Date(paste0(unique(TB_trawl_yr$year)[-1],"-01-01"), format = "%Y-%m-%d"),
-                                                     variable = .x) %>%
-                                       dplyr::rename(value = !!names(.[1])) %>%
-                                       bind_rows(data.frame(value = NA_real_, time.var = NA_real_, Date = as.Date("2008-01-01"), variable =.x))) %>%
-                                     bind_rows
-gains = trawl_yr_turnover %>%
-  dplyr::filter(variable == "appearance")
+#### patterns of Hill diversity through time}
+## hill
 
-losses = trawl_yr_turnover %>%
-  dplyr::filter(variable == "disappearance")
+hill_time = function(x,...){
+  hillR::hill_taxa(TB_trawl_taxasite %>% dplyr::select(-Date,-date_id), q = x) %>%
+    data.frame %>% dplyr::mutate(q = paste0("q",as.character(x))) %>% setNames(.,c('value','q')) %>%
+    bind_cols(TB_trawl_taxasite %>% dplyr::select(Date, date_id),.)
+}
+# debugonce(hill_time)
+hill_time_df = furrr::future_map(seq(0,3, by = 0.1), ~hill_time(.x)) %>%
+  bind_rows %>%
+  group_by(Date, date_id) %>% 
+  pivot_wider(names_from = 'q', values_from = 'value') %>%
+  dplyr::mutate(across(contains('q'), list(~(.x/q0)*100), .names = "{.col}_eff")) %>%
+  dplyr::mutate(month = month(Date)) %>%
+  dplyr::select(date_id, month, contains('eff'))
 
-total = trawl_yr_turnover %>%
-  dplyr::filter(variable == "total")
+eff_cols = names(hill_time_df)[grepl("*eff", names(hill_time_df))]
+
+model_qD = function(x,...){
+  form_string = paste(x," ~ date_id + s(month, bs = 'cc', k = 12)")
+  bayes_form = bf(formula = formula(form_string))
+  mod = brm(bayes_form,
+            data = hill_time_df,
+            family = gaussian(),
+            cores = 4, seed = 42,
+            iter = 30000, warmup = 25000, thin = 10,
+            control = list(adapt_delta = 0.99),
+            save_pars = save_pars(all = TRUE),
+            file = paste0(here::here("sub-projects/trawl/derived-data"),"/",as.character(x),"_full.rds"),
+            file_refit = 'on_change')
+
+  return(posterior_summary(mod, pars = 'date_id', probs = c(0.025,0.25,0.5,0.75,0.975)))
+}
+
+if(rerunD){
+  # debugonce(model_qD)
+eff_cols %>%
+    furrr::future_map(~model_qD(.x)) %>%
+    setNames(., nm = eff_cols) %>%
+    saveRDS(file = here::here("sub-projects/trawl/derived-data/qD_coefs.rds"))
+}
+
+qD_coefs = readRDS( file = here::here("sub-projects/trawl/derived-data/qD_coefs.rds"))
+qD_coefs_df = qD_coefs %>% lapply(., data.frame) %>% bind_rows(.id = "model") %>%
+  dplyr::mutate(q = as.numeric(sub("^q(\\d{1}|\\d{1}.\\d{1}).*","\\1", model)))
+
+q0.1_bayes_full_mod = readRDS(file = here::here("sub-projects/trawl/derived-data/q0.1_eff_full.rds"))
+
+ceff0.1 <- conditional_effects(q0.1_bayes_full_mod, 'date_id')
+
+ceff0.1_df = data.frame(
+  date_id = ceff0.1$date_id$date_id,
+  qD = "q0.1_eff",
+  estimate = ceff0.1$date_id$estimate__,
+  upper = ceff0.1$date_id$upper__,
+  lower = ceff0.1$date_id$lower__
+)
+
+q0.5_bayes_full_mod = readRDS(file = here::here("sub-projects/trawl/derived-data/q0.5_eff_full.rds"))
+
+ceff0.5 <- conditional_effects(q0.5_bayes_full_mod, 'date_id')
+
+ceff0.5_df = data.frame(
+  date_id = ceff0.5$date_id$date_id,
+  qD = "q0.5_eff",
+  estimate = ceff0.5$date_id$estimate__,
+  upper = ceff0.5$date_id$upper__,
+  lower = ceff0.5$date_id$lower__
+)
+
+q2_bayes_full_mod = readRDS(file = here::here("sub-projects/trawl/derived-data/q2_eff_full.rds"))
+
+ceff2 <- conditional_effects(q2_bayes_full_mod, 'date_id')
+
+ceff2_df = data.frame(
+  date_id = ceff2$date_id$date_id,
+  qD = "q2_eff",
+  estimate = ceff2$date_id$estimate__,
+  upper = ceff2$date_id$upper__,
+  lower = ceff2$date_id$lower__
+)
+
+ceff_full = vctrs::vec_c(ceff0.1_df, ceff0.5_df, ceff2_df) %>%
+  dplyr::mutate(Date = as.Date(date_id, origin = "2007-01-01"))
+
+hill_time_df %>%
+  dplyr::select(Date, date_id, q0.1_eff, q0.5_eff, q2_eff) %>%
+  pivot_longer(-Date:-date_id, names_to = "qD", values_to = "value") %>%
+  bind_rows(ceff_full) %>%
+  ggplot(aes(x = Date, y = value, group = qD, color = qD))+
+  geom_ribbon(data = na.omit(ceff_full), aes(x = Date, ymin = lower, ymax = upper, group = qD, fill = qD),
+              color = NA, alpha =0.3, inherit.aes = FALSE)+
+  geom_line(data= na.omit(ceff_full), aes(x = Date, y = estimate, group = qD, color = qD), inherit.aes = FALSE)+
+  geom_point(size = 1.5,show.legend=FALSE)+
+  geom_path(size = 1.2,show.legend=FALSE)+
+  guides(fill = 'none')+
+  theme_tufte()+
+  geom_rangeframe(data = hill_time_df %>%
+  dplyr::select(Date, date_id, q0.1_eff, q0.5_eff, q2_eff) %>%
+  pivot_longer(-Date:-date_id, names_to = "qD", values_to = "value"), aes(x = Date, y =value), sides = "bl", color = 'black', inherit.aes = FALSE)+
+  scale_color_manual(values = viridis(n = 3),labels = c(expression(italic(''^0.1*D)),
+                                                        expression(italic(''^1*D)),
+                                                        expression(italic(''^2*D)))) +
+  scale_fill_manual(values = viridis(n = 3),labels = c(expression(italic(''^0.1*D)),
+                                                       expression(italic(''^1*D)),
+                                                       expression(italic(''^2*D))))+
+  scale_y_continuous(name = expression("Effective species (%)"), limits = c(0,100),
+                     expand = c(0.01,0.01)) +
+  scale_x_date(date_breaks = 'year', limits = c(as.Date("2009-01-01"),as.Date("2019-12-31")),
+               date_labels = "%Y", expand = c(0.01,0.01))+
+  guides(color = guide_legend(nrow = 1))+
+  annotate('text', label = 'A', x = as.Date("2009-01-01"), y = Inf, size = 8, hjust = 0, vjust = 1, family ='serif')+
+  theme(axis.title.x = element_blank(),
+        legend.title = element_blank(),
+        legend.background = element_rect(fill = 'transparent', color = NA),
+        legend.position = c(0,0),
+        legend.justification = c(0,0)) -> hill_time_plot
+
+qD_coefs_df = qD_coefs_df %>%
+  dplyr::mutate(across(c("Estimate",matches("Q\\d{1,2}")), ~.x *365))
+
+qD_coefs_df %>% 
+  ungroup %>%
+  dplyr::filter(q != 0) %>%
+  ggplot()+
+  geom_ribbon(aes(y = q, xmin = Q2.5, xmax = Q97.5), color = 'lightgrey', alpha = 0.3)+
+  geom_ribbon(aes(y = q, xmin = Q25, xmax = Q75), color = 'lightgrey', alpha = 0.5)+
+  geom_path(aes(y = q, x = Estimate), size = 1.2)+
+  annotate('text', label = 'B', x = -2.5, y = 0, hjust = 0, vjust = 1, size = 8, family = 'serif')+
+  theme_tufte()+
+  geom_rangeframe(data = qD_coefs_df %>% 
+  ungroup %>%
+  dplyr::filter(q != 0),
+  sides = "br", color = "black")+
+  scale_y_continuous(name = expression(italic(""^q*"D")), 
+                         trans = scales::reverse_trans(),
+                     limits = c(3,0), expand = c(0.01,0.01), position = 'right')+
+  scale_x_continuous(name = expression('Temporal trend ('*Delta*'%/year)'),
+                     expand = c(0.01,0.01), limits = c(-2.5,0)) -> qD_trend_plot
+
+g4 <- ggplotGrob(hill_time_plot)
+g5 <- ggplotGrob(qD_trend_plot)
+g4$heights <- unit.pmax(g4$heights, g5$heights)
+g5$heights <- unit.pmax(g4$heights, g5$heights)
+grid.arrange(g4,g5, layout_matrix = cbind(1,1,1,1,2,2))
+
+even_ceff <- conditional_effects(even_bayes_full_mod, 'date_id')
+# plot(ceff)
+
+even_ceff_plot = data.frame(
+  date = round(even_ceff$date_id$date_id,0),
+  estimate = even_ceff$date_id$estimate__,
+  upper = even_ceff$date_id$upper__,
+  lower = even_ceff$date_id$lower__
+) %>%
+  dplyr::mutate(Date = as.Date(date, origin = as.Date("2007-01-01")))
+
+# Add in horizontal lines
 
@@
 
-Consistent with the pattern of continued accumulation of new species throughout the sampling series and relatively stable effort-controlled richness, species gains (`r round(mean(gains$value, na.rm = TRUE),2)` $\pm$ `r round(sd(gains$value, na.rm = TRUE),2)` SD) and losses (`r round(mean(losses$value, na.rm = TRUE),2)` $\pm$ `r round(sd(losses$value, na.rm = TRUE),2)` SD) generally balanced over time (Figure 1b).
-Total turnover was variable but relatively stable (`r round(mean(total$value, na.rm = TRUE),2)` $\pm$ `r round(sd(total$value, na.rm = TRUE),2)` SD) and exhibited no detectable trend or coherent seasonal component.
+Consistent with the pattern of continued accumulation of new species throughout the sampling series and relatively stable effort-controlled richness, species gains (`r round(mean(gains$value, na.rm = TRUE),2)` $\pm$ `r round(sd(gains$value, na.rm = TRUE),2)` SD) and losses (`r round(mean(losses$value, na.rm = TRUE),2)` $\pm$ `r round(sd(losses$value, na.rm = TRUE),2)` SD) generally balanced over time.
+Total turnover was variable but relatively stable (`r round(mean(total$value, na.rm = TRUE),2)` $\pm$ `r round(sd(total$value, na.rm = TRUE),2)` SD) and exhibited no detectable trend or coherent seasonal component (Figure 1B).
+Species turnover was likely confined to species with moderate relative abundances.
+While we observed declines in the effective number of species for highly rare (^0.1^D; conditional effects `r round(summary(q0.1_bayes_full_mod)[['fixed']]['date_id','Estimate'],3)`, 95% CI: `r round(summary(q0.1_bayes_full_mod)[['fixed']]['date_id','l-95% CI'],3)`--`r round(summary(q0.1_bayes_full_mod)[['fixed']]['date_id','u-95% CI'],3)`) and highly abundant species (^2^D; `r round(summary(q2_bayes_full_mod)[['fixed']]['date_id','Estimate'],3)`, 95% CI: `r round(summary(q2_bayes_full_mod)[['fixed']]['date_id','l-95% CI'],3)`--`r round(summary(q2_bayes_full_mod)[['fixed']]['date_id','u-95% CI'],3)`), declines were greater for diversity orders describing moderately abundant species (^0.5^D; `r round(summary(q0.5_bayes_full_mod)[['fixed']]['date_id','Estimate'],3)`, 95% CI: `r round(summary(q0.5_bayes_full_mod)[['fixed']]['date_id','l-95% CI'],3)`--`r round(summary(q0.5_bayes_full_mod)[['fixed']]['date_id','u-95% CI'],3)`, Figure 2).
+These changes in the distribution of relative abundances within the community led to a decrease in the community evenness through time (Figure X).
+Gini coefficients normalized for species richness varied from `r mth_even %>% dplyr::select(gini_norm) %>% min %>% unlist %>% round(3)` to `r mth_even %>% dplyr::select(gini_norm) %>% max %>% unlist %>% round(3)` and exhibited estimated declines from initial values of `r even_ceff_plot %>% slice_min(date) %>% dplyr::select(estimate) %>% unlist %>% round(3)` (`r even_ceff_plot %>% slice_min(date) %>% dplyr::select(lower) %>% unlist %>% round(3)`--`r even_ceff_plot %>% slice_min(date) %>% dplyr::select(upper) %>% unlist %>% round(3)` 95% CI) to `r even_ceff_plot %>% slice_max(date) %>% dplyr::select(estimate) %>% unlist %>% round(3)` (`r even_ceff_plot %>% slice_max(date) %>% dplyr::select(lower) %>% unlist %>% round(3)`--`r even_ceff_plot %>% slice_max(date) %>% dplyr::select(upper) %>% unlist %>% round(3)` 95% CI) in 2019.
 
-```{r turnover plot ,echo = FALSE, warning=FALSE, message=FALSE, fig.cap = "Figure 2. Total species turnover and partitioning of species gains and losses over time."}
-trawl_mth_turnover %>%
-  na.omit %>%
+```{r evenness plot, echo=FALSE, warning=FALSE, message=FALSE,fig.cap= "Figure 4.
+Evenness in species' relative abundances normalized to species richness varied seasonally and exhibited a moderate decrease through time.
+The blue line represents the mean estimated trend surrounded by the 5^th^ and 95^th^ posterior percentile "}
+
+even_ceff_plot %>%
   ggplot()+
-  geom_line(aes(x = Date, y = value, group = variable, color = variable), size = 1.1)+
-  scale_color_manual(values = viridis(n = 3, option = 'viridis'))+
-  scale_y_continuous(name = 'Species turnover',limits = c(0,1), expand = c(0.01,0.01))+
+  geom_ribbon(aes(x = Date, ymin = lower, ymax = upper), color = "grey", fill = 'grey', alpha = 0.4)+
+  geom_line(aes(x = Date, estimate), color = 'blue', size = 1.1)+
+  geom_point(data = mth_even, aes(x = Date, y = gini_norm), color = 'black')+
+  geom_line(data = mth_even, aes(x = Date, y = gini_norm), color = 'black', size = 1.2)+
   scale_x_date(date_breaks = 'year', limits = c(as.Date("2009-01-01"),as.Date("2019-12-31")),
                date_labels = "%Y")+
-  theme(legend.position = c(0,1),
-        legend.justification = c(0,1),
-        legend.background = element_rect(fill = 'transparent', color = NA),
-        legend.title = element_blank(),
-        axis.title.x = element_blank())
+  scale_y_continuous(name = "Normalized Gini coefficient", limits = c(0,0.55), expand = c(0.01,0.01),
+                     breaks = c(0,0.25,0.5))+
+  theme_tufte() +
+  geom_rangeframe(data = mth_even,aes(x = Date, y = gini_norm),
+                  sides = "bl", color = "black", na.rm = TRUE, inherit.aes = FALSE)+
+  theme(axis.title.x = element_blank())
 ```
 
-```{r annual qD, echo=FALSE, warning=FALSE, message=FALSE}
-set.seed(123)
-q2_boots = boot_sample_groups(TB_trawl_taxasite %>% dplyr::select(-julian_date,-Date,-month,-biweekly), 
-                   group_var = 'year',
-                   qD = 2,
-                   n_perm = nperm)
-set.seed(123)
-q1_boots = boot_sample_groups(TB_trawl_taxasite %>% dplyr::select(-julian_date,-Date,-month,-biweekly), 
-                              group_var = 'year',
-                              qD = 1,
-                              n_perm = nperm)
-
-qD_df = q2_boots %>% 
-  # summarise q2 by year
-  group_by(year) %>%
-  dplyr::summarise(across(q2, list(mean = ~mean(.x, na.rm = TRUE),
-                                   median = ~quantile(.x, 0.5, na.rm = TRUE),
-                                   quant2.5= ~quantile(.x, 0.025, na.rm = TRUE),
-                                   quant25= ~quantile(.x, 0.25, na.rm = TRUE),
-                                   quant75= ~quantile(.x, 0.75, na.rm = TRUE),
-                                   quant97.5= ~quantile(.x, 0.975, na.rm = TRUE)), .names = "{.fn}")) %>%
-  dplyr::mutate(Date = as.Date(paste(year,"01","01", sep = "-"), format = "%Y-%m-%d"),
-                q_order = "q2") %>%
-  bind_rows(
-    q1_boots %>%
-      # summarise q1 by year
-      group_by(year) %>%
-      dplyr::summarise(across(q1, list(mean = ~mean(.x, na.rm = TRUE),
-                                       median = ~quantile(.x, 0.5, na.rm = TRUE),
-                                       quant2.5= ~quantile(.x, 0.025, na.rm = TRUE),
-                                       quant25= ~quantile(.x, 0.25, na.rm = TRUE),
-                                       quant75= ~quantile(.x, 0.75, na.rm = TRUE),
-                                       quant97.5= ~quantile(.x, 0.975, na.rm = TRUE)), .names = "{.fn}")) %>%
-      dplyr::mutate(Date = as.Date(paste(year,"01","01", sep = "-"), format = "%Y-%m-%d"),
-                    q_order = "q1")
-   ) 
-# 
-# annual_evenness_boots = boot_gini_groups(TB_trawl_taxasite %>% dplyr::select(-julian_date,-Date,-month,-biweekly), 
-#                                 group_var = 'year',
-#                                 n_perm = nperm)
-# 
-# annual_evenness_df = annual_evenness_boots %>%
-#   dplyr::select(-boot_id) %>%
-#   pivot_longer(-year, names_to = 'measure', values_to = 'value') %>%
-#   group_by(year,measure) %>%
-#   dplyr::summarise(across(value, list(mean = ~mean(.x, na.rm = TRUE),
-#                                       median = ~quantile(.x, 0.5, na.rm = TRUE),
-#                                       quant2.5= ~quantile(.x, 0.025, na.rm = TRUE),
-#                                       quant25= ~quantile(.x, 0.25, na.rm = TRUE),
-#                                       quant75= ~quantile(.x, 0.75, na.rm = TRUE),
-#                                       quant97.5= ~quantile(.x, 0.975, na.rm = TRUE)), .names = "{.fn}")) %>%
-#   dplyr::mutate(Date = as.Date(paste(year,"01","01", sep = "-"), format = "%Y-%m-%d")) %>%
-#   ungroup
-
-annual_evenness_df = TB_trawl_taxasite_yr %>%
-  dplyr::select(-year) %>%
-  apply(., 1, gini_even) %>%
-      t() %>%
-      data.frame() %>%
-      bind_cols(TB_trawl_taxasite_yr$year, .) %>%
-      setNames(., c("year", "gini_raw", "gini_norm")) %>%
-  pivot_longer(-year, names_to = "measure", values_to = "median") %>%
-  dplyr::mutate(Date = as.Date(paste(year,"01","01", sep = "-"), format = "%Y-%m-%d")) %>%
-  ungroup
-
-group_stats %>%
-  dplyr::filter(index == "pct_rare") -> rarity
-
-```
-
-Species turnover was likely confined to species with moderate to low relative abundances.
-The effective number of highly abundant species, *^2^D*, was variable but stable through time with calculated values *ca.* `r qD_df %>% dplyr::filter(q_order == 'q2') %>% dplyr::summarise(across(median, ~median(.x ,na.rm = TRUE))) %>% round(2)` $\pm$ `r qD_df %>% dplyr::filter(q_order == 'q2') %>% dplyr::summarise(across(median, ~sd(.x, na.rm = TRUE))) %>% round(1)` (mean $\pm$ 1 SD) (range: `r qD_df %>% dplyr::filter(q_order == 'q2')%>% slice_min(median) %>% dplyr::select(median) %>% round(2)` to  `r qD_df %>% dplyr::filter(q_order == 'q2') %>% slice_max(median) %>% dplyr::select(median) %>% round(1)`; Figure 3 __*supplemental?*__).
-In contrast, the percentage of rare species increased slightly through time from `r rarity %>% slice_min(year) %>% dplyr::select(median) %>% round(2)` to `r rarity %>% slice_max(year) %>% dplyr::select(median) %>% round(2)`.
-Additionally, the evenness in species abundances showed a clear decline through time from a median value of `r annual_evenness_df %>% dplyr::filter(measure == 'gini_norm') %>% slice_min(Date) %>% dplyr::select(median) %>% round(2)` in `r min(annual_evenness_df$year,na.rm = TRUE)` to `r annual_evenness_df %>% dplyr::filter(measure=='gini_norm') %>% slice_max(Date) %>% dplyr::select(median) %>% round(2)` in `r max(annual_evenness_df$year, na.rm = TRUE)`.
-
-```{r diversity2 plot, echo = FALSE, warning=FALSE, message=FALSE, fig.cap="Figure 3.
-Temporal trends in order of diversity q = 2, ^2^D highlight relative stability in the number of dominant species in the community through time.
-^2^D is equivalent to 1/Simpson's diversity index and captures the effective number of highly abundant species in the community.", include=FALSE}
-qD_df %>%
-  dplyr::filter(q_order == "q2") %>%
-  ggplot()+
-  geom_ribbon(aes(x = Date, ymin = quant2.5, ymax = quant97.5, group = q_order, fill = q_order), alpha = 0.5)+
-  geom_line(aes(x = Date, y = median, group = q_order, color = q_order), size = 1.2)+
-  geom_point(aes(x = Date, y= mean, group = q_order), shape = 6)+
-  scale_y_continuous(name = expression("Effective species ("~italic(''^2*D)~")"),limits = c(0,11))+
-  scale_color_manual(labels = c("q2"), values = viridis(n = 1, option = 'viridis'))+
-  scale_fill_manual(labels = c("q2"),values = viridis(n = 1, alpha = 0.5, option = 'viridis'))+
-  theme(legend.title = element_blank(),
-        legend.position = "none",
-        legend.justification = c(0,1))
-
-```
-
-```{r evenness, echo = FALSE, warning=FALSE, message=FALSE, fig.cap= "Figure 4. Species rarity and evenness in relative abundances through the data series." }
-
-annual_evenness_df %>%
-  dplyr::filter(measure == 'gini_norm') %>%
-  ggplot()+
-  # geom_ribbon(aes(x = Date, ymin = quant2.5, ymax = quant97.5), alpha = 0.3) +
-  geom_line(aes(x = Date, y = median), size = 1.1) +
-  geom_point(aes(x = Date, y = median), shape = 22, size = 3)+
-  scale_y_continuous(name = "Normalized Gini coefficient", limits = c(0,0.2), expand = c(0.01,0.01))+
-  scale_x_date(date_breaks = 'year', limits = c(as.Date("2009-01-01"),as.Date("2019-12-31")),
-               date_labels = "%Y")+
-  theme(axis.title.x = element_blank())-> evenness_plot
-
-evenness_plot
-
-```
-
-```{r spp contributions, echo=FALSE, warning=FALSE, message=FALSE}
+```{r spp contributions, echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Figure 5."}
 
@@
   dplyr::select(-Abundance) %>%
+  ungroup %>%
   group_by(Common_name) %>%
@@
   arrange(desc(rel_abun)) %>%
-  na.omit %>%
+  na.omit %>% dplyr::filter(!grepl("unspecified", Common_name, ignore.case = TRUE)) %>%
   dplyr::select(Common_name) %>%
@@
 
-TB_trawl_order_names = fuzzySim::spCodes(TB_trawl_order, nchar.gen = 4, nchar.sp = 6)
+TB_trawl_order_names = fuzzySim::spCodes(TB_trawl_order, nchar.gen = 4, nchar.sp = 6) %>%
+  setNames(.,make.names(TB_trawl_order))
 
-TB_trawl_taxasite_yr_dis = TB_trawl_taxasite_yr %>%
-  pivot_longer(-year,names_to = 'Common_name', values_to = 'Abundance') %>%
-  pivot_wider(names_from = 'year', values_from = 'Abundance') %>%
+TB_trawl_taxasite_dis = TB_trawl_taxasite_long %>%
+  dplyr::select(-Date) %>%
+  pivot_wider(names_from = 'date_id', values_from = 'Abundance') %>%
   column_to_rownames('Common_name')
 
-TB_trawl_q2_dis = dis1(TB_trawl_taxasite_yr_dis, q = 2, type = 'tax') %>%
+TB_trawl_q0.1_dis = dis1(TB_trawl_taxasite_dis, q = 0.1, type = 'tax') %>%
   .[,TB_trawl_order] %>%
@@
   pivot_longer(-dis_type, names_to = 'Common_name', values_to = 'value') %>%
-  dplyr::mutate(Common_name = factor(Common_name, make.names(TB_trawl_order)))
+  dplyr::mutate(common_label = recode(Common_name, !!!TB_trawl_order_names),
+                rel_value = value/sum(value, na.rm = TRUE))
 
-TB_trawl_q1_dis = dis1(TB_trawl_taxasite_yr_dis, q = 1, type = 'tax') %>%
+TB_trawl_q0.1_cont = TB_trawl_q0.1_dis %>%
+  dplyr::filter(floor(rel_value*100) >=1) %>%
+  nrow
+
+TB_trawl_q0.5_dis = dis1(TB_trawl_taxasite_dis, q = 0.5, type = 'tax') %>%
   .[,TB_trawl_order] %>%
@@
   pivot_longer(-dis_type, names_to = 'Common_name', values_to = 'value') %>%
-  dplyr::mutate(Common_name = factor(Common_name, make.names(TB_trawl_order)))
+  dplyr::mutate(common_label = recode(Common_name, !!!TB_trawl_order_names),
+                rel_value = value/sum(value, na.rm = TRUE))
 
-TB_trawl_q0_dis = dis1(TB_trawl_taxasite_yr_dis, q = 0, type = 'tax') %>%
+TB_trawl_q0.5_cont = TB_trawl_q0.5_dis %>%
+  dplyr::filter(floor(rel_value*100) >=1) %>%
+  nrow
+
+TB_trawl_q1_dis = dis1(TB_trawl_taxasite_dis, q = 1, type = 'tax') %>%
   .[,TB_trawl_order] %>%
@@
   pivot_longer(-dis_type, names_to = 'Common_name', values_to = 'value') %>%
-  dplyr::mutate(Common_name = factor(Common_name, make.names(TB_trawl_order)))
+  dplyr::mutate(common_label = recode(Common_name, !!!TB_trawl_order_names),
+                rel_value = value/sum(value, na.rm = TRUE))
 
-q0_dis_plot = TB_trawl_q0_dis %>%
+TB_trawl_q1_cont = TB_trawl_q1_dis %>%
+  dplyr::filter(floor(rel_value*100) >=1) %>%
+  nrow
+
+TB_trawl_q2_dis = dis1(TB_trawl_taxasite_dis, q = 2, type = 'tax') %>%
+  .[,TB_trawl_order] %>%
+  data.frame %>%
+  rownames_to_column('dis_type') %>%
+  dplyr::filter(dis_type == "UqN") %>%
+  pivot_longer(-dis_type, names_to = 'Common_name', values_to = 'value') %>%
+  dplyr::mutate(common_label = recode(Common_name, !!!TB_trawl_order_names),
+                rel_value = value/sum(value, na.rm = TRUE))
+
+TB_trawl_q2_cont = TB_trawl_q2_dis %>%
+  dplyr::filter(floor(rel_value*100) >=1) %>%
+  nrow
+
+## Make plots
+q0.1_dis_plot = TB_trawl_q0.1_dis %>%
+  dplyr::mutate(Common_name = factor(Common_name, levels = make.names(TB_trawl_order)),
+                common_label = factor(common_label, levels = TB_trawl_order_names[make.names(TB_trawl_order)])) %>%
+  slice_head(n = 20) %>%
   ggplot()+
-  geom_col(aes(x= Common_name, y = value));q0_dis_plot
+  geom_col(aes(x= common_label, y = value))+
+  scale_y_continuous(name = "Species contribution", limits = c(0,0.06), expand = c(0.0001,0.0001))+
+  theme_tufte()+
+  geom_rangeframe(sides = "bl", color = "black")+
+  annotate("text", label = expression(italic(""^q*"D = 0.1")), x = Inf, y = Inf, vjust = 1, hjust = 1, size = 8, family = "serif")+
+  theme(axis.text.x = element_blank(),
+        axis.title = element_blank());
+
+q0.5_dis_plot = TB_trawl_q0.5_dis %>%
+  dplyr::mutate(Common_name = factor(Common_name, levels = make.names(TB_trawl_order)),
+                common_label = factor(common_label, levels = TB_trawl_order_names[make.names(TB_trawl_order)])) %>%
+    slice_head(n = 20) %>%
+ggplot()+
+  geom_col(aes(x= common_label, y = value))+
+  scale_y_continuous(name = "Species contribution", limits = c(0,NA), expand = c(0.0001,0.0001))+
+  theme_tufte()+
+  geom_rangeframe(sides = "bl", color = "black")+
+  annotate("text", label = expression(italic(""^q*"D = 0.5")), x = Inf, y = Inf, vjust = 1, hjust = 1, size = 8, family = "serif")+
+  theme(axis.text.x = element_blank(),
+        axis.title = element_blank());
 
 q1_dis_plot = TB_trawl_q1_dis %>%
+  dplyr::mutate(Common_name = factor(Common_name, levels = make.names(TB_trawl_order)),
+                common_label = factor(common_label, levels = TB_trawl_order_names[make.names(TB_trawl_order)])) %>%
+    slice_head(n = 20) %>%
 ggplot()+
-  geom_col(aes(x= Common_name, y = value));q1_dis_plot
+  geom_col(aes(x= common_label, y = value))+
+  scale_y_continuous(name = "Species contribution", limits = c(0,NA), expand = c(0.0001,0.0001))+
+  theme_tufte()+
+  geom_rangeframe(sides = "bl", color = "black")+
+  annotate("text", label = expression(italic(""^q*"D = 1")), x = Inf, y = Inf, vjust = 1, hjust = 1, size = 8, family = "serif")+
+  theme(axis.text.x = element_blank(),
+        axis.title = element_blank());
 
 q2_dis_plot = TB_trawl_q2_dis %>%
+  dplyr::mutate(Common_name = factor(Common_name, levels = make.names(TB_trawl_order)),
+                common_label = factor(common_label, levels = TB_trawl_order_names[make.names(TB_trawl_order)])) %>%
+    slice_head(n = 20) %>%
 ggplot()+
-  geom_col(aes(x= Common_name, y = value));q2_dis_plot
+  geom_col(aes(x= common_label, y = value))+
+  scale_y_continuous(name = "Species contribution", limits = c(0,NA), expand = c(0.0001,0.0001))+
+  theme_tufte()+
+  geom_rangeframe(sides = "bl", color = "black")+
+  annotate("text", label = expression(italic(""^q*"D = 2")), x = Inf, y = Inf, vjust = 1, hjust = 1, size = 8, family = "serif")+
+  theme(axis.text.x = element_text(angle = 60, vjust = 1, hjust = 1),
+        axis.title = element_blank())
+
+grid.draw(rbind(ggplotGrob(q0.5_dis_plot),ggplotGrob(q1_dis_plot), ggplotGrob(q2_dis_plot), size = 'last'))
 
 ```
+
+```{r spp dynamics, echo=FALSE, warning=FALSE, message=FALSE, fig.cap = "Figure 5.
+Scaled abundance of the species with the largest contribution to community dissimilarity within the timeseries at orders of diversity q = 1 (top) and q = 2 (bottom)." }
+
+TB_q2_spp = TB_trawl_q2_dis %>%
+  arrange(desc(value)) %>%
+ dplyr::select(Common_name) %>%
+  unlist %>% .[1:5]
+
+TB_q1_spp = TB_trawl_q1_dis %>%
+  arrange(desc(value)) %>%
+ dplyr::select(Common_name) %>%
+  unlist %>% .[1:5]
+
+TB_q0.5_spp = TB_trawl_q0.5_dis %>%
+  arrange(desc(value)) %>%
+ dplyr::select(Common_name) %>%
+  unlist %>% .[1:5]
+
+TB_q0.1_spp = TB_trawl_q0.1_dis %>%
+  arrange(desc(value)) %>%
+ dplyr::select(Common_name) %>%
+  unlist %>% .[1:5]
+
+TB_q2_spp_df = TB_trawl_taxasite_long %>%
+  dplyr::mutate(fixed_common = make.names(Common_name)) %>%
+  dplyr::filter(fixed_common %in% TB_q2_spp) %>%
+  left_join(TB_trawl_effort_mth, by = 'Date') %>%
+  group_by(Common_name) %>%
+  dplyr::mutate(corrAbundance = Abundance/trawl_n) %>%
+  dplyr::mutate(scale_n = scale(corrAbundance, center = FALSE, scale = TRUE))
+
+TB_q1_spp_df = TB_trawl_taxasite_long %>%
+  dplyr::mutate(fixed_common = make.names(Common_name)) %>%
+  dplyr::filter(fixed_common %in% TB_q1_spp) %>%
+  left_join(TB_trawl_effort_mth, by = 'Date') %>%
+  group_by(Common_name) %>%
+  dplyr::mutate(corrAbundance = Abundance/trawl_n) %>%
+  dplyr::mutate(scale_n = scale(corrAbundance, center = FALSE, scale = TRUE))
+
+TB_q0.5_spp_df = TB_trawl_taxasite_long %>%
+  dplyr::mutate(fixed_common = make.names(Common_name)) %>%
+  dplyr::filter(fixed_common %in% TB_q0.5_spp) %>%
+  left_join(TB_trawl_effort_mth, by = 'Date') %>%
+  group_by(Common_name) %>%
+  dplyr::mutate(corrAbundance = Abundance/trawl_n) %>%
+  dplyr::mutate(scale_n = scale(corrAbundance, center = FALSE, scale = TRUE))
+
+TB_q0.1_spp_df = TB_trawl_taxasite_long %>%
+  dplyr::mutate(fixed_common = make.names(Common_name)) %>%
+  dplyr::filter(fixed_common %in% TB_q0.1_spp) %>%
+  left_join(TB_trawl_effort_mth, by = 'Date') %>%
+  group_by(Common_name) %>%
+  dplyr::mutate(corrAbundance = Abundance/trawl_n) %>%
+  dplyr::mutate(scale_n = scale(corrAbundance, center = FALSE, scale = TRUE))
+
+TB_q2_spp_plot = TB_q2_spp_df %>%
+  ggplot()+
+  geom_line(aes(x = Date, y = scale_n, group = Common_name, color = Common_name), size = 1.2)+
+  scale_color_viridis(discrete = TRUE)+
+  scale_y_continuous(name = "Scaled Abundance", expand = c(0.01,0.01))+
+  scale_x_date(date_breaks = 'year', limits = c(as.Date("2009-01-01"),as.Date("2019-12-31")),
+               date_labels = "%Y", expand = c(0.01,0.01))+
+  theme_tufte()+
+  geom_rangeframe(data = TB_q2_spp_df, aes(x = Date, y = scale_n),
+                  sides = 'bl', color = 'black', inherit.aes = FALSE)+
+  annotate('text', label = expression(italic(""^q*"D = 2")), x = as.Date("2019-12-31"), y = Inf, vjust = 1, hjust = 1, size = 8, family = 'serif')+
+  theme(legend.title = element_blank(),
+        axis.title.x = element_blank(),
+        legend.position = c(0,1),
+        legend.justification = c(0,1),
+        legend.background = element_rect(fill = 'transparent', color = NA));TB_q2_spp_plot
+
+TB_q1_spp_plot = TB_q1_spp_df %>%
+  ggplot()+
+  geom_line(aes(x = Date, y = scale_n, group = Common_name, color = Common_name), size = 1.2)+
+  scale_color_viridis(discrete = TRUE)+
+  scale_y_continuous(name = "Scaled Abundance", expand = c(0.01,0.01))+
+  scale_x_date(date_breaks = 'year', limits = c(as.Date("2009-01-01"),as.Date("2019-12-31")),
+               date_labels = "%Y", expand = c(0.01,0.01))+
+  theme_tufte()+
+  geom_rangeframe(data = TB_q1_spp_df, aes(x = Date, y = scale_n),
+                  sides = 'bl', color = 'black', inherit.aes = FALSE)+
+  annotate('text', label = expression(italic(""^q*"D = 1")), x = as.Date("2019-12-31"), y = Inf, vjust = 1, hjust = 1, size = 8, family = 'serif')+
+  theme(legend.title = element_blank(),
+        axis.title.x = element_blank(),
+        legend.position = c(0,1),
+        legend.justification = c(0,1),
+        legend.background = element_rect(fill = 'transparent', color = NA));TB_q1_spp_plot
+
+TB_q0.5_spp_plot = TB_q0.5_spp_df %>%
+  ggplot()+
+  geom_line(aes(x = Date, y = scale_n, group = Common_name, color = Common_name), size = 1.2)+
+  scale_color_viridis(discrete = TRUE)+
+  scale_y_continuous(name = "Scaled Abundance", expand = c(0.01,0.01))+
+  scale_x_date(date_breaks = 'year', limits = c(as.Date("2009-01-01"),as.Date("2019-12-31")),
+               date_labels = "%Y", expand = c(0.01,0.01))+
+  theme_tufte()+
+  geom_rangeframe(data = TB_q0.5_spp_df, aes(x = Date, y = scale_n),
+                  sides = 'bl', color = 'black', inherit.aes = FALSE)+
+  annotate('text', label = expression(italic(""^q*"D = 0.5")), x = as.Date("2019-12-31"), y = Inf, vjust = 1, hjust = 1, size = 8, family = 'serif')+
+  theme(legend.title = element_blank(),
+        axis.title.x = element_blank(),
+        legend.position = c(0,1),
+        legend.justification = c(0,1),
+        legend.background = element_rect(fill = 'transparent', color = NA));TB_q0.5_spp_plot
+
+TB_q0.1_spp_plot = TB_q0.1_spp_df %>%
+  ggplot()+
+  geom_line(aes(x = Date, y = scale_n, group = Common_name, color = Common_name))+
+  scale_color_viridis(discrete = TRUE)+
+  scale_y_continuous(name = "Scaled Abundance", expand = c(0.01,0.01))+
+  scale_x_date(date_breaks = 'year', limits = c(as.Date("2009-01-01"),as.Date("2019-12-31")),
+               date_labels = "%Y", expand = c(0.01,0.01))+
+  theme_tufte()+
+  geom_rangeframe(data = TB_q0.1_spp_df, aes(x = Date, y = scale_n),
+                  sides = 'bl', color = 'black', inherit.aes = FALSE)+
+  annotate('text', label = expression(italic(""^q*"D = 0.1")), x = as.Date("2019-12-31"), y = Inf, vjust = 1, hjust = 1, size = 8, family = 'serif')+
+  theme(legend.title = element_blank(),
+        axis.title.x = element_blank(),
+        legend.position = c(0,1),
+        legend.justification = c(0,1),
+        legend.background = element_rect(fill = 'transparent', color = NA));TB_q0.1_spp_plot
+
+grid.draw(rbind(ggplotGrob(TB_q1_spp_plot), ggplotGrob(TB_q2_spp_plot), size = 'last'))
+
+```
+
+```{r trawl contributions,echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Figure 6.
+The contribution of individual trawl-dates to dissimilarity of the entire timeseries for diversity order q = 0.1 (top), q = 1 (middle), and q = 2 (bottom)." }
+
+TB_trawl_q0_dis2 = dis1(TB_trawl_taxasite_dis, q = 0, type = 'tax', type2 = 'k') %>%
+  data.frame(check.names = FALSE) %>% 
+  rownames_to_column('dis_type') %>%
+  pivot_longer(-dis_type,names_to ='date_id', values_to = 'value') %>%
+  dplyr::mutate(date_id = as.numeric(date_id)) %>%
+  left_join(TB_trawl_taxasite %>% dplyr::select(Date, date_id))
+
+TB_trawl_q0.5_dis2 = dis1(TB_trawl_taxasite_dis, q = 0.5, type = 'tax', type2 = 'k') %>%
+  data.frame(check.names = FALSE) %>% 
+  rownames_to_column('dis_type') %>%
+  pivot_longer(-dis_type,names_to ='date_id', values_to = 'value') %>%
+  dplyr::mutate(date_id = as.numeric(date_id)) %>%
+  left_join(TB_trawl_taxasite %>% dplyr::select(Date, date_id))
+
+TB_trawl_q1_dis2 = dis1(TB_trawl_taxasite_dis, q = 1, type = 'tax', type2 = 'k') %>%
+  data.frame(check.names = FALSE) %>% 
+  rownames_to_column('dis_type') %>%
+  pivot_longer(-dis_type,names_to ='date_id', values_to = 'value') %>%
+  dplyr::mutate(date_id = as.numeric(date_id)) %>%
+  left_join(TB_trawl_taxasite %>% dplyr::select(Date, date_id))
+
+TB_trawl_q2_dis2 = dis1(TB_trawl_taxasite_dis, q = 2, type = 'tax', type2 = 'k') %>%
+  data.frame(check.names = FALSE) %>% 
+  rownames_to_column('dis_type') %>%
+  pivot_longer(-dis_type,names_to ='date_id', values_to = 'value') %>%
+  dplyr::mutate(date_id = as.numeric(date_id)) %>%
+  left_join(TB_trawl_taxasite %>% dplyr::select(Date, date_id))
+TB_trawl_q0_dis2 = dis1(TB_trawl_taxasite_dis, q = 0, type = 'tax', type2 = 'k') %>%
+  data.frame(check.names = FALSE) %>% 
+  rownames_to_column('dis_type') %>%
+  pivot_longer(-dis_type,names_to ='date_id', values_to = 'value') %>%
+  dplyr::mutate(date_id = as.numeric(date_id)) %>%
+  left_join(TB_trawl_taxasite %>% dplyr::select(Date, date_id))
+
+TB_trawl_q0.1_dis2 = dis1(TB_trawl_taxasite_dis, q = 0.1, type = 'tax', type2 = 'k') %>%
+  data.frame(check.names = FALSE) %>% 
+  rownames_to_column('dis_type') %>%
+  pivot_longer(-dis_type,names_to ='date_id', values_to = 'value') %>%
+  dplyr::mutate(date_id = as.numeric(date_id)) %>%
+  left_join(TB_trawl_taxasite %>% dplyr::select(Date, date_id))
+
+TB_trawl_q1_dis2 = dis1(TB_trawl_taxasite_dis, q = 1, type = 'tax', type2 = 'k') %>%
+  data.frame(check.names = FALSE) %>% 
+  rownames_to_column('dis_type') %>%
+  pivot_longer(-dis_type,names_to ='date_id', values_to = 'value') %>%
+  dplyr::mutate(date_id = as.numeric(date_id)) %>%
+  left_join(TB_trawl_taxasite %>% dplyr::select(Date, date_id))
+
+TB_trawl_q2_dis2 = dis1(TB_trawl_taxasite_dis, q = 2, type = 'tax', type2 = 'k') %>%
+  data.frame(check.names = FALSE) %>% 
+  rownames_to_column('dis_type') %>%
+  pivot_longer(-dis_type,names_to ='date_id', values_to = 'value') %>%
+  dplyr::mutate(date_id = as.numeric(date_id)) %>%
+  left_join(TB_trawl_taxasite %>% dplyr::select(Date, date_id))
+
+# plot contributions of each trawl to differences
+TB_trawl_q0_dis2 %>%
+  dplyr::filter(dis_type == "UqN")%>%
+  ggplot(aes(x = Date, y = value))+
+  geom_point()+
+  geom_path()+
+  scale_y_continuous(expand = c(0.0001,0.0001))+
+   scale_x_date(date_breaks = 'year', limits = c(as.Date("2009-01-01"),as.Date("2019-12-31")),
+               date_labels = "%Y")+
+  theme(axis.title = element_blank(),
+        axis.text.x = element_blank())-> TB_q0_dis2_plot
+
+TB_trawl_q0.1_dis2 %>%
+  dplyr::filter(dis_type == "UqN")%>%
+  ggplot(aes(x = Date, y = value))+
+  geom_point()+
+  geom_path()+
+  scale_y_continuous(expand = c(0.0001,0.0001))+
+   scale_x_date(date_breaks = 'year', limits = c(as.Date("2009-01-01"),as.Date("2019-12-31")),
+               date_labels = "%Y")+
+  theme(axis.title = element_blank(),
+        axis.text.x = element_blank())-> TB_q0.1_dis2_plot
+
+TB_trawl_q1_dis2 %>%
+  dplyr::filter(dis_type == "UqN")%>%
+  ggplot(aes(x = Date, y = value))+
+  geom_point()+
+  geom_path()+
+  scale_y_continuous(expand = c(0.0001,0.0001))+
+   scale_x_date(date_breaks = 'year', limits = c(as.Date("2009-01-01"),as.Date("2019-12-31")),
+               date_labels = "%Y")+
+  theme(axis.title = element_blank(),
+        axis.text.x = element_blank())-> TB_q1_dis2_plot
+TB_trawl_q2_dis2 %>%
+  dplyr::filter(dis_type == "UqN")%>%
+  ggplot(aes(x = Date, y = value))+
+  geom_point()+
+  geom_path()+
+  annotate('text', label = "")+
+  scale_y_continuous(expand = c(0.0001,0.0001))+
+   scale_x_date(date_breaks = 'year', limits = c(as.Date("2009-01-01"),as.Date("2019-12-31")),
+               date_labels = "%Y")+
+  theme(axis.title= element_blank()) -> TB_q2_dis2_plot
+
+grid.draw(rbind(ggplotGrob(TB_q0.1_dis2_plot),
+                ggplotGrob(TB_q1_dis2_plot), 
+                ggplotGrob(TB_q2_dis2_plot), size = 'last'))
+```
+
+Changes in the estuarine community, in both rare and common species, were not evenly distributed among taxa (Figure 5).
+For example, dissimilarity in rarer species (i.e., low diversity orders, *^0.1^D*), was contributed by a relatively large number of species (~`r TB_trawl_q0.1_cont` contibuted $\geq$ 1% to total dissimilarity) and individual species effects were relatively diffuse (largest contribution was `r round(max(TB_trawl_q0.1_dis$rel_value*100),1)`).
+On the contrary, few species contributed to dissimilarity in more abundant species (~`r TB_trawl_q2_cont` contribute $\geq$ 1% to total dissimilarity) and two taxonomic groups contributed `~90% to total dissimilarity (Penaeid spp.
+and *Micropogonias undulatus*).
+
+Further, community changes were not equally distributed through time (Figure 6). New
 
@@
 
+We are grateful the LUMCON staff for the logistical support of LUMCON's research, education, and outreach activities allowing the collection of these data.
+Notably, we extend thanks to the LUMCON vessels staff, crew of the R/V Pelican, the number of LUMCON instructors who supported the safe and successful collection of biological data, and the environmental monitoring department for management of environmental data..
+.
+Trawl sampling was collected under **permit information**...
+
 \newpage
@@
 
-\newpage
+<div id="refs"></div>
 
-```{r supplemental figure 1, echo=FALSE, warning=FALSE, message=FALSE}
+# Appendix
 
-TB_trawl_data %>%
-  # exclude 2020 & 2021
-  dplyr::filter(year %ni% year_removals) %>%
-  dplyr::filter(!duplicated(Common_name )) %>%
-  dplyr::mutate(Date = as.Date(Date)) %>%
-  arrange(Date) %>%
-  dplyr::mutate(richness = 1:n())-> TB_time_accum
+```{ r map fig S1, echo = FALSE, warning = FALSE, message= FALSE, }
 
-TB_annual_accum <- TB_trawl_data %>%
-  # exclude 2020 & 2021
-  dplyr::filter(year %ni% year_removals) %>%
-  mutate(pres = 1) %>% group_by(year) %>%
-  filter(!duplicated(Common_name)) %>%
-  summarise(richness = sum(pres)) %>%
-  mutate(Date = as.Date(paste(as.character(year),"01","01", sep = "-"), format = "%Y-%m-%d", origin = "2000-01-01"))
+```
 
-### create timeseries figure
-TB_time_df <- TB_time_accum %>%
-  dplyr::select(Date, year, richness) %>%
-  mutate(data_type = 'continuous') %>%
-  bind_rows(TB_annual_accum %>% 
-              mutate(data_type = "ann_raw")) %>%
-  bind_rows(group_stats %>% 
-              dplyr::filter(index == "S_n") %>%
-              dplyr::select(Date, year, richness = 'median') %>%
-              dplyr::mutate(data_type = "rarefied")) %>%
-  bind_rows(group_stats %>% 
-              dplyr::filter(index == 'S_asymp') %>%
-              dplyr::select(Date, year, richness = 'median') %>%
-              dplyr::mutate(data_type = "ann_asymp")) %>%
-  dplyr::mutate(data_type = factor(data_type, levels = c("continuous", "rarefied", "ann_raw", "ann_asymp"))) %>%
-  dplyr::filter(data_type == "S_n")
+```{r env data fig S2, echo=FALSE, warning=FALSE, message=FALSE, fig.cap= "Figure S2.
+Time series of environmental variables a) water temperature and b) salinity measured at the Terrebonne Bay environmental monitoring station (XX N, XX W).
+Data were provided by the Environmental Monitoring department of LUMCON.
+Periods of no data in the salinity series represent periods of no data due to storm damage to monitoring stations."}
 
-S_n_lab = paste0("S[",S_n,"]")
+source(here::here("sub-projects/trawl/R/load_enviroData.R"))
 
-rich_time <-
-  ggplot(TB_time_df, aes(x = Date, y = richness, group = data_type)) +
-  geom_segment(data = TB_time_df %>%
-                 dplyr::filter(data_type %ni% 'continuous') %>%
-                 pivot_wider(Date, names_from = data_type, values_from = richness),
-               aes(x = Date, xend = Date, y = ann_asymp, yend = rarefied ),
-               color = viridis(n = 3, alpha = c(1,1,1), option = 'viridis')[3],
-               inherit.aes = F) +
-  geom_point(data = TB_time_df, aes(colour = data_type),size = 1.5) +
-  geom_line(data = TB_time_df %>% dplyr::filter(!grepl('ann_asymp', data_type)), aes(colour = data_type),size = 1.2) +
-  scale_x_date(date_breaks = "1 year", date_labels = "%Y",limits = c(as.Date("2009-01-01"),as.Date("2019-12-31"))) +
-  scale_y_continuous(name = "Species Richness")+
-  scale_colour_manual(labels = c("continuous", bquote(italic("S"[.(S_n[1])])),expression(italic("S"["asymp"]))), values = viridis(n = 3, alpha = c(1,1,1), option = 'viridis')) +
-  # scale_alpha_manual(values = c(1,1,0.3))+
-  theme(legend.position = c(0, 1), legend.justification = c(0, 1), legend.background = element_rect(fill = "transparent", colour = NA),
-        legend.title = element_blank(), legend.text.align = 0,
-        # axis.title.x = element_blank(), axis.text.x = element_blank(),
-        legend.spacing.y = unit(-0.1, 'cm'))
+temperature_plot = 
+temperature_series %>%
+  dplyr::filter(year(Date) %ni% year_removals) %>%
+  ggplot()+
+  # geom_ribbon(aes(x = Date, ymin = lower, ymax = upper), alpha = 0.5)+
+  geom_line(aes(x = Date, y = TB_tempC_series), size = 1)+
+  scale_y_continuous(name = expression("Temperature ("~degree*C~")"), limits = c(0,NA),
+                     expand = c(0.01,0.01))+
+  scale_x_date(date_breaks = "year", limits = c(as.Date("2009-01-01"),as.Date("2019-12-31")),
+               date_labels = "%Y",expand = c(0.01,0.01))+
+  annotate('text', label = 'A', x = -Inf, y = Inf, vjust = 1, hjust = 0, size = 5, family = 'serif')+
+  theme_tufte()+
+  geom_rangeframe(sides = "bl", color = "black")+
+  theme(axis.title.x = element_blank(),
+        axis.text.x = element_blank())
+salinity_plot = 
+salinity_series %>%
+  ggplot()+
+  geom_line(aes(x = Date, y = TB_sal), size = 1, color = 'blue')+
+   scale_x_date(date_breaks = "year", limits = c(as.Date("2009-01-01"),as.Date("2019-12-31")),
+               date_labels = "%Y",expand = c(0.01,0.01))+
+  scale_y_continuous(name = "Salinity (PSU)", limits = c(0,NA), expand =c(0.01,0.01))+
+    annotate('text', label = 'B', x = -Inf, y = Inf, vjust = 1, hjust = 0, size = 5, family = 'serif')+
+  theme_tufte()+
+  geom_rangeframe(sides = "bl", color = "black")+
+  theme(axis.title.x = element_blank())
+
+grid.draw(rbind(ggplotGrob(temperature_plot), ggplotGrob(salinity_plot), size = 'last'))
+```
+
+```{r supplemental figure s3, fig.cap = "Figure S3."}
+
+# TB_trawl_data %>%
+#   # exclude 2020 & 2021
+#   dplyr::filter(year %ni% year_removals) %>%
+#   dplyr::filter(!duplicated(Common_name )) %>%
+#   dplyr::mutate(Date = as.Date(Date)) %>%
+#   arrange(Date) %>%
+#   dplyr::mutate(richness = 1:n())-> TB_time_accum
+# 
+# TB_annual_accum <- TB_trawl_data %>%
+#   # exclude 2020 & 2021
+#   dplyr::filter(year %ni% year_removals) %>%
+#   mutate(pres = 1) %>% group_by(year) %>%
+#   filter(!duplicated(Common_name)) %>%
+#   summarise(richness = sum(pres)) %>%
+#   mutate(Date = as.Date(paste(as.character(year),"01","01", sep = "-"), format = "%Y-%m-%d", origin = "2000-01-01"))
+# 
+# 
+# ### create timeseries figure
+# TB_time_df <- TB_time_accum %>%
+#   dplyr::select(Date, year, richness) %>%
+#   mutate(data_type = 'continuous') %>%
+#   bind_rows(TB_annual_accum %>% 
+#               mutate(data_type = "ann_raw")) %>%
+#   bind_rows(group_stats %>% 
+#               dplyr::filter(index == "S_n") %>%
+#               dplyr::select(Date, year, richness = 'median') %>%
+#               dplyr::mutate(data_type = "rarefied")) %>%
+#   bind_rows(group_stats %>% 
+#               dplyr::filter(index == 'S_asymp') %>%
+#               dplyr::select(Date, year, richness = 'median') %>%
+#               dplyr::mutate(data_type = "ann_asymp")) %>%
+#   dplyr::mutate(data_type = factor(data_type, levels = c("continuous", "rarefied", "ann_raw", "ann_asymp"))) %>%
+#   dplyr::filter(data_type == "S_n")
+# 
+# S_n_lab = paste0("S[",S_n,"]")
+# 
+# rich_time <-
+#   ggplot(TB_time_df, aes(x = Date, y = richness, group = data_type)) +
+#   geom_segment(data = TB_time_df %>%
+#                  dplyr::filter(data_type %ni% 'continuous') %>%
+#                  pivot_wider(Date, names_from = data_type, values_from = richness),
+#                aes(x = Date, xend = Date, y = ann_asymp, yend = rarefied ),
+#                color = viridis(n = 3, alpha = c(1,1,1), option = 'viridis')[3],
+#                inherit.aes = F) +
+#   geom_point(data = TB_time_df, aes(colour = data_type),size = 1.5) +
+#   geom_line(data = TB_time_df %>% dplyr::filter(!grepl('ann_asymp', data_type)), aes(colour = data_type),size = 1.2) +
+#   scale_x_date(date_breaks = "1 year", date_labels = "%Y",limits = c(as.Date("2009-01-01"),as.Date("2019-12-31"))) +
+#   scale_y_continuous(name = "Species Richness")+
+#   scale_colour_manual(labels = c("continuous", bquote(italic("S"[.(S_n[1])])),expression(italic("S"["asymp"]))), values = viridis(n = 3, alpha = c(1,1,1), option = 'viridis')) +
+#   # scale_alpha_manual(values = c(1,1,0.3))+
+#   theme(legend.position = c(0, 1), legend.justification = c(0, 1), legend.background = element_rect(fill = "transparent", colour = NA),
+#         legend.title = element_blank(), legend.text.align = 0,
+#         # axis.title.x = element_blank(), axis.text.x = element_blank(),
+#         legend.spacing.y = unit(-0.1, 'cm'))
 
@@
 
-group_stats %>%
-  dplyr::filter(index == "pct_rare") %>%
-  dplyr::mutate(year = as.Date(year, format = "%Y")) %>%
-  ggplot()+
-  geom_point(aes(x =Date, y = median), size = 3, shape = 22)+
-  geom_path(aes(x = Date, y = median), size = 1.1)+
-  scale_y_continuous(name = "Percent rare species (%)", limits = c(75 ,100), expand = c(0.01,0.01))+
-  scale_color_manual(values = viridis(n =1, option = 'viridis' ))+
-  scale_fill_manual(values = viridis(n = 1, option = 'viridis'))+
-  scale_x_date(date_breaks = 'year', limits = c(as.Date("2009-01-01"),as.Date("2019-12-31")),
-               date_labels = "%Y")+
-  theme(axis.title.x = element_blank())-> rarity_plot
-
+# group_stats %>%
+#   dplyr::filter(index == "pct_rare") %>%
+#   dplyr::mutate(year = as.Date(year, format = "%Y")) %>%
+#   ggplot()+
+#   geom_point(aes(x =Date, y = median), size = 3, shape = 22)+
+#   geom_path(aes(x = Date, y = median), size = 1.1)+
+#   scale_y_continuous(name = "Percent rare species (%)", limits = c(75 ,100), expand = c(0.01,0.01))+
+#   scale_color_manual(values = viridis(n =1, option = 'viridis' ))+
+#   scale_fill_manual(values = viridis(n = 1, option = 'viridis'))+
+#   scale_x_date(date_breaks = 'year', limits = c(as.Date("2009-01-01"),as.Date("2019-12-31")),
+#                date_labels = "%Y")+
+#   theme(axis.title.x = element_blank())-> rarity_plot
+#   
 ```
@@
 ^0^D is equal to the total number of species"}
-TB_trawl_yr_evenness = TB_trawl_taxasite_yr %>%
-  split(., seq(1:nrow(.))) %>%
-  purrr::map(~new_fun(.x, seq(0,4,0.1), "E3")) %>%
-  setNames(., nm = TB_trawl_taxasite_yr$year) %>%
-  purrr::map(function(a) a %>% t %>% data.frame %>%
-               setNames(., nm = seq(0,4,0.1))) %>%
-          bind_rows(.id = 'year') %>%
-  pivot_longer(-year, names_to = 'q', values_to = 'eff_spp') %>%
-  dplyr::mutate(Date = as.Date(paste0(year,"-01-01"), format = "%Y-%m-%d")) %>%
-  dplyr::mutate(across(q, as.numeric))
-
-TB_trawl_q1_plot =
-  TB_trawl_yr_evenness %>%
-  dplyr::filter(q == 1) %>%
-  ggplot()+
-  geom_line(aes(x = Date, y = eff_spp))+
-  scale_y_continuous(name = 'Eff. Species (%)', limits = c(0,0.2))+
-  scale_x_date(breaks = as.Date(c("2009-01-01","2014-01-01","2019-01-01"),format = "%Y-%m-%d"),
-               date_labels = "%Y")+
-  theme(axis.title.x = element_blank())+
-  annotate('text', x = as.Date(Inf), y = as.Date(Inf), label = expression(italic(""^1*D)), size =5,
-           hjust = 1, vjust = 1)
-
-TB_trawl_q2_plot =
-  TB_trawl_yr_evenness %>%
-  dplyr::filter(q == 2) %>%
-  ggplot()+
-  geom_line(aes(x = Date, y = eff_spp))+
-  scale_y_continuous(name = 'Eff. Species (%)', limits = c(0,0.15))+
-  scale_x_date(breaks = as.Date(c("2009-01-01","2014-01-01","2019-01-01"),format = "%Y-%m-%d"),
-               date_labels = "%Y")+
-  theme(axis.title.x = element_blank(),
-        axis.title.y = element_blank())+
-  annotate('text', x = as.Date(Inf), y = as.Date(Inf), label = expression(italic(""^2*D)), size =5,
-           hjust = 1, vjust = 1)
-
-TB_trawl_yr_evenness %>%
-  ggplot() +
-  geom_path(aes(x = q, y = eff_spp, group = year, color = year), size = 1.1)+
-  scale_y_continuous(name = 'Effective species (%)', limits = c(0,1), expand = c(0.01,0.01))+
-  scale_x_continuous(name = expression(italic(""^q*D)), limits = c(0,3), expand = c(0.02,0.02)) +
-  scale_color_manual(values = viridis(n = 12, option = 'viridis')) +
-  annotation_custom(
-    ggplotGrob(TB_trawl_q1_plot),
-    xmin = 0.75, xmax = 1.9, ymin = 0.5, ymax = 1
-  )+
-  annotation_custom(
-    ggplotGrob(TB_trawl_q2_plot),
-    xmin = 2, xmax = 3, ymin = 0.5, ymax = 1
-  )+
-  theme(legend.title = element_blank(),
-        legend.position = 'top')+
-  guides(color=guide_legend(nrow=2,byrow=TRUE))
+# TB_trawl_yr_evenness = TB_trawl_taxasite_yr %>%
+#   split(., seq(1:nrow(.))) %>%
+#   purrr::map(~new_fun(.x, seq(0,4,0.1), "E3")) %>%
+#   setNames(., nm = TB_trawl_taxasite_yr$year) %>%
+#   purrr::map(function(a) a %>% t %>% data.frame %>%
+#                setNames(., nm = seq(0,4,0.1))) %>%
+#           bind_rows(.id = 'year') %>%
+#   pivot_longer(-year, names_to = 'q', values_to = 'eff_spp') %>%
+#   dplyr::mutate(Date = as.Date(paste0(year,"-01-01"), format = "%Y-%m-%d")) %>%
+#   dplyr::mutate(across(q, as.numeric))
+# 
+# TB_trawl_q1_plot =
+#   TB_trawl_yr_evenness %>%
+#   dplyr::filter(q == 1) %>%
+#   ggplot()+
+#   geom_line(aes(x = Date, y = eff_spp))+
+#   scale_y_continuous(name = 'Eff. Species (%)', limits = c(0,0.2))+
+#   scale_x_date(breaks = as.Date(c("2009-01-01","2014-01-01","2019-01-01"),format = "%Y-%m-%d"),
+#                date_labels = "%Y")+
+#   theme(axis.title.x = element_blank())+
+#   annotate('text', x = as.Date(Inf), y = as.Date(Inf), label = expression(italic(""^1*D)), size =5,
+#            hjust = 1, vjust = 1)
+# 
+# TB_trawl_q2_plot =
+#   TB_trawl_yr_evenness %>%
+#   dplyr::filter(q == 2) %>%
+#   ggplot()+
+#   geom_line(aes(x = Date, y = eff_spp))+
+#   scale_y_continuous(name = 'Eff. Species (%)', limits = c(0,0.15))+
+#   scale_x_date(breaks = as.Date(c("2009-01-01","2014-01-01","2019-01-01"),format = "%Y-%m-%d"),
+#                date_labels = "%Y")+
+#   theme(axis.title.x = element_blank(),
+#         axis.title.y = element_blank())+
+#   annotate('text', x = as.Date(Inf), y = as.Date(Inf), label = expression(italic(""^2*D)), size =5,
+#            hjust = 1, vjust = 1)
+# 
+# TB_trawl_yr_evenness %>%
+#   ggplot() +
+#   geom_path(aes(x = q, y = eff_spp, group = year, color = year), size = 1.1)+
+#   scale_y_continuous(name = 'Effective species (%)', limits = c(0,1), expand = c(0.01,0.01))+
+#   scale_x_continuous(name = expression(italic(""^q*D)), limits = c(0,3), expand = c(0.02,0.02)) +
+#   scale_color_manual(values = viridis(n = 12, option = 'viridis')) +
+#   annotation_custom(
+#     ggplotGrob(TB_trawl_q1_plot),
+#     xmin = 0.75, xmax = 1.9, ymin = 0.5, ymax = 1
+#   )+
+#   annotation_custom(
+#     ggplotGrob(TB_trawl_q2_plot),
+#     xmin = 2, xmax = 3, ymin = 0.5, ymax = 1
+#   )+
+#   theme(legend.title = element_blank(),
+#         legend.position = 'top')+
+#   guides(color=guide_legend(nrow=2,byrow=TRUE))
 

### 2022-06-17 sub-projects/trawl/trawl_README.Rmd
workflow redo fixed links for new workflow.
Big commit. Updated qD models and plots. work on manuscript to finalize results

--- 2021-07-28 analyses/trawl/trawl_README.Rmd
@@
 knit: (function(inputFile, encoding) { 
-      out_dir <- "docs";
+      out_dir <- here::here("sub-projects/trawl/docs");
       rmarkdown::render(inputFile,
@@
 2. "datascript.R" (sourcing this document will call the 'packages.R' script)
-3. "trawl_rarefaction.R"
+3. "analyze_rarefaction.R"
 4. "trawl_specaccum.R"
+5. "analyze_hill_diversity.R"

### 2022-06-17 sub-projects/trawl/trawl_summary.Rmd
Big commit. Updated qD models and plots. work on manuscript to finalize results

--- 2021-07-28 trawl_summary.Rmd
@@
 knit: (function(inputFile, encoding) { 
-      out_dir <- './docs';
+      out_dir <- here::here('sub-projects/trawl/docs');
       rmarkdown::render(inputFile,
                         encoding=encoding, 
-                        output_file=file.path(dirname(inputFile), out_dir, 'trawl_summary.html')) })
+                        output_file=file.path(out_dir, 'trawl_summary.html')) })
 output: 
@@
 <!-- #  -->
-<!-- # `r knitr::include_graphics("./figures/env_facet_plot.png")` -->
+<!-- # `r knitr::include_graphics(here::here("sub-projects/trawl/docs/figures/env_facet_plot.png"))` -->
 
@@
 
-date_lists = TB_trawl_commonsite %>%
-  named_group_split(date_id) %>%
-  map(., ~.x %>% select(-year, -month,-date_id))
-
-beta_lists <- lapply(date_lists, function(x,r){ betapart::beta.temp(x = x, y = r, index.family = 'jaccard')}, x = date_lists[[1]]) 
-beta_dates <- gsub('^([0-9]{4}-)([0-9]{1})$', '\\10\\2', names(beta_lists))
-beta_df <- bind_rows(beta_lists) %>% mutate(Date = as.Date(paste0(beta_dates,"-01"), "%Y-%m-%d")) %>% #select(Date, everything()) %>%
-  pivot_longer(-Date, names_to = "partition", values_to = "value")
-
-rich_time <- 
-  ggplot(TB_time_df, aes(x = Date, y = richness, group = data_type)) +
-  geom_point(aes(colour = data_type),size = 1.5) +
-  geom_line(aes(colour = data_type),size = 1.2) +
-  scale_x_date(date_breaks = "1 year", date_labels = "%Y") + 
-  scale_y_continuous(name = "Species Richness")+
-  scale_colour_manual(name = "", values = viridis(4)[c(2,3)]) +
-  theme_minimal() +
-  theme(legend.position = c(0, 1), legend.justification = c(0, 1), legend.background = element_rect(fill = "transparent", colour = NA),
-        axis.title.x = element_blank(), axis.text.x = element_blank(),
-        legend.spacing.y = unit(-0.1, 'cm'))
-
- jaccard_time <-
-  ggplot(beta_df, aes(x = Date, y = value, group = partition)) + 
-   geom_point(aes(colour = partition), size = 1.5) +
-  geom_line(aes(colour = partition), size = 1.2) +
-  scale_y_continuous(name = "Jaccard dissimilarity", limits = c(0,1.1), expand = c(0.01,0.01))+
-  scale_colour_manual(name = "", values = viridis(7)[c(2,4,7)], labels = c("jaccard", "nestedness","turnover")) +
-  scale_x_date(date_breaks = "1 year", date_labels = "%Y") + 
-   theme_minimal() +
-  theme(legend.background = element_rect(colour = NA, fill = 'transparent'),
-        legend.position = c(0,1), legend.justification = c(0,1), axis.title.x = element_blank(),
-        legend.spacing.y = unit(-0.2, 'cm'))
-
-grid.arrange(rich_time, jaccard_time, ncol = 1)
+# date_lists = TB_trawl_commonsite %>%
+  # named_group_split(date_id) %>%
+#   map(., ~.x %>% select(-year, -month,-date_id))
+# 
+# beta_lists <- lapply(date_lists, function(x,r){ betapart::beta.temp(x = x, y = r, index.family = 'jaccard')}, x = date_lists[[1]]) 
+# beta_dates <- sapply(as.numeric(names(beta_lists)), function(x) as.Date(x, origin = as.Date("2007-01-01"))) 
+# beta_df <- bind_rows(beta_lists) %>% mutate(Date = as.Date(paste0(beta_dates,"-01"), "%Y-%m-%d")) %>% #select(Date, everything()) %>%
+#   pivot_longer(-Date, names_to = "partition", values_to = "value")
+# 
+# rich_time <- 
+#   ggplot(TB_time_df, aes(x = Date, y = richness, group = data_type)) +
+#   geom_point(aes(colour = data_type),size = 1.5) +
+#   geom_line(aes(colour = data_type),size = 1.2) +
+#   scale_x_date(date_breaks = "1 year", date_labels = "%Y") + 
+#   scale_y_continuous(name = "Species Richness")+
+#   scale_colour_manual(name = "", values = viridis(4)[c(2,3)]) +
+#   theme_minimal() +
+#   theme(legend.position = c(0, 1), legend.justification = c(0, 1), legend.background = element_rect(fill = "transparent", colour = NA),
+#         axis.title.x = element_blank(), axis.text.x = element_blank(),
+#         legend.spacing.y = unit(-0.1, 'cm')) 
+# 
+#  jaccard_time <-
+#   ggplot(beta_df, aes(x = Date, y = value, group = partition)) + 
+#    geom_point(aes(colour = partition), size = 1.5) +
+#   geom_line(aes(colour = partition), size = 1.2) +
+#   scale_y_continuous(name = "Jaccard dissimilarity", limits = c(0,1.1), expand = c(0.01,0.01))+
+#   scale_colour_manual(name = "", values = viridis(7)[c(2,4,7)], labels = c("jaccard", "nestedness","turnover")) +
+#   # scale_x_date(date_breaks = "1 year", date_labels = "%Y") + 
+#    theme_minimal() +
+#   theme(legend.background = element_rect(colour = NA, fill = 'transparent'),
+#         legend.position = c(0,1), legend.justification = c(0,1), axis.title.x = element_blank(),
+#         legend.spacing.y = unit(-0.2, 'cm')) 
+#    
+#  
+# grid.arrange(rich_time, jaccard_time, ncol = 1)
 

### 2022-06-17 datascript.R

@@ -4,7 +4,7 @@ here::i_am("datascript.R")
 
 # import biology data if it has been greater than 1 month since download
 load(here::here("data/biology_sysDate.rda"))
-ifelse((Sys.Date()-biology_sysDate) >= 30, source(here::here("sub-projects/trawl/R/import_bioData.R")),source(here::here("sub-projects/trawl/R/load_bioData.R")))
+ifelse((Sys.Date()-biology_sysDate) >= 50, source(here::here("sub-projects/trawl/R/import_bioData.R")),source(here::here("sub-projects/trawl/R/load_bioData.R")))
 rm(biology_sysDate)
 
 # important model variables for referencing

### 2022-06-17 packages.R

@@ -20,8 +20,8 @@ pacman::p_load(
   taxize, hillR, codyn, gridExtra, fuzzySim
 )
 
-devtools::install_github(c("jimjunker1/junkR")) # , "ropensci/rfishbase"))
-# library(junkR)
+# devtools::install_github(c("jimjunker1/junkR")) # , "ropensci/rfishbase"))
+library(junkR)
 # devtools::install_github('MoBiodiv/mobr')
 library(mobr)
 

### 2022-06-17 sub-projects/trawl/R/full_analyses.R

@@ -5,7 +5,26 @@ source(here::here("sub-projects/trawl/R/Evenness.R"))
 
 nperm = 99
 
-year_removals = c("2007","2020","2021")
+year_removals = c("2007","2020","2021","2022")
+
+## Salinity data
+
+# salinity
+
+sal_paths = list.files(path = here::here("data/environment"), "Terrebonne.*salinity.*2020.*", full.names = TRUE)
+TB_salinity_df <<- lapply(sal_paths, read_csv,
+                          col_types = cols('Date/Time' = col_datetime(format = "%m/%d/%Y %H:%M"))) %>%
+  bind_rows %>%
+  dplyr::select(datetime = 'Date/Time', sal_psu = contains('salinity')) %>%
+  dplyr::mutate(Date = as.Date(datetime)) %>%
+  dplyr::select(-datetime) %>%
+  group_by(Date) %>%
+  summarise_all(mean, na.rm = TRUE) %>%
+  full_join(data.frame(Date = seq(min(TB_trawl_data$Date), max(TB_trawl_data$Date), by = 1),
+                       sal_psu_mod = NA)) 
+
+TB_salinity_df %>% ggplot()+
+  geom_line(aes(x = Date, y = sal_psu))
 
 ##create taxa by site matrix
 TB_trawl_taxasite <- TB_trawl_data %>%
@@ -25,7 +44,14 @@ TB_trawl_taxasite <- TB_trawl_data %>%
 TB_trawl_taxasite_long = TB_trawl_taxasite %>%
   pivot_longer(-Date:-date_id, names_to = "Common_name", values_to = "Abundance")
 
-
+TB_trawl_effort_mth = TB_trawl_data %>%
+  dplyr::filter(year(Date) %ni% year_removals) %>%
+  dplyr::select(Date, date_id) %>%
+  group_by(date_id) %>%
+  dplyr::summarise(trawl_n = n()) %>%
+  dplyr::mutate(Date = as.Date(date_id, origin = "2007-01-01")) %>%
+  dplyr::select(Date, trawl_n)
+  
 ## Goals estimate the rarified richness through time
 ## Show changes in evenness and Hill #s
 ## Look at compositon 
@@ -156,7 +182,6 @@ total = trawl_mth_turnover %>%
 mean(gains$value)
 mean(losses$value)
 
-
 mth_group_stats %>%
   dplyr::filter(index == 'S_n') %>%
   ggplot(aes( x= Date, y = median))+
[…]

### 2022-06-17 sub-projects/trawl/R/import_bioData.R

@@ -38,18 +38,18 @@ here::i_am("sub-projects/trawl/R/import_bioData.R")
    TB_trawl_data <- TB_trawl_data %>%
     filter(!is.na(Species)) %>%
     mutate(Species = stringr::str_replace(Species,"spp(?!\\.)","spp."),
-           Species = gsub( "mix|- mix|- mixed| mixed","",Species, ignore.case = TRUE),
+           Species = gsub( "mix|- mix|- mixed| mixed|, unspecified|- ","",Species, ignore.case = TRUE),
            species_mod = case_when(grepl("Litopanaeus|Litopenaeus|Farfantepenaeus|Farfantepanaeus|Farfantapenaeus", Species, ignore.case = TRUE) ~ "Litopenaeus setiferus/Farfantepenaeus aztecus,White Shrimp/Brown Shrimp",
                                    grepl("Ariopsis felis|Ariopsisis|Ariosis|Bagre", Species) ~ "Ariopsis felis/Bagre marinus, Hardhead Catfish/Gafftopsail Catfish",
-                                   grepl("Family Naticidae", Species) ~ "Family: Naticidae/Urosalpinx cinerea, Moon Snail/Oyster drill snail",
+                                   grepl("Family Naticidae|Family Naticidae, Moon Snail; Urosalpinx cinerea, Atlantic Oyster Drill Snail|Urosalpinx cinerea, Atlantic Oyster Drill Snail", Species) ~ "Family: Naticidae, Moon Snail/Oyster drill snail",
                                    grepl("midshipmen", Species) ~ "Porichthys plectrodon, Atlantic Midshipman",
                                    grepl("shimp", Species) ~ "Litopenaeus setiferus/Farfantepenaeus aztecus,White Shrimp/Brown Shrimp",
                                    grepl("Puffer", Species, ignore.case = TRUE) ~ "Sphoeroides parvus, Least Pufferfish",
                                    grepl("hermit crab", Species) ~ "Superfamily: Paguroidea, Hermit Crab",
                                    grepl("jellyish", Species, ignore.case = TRUE) ~ "Class: Scyphozoa",
                                    grepl("mantis", Species, ignore.case = TRUE) ~ "Order: Stomatopoda, Mantis Shrimp",
-                                   grepl("Menticcirhus spp.", Species) ~ "Menticcirhus spp., Kingfish",
[…]

### 2022-06-17 sub-projects/trawl/R/load_enviroData.R

@@ -10,9 +10,9 @@ roundUP <<- function(x,to=10){
   to*(x%/%to + as.logical(x%%to))
 }
 
-tempF_to_C <<- function(F){(5/9)*(F-32)}
+tempF_to_C <- function(F){(5/9)*(F-32)}
 
-TB_temp_df <<- bind_rows(temp_files) %>%
+TB_temp_df <- bind_rows(temp_files) %>%
   dplyr::select(datetime = 'Date/Time', temp_C = 'Water Temp C') %>%
   dplyr::mutate(Date = as.Date(datetime)) %>%
   dplyr::select(-datetime) %>%
@@ -37,7 +37,7 @@ TB_temp_df <<- bind_rows(temp_files) %>%
 #          yday = yday(datetime))
 
 sal_paths = list.files(path = here::here("data/environment"), "Terrebonne.*salinity.*2020.*", full.names = TRUE)
-TB_salinity_df <<- lapply(sal_paths, read_csv,
+TB_salinity_df <- lapply(sal_paths, read_csv,
                           col_types = cols('Date/Time' = col_datetime(format = "%m/%d/%Y %H:%M"))) %>%
   bind_rows %>%
   dplyr::select(datetime = 'Date/Time', sal_psu = contains('salinity')) %>%
@@ -55,9 +55,9 @@ marine_center_files = lapply(marine_center_paths, read_csv, col_type = cols(`Dat
         group_by(Date) %>%
         summarise_all(mean, na.rm = TRUE))
 
-MC_salinity_df <<- marine_center_files[[1]] %>% dplyr::select(Date, sal_psu = "Sal")
-MC_temperature_df <<- marine_center_files[[2]] %>% dplyr::select(Date, temp_C = 'Water Temp C')
-MC_depth_df <<- marine_center_files[[3]] %>% dplyr::select(Date, depth_m = 'Water Depth M')
+MC_salinity_df <- marine_center_files[[1]] %>% dplyr::select(Date, sal_psu = "Sal")
+MC_temperature_df <- marine_center_files[[2]] %>% dplyr::select(Date, temp_C = 'Water Temp C')
+MC_depth_df <- marine_center_files[[3]] %>% dplyr::select(Date, depth_m = 'Water Depth M')
 ## combine the TB, MC, and regional datasets to fill in gaps
 
 regional_temp_paths = list.files(path = here::here("data/environment"), "^X.*.nc", full.names = TRUE)
[…]

### 2022-06-17 sub-projects/trawl/R/run_evenness_models.R

@@ -1,0 +1,47 @@
+# run evenness models for GoF measures
+even_bayes_full_mod = brm(bf(gini_norm ~ date_id + s(month, bs = 'cc', k = 12)),
+                          data = mth_even, family = gaussian(),
+                          cores = 4, seed = 42,
+                          iter = 7000, warmup = 5000, thin = 10,
+                          control = list(adapt_delta = 0.99),
+                          save_pars = save_pars(all = TRUE),
+                          file = here::here("sub-projects/trawl/derived-data/even_full.rds"),
+                          file_refit = 'on_change')
+even_bayes_full_mod <- add_criterion(even_bayes_full_mod, c("loo"),
+                                     file = here::here("sub-projects/trawl/derived-data/even_full.rds"))
+
+# summary(even_bayes_full_mod)
+# plot(even_bayes_full_mod)
+#estimate the probability of being zero or below
+date_draws = as.data.frame(even_bayes_full_mod)$b_date_id
+percentile <- ecdf(date_draws)
+
+# estimate 
+# msms <- conditional_smooths(even_bayes_full_mod)
+# plot(msms)
+ceff <- conditional_effects(even_bayes_full_mod, 'date_id')
+# plot(ceff)
+
+even_bayes_s_mod = brm(bf(gini_norm ~ s(month, bs = 'cc', k = 12)),
+                          data = mth_even, family = gaussian(),
+                          cores = 4, seed = 42,
+                          iter = 7000, warmup = 5000, thin = 10,
+                          control = list(adapt_delta = 0.99),
+                          save_pars = save_pars(all = TRUE),
+                          file = here::here("sub-projects/trawl/derived-data/even_s.rds"),
+                          file_refit = 'on_change')
+even_bayes_s_mod <- add_criterion(even_bayes_s_mod, c("loo"),
+                                     file = here::here("sub-projects/trawl/derived-data/even_s.rds"))
+
+even_bayes_null_mod = brm(bf(gini_norm ~ 1),
+                       data = mth_even, family = gaussian(),
+                       cores = 4, seed = 42,
+                       iter = 7000, warmup = 5000, thin = 10,
+                       control = list(adapt_delta = 0.99),
+                       save_pars = save_pars(all = TRUE),
+                       file = here::here("sub-projects/trawl/derived-data/even_null.rds"),
+                       file_refit = 'on_change')
[…]

### 2022-06-17 sub-projects/trawl/docs/figures/SAC_yr_plot.R

@@ -1,0 +1,12 @@
+SAC_yr_plot <- function(){
+SAC_yr = ggplot(TB_trawl_taxasite_yr, aes(x = sites, y = richness, group = year, colour = year)) +
+  geom_path(size = 1.5) +# geom_ribbon(aes(x = sites, ymin = (richness - 1.96*sd), ymax = (richness + 1.96*sd), fill = year), alpha = 0.2) +
+  scale_y_continuous(name = expression(Sigma~"species"),breaks = seq(0, roundUP(max(TB_trawl_taxasite_yr$richness), to = 10), by = 10), labels = seq(0, roundUP(max(TB_trawl_taxasite_yr$richness), to = 10), by = 10)) +
+  scale_x_continuous(name = "Trawls", breaks = seq(0, roundUP(max(TB_trawl_taxasite_yr$sites), to = 10), by = 5)) +
+  scale_colour_viridis(discrete = TRUE) + scale_fill_viridis(discrete = TRUE);SAC_yr
+
+### need to break this out by individual trawls not by month ##
+tiff(file = "./figures/trawl_specaccum_yr.tiff", height = 5, width = 5, units = "in", res = 450, compression = "lzw")
+SAC_yr
+dev.off()
+}

### 2022-06-17 sub-projects/trawl/docs/figures/diversity_time_plots.R

@@ -1,0 +1,28 @@
+### diversity by time plot ###
+
+ rich_time <- 
+  ggplot(TB_time_df, aes(x = Date, y = richness, group = data_type)) +
+  geom_point(aes(colour = data_type),size = 1.5) +
+  geom_line(aes(colour = data_type),size = 1.2) +
+  scale_x_date(date_breaks = "1 year", date_labels = "%Y") + 
+  scale_y_continuous(name = "Species Richness")+
+  scale_colour_manual(name = "", values = viridis(4)[c(2,3)]) +
+  theme(legend.position = c(0, 1), legend.justification = c(0, 1), legend.background = element_rect(fill = "transparent", colour = NA),
+        # axis.title.x = element_blank(), axis.text.x = element_blank(),
+        legend.spacing.y = unit(-0.1, 'cm'));rich_time
+
+ jaccard_time <-
+  ggplot(beta_df, aes(x = Date, y = value, group = partition)) + 
+   geom_point(aes(colour = partition), size = 1.5) +
+  geom_line(aes(colour = partition), size = 1.2) +
+  scale_y_continuous(name = "Jaccard dissimilarity", limits = c(0,1.1), expand = c(0.01,0.01))+
+  scale_colour_manual(name = "", values = viridis(7)[c(2,4,7)], labels = c("jaccard", "nestedness","turnover")) +
+  scale_x_date(date_breaks = "1 year", date_labels = "%Y") + 
+  theme(legend.background = element_rect(colour = NA, fill = 'transparent'),
+        legend.position = c(0,1), legend.justification = c(0,1), axis.title.x = element_blank(),
+        legend.spacing.y = unit(-0.2, 'cm'))
+
+ tiff("./figures/TB_temporal_diversity.tiff", res = 400, width = 5, height = 7.5, units = "in", compression = "lzw")
+ grid.arrange(rich_time, jaccard_time, ncol = 1)
+ dev.off()
+ 

### 2022-06-17 sub-projects/trawl/docs/figures/env_facet_plot.R

@@ -1,0 +1,10 @@
+env_plot <- function(){
+env_facet_plot <- ggplotGrob(ggplot(env_long, aes(x = datetime, y = value, group = env_var, colour = env_var)) +
+                               geom_line() + scale_colour_viridis_d() +
+                               facet_grid(rows = vars(env_var), scales = "free_y")+
+  theme(axis.title = element_blank(), legend.position = "none"))
+
+png(file = "./figures/env_facet_plot.png", res = 400, height = 10, width = 5, units = "in")
+grid.draw(env_facet_plot)
+dev.off()
+}

### 2022-06-17 sub-projects/trawl/docs/figures/figure_script.R

@@ -1,0 +1,47 @@
+# working figures #
+TB_core_day = TB_core_summ %>%
+  mutate(yday = yday(Date)) %>%
+  group_by(yday) %>%
+  mutate(day = as.Date(yday-1,  origin = "2020-01-01"))
+
+hydro_plot = ggplot(hydro_summ, aes(x = DATE)) + 
+  geom_line(aes(y = temp_C_na.rm_mean), colour = 'blue', size = 1.5)+
+  geom_line(aes(y = sal_psu_na.rm_mean), colour = 'lightblue', size = 1.5)+
+  geom_ribbon(aes(ymin = temp_C_min, ymax = temp_C_max), fill = 'blue', alpha = 0.5)+
+  geom_ribbon(aes(ymin= sal_psu_min, ymax = sal_psu_max), fill = 'lightblue', alpha = 0.5) +
+  scale_y_continuous(name = expr("Temperature ("*degree*"C) | Salinity (PSU)"))+
+  scale_x_date(breaks = "1 months", date_labels = "%b", limits = c(as.Date("2020-01-01"),as.Date("2020-12-31")), expand = c(0,0.5)) +
+  geom_vline(data = TB_core_day, aes(xintercept = day), size = 2) +
+  theme(panel.grid.minor.x = element_line(colour = 'lightgrey'),
+        panel.grid.major.x = element_line(colour = 'lightgrey'));hydro_plot
+
+do_plot = ggplot(do_summ, aes(x = DATE)) +
+  geom_line(aes(y = na.rm_mean), colour = 'red', size = 1.5) +
+  geom_ribbon(aes(ymin = min, ymax = max), fill = 'red', alpha = 0.5)+
+  scale_y_continuous(name = 'Dissolved Oxygen (mg/L)', limits = c(0,NA))+
+  scale_x_date(breaks = "1 months", date_labels = "%b", limits = c(as.Date("2020-01-01"),as.Date("2020-12-31")), expand = c(0,0.5)) +
+  geom_vline(data = TB_core_day, aes(xintercept = day), size = 2)+
+  theme(axis.text.x = element_blank(), axis.title.x = element_blank(),
+        panel.grid.minor.x = element_line(colour = 'lightgrey'),
+        panel.grid.major.x = element_line(colour = 'lightgrey'));do_plot
+
+tiff(file = "./figures/env_plot.tiff", res = 400, width = 5, height = 4, units = "in", compression = "lzw")
[…]

### 2022-09-28 sub-projects/trawl/docs/ms/ms.RMD
updated ms

@@
 Shifts in biodiversity are variable, nuanced and difficult to predict, yet, understanding how communities change through time is crucial for predicting current and future changes to biological systems and the services they provide.
-We document a decade of biodiversity change in a shallow estuarine nekton community...
+We document a decade of biodiversity change in the nekton community of a shallow-estuary...
 
@@
   geom_rangeframe(sides = "l")+
-  annotate('text', label = "A", x = as.Date("2009-01-30"), y = 11, family ='serif', size = 8, hjust = 0)+
+  annotate('text', label = "A", x = as.Date("2009-01-30"), y = 11, family ='serif', size = 6, hjust = 0)+
   theme(axis.title.x = element_blank(),
@@
   geom_rangeframe(sides = "lb", color = 'black')+
-  annotate('text', label = "B", x = as.Date("2009-01-30"), y = 1, family = 'serif', vjust = 1, size = 8, hjust = 0)+
+  annotate('text', label = "B", x = as.Date("2009-01-30"), y = 1, family = 'serif', vjust = 1, size = 6, hjust = 0)+
   theme(legend.position = "none",
@@
   guides(color = guide_legend(nrow = 1))+
-  annotate('text', label = 'A', x = as.Date("2009-01-01"), y = Inf, size = 8, hjust = 0, vjust = 1, family ='serif')+
+  annotate('text', label = 'A', x = as.Date("2009-01-01"), y = Inf, size = 6, hjust = 0, vjust = 1, family ='serif')+
   theme(axis.title.x = element_blank(),
@@
   geom_path(aes(y = q, x = Estimate), size = 1.2)+
-  annotate('text', label = 'B', x = -2.5, y = 0, hjust = 0, vjust = 1, size = 8, family = 'serif')+
+  annotate('text', label = 'B', x = -2.5, y = 0, hjust = 0, vjust = 1, size = 6, family = 'serif')+
   theme_tufte()+
@@
 
-```{r spp contributions, echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Figure 5."}
+```{r spp contributions, fig.height=8, fig.width=3.5, dpi=450, fig.cap="Figure 5."}
 
@@
   geom_rangeframe(sides = "bl", color = "black")+
-  annotate("text", label = expression(italic(""^q*"D = 0.1")), x = Inf, y = Inf, vjust = 1, hjust = 1, size = 8, family = "serif")+
+  annotate("text", label = expression(italic(""^q*"D = 0.1")), x = Inf, y = Inf, vjust = 1, hjust = 1, size = 6, family = "serif")+
   theme(axis.text.x = element_blank(),
@@
   geom_rangeframe(sides = "bl", color = "black")+
-  annotate("text", label = expression(italic(""^q*"D = 0.5")), x = Inf, y = Inf, vjust = 1, hjust = 1, size = 8, family = "serif")+
+  annotate("text", label = expression(italic(""^q*"D = 0.5")), x = Inf, y = Inf, vjust = 1, hjust = 1, size = 6, family = "serif")+
   theme(axis.text.x = element_blank(),
@@
   geom_rangeframe(sides = "bl", color = "black")+
-  annotate("text", label = expression(italic(""^q*"D = 1")), x = Inf, y = Inf, vjust = 1, hjust = 1, size = 8, family = "serif")+
+  annotate("text", label = expression(italic(""^q*"D = 1")), x = Inf, y = Inf, vjust = 1, hjust = 1, size = 6, family = "serif")+
   theme(axis.text.x = element_blank(),
@@
   geom_rangeframe(sides = "bl", color = "black")+
-  annotate("text", label = expression(italic(""^q*"D = 2")), x = Inf, y = Inf, vjust = 1, hjust = 1, size = 8, family = "serif")+
+  annotate("text", label = expression(italic(""^q*"D = 2")), x = Inf, y = Inf, vjust = 1, hjust = 1, size = 6, family = "serif")+
   theme(axis.text.x = element_text(angle = 60, vjust = 1, hjust = 1),
@@
                   sides = 'bl', color = 'black', inherit.aes = FALSE)+
-  annotate('text', label = expression(italic(""^q*"D = 2")), x = as.Date("2019-12-31"), y = Inf, vjust = 1, hjust = 1, size = 8, family = 'serif')+
+  annotate('text', label = expression(italic(""^q*"D = 2")), x = as.Date("2019-12-31"), y = Inf, vjust = 1, hjust = 1, size = 6, family = 'serif')+
   theme(legend.title = element_blank(),
@@
         legend.justification = c(0,1),
-        legend.background = element_rect(fill = 'transparent', color = NA));TB_q2_spp_plot
+        legend.background = element_rect(fill = 'transparent', color = NA));#TB_q2_spp_plot
 
@@
                   sides = 'bl', color = 'black', inherit.aes = FALSE)+
-  annotate('text', label = expression(italic(""^q*"D = 1")), x = as.Date("2019-12-31"), y = Inf, vjust = 1, hjust = 1, size = 8, family = 'serif')+
+  annotate('text', label = expression(italic(""^q*"D = 1")), x = as.Date("2019-12-31"), y = Inf, vjust = 1, hjust = 1, size = 6, family = 'serif')+
   theme(legend.title = element_blank(),
@@
         legend.justification = c(0,1),
-        legend.background = element_rect(fill = 'transparent', color = NA));TB_q1_spp_plot
+        legend.background = element_rect(fill = 'transparent', color = NA));#TB_q1_spp_plot
 
@@
                   sides = 'bl', color = 'black', inherit.aes = FALSE)+
-  annotate('text', label = expression(italic(""^q*"D = 0.5")), x = as.Date("2019-12-31"), y = Inf, vjust = 1, hjust = 1, size = 8, family = 'serif')+
+  annotate('text', label = expression(italic(""^q*"D = 0.5")), x = as.Date("2019-12-31"), y = Inf, vjust = 1, hjust = 1, size = 6, family = 'serif')+
   theme(legend.title = element_blank(),
@@
         legend.justification = c(0,1),
-        legend.background = element_rect(fill = 'transparent', color = NA));TB_q0.5_spp_plot
+        legend.background = element_rect(fill = 'transparent', color = NA));#TB_q0.5_spp_plot
 
@@
                   sides = 'bl', color = 'black', inherit.aes = FALSE)+
-  annotate('text', label = expression(italic(""^q*"D = 0.1")), x = as.Date("2019-12-31"), y = Inf, vjust = 1, hjust = 1, size = 8, family = 'serif')+
+  annotate('text', label = expression(italic(""^q*"D = 0.1")), x = as.Date("2019-12-31"), y = Inf, vjust = 1, hjust = 1, size = 6, family = 'serif')+
   theme(legend.title = element_blank(),
@@
         legend.justification = c(0,1),
-        legend.background = element_rect(fill = 'transparent', color = NA));TB_q0.1_spp_plot
-
-grid.draw(rbind(ggplotGrob(TB_q1_spp_plot), ggplotGrob(TB_q2_spp_plot), size = 'last'))
+        legend.background = element_rect(fill = 'transparent', color = NA));#TB_q0.1_spp_plot
+
+grid.draw(rbind(ggplotGrob(TB_q0.5_spp_plot), ggplotGrob(TB_q2_spp_plot), size = 'last'))
 
@@
 ```{r trawl contributions,echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Figure 6.
-The contribution of individual trawl-dates to dissimilarity of the entire timeseries for diversity order q = 0.1 (top), q = 1 (middle), and q = 2 (bottom)." }
+The contribution of individual trawl-dates to dissimilarity of the entire timeseries for diversity order q = 0.5 (top), q = 1 (middle), and q = 2 (bottom)." }
 
@@
   left_join(TB_trawl_taxasite %>% dplyr::select(Date, date_id))
+
 TB_trawl_q0_dis2 = dis1(TB_trawl_taxasite_dis, q = 0, type = 'tax', type2 = 'k') %>%
@@
                date_labels = "%Y")+
+  theme_tufte()+
+  geom_rangeframe(sides = "lb", color = "black")+
+  annotate('text', label = expression(italic(''^q*"D = 0")), x = as.Date("2009-01-01"), y = Inf, size = 6, family = 'serif')+
   theme(axis.title = element_blank(),
@@
                date_labels = "%Y")+
+  theme_tufte()+
+  geom_rangeframe(sides = "lb", color = "black")+
+  annotate('text', label = expression(italic(''^q*"D = 0.1")), x = as.Date("2009-01-01"), y = Inf, size = 6, family = 'serif')+
   theme(axis.title = element_blank(),
         axis.text.x = element_blank())-> TB_q0.1_dis2_plot
+
+TB_trawl_q0.5_dis2 %>%
+  dplyr::filter(dis_type == "UqN")%>%
+  ggplot(aes(x = Date, y = value))+
+  geom_point()+
+  geom_path()+
+  scale_y_continuous(expand = c(0.0001,0.0001))+
+   scale_x_date(date_breaks = 'year', limits = c(as.Date("2009-01-01"),as.Date("2019-12-31")),
+               date_labels = "%Y")+
+  theme_tufte()+
+  geom_rangeframe(sides = "lb", color = "black")+
+  annotate('text', label = expression(italic(''^q*"D = 0.5")), x = as.Date("2019-12-31"), y = Inf, size = 6, family = 'serif', vjust = 1, hjust =1)+
+  theme(axis.title = element_blank(),
+        axis.text.x = element_blank())-> TB_q0.5_dis2_plot
 
@@
                date_labels = "%Y")+
+  theme_tufte()+
+  geom_rangeframe(sides = "lb", color = "black")+
+  annotate('text', label = expression(italic(''^q*"D = 1")), x = as.Date("2019-12-31"), y = Inf, size = 6, family = 'serif', vjust = 1, hjust = 1)+
   theme(axis.title = element_blank(),
         axis.text.x = element_blank())-> TB_q1_dis2_plot
+
 TB_trawl_q2_dis2 %>%
@@
   geom_path()+
-  annotate('text', label = "")+
   scale_y_continuous(expand = c(0.0001,0.0001))+
@@
                date_labels = "%Y")+
+  theme_tufte()+
+  geom_rangeframe(sides = "lb", color = "black")+
+  annotate('text', label = expression(italic(''^q*"D = 2")), x = as.Date("2019-12-31"), y = Inf, size = 6, family = 'serif', vjust = 1, hjust = 1)+
   theme(axis.title= element_blank()) -> TB_q2_dis2_plot
 
-grid.draw(rbind(ggplotGrob(TB_q0.1_dis2_plot),
+grid.draw(rbind(ggplotGrob(TB_q0.5_dis2_plot),
                 ggplotGrob(TB_q1_dis2_plot), 
@@
 
-```{ r map fig S1, echo = FALSE, warning = FALSE, message= FALSE, }
-
-```
-
-```{r env data fig S2, echo=FALSE, warning=FALSE, message=FALSE, fig.cap= "Figure S2.
+```{r map fig S1 }
+
+```
+
+```{r env data fig S2, fig.cap= "Figure S2.
 Time series of environmental variables a) water temperature and b) salinity measured at the Terrebonne Bay environmental monitoring station (XX N, XX W).
@@
                date_labels = "%Y",expand = c(0.01,0.01))+
-  annotate('text', label = 'A', x = -Inf, y = Inf, vjust = 1, hjust = 0, size = 5, family = 'serif')+
+  annotate('text', label = 'A', x = as.Date("2009-01-01"), y = Inf, vjust = 1, hjust = 0, size = 6, family = 'serif')+
   theme_tufte()+
@@
   scale_y_continuous(name = "Salinity (PSU)", limits = c(0,NA), expand =c(0.01,0.01))+
-    annotate('text', label = 'B', x = -Inf, y = Inf, vjust = 1, hjust = 0, size = 5, family = 'serif')+
+    annotate('text', label = 'B', x = as.Date("2009-01-01"), y = Inf, vjust = 1, hjust = 0, size = 6, family = 'serif')+
   theme_tufte()+
